### 2021-04-29 util/_scaling/Instructions.tex

\documentclass{article}
\title{CPScale Instruction Manual}
\author{Dan Graves}
\begin{document}
\maketitle
\section{Introduction}

This docuement describes how to use CPScale, the Chombo/Proto scaling
infrastructure.    Given a template for an input file, a template for
a batch script and some command line inputs, CPScale produces a
directory  for a series of runs which comprise a weak scaling test.
CPScale also generates a script to submit the jobs.   Between each
scale, the grid refinement is doubled.   Both the MPI ranks and the
processor count are multiplied by eight.

For now, the pattern for number of nodes is fixed at 1, 8, 64....
nnnn
\section{Command Line Arguments}
  \begin{itemize}
\item \tt{--help} provides helpful information (mostly what these
  arguments mean).
\item \tt{--procs}  The minimum number of MPI process.  Say, for
  example this is 3.   Then the next run in the scaling test will have
  24 processes and so on.   This should be smaller than the number of
  CPUs per node on the target machine.
\item \tt{--input} name the input file template.   Examples are
  provided.   Relative path is okay to use here.  pp
\item \tt{--batch} name the batch file template.   Examples are
  provided.   Relative path is okay to use here.pp
\item \tt{--max\_proc}  maximum number of MPI processes to use here.
  This is a not-to-exceed number so the largest run can be smaller
  than this.
\item \tt{--executable\_name} Name of the executable you want run.
  Absolute paths are best here but if you must use a relative path,
  remember that this will be run from a directory two levels deeper
  than the one you are in.   So if you run this script in the same
  directory that you have your executable, prefix the name with
  "../..''.
\item \tt{--nx}  Resolution of smallest calculation.
\item \tt{--prefix} Name of the test (directory will have this in the name).  
\end{itemize}

\section{Usage pattern}

Say a user has an executable file named \tt{blah.exe} in her directory
"/home/awesomeuser/execfiles''.   She wants 2 processes per node up to
128 processes.   She has an input template called \tt{inputs} and a
batch template called \tt{batch}.   The wants the minimum resolution
in each directon to be 64.   The command would look like
\begin{verbatim}
<prompt>  ./configure.scaling --nx=64 --input=inputs --batch=batch \
            --executable_name="/home/awesomeuser/execfiles/main.exe" \
           --procs=2 --max_proc=128
\end{verbatim}

\end{document}

### 2023-02-01 src/EBCM/Chombo_EBCMGraph.H
starting on cell merging technology.  gonna be pretty cool.

@@ -1,0 +1,77 @@
+#ifndef __PROTO_EBCMGraph__
+#define __PROTO_EBCMGraph__
+
+#include "implem/Proto_IrregGraph.H"
+#include "EBProto.H"
+#include "Proto_RealVect.H"
+using std::vector;
+using std::set;
+
+namespace EBCM
+{
+  class BlobVolIndex;
+  
+  ///BlobFaceIndex are made by collecting up EBIndex<cent> faces along a merged cell.  can be an EB face
+  template<CENTERING cent>
+  class BlobFaceIndex
+  {
+  public:
+    //centroid location
+    RealVect m_cent;
+    BlobVolIndex m_lo;
+    BlobVolIndex m_hi;
+    IndexedMoments<DIM> m_facmom;
+    defineAsRegular();
+
+  };
+
+  
+  class BlobVoluIndex
+  {
+  public:
+    vector<BlobFaceIndex<XFACE> > m_xfaces;
+    vector<BlobFaceIndex<YFACE> > m_yfaces;
+    vector<BlobFaceIndex<ZFACE> > m_zfaces;
+    BlobFaceIndex<      BOUNDARY> m_ebface;
+    
+    bool                          m_regular;
+    //centroid location
+    RealVect m_cent;
+    IndexedMoments<DIM> m_volmom;
+    IndexedMoments<DIM> m_ebfmom;
+    Point    m_pt; //just used as a unique identifier
+    defineAsRegular();
+  };
+
+  class BlobGraph
+  {
+  public:
+    //tells which cells eb thinks are regular, irregular covered
+    shared_ptr<EBGraph> m_graph;
+
+    //going to be different than EBGraph info because of coarsening
+    PointSet            m_regular;
+    PointSet            m_irregular;
+    PointSet            m_covered;
+    
+    
+    bool isRegular(Point a_pt) const
+    {
+      return m_regular.contains(a_pt);
+    }
+    
+    bool isIrregular(Point a_pt) const
+    {
+      return m_irregular.contains(a_pt);
+    }
+
+    bool isCovered(Point a_pt) const
+    {
+      return m_covered.contains(a_pt);
+    }
+    
+  };
+}
+
+
+#endif

### 2023-02-02 src/EBCM/Chombo_EBCMGraph.H
progress on the easy part of ebcm

@@ -43,33 +43,82 @@ namespace EBCM
     defineAsRegular();
   };
 
-  class BlobGraph
+  class boxmap_t
   {
   public:
-    //tells which cells eb thinks are regular, irregular covered
-    shared_ptr<EBGraph> m_graph;
-
+  
     //going to be different than EBGraph info because of coarsening
     PointSet            m_regular;
     PointSet            m_irregular;
     PointSet            m_covered;
-    
-    
-    bool isRegular(Point a_pt) const
+    boxmap_t()
     {
-      return m_regular.contains(a_pt);
+      m_regular.clear();
+      m_irregular.clear();
+      m_covered.clear();
     }
-    
-    bool isIrregular(Point a_pt) const
+  }
+  class BlobGraph
+  {
+  public:
+
+    shared_ptr<std::set<EBIndex<CELL> > >
+    fillVolumesFromEB(shared_ptr<EBGraph> a_graph,
+                      shared_ptr<EBData>  a_data,
+                      Real                a_dx)
+
     {
-      return m_irregular.contains(a_pt);
+      shared_ptr<std::set<EBIndex<CELL> > > retval(new std::set<EBIndex<CELL> >() );
+      auto valid= a_graph.validBox();
+      for(auto bit = valid.begin(); bit != valid.end(); ++bit)
+      {
+        if(a_graph->isCovered(*bit))
+        {
+          //covered bits are not part of the solution 
+        }
+        else if( a_graph->isRegular())
+        {
+          
+        }
+        auto vofs = a_graph->getVoFs(*bit);
+        for(int ivof = 0; ivof < vofs.size(); ivof++)
+        {
+          const auto& vof = vofs[ivof];
+        }
+      }
+
+      return retval;
     }
 
-    bool isCovered(Point a_pt) const
+    BlobGraph(shared_ptr<EBGraph> a_graph,
+              shared_ptr<EBData>  a_data,
+              Real                a_dx,
+              bool                a_mergeSmallCells) const
     {
-      return m_covered.contains(a_pt);
+
+      shared_ptr<std::set<EBIndex<CELL> > > allEBVols = fillVolumesFromEB(a_graph, a_data, a_dx);
+
+      if(a_mergeSmallCells)
+      {
+        m_volumes = mergeSmallVolumes(allEBVols);
+      }
+      else
+      {
+        m_volumes = allEBVols;
+      }
+      return retval;
+                         
     }
-    
+  private:
+              
[…]

### 2023-02-03 example/DomainDecomposition/common/EBMultigrid.cpp
Rebuilt HO div op is working now. Plus better generic BC management
Reworking the laplac op with new setup and BC manager

@@ -384,7 +384,7 @@ getStencilComponents(const shared_ptr<GeometryService<2> >   & a_geoserv,
                      const Chombo4::DataIndex & a_dit)
 {
   typedef Proto::EBStencilArchive<CELL, CELL, 2, Real> archive_t;
-  typedef Proto::EBStencilHO<CELL, CELL, 2, Real> ho_t;
+  // typedef Proto::EBStencilHO<CELL, CELL, 2, Real> ho_t; // FIXME
   using Chombo4::Box;
   typedef IndexedMoments<DIM  , 2> IndMomDIM;
   typedef IndexedMoments<DIM-1, 2> IndMomSDMinOne;
@@ -428,17 +428,19 @@ getStencilComponents(const shared_ptr<GeometryService<2> >   & a_geoserv,
   Bx domainbx = ProtoCh::getProtoBox(m_domain);
   Point pghost= ProtoCh::getPoint(m_nghost);
 
-  ho_t::getStencil(a_dstVoFs, a_wstencil, inhoContr, a_regStencilInterior, 
-                   regStencilBCS, BCApplyBoxes, regApplyBox, bcsOnly,
-                   m_stenname,  m_dombcname, m_ebbcname,
-                   valbx, valbx,  domainbx, domainbx,
-                   pghost,  pghost,    
-                   graph,  graph,
-                   voludata,  ebfadata, 
-                   xfacdata,  yfacdata, zfacdata,   
-                   ebnorxdata, ebnorydata,
-                   ebnorzdata,
-                   m_dx, false, Point::Zeros());
+  // FIXME need to update this interface, but as of right now we don't use this code so it is a problem for later
+  CH_assert(false);
+  // ho_t::getStencil(a_dstVoFs, a_wstencil, inhoContr, a_regStencilInterior,
+  //                  regStencilBCS, BCApplyBoxes, regApplyBox, bcsOnly,
+  //                  m_stenname,  m_dombcname, m_ebbcname,
+  //                  valbx, valbx,  domainbx, domainbx,
+  //                  pghost,  pghost,
+  //                  graph,  graph,
+  //                  voludata,  ebfadata,
+  //                  xfacdata,  yfacdata, zfacdata,
+  //                  ebnorxdata, ebnorydata,
+  //                  ebnorzdata,
+  //                  m_dx, false, Point::Zeros());
 
   fillInhoContr(inhoContr,a_dstVoFs,a_dit);
 

### 2023-02-03 example/DomainDecomposition/common/EBPetscSolver.H

@@ -20,6 +20,7 @@
 #include "petscviewer.h"
 #include "Chombo_EBChombo.H"
 #include "Chombo_EBLevelBoxData.H"
+#include "hoeb/Proto_EBDomainBC.H"
 #include "EBMultigridFunctions.H"
 
 /// Framework to solve an elliptic equation using PETSc (PeTSC? PETsC? PETsC?)
@@ -39,6 +40,7 @@ public:
   typedef EBDictionary<order, Real, CELL, CELL>                dictionary_t;
   typedef EBStencil<order, Real, CELL, CELL>                    ebstencil_t;
 
+  // DEPRECATED, use updated version with better BC management
   EBPetscSolver(const shared_ptr<GeometryService<order> >  & a_geoserv,
                 const shared_ptr<dictionary_t           >  & a_ebdictionary,
                 const shared_ptr<LevelData<EBGraph> >      & a_graphs,
@@ -50,6 +52,18 @@ public:
                 Real a_dx,   Real a_alpha, Real a_beta, Point a_ghost,
                 const vector<shared_ptr<BaseExactSolution<order> > > & a_boundarySolutions = vector<shared_ptr<BaseExactSolution<order> > >(),
                 const shared_ptr<BaseExactSolution<order> > & a_boundarySolutionsEB = nullptr)
+  {
+    CH_assert(false);
+  }
+
+  EBPetscSolver(const shared_ptr<GeometryService<order> >  & a_geoserv,
+                const shared_ptr<dictionary_t           >  & a_ebdictionary,
+                const shared_ptr<LevelData<EBGraph> >      & a_graphs,
+                const Chombo4::DisjointBoxLayout                    & a_grids,
+                const Chombo4::Box                                  & a_domain,
+                string a_stencilName,
+                Real a_dx,   Real a_alpha, Real a_beta, Point a_ghost,
+                const Proto::EBDomainBC<1, order>    & a_domainBC)
   {
     CH_TIME("EBPetscSolver::EBPetscSolver");
     m_geoserv      =    a_geoserv;
@@ -63,33 +77,27 @@ public:
     m_beta         =    a_beta;
     m_nz_init_guess = false;
     m_prestring[0] = '\0';
-    for(int iface = 0; iface < 2*DIM; iface++)
-    {
-      m_domainBCName[iface] = a_domainBCName[iface];
-    }
-    m_ebbcName = a_ebbcName;
[…]

### 2023-02-03 src/BoxTools/Chombo_SPACE.H

@@ -229,33 +229,7 @@ compile-time cpp macro that controls the dimensionality of
         for (int i1 = 0; i1 != n1; ++i1) {,
         for (int i2 = 0; i2 != n2; ++i2) {)
     D_TERM(},},})
-*/#ifdef DOXYGEN
-/**
-@ingroup macros
-
-  The D_CALL(func, args) macro expands to a comma-separated list of
-  1, 2, or all 3 of the arguments of the call, depending on the
-  value of CH_SPACEDIM.  This can be used to write portable
-  function calls that depend on 1, 2, or 3 arguments, corresponding
-  to the value of CH_SPACEDIM.
-
-  For example:
-  template<T> T ExampleFunction(int a, bool b)
-    {
-    // do stuff
-    };
-  D_CALLS(ExampleFunction, 2, true)
-
-  where the macro evaluates
-
-     ExampleFunction<0>(2, true); // if CH_SPACEDIM >= 1
-     ExampleFunction<1>(2, true); // if CH_SPACEDIM >= 2
-     ExampleFunction<2>(2, true); // if CH_SPACEDIM >= 3
-
 */
-#endif
-#  define D_CALLS(func, args...) D_TERM(func<0>(args);, func<1>(args);, func<2>(args);)
-
 #endif
 #  define D_INVTERM(a,b,c) c b a
 #  define D_INVTERM6(a,b,c,d,e,f) c b a

### 2023-02-03 src/EBProto/EBProto.H

@@ -13,6 +13,15 @@ namespace Proto
   constexpr std::array<CENTERING, Chombo4::SpaceDim>   REG_FACES{D_DECL(XFACE, YFACE, ZFACE)};
   constexpr std::array<CENTERING, Chombo4::SpaceDim+1> ALL_FACES{BOUNDARY, D_DECL(XFACE, YFACE, ZFACE)};
 
+  inline int FACE_DIR(CENTERING cent)
+  {
+    int retval = -1;
+    if (cent == XFACE) { retval = 0;}
+    else if (cent == YFACE) { retval = 1;}
+    else if (cent == ZFACE) { retval = 2;}
+    return retval;
+  }
+
   /// Return the index into a SpaceDim*2 vector
   /// use case is:
   /// for (int dir = 0; dir != SpaceDim; dir++)

### 2023-02-03 src/EBProto/Proto_EBGraph.H

@@ -10,13 +10,13 @@ using std::set;
 namespace Proto
 {
 
-  ///
+  /// FIXME forgive the rant, but this class causes many cascading challenges
   /// There is an important lesson to be learned here about template usage. On the surface this class makes a lot of sense as a template, it does something fairly different depending upon the centering. The problem with this becomes, now anything that uses this must also be dependent on the centering also. As a result, there is no sane way to loop over each direction or do things in a direction independent way, leading to lots of code reuse
-  /// REVIEW Consider changing this to store the centering as a trait of the index, rather than as a template
+  /// REVIEW Consider changing this to store the centering as a trait of the index, rather than as a template.
   template<CENTERING cent>
   class EBIndex
   {
-  public: //private: //FIXME this is bad design, especially for such a simple class
+  public: //private: //FIXME this is strange design, especially for such a simple class. The naming/lack of docs is hard
 
     Point m_pt;
     //for faces, the high cell. for cells, this is the cell
@@ -167,6 +167,7 @@ namespace Proto
       }
       return retval;
     }
+
     //for getting the vof of a cut face 
     inline EBIndex<CELL> getVoF() const
     {
@@ -177,7 +178,6 @@ namespace Proto
       retval.m_isBoundary = false;
       return retval;
     }
-
 
     //for getting the  boundary face  of a vof
     inline EBIndex<BOUNDARY> getCutFace() const
@@ -211,6 +211,34 @@ namespace Proto
       return retval;
     }
     
+    //for getting the  boundary face  of a vof
+    inline RealVect getCenter(double a_dx) const
+      {
+        RealVect loc;
+        for (int idir = 0; idir != DIM; idir++)
+          {
+            loc[idir] = m_pt[idir] + 0.5;
+          }
+        // cent == CELL is the default
+        if(cent == XFACE)
+          {
+            loc[0] -= 0.5;
+          }
+        else if(cent == YFACE)
+          {
+            loc[1] -= 0.5;
+          }
+        else if(cent == ZFACE)
+          {
+            loc[2] -= 0.5;
+          }
+        else if(cent == BOUNDARY)
+          {
+            PR_assert(false);
+          }
+        loc *= a_dx;
+        return loc;
+      }
 
     void defineAsRegular(const Point& a_pt)
     {
@@ -289,6 +317,54 @@ namespace Proto
[…]

### 2023-02-03 src/EBProto/Proto_MomentHolder.H

@@ -40,8 +40,9 @@ namespace Proto
                  const EBNormalData & a_YEBNormData,
                  const EBNormalData & a_ZEBNormData)
       {
-        m_VoluData = &a_VoluData;
-        m_EBFaceData = &a_EBFaceData;
+        // I promise not to change things. Is casting away consts good? No. But this is a bandaid for bigger problems
+        m_VoluData = const_cast<VoluData*>(&a_VoluData);
+        m_EBFaceData = const_cast<EBFaData*>(&a_EBFaceData);
 #if DIM >= 1
         m_XFaceData = &a_XFacData;
         m_XEBNormData = &a_XEBNormData;

### 2023-02-03 src/EBProto/hoeb/Proto_EBDomainBC.H

@@ -82,6 +82,58 @@ namespace Proto
           }
       }
 
+    // Sometimes we need to work with a single component object.
+    // Hopefully typename T is cheap to copy
+    inline EBDomainBCRegister<T, 1>
+    makeSingleComponent(int a_comp)
+      {
+        EBDomainBCRegister<T, 1> newSingleComp;
+        // copy all the regular values
+        for(int dir = 0; dir!=DIM; dir++)
+          {
+            for(SideIterator sit; sit.ok(); ++sit)
+              {
+                newSingleComp.setRegComp(this-getRegComp(dir, sit(), a_comp),
+                                         dir, sit(), 0);
+              }
+          }
+        // copy the EB
+        newSingleComp.setEBComp(this->getEBComp(a_comp));
+
+        return newSingleComp;
+      }
+
+    // THIS ONLY EXISTS FOR BACKWARD COMPATIBILITY REASONS
+    // DO NOT USE UNLESS NECECCARY
+    void
+    fillFlatArray(string a_bcnames[2*DIM],
+                  int a_comp=0) const
+      {
+        for(int ivec = 0; ivec != 2*DIM; ivec++)
+          {
+            int idir;
+            Side::LoHiSide iside;
+            ebp_face(ivec, idir, iside);
+            a_bcnames[ivec] = getRegComp(idir, iside, a_comp);
+          }
+      }
+
+    void
+    fillFlatArray(vector<string> a_bcnames[2*DIM]) const
+      {
+        for(int ivec = 0; ivec != 2*DIM; ivec++)
+          {
+            for(int comp = 0; comp!=DIM; comp++)
+              {
+                a_bcnames[ivec].resize(DIM);
+                int idir;
+                Side::LoHiSide iside;
+                ebp_face(ivec, idir, iside);
+                a_bcnames[ivec][comp] = getRegComp(idir, iside, comp);
+              }
+          }
+      }
+
   private:
     std::array<std::array<std::array<T, Comps>, 2>, DIM> m_regbcData;
     std::array<T, Comps> m_ebbcData;
@@ -97,14 +149,30 @@ namespace Proto
   {
   public:
 
-    EBDomainBCtypes<Comps>&
-    getBCtypes()
+    inline
+    EBDomainBCtypes<Comps>
+    getBCtypes() const
       {
         return m_bcTypes;
       }
 
+    inline
+    EBDomainBCfuncs<Comps, order>
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_EBStencilHO.H

@@ -69,6 +69,8 @@ namespace Proto
                     const Point                        & a_vofPt); 
    
     ///   returns true if there are domain boundary conditions
+    ///   DEPRECATED, this is ugly to call and encourages bad design choices
+    ///   This is probaly in various stages of broken
     inline static bool
     getStencil(vector<EBIndex<CELL> >                    & a_dstVoFs,
                vector<LocalStencil<CELL, Real> >       & a_stencil,
@@ -103,6 +105,29 @@ namespace Proto
                const vector<shared_ptr<BaseExactSolution<order> > > & a_boundarySolutions = vector<shared_ptr<BaseExactSolution<order> > >(),
                const shared_ptr<BaseExactSolution<order> > & a_boundarySolutionsEB = nullptr);
 
+    ///   returns true if there are domain boundary conditions
+    inline static bool
+    getStencil(vector<EBIndex<CELL> >                    & a_dstVoFs,
+               vector<LocalStencil<CELL, Real> >       & a_stencil,
+               vector<Real>                            & a_inhoContr,
+               Stencil<Real>                           & a_regStencilInterior,
+               vector<Stencil<Real> >                    a_regStencilBCS[2*DIM],
+               vector<Box>                                 a_BCApplyBoxes[2*DIM],
+               Box                                       & a_regApplyBox,
+               bool                                      & a_bcOnly,
+               string                                      a_stencilName,
+               const Box                                 & a_srcValid,
+               const Box                                 & a_dstValid,
+               const Box                                 & a_srcDomain,
+               const Box                                 & a_dstDomain,
+               const Point                               & a_srcGhost,
+               const Point                               & a_dstGhost,
+               const EBGraph                             & a_srcGraph,
+               const EBGraph                             & a_dstGraph,
+               const MomentHolder<order>                 & a_momentData, // holds all geoservice info on a box
+               const EBDomainBC<1, order>                & a_domainBC, // all the BC info
+               Real                                      a_dx);
+
     ///Gets WLS Poisson stencil
     inline static bool
     getWLSPoissonStencil(vector<EBIndex<CELL> >                    & a_dstVoFs,
@@ -113,26 +138,14 @@ namespace Proto
                          vector<Box>                                 a_BCApplyBoxes[2*DIM],
                          Box                                       & a_regApplyBox,
                          string                                      a_stencilName,
-                         string                                      a_domainBCName[2*DIM],
-                         string                                      a_ebbcName,
                          const Box                                 & a_validBox,
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_EBStencilHOImplem.H

@@ -193,6 +193,8 @@ namespace Proto
              const vector<shared_ptr<BaseExactSolution<order> > > & a_boundarySolutions,
              const shared_ptr<BaseExactSolution<order> > & a_boundarySolutionsEB)
   {
+    CH_assert(false); // If you get here, switch to the updated getStencil
+
     PR_TIME("getStencil");
     a_bcOnly = false;
     if(a_stencilName == string("Weighted_Least_Squares_Poisson"))
@@ -299,7 +301,62 @@ namespace Proto
     }
     return false;//never gets here but this shuts up some compilers;
   }
- 
+
+    //Gets high-order stencil. First implementation gives you the stencil for Poisson operator
+  //All Neumann stencil is needed for EBMultigrid, it still needs to be checked.
+  //Returns whether there are domain boundary conditions
+  template <int order>
+  bool
+  EBStencilHO<CELL, CELL,  order, Real>::
+  getStencil(vector<EBIndex<CELL> >                    & a_dstVoFs,
+             vector<LocalStencil<CELL, Real> >       & a_stencil,
+             vector<Real>                            & a_inhoContr,
+             Stencil<Real>                           & a_regStencilInterior,
+             vector<Stencil<Real> >                    a_regStencilBCS[2*DIM],
+             vector<Box>                                 a_BCApplyBoxes[2*DIM],
+             Box                                       & a_regApplyBox,
+             bool                                      & a_bcOnly,
+             string                                      a_stencilName,
+             const Box                                 & a_srcValid,
+             const Box                                 & a_dstValid,
+             const Box                                 & a_srcDomain,
+             const Box                                 & a_dstDomain,
+             const Point                               & a_srcGhost,
+             const Point                               & a_dstGhost,
+             const EBGraph                             & a_srcGraph,
+             const EBGraph                             & a_dstGraph,
+             const MomentHolder<order>                 & a_momentData,
+             const EBDomainBC<1, order>              & a_domainBC,
+             Real                                      a_dx)
+  {
+    PR_TIME("getStencil");
+    a_bcOnly = false;
+    if(a_stencilName == string("Weighted_Least_Squares_Poisson"))
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_WLSCell.H

@@ -12,11 +12,14 @@ namespace Proto
 {
 
   /// A small class to hold parameters about how a stencil should be formed
-  struct StencilTraits
+  /// This exists for the meta data we need about stencil creation, and as an interface
+  class StencilTraits
   {
+  public:
     void
-    readStencilTraits(const std::string a_PPprefix)
+    readInputs(const std::string a_PPprefix)
       {
+        // FIXME use prefix, and better names
         ParmParse pp;
         pp.get("radius", m_radius);
         pp.get("powerE", m_weightPower);
@@ -34,7 +37,7 @@ namespace Proto
 
     StencilTraits()
       {
-        readStencilTraits("");
+        readInputs("");
       }
 
     StencilTraits(const int a_order)
@@ -51,6 +54,11 @@ namespace Proto
     inline int neighListType() const
       { return m_neighListType;}
 
+    inline int smallCellTol() const
+      { return m_smallCellTol;}
+
+  private:
+    /// Defaults are generally invalid, should be set in the constructor
     // How many cells around the stencil center to grab
     int m_radius = 0;
     // The weighting power to use
@@ -58,11 +66,11 @@ namespace Proto
     // Neighbor list type. 0-FaceBased or 1-CellBased
     int m_neighListType = 0;
     // at what point do small cells stop being relevant
-    Real m_smallCellTol = 1e-11; // FIXME
+    Real m_smallCellTol = 1e-11; // FIXME real aware
   };
 
   template<int order> 
-  class BaseExactVelocity
+  class BaseExactVelocity // FIXME a subset of exact solutions, don't reinvent them here
   {
   public:
     typedef IndexedMoments<DIM  , order> IndMomDIM;
@@ -272,9 +280,11 @@ namespace Proto
     typedef HostIrregData<ZFACE, IndMomSDMinOne, 1>  ZFacData;
     typedef HostIrregData<CELL    ,  IndMomDIM , 1>  EBNormalData;
 
+    // FIXME we need to stop using the dombcName strings. Maybe a single comp EBDomRegister is general enough?
+
     //Gets all the moments and geometric info for the neighbors cells, boundary faces
     //and EB faces. Stores all this info in the Neighbors object.
-    // DEPRECATED
+    // DEPRECATED now lives in neighbors
     void
     getMomentsInfoFromNeighbors(Vector<EBIndex<CELL> > & a_vols,
                                 const EBGraph          & a_graph,
@@ -286,11 +296,14 @@ namespace Proto
                                 const EBNormalData     & a_ebnormxdata,
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_WLSCellImplem.H

@@ -3,40 +3,16 @@
 
 namespace Proto
 {
-  //Gets all the moments and geometric info for the neighbors cells, boundary faces
-  //and EB faces. Stores all this info in the Neighbors object.
-  template<CENTERING cent, int order>
-  void
-  BaseWLSFlux<cent, order>::
-  getMomentsInfoFromNeighbors(Vector<EBIndex<CELL> >  & a_vols,
-                              const EBGraph           & a_graph,
-                              const VoluData          & a_voludata,
-                              const EBFaData          & a_ebfadata,
-                              const XFacData          & a_xfacdata,
-                              const YFacData          & a_yfacdata,
-                              const ZFacData          & a_zfacdata,
-                              const EBNormalData      & a_ebnormxdata,
-                              const EBNormalData      & a_ebnormydata,
-                              const EBNormalData      & a_ebnormzdata,
-                              Neighbors<order>  & a_neigh,
-                              int                       a_neighType,
-                              string                    a_ebbcName,
-                              string                    a_dombcName[2*DIM],
-                              Real                    a_dx) const
-  {
-    CH_assert(false); //DEPRECATED, see Proto_WLSneighbors for re-homed function
-  }
-
   //Compute the Moments Matrix
   template<CENTERING cent, int order>
   void
   BaseWLSFlux<cent, order>::
   getShiftedMomentMatrix(Chombo4::LAPACKMatrix    & a_Mvol,
-                           RealVect               & a_faceLoc,
-                           Real                   a_dx,
-                           const Neighbors<order> & a_neigh,
-                           string                   a_ebbcName,
-                           string                   a_dombcName[2*DIM]) const
+                         RealVect               & a_faceLoc,
+                         Real                     a_dx,
+                         const Neighbors<order> & a_neigh,
+                         string                   a_ebbcName,
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_WLSStencil.H

@@ -24,26 +24,17 @@ namespace Proto
     ///
     //Gets Laplacian WLS flux divergence stencil
     inline void
-    getLaplaWLSDivFStencil(LocalStencil< CELL,  Real>        & a_vofStencil,
-                           const EBIndex<CELL>                 & a_vof,
-                           const EBGraph                       & a_graph,
-                           const VoluData                      & a_voludata,
-                           const EBFaData                      & a_ebfadata,
-                           const XFacData                      & a_xfacdata,
-                           const YFacData                      & a_yfacdata,
-                           const ZFacData                      & a_zfacdata,
-                           const EBNormalData                  & a_ebnormxdata,
-                           const EBNormalData                  & a_ebnormydata,
-                           const EBNormalData                  & a_ebnormzdata,
-                           const BaseWLSFlux<XFACE   , order>  & a_xfaceflux,
-                           const BaseWLSFlux<YFACE   , order>  & a_yfaceflux,
-                           const BaseWLSFlux<ZFACE   , order>  & a_zfaceflux,
-                           const BaseWLSFlux<BOUNDARY, order>  & a_ebflux,
-                           string                                a_ebbcName,
-                           string                                a_dombcName[2*DIM],
-                           Real                                & a_inhoTerm,
-                           int                                 & a_neighType,
-                           Real                                a_dx);
+    getLapWLSDivFStencil(LocalStencil< CELL,  Real>          & a_vofStencil,
+                         Real                                & a_inhoTerm,
+                         const EBIndex<CELL>                 & a_vof,
+                         const EBGraph                       & a_graph,
+                         const MomentHolder<order>           & a_momentData,
+                         const LapWLSFlux<XFACE   , order>   & a_xfaceflux,
+                         const LapWLSFlux<YFACE   , order>   & a_yfaceflux,
+                         const LapWLSFlux<ZFACE   , order>   & a_zfaceflux,
+                         const LapWLSFlux<BOUNDARY, order>   & a_ebflux,
+                         int                                 a_neighType,
+                         Real                                a_dx);
 
     //Gets Advection WLS flux divergence stencil
     inline void
@@ -95,6 +86,7 @@ namespace Proto
     // return a vector of stencils, one per component
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_WLSStencilImplem.H

@@ -83,7 +83,7 @@ namespace Proto
   template < int order>
   Real
   WLSStencil<order>::
-  getLapinhomogTerm(
+  getDistanceWeightedFluxAvgStencil(
     Real                           a_inhomogTermM,
     Real                           a_inhomogTermP,
     const RealVect                 a_centroid,
@@ -116,35 +116,46 @@ namespace Proto
 
 
   //Gets Laplacian WLS flux divergence stencil
+  //FIXME Short rant here.
+  //      This class is bad and there are few things to fix. First every dimension is unlooped, and asking for mistakes. If 3D breaks look here first.
+  //      Also the flux opjects really don't need to live outside of this function.
+  //      So we pretty much do the same thing for every operator, with a little templating the sum over each flux part could just be done once and reused
+  //      I don't really know why these functions all live in a class together.
   template < int order>
   void
   WLSStencil<order>::
-  getLaplaWLSDivFStencil(LocalStencil< CELL,  Real>          & a_vofStencil,
-                         const EBIndex<CELL>                   & a_vof,
-                         const EBGraph                         & a_graph,
-                         const VoluData                        & a_voludata,
-                         const EBFaData                        & a_ebfadata,
-                         const XFacData                        & a_xfacdata,
-                         const YFacData                        & a_yfacdata,
-                         const ZFacData                        & a_zfacdata,
-                         const EBNormalData                    & a_ebnormxdata,
-                         const EBNormalData                    & a_ebnormydata,
-                         const EBNormalData                    & a_ebnormzdata,
-                         const BaseWLSFlux<XFACE, order>  & a_xfaceflux,
-                         const BaseWLSFlux<YFACE, order>  & a_yfaceflux,
-                         const BaseWLSFlux<ZFACE, order>  & a_zfaceflux,
-                         const BaseWLSFlux<BOUNDARY, order>  & a_ebflux,
-                         string                             a_ebbcName,
-                         string                             a_dombcName[2*DIM],
-                         Real                               & a_inhoTerm,
-                         int                                & a_neighType,
-                         Real                                  a_dx)
+  getLapWLSDivFStencil(LocalStencil< CELL,  Real>          & a_vofStencil,
+                       Real                                & a_inhoTerm,
+                       const EBIndex<CELL>                 & a_vof,
+                       const EBGraph                       & a_graph,
+                       const MomentHolder<order>           & a_momentData,
+                       const LapWLSFlux<XFACE   , order>   & a_xfaceflux,
[…]

### 2023-02-03 src/EBProto/hoeb/Proto_WLSneighbors.H

@@ -26,36 +26,9 @@ namespace Proto
         clear();
       };
 
-    Neighbors(Vector<IndMomDIM>      & a_volMom,
-              Vector<IndMomSDMinOne> & a_facMom,
-              Vector<IndMomDIM>      & a_ebfMom,
-              Vector<RealVect>       & a_volLoc,
-              Vector<RealVect>       & a_facLoc,
-              Vector<RealVect>       & a_ebfLoc,
-              Vector<Real>         & a_volneighFrac,
-              Vector<Real>         & a_ebfneighFrac,
-              Vector<Real>         & a_facneighFrac,
-              Vector<Vector<IndMomDIM> > & a_ebfneighNorm,
-              Vector<int>            & a_facneighDir,
-              Vector<Side::LoHiSide> & a_facneighSid)
-      {
-        m_volMom = a_volMom;
-        m_facMom = a_facMom;
-        m_ebfMom = a_ebfMom;
-        m_volLoc = a_volLoc;
-        m_facLoc = a_facLoc;
-        m_ebfLoc = a_ebfLoc;
-        m_volneighFrac = a_volneighFrac;
-        m_ebfneighFrac = a_ebfneighFrac;
-        m_facneighFrac = a_facneighFrac;
-        m_ebfneighNorm = a_ebfneighNorm;
-        m_facneighDir = a_facneighDir;
-        m_facneighSid = a_facneighSid;
-        check();
-      };
-
     inline void clear()
       {
+        m_cells.resize(0);
         m_volMom.resize(0);
         m_facMom.resize(0);
         m_ebfMom.resize(0);
@@ -87,9 +60,8 @@ namespace Proto
     getVoFsNeighbors(const EBIndex<cent> & a_face,
                      const EBIndex<CELL> & a_vof,
                      const int             a_radius,
-                     Neighbors<order>    & a_neigh,
                      const EBGraph       & a_graph,
-                     int                   a_neighType) const;
+                     int                   a_neighType);
 
     template<CENTERING cent>
     Vector<EBIndex<CELL> >
@@ -112,12 +84,41 @@ namespace Proto
     getMomentsInfoFromNeighbors(Vector<EBIndex<CELL> > & a_vols,
                                 const EBGraph          & a_graph,
                                 const MomentHolder<order>  & a_momentData,
-                                Neighbors<order> & a_neigh,
                                 string                   a_ebbcName,
                                 string                   a_dombcName[2*DIM], // order is is not obvious
                                 Real                   a_dx,
[…]

### 2023-02-03 src/EBProto/implem/Proto_Normalizor.H

@@ -7,6 +7,22 @@
 namespace Proto
 {
 
+  // Utilities related to moments
+  // get the volume of a regular cell, given dx. Dimensionality is accounted for
+  inline Real
+  getRegularVolume(const Real a_dx)
+  {
+    return D_TERM(a_dx, *a_dx, *a_dx);
+  }
+
+  // get the volume of a regular face, given dx. Dimensionality is accounted for
+  inline Real
+  getRegularArea(const Real a_dx)
+  {
+    return D_TERM(1, *a_dx, *a_dx);
+  }
+
+
   /// This class is used to provide nomalized moments (removes dependence on grid spacing)
   template <int order>
   class Normalizor
@@ -359,21 +375,58 @@ namespace Proto
         }
       }
     }
-  };
 
-// Other utilities related to moments
-  // get the volume of a regular cell, given dx. Dimensionality is accounted for
-  inline Real
-  getRegularVolume(const Real a_dx)
-  {
-    return D_TERM(a_dx, *a_dx, *a_dx);
-  }
-  // get the volume of a regular face, given dx. Dimensionality is accounted for
-  inline Real
-  getRegularArea(const Real a_dx)
-  {
-    return D_TERM(1, *a_dx, *a_dx);
-  }
+    // normalize a volume moment by removing dependence on dx
+    inline static void
+    normalizeFaceMoment(IndexedMoments<DIM-1, order> & a_faceMoment,
+                        const Real a_dx)
+      {
+        Real areaScaleFactor = getRegularArea(a_dx);
+        for(MomentIterator<DIM-1, order> iter; iter.ok(); ++iter)
+          {
+            const IndexTM<int, DIM-1>& p = iter();
+            a_faceMoment[iter()] /= (areaScaleFactor*POW(a_dx, p));
+          }
+      }
+
+    inline static void
+    normalizeFaceMoment(IndexedMoments<DIM, order> & a_faceMoment,
+                        const Real a_dx)
+      {
+        Real areaScaleFactor = getRegularArea(a_dx);
+        for(MomentIterator<DIM, order> iter; iter.ok(); ++iter)
+          {
+            const IndexTM<int, DIM>& p = iter();
+            a_faceMoment[iter()] /= (areaScaleFactor*POW(a_dx, p));
+          }
+      }
+
+    // normalize a face moment by removing dependence on dx
+    inline static void
[…]

### 2023-02-03 src/EBTools/Chombo_EBDictionary.H

@@ -16,8 +16,9 @@ namespace StencilNames
   static const string Poisson2("Second_Order_Poisson");
 
   ///WLS stencil
-  static const string PoissonWLS("Weighted_Least_Squares_Poisson");
-  static const string AdvectionWLS("Weighted_Least_Squares_Advection");
+  // FIXME these are going a slightly different direction and don't fit well anymore
+  // static const string PoissonWLS("Weighted_Least_Squares_Poisson");
+  // static const string AdvectionWLS("Weighted_Least_Squares_Advection");
 
   ///Signals Dirichlet BCs
   static const string Dirichlet("Dirichlet");

### 2023-02-03 src/EBTools/Chombo_EBDictionaryImplem.H

@@ -68,48 +68,49 @@ registerStencilWLS(string a_stencilName,
                 bool   a_needDiagonalWeights,
                 Point  a_dstGrow)
 {
-  PR_assert(!m_isClosed);
+  PR_assert(false); // FIXME
+  // PR_assert(!m_isClosed);
 
-  stencilKey key;
-  key.m_ebbcName    = a_ebbcName;
-  key.m_stencilName = a_stencilName;
-  int dstIndex = getIndex(a_dstDomain);
+  // stencilKey key;
+  // key.m_ebbcName    = a_ebbcName;
+  // key.m_stencilName = a_stencilName;
+  // int dstIndex = getIndex(a_dstDomain);
 
-  
-  shared_ptr< LevelData< EBGraph  >  > graphS = m_geoserv->getGraphs(    a_srcDomain);
-  shared_ptr< LevelData< EBGraph  >  > graphD = m_geoserv->getGraphs(    a_dstDomain);
-  shared_ptr< LevelData< VoluData >  > voldat = m_geoserv->getVoluData(  a_srcDomain);
-  shared_ptr< LevelData< EBFaData >  > ebfdat = m_geoserv->getEBFaceData(a_srcDomain);
-  shared_ptr< LevelData< XFacData >  > xfadat = m_geoserv->getXFaceData( a_srcDomain);
-  shared_ptr< LevelData< YFacData >  > yfadat = m_geoserv->getYFaceData( a_srcDomain);
-  shared_ptr< LevelData< ZFacData >  > zfadat = m_geoserv->getZFaceData( a_srcDomain);
 
-  shared_ptr< LevelData< EBNorData >  > ebnorxdatpld = m_geoserv->getEBNormalData_x(a_srcDomain);
-  shared_ptr< LevelData< EBNorData >  > ebnorydatpld = m_geoserv->getEBNormalData_y(a_srcDomain);
-  shared_ptr< LevelData< EBNorData >  > ebnorzdatpld = m_geoserv->getEBNormalData_z(a_srcDomain);
+  // shared_ptr< LevelData< EBGraph  >  > graphS = m_geoserv->getGraphs(    a_srcDomain);
+  // shared_ptr< LevelData< EBGraph  >  > graphD = m_geoserv->getGraphs(    a_dstDomain);
+  // shared_ptr< LevelData< VoluData >  > voldat = m_geoserv->getVoluData(  a_srcDomain);
[…]

### 2023-03-02 src/EBCM/Chombo_EBCMGraph.H
single level cell merge ready for testing

@@ -13,7 +13,6 @@ namespace EBCM
   using std::shared_ptr;
 
   typedef Proto::EBGraph       pr_ebgrap;
-  typedef Proto::EBData        pr_ebdata;
   typedef Chombo::GeometryService ch_geoserv;
   
   typedef Proto::pr_vof pr_vof;
@@ -599,15 +598,16 @@ namespace EBCM
     inline  int
       makeTheBlobs(shared_ptr<set<EBCMVolu > >           & a_soluVolumes,
                    shared_ptr<set<pr_vof   > >           & a_ebVolumes, 
-                   const EBGraph                         & a_graph,
-                   const EBData                          & a_data,
+                   const shared_ptr<ch_geoserv>          & a_geoserv,
+                   const Box                             & a_domain,
+                   const ch_dit                          & a_dit,
                    const double                          & a_dx,
                    bool                                    a_mergeSmallCells)
     {
       a_soluVolumes = shared_ptr< set< EBCMVolu > >(new set<EBCMVolu>());
       for(auto vof = a_ebVolumes.begin(); vof != a_ebVolumes.end(); ++vof)
       {
-        EBCMVolu volume = createEBCMVolume(*vof, a_graph, a_data, a_dx);
+        EBCMVolu volume = createEBCMVolume(*vof, a_geoserv, a_domain, a_dit, a_dx);
         a_soluVolumes.insert(volume);
       }
     
@@ -663,21 +663,29 @@ namespace EBCM
   }//end function
 
 
-///Class to make merged sparse embedded boundary description
-/**
- */
+  ///Class to make merged sparse embedded boundary description
+  /**
+   */
   template< int order>
   class EBCMGraph
   {
   public:
-
-    EBCMGraph(shared_ptr<pr_ebgrap>  a_graph,
-              shared_ptr<pr_ebdata>  a_data,
-              Real                   a_dx,
-              bool                   a_mergeSmallCells) const:
-      m_graph(a_graph), m_data(a_data), m_dx(a_dx)
+    //strong construction would be better but way less convenient
+    EBCMGraph()
     {
+      m_defined = false;
+    }
+
+    inline void 
+    define(const shared_ptr<ch_geoserv>          & a_geoserv,
+           const Box                             & a_domain,
+           const ch_dit                          & a_dit,
+           const double                          & a_dx,
+           bool                   a_mergeSmallCells) 
+    {
[…]

### 2023-04-05 example/DomainDecomposition/common/EBIBC.H
Div op working after merge

@@ -23,7 +23,7 @@ public:
         string  a_scalIC,
         string  a_loSideDomainBC[DIM],
         string  a_hiSideDomainBC[DIM],
-        string  a_ebbc = string("no_slip_wall"))
+        string  a_ebbc = string("NoSlipWall"))
   {
     define( a_veloIC,                     
             a_scalIC,                     
@@ -37,7 +37,7 @@ public:
          string  a_scalIC,
          string  a_loSideDomainBC[DIM],
          string  a_hiSideDomainBC[DIM],
-         string  a_ebbc = string("no_slip_wall"))
+         string  a_ebbc = string("NoSlipWall"))
   {
     m_isDefined = true;
     for(int idir = 0;  idir < DIM; idir++)
@@ -58,54 +58,6 @@ public:
     unsigned int index = ebp_index(idir, a_sd);
     return m_domainBC[index];
   }
-
-  string& operator()(unsigned int idir, Side::LoHiSide a_sd)
-  {
-    unsigned int index = ebp_index(idir, a_sd);
-    return m_domainBC[index];
-  }
-
-  void standardStencilStrings(string a_bcnames[2*DIM],
-                              string& a_ebbcname) const
-    {
-      for(int ivec = 0; ivec < 2*DIM; ivec++)
-        {
-          const string& faceBC = m_domainBC[ivec];
-          if(faceBC == "Neumann")
-            {
-              a_bcnames[ivec] = StencilNames::Neumann;
-            }
-          else if(faceBC == "Dirichlet")
-            {
-              a_bcnames[ivec] = StencilNames::Dirichlet;
-            }
-          else if(faceBC == "None")
-            {
-              a_bcnames[ivec] = StencilNames::NoBC;
-            }
-          else
-            {
-              MayDay::Error((("EBIBC: unknown bc string " + a_bcnames[ivec]).c_str()));
-            }
-        }
-
-      if(m_ebbc == "Neumann")
-        {
-         a_ebbcname = StencilNames::Neumann;
-        }
-      else if(m_ebbc == "Dirichlet")
-        {
-         a_ebbcname = StencilNames::Dirichlet;
-        }
-      else if(m_ebbc == "None")
-        {
-         a_ebbcname = StencilNames::NoBC;
-        }
-      else
-        {
-          MayDay::Error((("EBIBC: unknown eb bc string " + a_ebbcname).c_str()));
-        }
-    }
 
[…]

### 2023-04-05 example/HO-WLS/common/EBPetscSolver.H

@@ -18,25 +18,28 @@
 #include "petscvec.h"
 #include "petscksp.h"
 #include "petscviewer.h"
-#include "petscmat.h"
 #include "Chombo_EBChombo.H"
 #include "Chombo_EBLevelBoxData.H"
 #include "hoeb/Proto_EBDomainBC.H"
 #include "EBMultigridFunctions.H"
 
-/// Stuff petsc frameworks have in common
-/**
-*/
+/// Framework to solve an elliptic equation using PETSc
+/// Probably a good candidate to move into Chombo4/src
 template <int order>
-class BaseEBPetscSolver
+class EBPetscSolver
 {
 public:
   typedef GraphConstructorFactory< EBBoxData<CELL, int, 1> >  devifactint_t;
-  typedef GraphConstructorFactory<EBHostData<CELL, int, 1> >  host_fact_int_t;
-  typedef GraphConstructorFactory<EBHostData<CELL,Real, 1> >  host_fact_real_t;
+  typedef GraphConstructorFactory<EBHostData<CELL, int, 1> >  hostfactint_t;
+  typedef GraphConstructorFactory<EBHostData<CELL,Real, 1> > hostfactreal_t;
   typedef EBDictionary<order, Real, CELL, CELL>                dictionary_t;
-<<<<<<< HEAD
   typedef EBStencil<order, Real, CELL, CELL>                    ebstencil_t;
+
+  typedef CH4_Data_Choreography::DistributedData<EBBoxData< CELL, Real, 1> > devi_distrib_real_t;
+  typedef CH4_Data_Choreography::DistributedData<EBHostData<CELL, Real, 1> > host_distrib_real_t;
+  typedef CH4_Data_Choreography::DistributedData<EBBoxData< CELL, int , 1> > devi_distrib_int_t;
+  typedef CH4_Data_Choreography::DistributedData<EBHostData<CELL, int , 1> > host_distrib_int_t;
+  typedef CH4_Data_Choreography::DistributedData<EBGraph>                    graph_distrib_t;
 
   // DEPRECATED, use updated version with better BC management
   EBPetscSolver(const shared_ptr<GeometryService<order> >  & a_geoserv,
@@ -62,25 +65,6 @@ public:
                 string a_stencilName,
                 Real a_dx,   Real a_alpha, Real a_beta, Point a_ghost,
                 const Proto::EBDomainBC<1>    & a_domainBC)
-=======
[…]

### 2023-04-05 src/BaseTools/Chombo_LAPACKMatrix.H

@@ -12,7 +12,7 @@
 #define _LAPACKMATRIX_H_
 
 #include "Chombo_REAL.H"
-#include "Proto_LoHiSide.H"
+//#include "Proto_LoHiSide.H"
 #include <utility>
 #include "Chombo_NamespaceHeader.H"
 

### 2023-04-05 src/EBProto/EBProto.H

@@ -9,8 +9,24 @@ namespace Proto
   enum CENTERING {CELL=0,BOUNDARY,XFACE,YFACE,ZFACE};
 
   // A way to loop over each face type
-  constexpr std::array<CENTERING, DIM>   REG_FACES{D_DECL(XFACE, YFACE, ZFACE)};
-  constexpr std::array<CENTERING, DIM+1> ALL_FACES{BOUNDARY, D_DECL(XFACE, YFACE, ZFACE)};
+  constexpr std::array<CENTERING, DIM>   REG_FACES{
+    XFACE
+#if DIM>=2
+    ,YFACE
+#endif
+#if DIM>= 3
+    ,ZFACE
+#endif
+  };
+  constexpr std::array<CENTERING, DIM+1> ALL_FACES{BOUNDARY,
+    XFACE
+#if DIM>=2
+    ,YFACE
+#endif
+#if DIM>= 3
+    ,ZFACE
+#endif
+  };
 
   inline int FACE_DIR(CENTERING cent)
   {
@@ -34,9 +50,9 @@ namespace Proto
   inline int ebp_index(const int a_idir,
                        const Side::LoHiSide a_side)
   {
-    CH_assert(a_idir >= 0);
+    PR_assert(a_idir >= 0);
     //CH_assert(a_idir < Chombo4::SpaceDim); // FIXME add once dimensionality be better managed
-    return a_idir + a_side*Chombo4::SpaceDim;
+    return a_idir + a_side*DIM;
   }
 
   /// Get the side and direction from a vector index
@@ -52,10 +68,10 @@ namespace Proto
                        int& a_idir,
                        Side::LoHiSide& a_side)
   {
-    CH_assert(a_index >= 0);
+    PR_assert(a_index >= 0);
     //CH_assert(a_index < 2*Chombo4::SpaceDim); // FIXME add once dimensionality be better managed
-    a_idir = a_index%Chombo4::SpaceDim;
-    if (a_index/Chombo4::SpaceDim == 0)
+    a_idir = a_index%DIM;
+    if (a_index/DIM == 0)
       {
         a_side = Side::Lo;
       }

### 2023-04-05 src/EBProto/Proto_EBExactSolutions.H

@@ -975,7 +975,7 @@ public:
     Real diff = std::abs(retval - retval_simp);
     if ((diff > tol))
       {
-        pout() << diff << std::endl;
+        //pout() << diff << std::endl;
         Chombo4::MayDay::Error("broken elegance");
       }
     return retval_simp;

### 2023-04-05 src/EBProto/Proto_EBStencil.H

@@ -154,9 +154,9 @@ namespace Proto
     inline
     void apply(EBBoxData<       dstCenter, data_t, 1>  &   a_dst,
                const EBBoxData< srcCenter, data_t, 1>  &   a_src,
-               bool   a_initToZero,
-               double a_scale     ,
-               bool a_printStuff= false)  const;
+               bool a_initToZero = true,
+               double a_scale = 1.0,
+               bool a_printStuff = false)  const;
                
 
     
@@ -164,8 +164,8 @@ namespace Proto
     inline
     void applyITZ(EBBoxData<       dstCenter, data_t, 1>  &   a_dst,
                   const EBBoxData< srcCenter, data_t, 1>  &   a_src,
-                  double a_scale      ,
-                  bool a_printStuff   = false)  const;
+                  double a_scale = 1.0,
+                  bool a_printStuff = false)  const;
                
 
     /// get the diagonal weights of the stencil

### 2023-04-05 src/EBProto/hoeb/Proto_EBStencilHOImplem.H

@@ -39,7 +39,7 @@ namespace Proto
     PR_TIME("isRegularStencil");
     using Chombo4::pout;
     bool retval = true;
-    Vector<EBIndex<CELL> > vof_cont;
+    vector<EBIndex<CELL> > vof_cont;
     vof_cont.push_back(a_vof);
     RealVect centroid;
     Real kappa;
@@ -390,7 +390,7 @@ namespace Proto
     //Reading parameters from the inputs file for WLS stencils
     StencilAttributes stenAttb;
 
-    Vector<int> ptVec;
+    vector<int> ptVec;
 
     //Reading parameters from the inputs file for WLS stencils
     ParmParse pp;
@@ -601,7 +601,7 @@ namespace Proto
     //Neighbor list type. 0-FaceBased or 1-CellBased
     int neighListType = 1;
 
-    Vector<int> ptVec;
+    vector<int> ptVec;
 
     //Reading parameters from the inputs file for WLS stencils
     ParmParse pp;
@@ -936,7 +936,7 @@ namespace Proto
     a_inhoContr.resize(a_dstVoFs.size());
 
     bool verbose = false;
-    Vector<int> ptVec;
+    vector<int> ptVec;
 
     //Reading parameters from the inputs file for WLS stencils
     StencilAttributes stenAttb;
@@ -1069,7 +1069,7 @@ namespace Proto
     a_inhoContr.resize(SpaceDim, vector<Real>(a_dstVoFs.size()));
 
     bool verbose = false;
-    Vector<int> ptVec;
+    vector<int> ptVec;
 
     //Reading parameters from the inputs file for WLS stencils
     StencilAttributes stenAttb;

### 2023-04-05 src/EBProto/hoeb/Proto_WLSCell.H

@@ -129,7 +129,7 @@ namespace Proto
   /**
    */
   template<int order> 
-  class ConstantVectorVel: public BaseExactVelocity<order>
+  class ConstantvectorVel: public BaseExactVelocity<order>
   {
   public:
     typedef IndexedMoments<DIM  , order> IndMomDIM;
@@ -139,7 +139,7 @@ namespace Proto
     ///  
     /**
      */
-    ConstantVectorVel(const RealVect & a_value)
+    ConstantvectorVel(const RealVect & a_value)
       :BaseExactVelocity<order>(true) // this is location based
     {
       m_value = a_value;
@@ -154,13 +154,13 @@ namespace Proto
   
     virtual RealVect getVelocityAtPoint(const RealVect& a_x) const;
   
-    virtual ~ConstantVectorVel()
+    virtual ~ConstantvectorVel()
     {
     }
   
   private:
     //weak construction is bad
-    ConstantVectorVel();
+    ConstantvectorVel();
   
     RealVect m_value;
   };
@@ -169,7 +169,7 @@ namespace Proto
   /**
    */
   template<int order> 
-  class PoiseuilleVectorVel: public BaseExactVelocity<order>
+  class PoiseuillevectorVel: public BaseExactVelocity<order>
   {
   public:
     typedef IndexedMoments<DIM  , order> IndMomDIM;
@@ -179,7 +179,7 @@ namespace Proto
     ///  
     /**
      */
-    PoiseuilleVectorVel(const Real & a_centerValue,
+    PoiseuillevectorVel(const Real & a_centerValue,
                         const Real & a_wallValue,
                         const Real & a_radius,
                         const RealVect & a_center)
@@ -200,13 +200,13 @@ namespace Proto
   
     virtual RealVect getVelocityAtPoint(const RealVect& a_x) const;
   
-    virtual ~PoiseuilleVectorVel()
+    virtual ~PoiseuillevectorVel()
     {
     }
   
   private:
     //weak construction is bad
-    PoiseuilleVectorVel();
+    PoiseuillevectorVel();
   
     RealVect m_center;
     Real m_radius;
@@ -282,7 +282,7 @@ namespace Proto
     //and EB faces. Stores all this info in the Neighbors object.
     // DEPRECATED now lives in neighbors
     void
-    getMomentsInfoFromNeighbors(Vector<EBIndex<CELL> > & a_vols,
+    getMomentsInfoFromNeighbors(vector<EBIndex<CELL> > & a_vols,
                                 const EBGraph          & a_graph,
[…]

### 2023-04-05 src/EBProto/hoeb/Proto_WLSCellImplem.H

@@ -141,7 +141,7 @@ namespace Proto
   {
     PR_TIME("getShiftedMomentMatrixFaces");
     using Chombo4::pout;
-    Vector<IndMomDIM> fac2volmom;
+    vector<IndMomDIM> fac2volmom;
     MomentIterator<DIM, order> momit;
     int nfac = a_neigh.sizeFaces();
     fac2volmom.resize(nfac);
@@ -532,7 +532,7 @@ namespace Proto
   getEBFluxMatrix(Chombo4::LAPACKMatrix    & a_fluxMatrix,
                   const EBIndex<cent>      & a_face,
                   RealVect                 & a_faceLoc,
-                  Vector<IndMomDIM>        & a_ebnorm,
+                  vector<IndMomDIM>        & a_ebnorm,
                   Real                     a_dx) const
   {
     PR_TIME("getEBFluxMatrix");
@@ -641,7 +641,7 @@ namespace Proto
   void
   BaseWLSFlux<cent, order>::
   getWeightsMatrixComponent(Chombo4::LAPACKMatrix  & a_weights,
-                            const Vector<int>      & a_weightDist,
+                            const vector<int>      & a_weightDist,
                             IndexTM<int, 2>         a_start) const
   {
     PR_TIME("getWeightsMatrixComponent");
@@ -901,18 +901,18 @@ namespace Proto
   // {
   //   PR_TIME("computeInhomogTerm");
   //   using Chombo4::pout;
-  //   Vector<IndMomSDMinOne> a_facmom = a_neigh.m_facMom;
-  //   Vector<IndMomDIM> a_ebfmom= a_neigh.m_ebfMom;
-  //   Vector<Vector<IndMomDIM> > a_ebfneighNorm = a_neigh.m_ebfneighNorm;
-  //   Vector<RealVect> a_facneighLoc = a_neigh.m_facLoc;
-  //   Vector<int> a_facneighDir = a_neigh.m_facneighDir;
-  //   Vector<Side::LoHiSide> a_facneighSid = a_neigh.m_facneighSid;
-  //   Vector<RealVect> a_ebfneighLoc = a_neigh.m_ebfLoc;
-  //   Vector<Real> ebfneighFrac = a_neigh.m_ebfneighFrac;
-  //   Vector<Real> facneighFrac = a_neigh.m_facneighFrac;
+  //   vector<IndMomSDMinOne> a_facmom = a_neigh.m_facMom;
+  //   vector<IndMomDIM> a_ebfmom= a_neigh.m_ebfMom;
[…]

### 2023-04-05 src/EBProto/hoeb/Proto_WLSStencilImplem.H

@@ -473,7 +473,7 @@ namespace Proto
     {
       EBIndex<BOUNDARY> cutface = a_vof.getCutFace();
       RealVect centroid, normal;
-      Vector<IndMomDIM> ebnorm (DIM);
+      vector<IndMomDIM> ebnorm (DIM);
       ebnorm[0] = a_ebnormxdata(a_vof, 0);
       for(MomentIterator<DIM, order> iter; iter.ok(); ++iter)
       {

### 2023-04-05 src/EBProto/hoeb/Proto_WLSneighbors.H

@@ -62,31 +62,31 @@ namespace Proto
     //increases by one for the neighbor cells sharing a face with the original
     //cells of radius one.
     template<CENTERING cent>
-    Vector<EBIndex<CELL> >
+    vector<EBIndex<CELL> >
     getVoFsNeighbors(const EBIndex<cent> & a_face,
                      const EBIndex<CELL> & a_vof,
                      const int             a_radius,
                      const EBGraph       & a_graph,
                      int                   a_neighType);
 
-    Vector<EBIndex<CELL> >
+    vector<EBIndex<CELL> >
     getCellNeighbors(const EBIndex<CELL> & a_vof,
                      const int             a_baseRadius,
                      const EBGraph       & a_graph);
 
     template<CENTERING cent>
-    Vector<EBIndex<CELL> >
+    vector<EBIndex<CELL> >
     getFaceNeighbors(const EBIndex<cent> & a_face,
                      const int             a_baseRadius,
                      const EBGraph       & a_graph);
 
-    Vector<EBIndex<CELL> >
+    vector<EBIndex<CELL> >
     growNeighbors(const int             a_baseRadius,
                   const EBGraph       & a_graph);
 
     // New version, use this
     void
-    getMomentsInfoFromNeighbors(Vector<EBIndex<CELL> > & a_vols,
+    getMomentsInfoFromNeighbors(vector<EBIndex<CELL> > & a_vols,
                                 const EBGraph          & a_graph,
                                 const MomentHolder<order>  & a_momentData,
                                 const EBDomainBC<1>      & a_domainBC,
@@ -103,7 +103,7 @@ namespace Proto
                            bool a_verbose = false)
       {
         MomentIterator<DIM,order> momit;
-        Vector<EBIndex<CELL> > vols;
+        vector<EBIndex<CELL> > vols;
         // REVIEW Make sure stencils are big enough. Size is not a sufficient measure, this should check the stencil is solvable
         // while (this->size() <= momit.size()+DIM)
         //   {
@@ -123,10 +123,10 @@ namespace Proto
       }
 
     inline void
-    scaleMoments(Vector<IndMomDIM>      & a_volMom,
[…]

### 2023-04-05 src/EBProto/implem/Proto_EBStencilImplem.H

@@ -91,66 +91,6 @@ namespace Proto
       }
     }
   }
-
-  //Constructor specifically for Weighted Least Squares stencils
-  template <int order, typename data_t, CENTERING srcCenter, CENTERING dstCenter>
-  EBStencil<order, data_t, srcCenter, dstCenter>::
-  EBStencil(string              a_stencilName,
-            string              a_domainBCName[2*DIM],
-            string              a_ebbcName,
-            const Box         & a_srcValid,
-            const Box         & a_dstValid,
-            const Box         & a_srcDomain,
-            const Box         & a_dstDomain,
-            const Point       & a_srcGhost,
-            const Point       & a_dstGhost,
-            const EBGraph     & a_srcGraph,
-            const EBGraph     & a_dstGraph,
-            const VoluData    & a_voludata,
-            const EBFaData    & a_ebfadata,
-            const XFacData    & a_xfacdata,
-            const YFacData    & a_yfacdata,
-            const ZFacData    & a_zfacdata,
-	    const EBNorData   & a_ebnorxdata,
-            const EBNorData   & a_ebnorydata,
-            const EBNorData   & a_ebnorzdata,
-            double              a_dx,
-            bool                a_periodiconly,
-            bool                a_needDiagonalWeights,
-            Point               a_dstGrown)
-  {
-    m_periodic_domain_bcs_only = a_periodiconly;
-    vector< EBIndex<dstCenter> >              dstVoFs;
-    vector< LocalStencil<srcCenter, data_t> > stencil;
-    vector< double > inhoContr;
-
-    m_hasDomainBCs = 
-      ho_t::getStencil(dstVoFs, stencil, inhoContr, m_regStencilInterior, 
-                       m_regStencilBCS, m_BCApplyBoxes, m_regApplyBox, m_bcsOnly,
-                       a_stencilName,  a_domainBCName, a_ebbcName,
-                       a_srcValid,  a_dstValid,
-                       a_srcDomain, a_dstDomain,     
-                       a_srcGhost,  a_dstGhost,    
-                       a_srcGraph,  a_dstGraph,
-                       a_voludata,  a_ebfadata,    
-                       a_xfacdata,  a_yfacdata, a_zfacdata,
-                       a_ebnorxdata, a_ebnorydata,
-                       a_ebnorzdata,
[…]

### 2023-04-05 src/EBTools/Chombo_EBLevelBoxData.H

@@ -642,21 +642,7 @@ public:
     }
 
   }
-  
 
-  ///
-  EBLevelBoxData&
-  operator+=(const EBLevelBoxData& a_input)
-  {
-    DisjointBoxLayout dbl = this->disjointBoxLayout();
-    DataIterator dit = dbl.dataIterator();
-    for(int ibox = 0;  ibox < dit.size(); ibox++)
-    {
-      (*this)[dit[ibox]] += a_input[dit[ibox]];
-    }
-    return *this;
-  }
-  
   ///
   static 
   void copyToDevice(      devi_distrib_t & a_deviDat,
@@ -776,7 +762,7 @@ public:
   }
 
   // Is there a reason this should not exist? There is no harm in sharing a smart pointer. The object already know what graph it came from, so there is no reason to pass around both the levelboxdata and graph separately.
-  shared_ptr<LevelData<EBGraph> >
+  shared_ptr<graph_distrib_t >
   getGraphs()
     {
       return m_graphs;
@@ -861,10 +847,12 @@ writeEBLevelHDF5(const string& a_filename,
                  const EBLevelBoxData<CELL, NUMCOMPS>  & a_data,
                  const EBLevelBoxData<CELL, 1       >  & a_kapp,
                  const Box                             & a_domain,
-                 shared_ptr<LevelData<EBGraph>  > a_graphs,
-                 Real                             a_coveredval = 0.0,
-                 Real a_dx= 1.0, Real a_dt=1.0, Real a_time=1.0,
-                 std::vector<std::string> a_varNames={})
+                 shared_ptr<CH4_Data_Choreography::DistributedData<EBGraph> >  a_graphs,
+                 Real                                    a_coveredval = 0.0,
+                 Real                                    a_dx= 1.0,
+                 Real                                    a_dt=1.0,
+                 Real                                    a_time=1.0,
+                 std::vector<std::string>                a_varNames={})
 {
 
 #ifdef CH_USE_HDF5

### 2023-04-05 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/notes.tex
very ebcm data holders

\begin{itemize}
\item BlobFaceIndex is a collection of EBIndexes
\item BlobVoluIndex is a merged bunch of EBIndex<CELL>
\item Merging and putting into the unstructured format should be
  separate things.
\item Working theory on how the usage pattern for this stuff will work:
  \begin{itemize}
  \item Build EB as normal.
  \item Put EB into irregular description.
    \item while still in irregular description, merge small cells ON
      BOX.
    \item  If we find we cannot merge on box, for now throw an error.
    \item  Later we can figure out Box to Box communication.
  \end{itemize}
\item Notes on memory overhead:
  \begin{itemize}
    \item This could mean  a large increase in the memory load for the
      geometric meta data but this can be managed by doing stuff in a
      carefully ordered manner:
      \begin{itemize}
      \item Build EBIS.
      \item Build BlobSpace using EBIS.  The irregular graph is a
        temporary here that gets deleted.
      \item Delete EBIS.
      \item Now if you build data and operators after this process is
        complete, the meta data overhead should be no worse than EBIS.
      \end{itemize}

  \end{itemize}

\end{itemize}

### 2023-04-05 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp

@@ -14,7 +14,8 @@
 #include "Chombo_GeometryService.H"
 #include "Chombo_EBDictionary.H"
 #include "Chombo_EBChombo.H"
-#include "Chombo_EBCMGraph.H"
+#include "Chombo_EBCM_Graph.H"
+#include "Chombo_EBCM_HostLevelData.H"
 #include "EBMultigrid.H"
 
 #include "DebugFunctions.H"
@@ -92,6 +93,16 @@ makeMergedGeometry(   shared_ptr< ebcm_meta  >  & a_ebcm,
   a_grids  = vecgrids[0];
   a_dx     = dx;
   a_domain = domain;
+
+  
+}
+
+/****/
+void
+makeEBCMData(   shared_ptr< ebcm_meta  >  & a_ebcm)
+{
+
+  EBCM::HostLevelData<double ,1, HOEB_MAX_ORDER>(a_ebcm, Chombo4::IntVect::Zero);
 }
 /**
    Print out max and min volume fraction in a meta.
@@ -166,6 +177,8 @@ int main(int a_argc, char* a_argv[])
     Real maxKapp, minKapp;
     //this tries out iteration and checks kappa
     checkKappa(maxKapp, minKapp, ebcm, grids);
+
+    makeEBCMData(ebcm);
   }
 
   //the stuff after the important stuff

### 2023-04-05 src/EBCM/Chombo_EBCM_Graph.H

@@ -1,0 +1,1254 @@
+#ifndef __Chombo_EBCM_Graph__
+#define __Chombo_EBCM_Graph__
+
+#include "implem/Proto_IrregGraph.H"
+#include "EBProto.H"
+#include "Proto_RealVect.H"
+#include "Chombo_ProtoInterface.H"
+using std::vector;
+using std::set;
+
+namespace EBCM
+{
+  using std::set;
+  using std::endl;
+  using std::shared_ptr;
+  using Chombo4::pout;
+  using Chombo4::MayDay;
+  
+  typedef Proto::EBGraph       pr_ebgrap;
+  
+  typedef Proto::EBIndex<CELL> pr_vof;
+  typedef Proto::Point         pr_pt;
+  typedef Proto::Box           pr_box;
+  typedef Chombo4::Box         ch_box;
+  typedef Chombo4::DataIndex   ch_dit;
+  
+  ///
+  template<CENTERING cent, int order>
+  class EBCM_Face
+  {
+  public:
+
+    pr_vof  m_lo;
+    pr_vof  m_hi;
+    IndexedMoments<DIM-1, order> m_facmom;
+    void defineAsRegular(pr_vof a_lo, pr_vof a_hi, Real a_dx)
+    {                                                  
+      m_lo = a_lo;
+      m_hi = a_hi;
+      m_facmom.setRegular(a_dx);
+    }
+
+    bool operator==(const EBCM_Face& a_input) const
+    {
+      return ((m_lo == a_input.m_lo)  && (m_hi == a_input.m_hi));
+    }
+
+    //for debugging.   proper IO would involve the moments.
+    inline void print() const
+    {
+      int icent = cent;
+      pout() << icent << "-side face:( " << m_lo << " , " << m_hi << " )" << endl;
+    }
+  };
+
+  template<int order>
+  class IrregFace
+  {
+  public:
+
+    pr_pt m_pt;
+    IndexedMoments<DIM, order> m_ebfmom;
+    void defineAsRegular(pr_vof a_vof)
+    {
+      m_pt =  a_vof.m_pt;
+
+      m_ebfmom.setToZero();
+    }
+
+    inline void print() const
+    {
+      pout() <<  "cut face:(" << m_pt << ")" << endl;
+    }
+
+  };
+
+  template<int order>
+  class EBCM_Volu
+  {
+  public:
+    typedef Chombo4::GeometryService<order> ch_geoserv;
[…]

### 2023-04-05 src/EBCM/Chombo_EBCM_HostLevelData.H

@@ -1,0 +1,72 @@
+#ifdef CH_LANG_CC
+/*
+ *      _______              __
+ *     / ___/ /  ___  __ _  / /  ___
+ *    / /__/ _ \/ _ \/  V \/ _ \/ _ \
+ *    \___/_//_/\___/_/_/_/_.__/\___/
+ *    Please refer to Copyright.txt, in Chombo's root directory.
+ */
+#endif
+
+#ifndef _EBCMHostLevelData_H____
+#define _EBCMHostLevelData_H____
+
+#include "Proto.H"
+#include "EBProto.H"
+#include "Chombo_ProtoInterface.H"
+#include "Chombo_EBChombo.H"
+#include "Chombo_ProtoFactories.H"
+
+#include "Chombo_SPMD.H"
+#include "Chombo_EBCM_VolBoxData.H"
+#include "Chombo_EBDataChoreography.H"
+#include "Chombo_GeometryService.H"
+#include <memory>
+namespace EBCM
+{
+  /// Simple structure to hold data on a level in an ebcm context.  volume data only
+  /**
+   */
+  template<typename data_t, int  NUMCOMPS, int order>
+  class HostLevelData
+  {
+  public:
+    typedef EBCM::VolBoxData<data_t, NUMCOMPS, order>            ebcm_fab_t;
+    typedef Chombo4::NullConstructorDataFactory<    ebcm_fab_t>  null_factory_t;
+    typedef CH4_Data_Choreography::DistributedData< ebcm_fab_t > mpi_frame_t;
+    typedef    EBCM::MetaDataLevel<        order >               ebcm_meta_t;
+    typedef    EBCM::SubVolumeIterator<    order >               ebcm_subvol_it;
+    typedef Chombo4::GeometryService<      order >               ch_geoserv;
+    typedef Chombo4::DisjointBoxLayout                           ch_dbl;
+    typedef Chombo4::ProblemDomain                               ch_probdom;
+    typedef Chombo4::DataIterator                                ch_dit;
+    typedef Chombo4::IntVect                                     ch_iv;
+    
+    HostLevelData(const shared_ptr<ebcm_meta_t>& a_meta,
+                  const ch_iv                  & a_ghost)
+    {
+      m_meta = a_meta;
+
+      const auto& graphs = (m_meta->m_graphs);
+      const auto& grids  = (m_meta->m_grids);
[…]

### 2023-04-05 src/EBCM/Chombo_EBCM_VolBoxData.H

@@ -1,0 +1,107 @@
+
+#ifndef _Chombo_EBCM_VolBoxData_H_
+#define _Chombo_EBCM_VolBoxData_H_
+
+#include <cmath>
+#include <cstdlib>
+#include <memory>
+#include "Proto.H"
+#include "EBProto.H"
+#include "Chombo_EBCM_Graph.H"
+
+using std::vector;
+using std::shared_ptr;
+
+namespace EBCM
+{
+  ///Holder for host EBCM data over a box.   volume only.
+  template <typename  data_t,  int ncomp, int order>
+  class VolBoxData
+  {
+  public:
+    typedef EBCM::EBCM_Graph< order >         ebcm_graph_t;
+    typedef Proto::HostBoxData<data_t, ncomp> pr_hostdat_t;
+    typedef Chombo4::MayDay                   ch_mayday;
+    ///
+    VolBoxData()
+    {
+    }
+
+
+    int nComp() const
+    {
+      return ncomp;
+    }
+
+    void define(const ebcm_graph_t& a_graph)
+    {
+      m_graph = a_graph;
+      pr_box prgid = ProtoCh::getProtoBox(a_graph.m_grid);
+      m_regdat.define(prgid);
+      if(a_graph.hasIrregular())
+      {
+        int numIrreg = a_graph.m_volumes->size();
+        int nvar = numIrreg*ncomp;
+        m_irrdat.resize(nvar);
+      }
+    }
+
+    
+
+    data_t* dataPtr(const pr_pt& a_pt, unsigned int a_icomp)
+    {
+      if(a_icomp >= ncomp)
+      {
+        ch_mayday::Error("VolBoxData access icomp too big");
+      }
+      data_t* retvalptr = NULL;
+      
+      bool useRegular = true;
+      int mapval = -4586;
+      if(m_graph.hasIrregular())
+      {
+        mapval = (*m_graph.m_map)(a_pt, 0);
+        useRegular = (mapval < 0);
+      }
+      if(useRegular)
+      {
+        retvalptr = &(m_regdat(a_pt, a_icomp));
+      }
+      else
+      {
+        int numVols = m_graph.m_volumes->size();
+        int vecvalcomp0 = mapval;
+        int idatavec  = vecvalcomp0 + a_icomp*numVols;
+        retvalptr = &(m_irrdat[idatavec]);
+      }
+      return retvalptr;
+    }
+    ///
+    /**
+       I will have to do something smarter than this for any performance  but for now, 
[…]

### 2023-04-07 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
pretty bold claims, there, hoss.

\documentclass{article}

%\include{macros}

\bibliographystyle{plain}

\usepackage{epsfig}
\usepackage{xcolor}
%%\usepackage{amssymb}
\usepackage{amsmath}

\newcommand{\Abold}{{\bf A}}
\newcommand{\abold}{{\bf a}}
\newcommand{\bbold}{{\bf b}}
\newcommand{\cbold}{{\bf c}}
\newcommand{\dbold}{{\bf d}}
\newcommand{\ebold}{{\bf e}}
\newcommand{\fbold}{{\bf f}}
\newcommand{\Fbold}{{\bf F}}
\newcommand{\gbold}{{\bf g}}
\newcommand{\hbold}{{\bf h}}
\newcommand{\ibold}{{\bf i}}
\newcommand{\jbold}{{\bf j}}
\newcommand{\kbold}{{\bf k}}
\newcommand{\lbold}{{\bf l}}
\newcommand{\mbold}{{\bf m}}
\newcommand{\Mbold}{{\bf M}}
\newcommand{\nbold}{{\bf n}}
\newcommand{\obold}{{\bf o}}
\newcommand{\pbold}{{\bf p}}
\newcommand{\qbold}{{\bf q}}
\newcommand{\rbold}{{\bf r}}
\newcommand{\sbold}{{\bf s}}
\newcommand{\tbold}{{\bf t}}
\newcommand{\ubold}{{\bf u}}
\newcommand{\vbold}{{\bf v}}
\newcommand{\wbold}{{\bf w}}
\newcommand{\xbold}{{\bf x}}
\newcommand{\ybold}{{\bf y}}
\newcommand{\zbold}{{\bf z}}
\newcommand{\bigzbold}{{\bf Z}}
\newcommand{\xspace}{\hspace{2 mm}}

\newcommand{\ahat}{{\hat a}}
\newcommand{\bhat}{{\hat b}}
\newcommand{\chat}{{\hat c}}
\newcommand{\dhat}{{\hat d}}
\newcommand{\ehat}{{\hat e}}
\newcommand{\fhat}{{\hat f}}
\newcommand{\ghat}{{\hat g}}
\newcommand{\hhat}{{\hat h}}
\newcommand{\ihat}{{\hat i}}
\newcommand{\jhat}{{\hat j}}
\newcommand{\khat}{{\hat k}}
\newcommand{\lhat}{{\hat l}}
\newcommand{\mhat}{{\hat m}}
\newcommand{\nhat}{{\hat n}}
\newcommand{\ohat}{{\hat o}}
\newcommand{\phat}{{\hat p}}
\newcommand{\qhat}{{\hat q}}
\newcommand{\rhat}{{\hat r}}
\newcommand{\shat}{{\hat s}}
\newcommand{\that}{{\hat t}}
\newcommand{\uhat}{{\hat u}}
\newcommand{\vhat}{{\hat v}}
\newcommand{\what}{{\hat w}}
\newcommand{\xhat}{{\hat x}}
\newcommand{\yhat}{{\hat y}}
\newcommand{\zhat}{{\hat z}}

\newcommand{\abar}{{\bar {\bf a}}}
\newcommand{\bbar}{{\bar {\bf b}}}
\newcommand{\cbar}{{\bar {\bf c}}}
\newcommand{\dbar}{{\bar {\bf d}}}
\newcommand{\ebar}{{\bar {\bf e}}}
\newcommand{\fbar}{{\bar {\bf f}}}
\newcommand{\gbar}{{\bar {\bf g}}}
%\newcommand{\hbar}{{\bar {\bf h}}}
\newcommand{\ibar}{{\bar {\bf i}}}
\newcommand{\jbar}{{\bar {\bf j}}}
\newcommand{\kbar}{{\bar {\bf k}}}
\newcommand{\lbar}{{\bar {\bf l}}}
\newcommand{\mbar}{{\bar {\bf m}}}
\newcommand{\nbar}{{\bar {\bf n}}}
\newcommand{\obar}{{\bar {\bf o}}}
\newcommand{\pbar}{{\bar {\bf p}}}
\newcommand{\qbar}{{\bar {\bf q}}}
\newcommand{\rbar}{{\bar {\bf r}}}
\newcommand{\sbar}{{\bar {\bf s}}}
\newcommand{\tbar}{{\bar {\bf t}}}
\newcommand{\ubar}{{\bar {\bf u}}}
\newcommand{\vbar}{{\bar {\bf v}}}
\newcommand{\wbar}{{\bar {\bf w}}}
\newcommand{\xbar}{{\bar {\bf x}}}
\newcommand{\ybar}{{\bar {\bf y}}}
\newcommand{\zbar}{{\bar {\bf z}}}

\newcommand{\dx}{{h}}
\newcommand{\nph}{{n + \frac{1}{2}}}
\newcommand{\iph}{{\ibold + \frac{1}{2}\ebold_d}}
\newcommand{\ipmh}{{\ibold \pm \frac{1}{2}\ebold_d}}
\newcommand{\imh}{{\ibold - \frac{1}{2}\ebold_d}}

\newcommand{\half}{\frac{1}{2}}
%\newcommand{\Fbold}{\mathbf{F}}
%\newcommand{\iphed}{{\ibold+\half\ebold^d}}
\newcommand{\deriv}{\partial}
\newcommand{\area}{\mathcal{A}}
\newcommand{\R}[1]{\mathbb{R}^{#1}}
\newcommand{\cf}{{\scriptscriptstyle F}}
\newcommand{\cn}{{\scriptscriptstyle N}}
\newcommand{\sEB}{{\scriptscriptstyle EB}}
\renewcommand{\vec}[1]{\mathbf{#1}} % Vector (bold)
\newcommand{\tens}[1]{\mathbf{#1}} % Tensor (bold)
\newcommand{\mat}[1]{\mathbf{#1}} % Matrix (bold)
\newcommand{\hatvec}[1]{\hat{\vec{#1}}} % Vector with a hat (bold)
\newcommand{\ddt}[1]{\frac{\partial #1}{\partial t}} % partial d/dt
\newcommand{\DDt}[1]{\frac{\text{d}#1}{\text{d}t}} % "total" d/dt
\newcommand{\ddr}[1]{\frac{\partial #1}{\partial r}} % d/dr
\newcommand{\ddx}[1]{\frac{\partial #1}{\partial x}} % d/dx
\newcommand{\ddy}[1]{\frac{\partial #1}{\partial y}} % d/dy
\newcommand{\ddz}[1]{\frac{\partial #1}{\partial y}} % d/dz
\newcommand{\ddxi}[1]{\frac{\partial #1}{\partial x_i}} % d/dx_i
\newcommand{\diverg}[1]{\nabla\cdot#1} % Divergence operator
\newcommand{\curl}[1]{\nabla \times #1} % Curl operator
\newcommand{\dOmega}{\text{d}\Omega} % Volume differential (Omega style)
\newcommand{\dV}{\text{d}V} % Volume differential
\newcommand{\dA}{\text{d}A} % Area differential
\newcommand{\labelEq}[1]{\label{eq:#1}\hbox{\tt #1 \quad}} % Use this to label an equation.
\newcommand{\refEq}[1]{(\ref{eq:#1})}   % Use this to reference an equation.
\newcommand{\labelSec}[1]{\label{sec:#1}} % Use this to label a section.
\newcommand{\refSec}[1]{\S\ref{sec:#1}} % Use this to reference a section.
\newcommand{\labelChap}[1]{\label{chap:#1}} % Use this to label a chapter.
\newcommand{\refChap}[1]{Chapter \ref{chap:#1}} % Use this to reference a chapter.
\newcommand{\labelApp}[1]{\label{app:#1}} % Use this to label an appendix.
\newcommand{\refApp}[1]{Appendix \ref{app:#1}} % Use this to reference an appendix.
\newcommand{\ib}{{\bf{i}}}    % bold italic i
\newcommand{\jb}{{\bf{j}}}    % bold italic j
\newcommand{\kb}{{\bf{k}}}    % bold italic k
\newcommand{\lb}{{\bf{l}}}    % bold italic l
\newcommand{\mb}{{\bf{m}}}    % bold italic m
\newcommand{\ub}{{\bf{u}}}    % bold italic u
\newcommand{\xb}{{\bf{x}}}    % bold italic x
\newcommand{\vb}{{\bf{v}}}    % (bold italic) VoF index
\newcommand{\fb}{{\bf{f}}}    % (bold italic) face index
\newcommand{\pb}{{\bf{p}}}    % (bold italic) multi-index p
\newcommand{\qb}{{\bf{q}}}    % (bold italic) multi-index q
\newcommand{\ebd}{{\bf{e}^d}}
\newcommand{\normal}[1]{\vec{n}_{#1}} % Outward normal.
\newcommand{\order}[1]{\mathcal{O}(#1)} % Order notation

\newcommand{\ed}{{\bf{e}_d}}
\newcommand{\Zbold}{{\bf{0}}}
\newcommand{\unitV}{\mathds{1}}
\newcommand{\eb}{\text{EB}}
\newcommand{\EB}{\text{EB}}
\newcommand{\vol}{\mathcal{V}}
\newcommand{\face}{\mathcal{F}}
\newcommand{\zerobold}{{\bf{0}}}
\newcommand{\xz}{{\bf{x}_0}}

\newcommand{\Dim}{D}
\newcommand{\dif}{\mathrm{d}}
\newcommand{\dt}{{\Delta t}}
\newcommand{\avg}[1]{\overline{#1}}
\newcommand{\avgI}[1]{\overline{#1}_{\ibold}}
\newcommand{\imhed}{{\ibold+\frac{1}{2}\ebold_d}}
\newcommand{\ipmhj}{{\ibold\pm\frac{1}{2}\ebold_d}}
\newcommand{\iphj}{{\ibold+\frac{1}{2}\ebold_d}}
\newcommand{\imhj}{{\ibold-\frac{1}{2}\ebold_d}}

\newcommand{\ipfed}[1]{\ibold+\frac{#1}{2}\ebold_d}
\newcommand{\imfed}[1]{\ibold-\frac{#1}{2}\ebold_d}
\newcommand{\ipmfed}[1]{\ibold\pm\frac{#1}{2}\ebold_d}
\newcommand{\eq}[1]{(\ref{#1})}

\newcommand{\nref}{n_{\text{ref}}}
\newcommand{\phio}{\phi^{\circ}}

\begin{document}

\title{Polynomial expansions of finite volume data in a cut cell context}
\author{P. Schwartz     \footnotemark[1]
   \and N. Overton-Katz \footnotemark[1]
   \and T. Ligocki      \footnotemark[1]
   \and H. Johansen     \footnotemark[1]
   \and D. T. Graves    \footnotemark[1]
   \and D. Devendran    \footnotemark[1]
   \and O. Anteparra    \footnotemark[1]}

\maketitle
\footnotetext[1]{Lawrence Berkeley National Laboratory, Berkeley,
  CA. Research at LBNL was supported financially by the Office of
  Advanced Scientific Computing Research of the US Department of
  Energy under contract number DE-AC02-05CH11231.}

\section
\begin{abstract}

  We discuss the mechanics of forming stable local polynomial
  expansions of finite volume data in the context of cut cell grids.
  We show that significant solvability issues can arise from certain weighting
  functions.    A very rudimentary but stable cell merger algorithm is
  presented in an attempt to show that these solvability issues are
  really an artifact of small-cell instabilties.

\end{abstract}

  function 
We present an algorithm to produce the necessary geometric information
for finite volume calculations in the context of Cartesian grids with
embedded boundaries.      Given an order of accuracy for the
overall calculation, we show what accuracy is required for each of the
geometric quantites and we demonstrate how to calculate the moments
using the divergence theorem.   We demonstrate that, for  a known
flux, these moments can be used to create a flux divergence of the
expected order.

\end{abstract}
\section{Introduction}

Throughout this paper, we use the following compact ``multi-index'' notation:
\begin{align*}
(\xbold - \xbar)^\pbold &= \prod\limits^D_{d=1} (x_d - {\bar x}_d)^{p_d} \\
\pbold! &= \prod\limits^D_{d = 1} p_d!
\end{align*}
Given a point in space $\xbar$, and a $D$-dimensional integer vector
$\pbold$, we define $m_v^\pbold(\xbar)$ to be the $\pbold^{th}$
moment of the volume $V$ relative to the point $\xbar$.
\begin{equation}
m_v^\pbold(\xbar)  =  \int\limits_{V} (\xbold - \xbar)^\pbold dV
\label{eqn::volmoment}
\end{equation}
Clearly, the volume of the cut cell $|V| = m_v^\zbold$,
  where $\zbold$ is the zero vector.
We define the face moments $m_{d\pm}^\pbold(\xbar)$ to be the $\pbold^{th}$  
moments (relative to the point $\xbar$) of the faces $A_{d\pm}$.
\begin{equation}
m_{d\pm}^\pbold(\xbar)  = \int\limits_{A_{d\pm}} (\xbold - \xbar)^\pbold dA
\label{eqn::facemoment}
\end{equation}
We define two moments corresponding to the embedded boundary face $A_B$: $m^{\pbold}_{B}$ and $m^{\pbold}_{B,d}$: 
\begin{equation}
m^{\pbold}_{B}(\xbar)  = \int\limits_{A_B} (\xbold
-\xbar)^\pbold \,  dA
\label{eqn::ebmomentB}
\end{equation}
and
\begin{equation}
m^{\pbold}_{B,d}(\xbar)  = \int\limits_{A_B} (\xbold
-\xbar)^\pbold \, n_d(\xbold) \, dA.
\label{eqn::ebmoment}
\end{equation}
Note that (\ref{eqn::ebmoment}) includes the normal to the embedded boundary face.

Given a sufficiently smooth function $\psi$, we can approximate $\psi$
in the neighborhood of $\xbar$ using a multi-dimensional Taylor expansion:
\begin{equation}
\psi(\xbold) = \sum_{|\qbold| < Q} \frac{1}{\qbold!}\psi^{(\qbold)}(\xbar)
\, (\xbold - \xbar)^\qbold + O(\dx^{Q}),
\label{eqn::taylor}
\end{equation}
with the multi-index partial derivative notation
\begin{equation}
\psi^{(\qbold)} = 
  \partial^{\qbold} \psi =
  \frac{\partial^{q_1}}{\partial x_1^{q_1}} \dots
  \frac{\partial^{q_D}}{\partial x_D^{q_D}} \psi \, .
\end{equation}
We express averages over volumes as 
\begin{equation*}
  \left< \nabla \cdot \Fbold \right>_V \equiv \frac{1}{|V|} 
  \int\limits_{V} \left( \nabla \cdot \Fbold \right) \, dV
\end{equation*}
We define the volume fraction $\kappa$ to be fraction of the volume
of the cell inside the solution domain, so that 
\begin{equation}
\kappa = h^{-D} |V| = h^{-D} m_v^\zbold \quad .
\label{eqn::kappa}
\end{equation}

### 2023-04-07 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
progress on ebcm paper

@@
 \title{Polynomial expansions of finite volume data in a cut cell context}
-\author{P. Schwartz     \footnotemark[1]
-   \and N. Overton-Katz \footnotemark[1]
-   \and T. Ligocki      \footnotemark[1]
+\author{N. Overton-Katz \footnotemark[1]
    \and H. Johansen     \footnotemark[1]
@@
   Energy under contract number DE-AC02-05CH11231.}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}\
 
-\section
 \begin{abstract}
@@
   functions.    A very rudimentary but stable cell merger algorithm is
-  presented in an attempt to show that these solvability issues are
-  really an artifact of small-cell instabilties.
+  presented as we present evidence that these solvability issues may be
+  an artifact of small-cell instabilties.
 
@@
 
-  function 
-We present an algorithm to produce the necessary geometric information
-for finite volume calculations in the context of Cartesian grids with
-embedded boundaries.      Given an order of accuracy for the
-overall calculation, we show what accuracy is required for each of the
-geometric quantites and we demonstrate how to calculate the moments
-using the divergence theorem.   We demonstrate that, for  a known
-flux, these moments can be used to create a flux divergence of the
-expected order.
-
-\end{abstract}
 \section{Introduction}
 
-Throughout this paper, we use the following compact ``multi-index'' notation:
+Embedded boundary (EB) grids are formed when one passes an  surface
+through a Cartesian mesh.    For sufficiently complex geomtries, these methods
+are very attactive because grid generation is a solved problem
+and not computationally overwhelming \cite{trebotich-graves}.
+
+In the current context, we form the cutting surface as the zero
+surface of a function  of space $I(\xbold)$, $\xbold \in R^D$.
+For smooth ($I$),  moments can be generated to any
+accuracy \cite{geometry_paper}.
+
+EB grids can produce cells that arbitrarily small.    This produces
+algorithmic difficulties that generations of researchers have labored
+to overcome with great success.   EB methods are used for high speed
+compressible flows \cite{compresible_ns_paper, ebamrhscl} and for
+slower, incompressible applications \cite{miller-trebotich}.
+
+Formally, the underlying description of space
+is given by rectangular control volumes on a Cartesian mesh
+$\Upsilon_\ibold = [(\ibold-\half {\ubold})h, (\ibold+\half
+{\ubold})h], \ibold \in \bigzbold^D$, where $D$ is the dimensionality
+of the problem, $h$ is the mesh spacing, and ${\ubold}$ is the vector
+whose entries are all one (note we use bold font $\ubold = (u_1, \dots, u_d,
+\dots, u_D)$ to indicate a vector quantity).
+Given an irregular domain $\Omega$, we
+obtain control volumes $V_\ibold = \Upsilon_\ibold \bigcap \Omega$ and
+faces $A_{\ibold,d\pm} = A_{\ibold \pm \half \ebold_d}$ which are the
+intersection of the boundary of $\partial V_\ibold$ with the
+coordinate planes $\{{\xbold}:x_d = (i_d \pm \half)h \}$ ($\ebold_d$ is
+the unit vector in the $d$ direction).  We also
+define $A_{B,\ibold}$ to be the intersection of the boundary of the
+irregular domain with the Cartesian control volume: $A_{B,\ibold}
+= \partial \Omega \bigcap \Upsilon_\ibold$.
+
+\section {Finite volume notation}
+
+Throughout this paper, we use the following compact notation:
 \begin{align*}
@@
 \end{equation}
-Clearly, the volume of the cut cell $|V| = m_v^\zbold$,
-  where $\zbold$ is the zero vector.
-We define the face moments $m_{d\pm}^\pbold(\xbar)$ to be the $\pbold^{th}$  
-moments (relative to the point $\xbar$) of the faces $A_{d\pm}$.
-\begin{equation}
-m_{d\pm}^\pbold(\xbar)  = \int\limits_{A_{d\pm}} (\xbold - \xbar)^\pbold dA
-\label{eqn::facemoment}
-\end{equation}
-We define two moments corresponding to the embedded boundary face $A_B$: $m^{\pbold}_{B}$ and $m^{\pbold}_{B,d}$: 
-\begin{equation}
-m^{\pbold}_{B}(\xbar)  = \int\limits_{A_B} (\xbold
--\xbar)^\pbold \,  dA
-\label{eqn::ebmomentB}
-\end{equation}
-and
-\begin{equation}
-m^{\pbold}_{B,d}(\xbar)  = \int\limits_{A_B} (\xbold
--\xbar)^\pbold \, n_d(\xbold) \, dA.
-\label{eqn::ebmoment}
-\end{equation}
-Note that (\ref{eqn::ebmoment}) includes the normal to the embedded boundary face.
 
 Given a sufficiently smooth function $\psi$, we can approximate $\psi$
-in the neighborhood of $\xbar$ using a multi-dimensional Taylor expansion:
+in the neighborhood of $\xbar$ using a Taylor expansion to order $P$:
 \begin{equation}
-\psi(\xbold) = \sum_{|\qbold| < Q} \frac{1}{\qbold!}\psi^{(\qbold)}(\xbar)
-\, (\xbold - \xbar)^\qbold + O(\dx^{Q}),
-\label{eqn::taylor}
+\psi(\xbold)  =  \sum\limits_{p < P} C^p (\xbar - \xbar)^p \label{eqn::taylor}
 \end{equation}
-with the multi-index partial derivative notation
+where $C^p$ this appropriate Taylor coefficient.  In three dimensions,
 \begin{equation}
-\psi^{(\qbold)} = 
-  \partial^{\qbold} \psi =
-  \frac{\partial^{q_1}}{\partial x_1^{q_1}} \dots
-  \frac{\partial^{q_D}}{\partial x_D^{q_D}} \psi \, .
+  C^p =\frac(1){p!}
+      \frac{\partial^{p_0}}{\partial x_0}
+      \frac{\partial^{p_1}}{\partial x_1}
+      \frac{\partial^{p_2}}{\partial x_2}  (\psi).
 \end{equation}
-We express averages over volumes as 
+
+In finite volume  methods, we define grid data to be
+averages over volumes.   So if we discretize the smooth function
+$\psi$, the average over the volume $\ibold$ is given by
 \begin{equation*}
-  \left< \nabla \cdot \Fbold \right>_V \equiv \frac{1}{|V|} 
-  \int\limits_{V} \left( \nabla \cdot \Fbold \right) \, dV
+ V_\ibold <\psi>_\ibold = \int\limits_{V_\ibold} \psi(\xbold) dV
 \end{equation*}
-We define the volume fraction $\kappa$ to be fraction of the volume
-of the cell inside the solution domain, so that 
-\begin{equation}
-\kappa = h^{-D} |V| = h^{-D} m_v^\zbold \quad .
-\label{eqn::kappa}
-\end{equation}
+If we insert the Taylor expansion \ref{eqn::taylor}, we get a discrete
+approximation to the smooth function $\psi$ that is accurate to order $P$.
+\begin{equation*}
+ V_\ibold <\psi>_\ibold = \sum\limits_{p < P} C^p m^p. 
+\end{equation*}
+This forms a local polynomial expansion of $\psi$ around the volume
+$\ibold$ expressed in terms  moments ($m$)  which are the natural
+products of grid generation.
+Modern, higher order embedded boundary methods use this description
+directly to generate stencils
+ \cite{nate-stokes-paper,  dharshi-poisson, geometry-paper}.    At the core
+of these algorithms is a similar procedure for finding the Taylor
+coefficients $C$ which is
+worth discussing.
+
+\section
+\end{document}

### 2023-04-07 example/DomainDecomposition/EBPETSc/src/EBPetscSolver.H
PETSc update from merge

@@ -1,542 +1,0 @@
-#ifdef CH_LANG_CC
-/*
- *      _______              __
- *     / ___/ /  ___  __ _  / /  ___
- *    / /__/ _ \/ _ \/  V \/ _ \/ _ \
- *    \___/_//_/\___/_/_/_/_.__/\___/
- *    Please refer to Copyright.txt, in Chombo's root directory.
- */
-#endif
-
-#ifndef _EBPoissonPetscSolver_H_
-#define _EBPoissonPetscSolver_H_
-
-#ifdef CH_USE_PETSC
-#include "petsc.h"
-#include "petscmat.h"
-#include "petscksp.h"
-#include "petscviewer.h"
-
-#include "Chombo_EBLevelBoxData.H"
-
-
-/// Framework to solve an elliptic equation using PETsC (PETsC?  petsC?)
-/**
-   This is an an adaptation to the new reality of Mark Adams' PetscSolver framework.
-   If it were any cooler, he would have to add another d to his name.  
-   dtg 
-   9-18-2020
-*/
-template <int order>
-class EBPetscSolver
-{
-public:
-  typedef GraphConstructorFactory< EBBoxData<CELL, int, 1> >  devifactint_t;
-  typedef GraphConstructorFactory<EBHostData<CELL, int, 1> >  hostfactint_t;
-  typedef GraphConstructorFactory<EBHostData<CELL,Real, 1> > hostfactreal_t;
-  typedef EBDictionary<order, Real, CELL, CELL>                dictionary_t;
-
-  EBPetscSolver(const shared_ptr<GeometryService<order> >  & a_geoserv,
-                const shared_ptr<dictionary_t           >  & a_ebdictionary,
-                const shared_ptr<LevelData<EBGraph> >      & a_graphs,
-                const DisjointBoxLayout                    & a_grids,
-                const Box                                  & a_domain,
-                string a_stencilName,
-                string a_domainBCName[2*DIM],
-                string a_ebbcName,
-                Real a_dx,   Point a_ghost)
-  {
-    m_geoserv      =    a_geoserv;
-    m_ebdictionary =    a_ebdictionary;
-    m_graphs       =    a_graphs;
-    m_grids        =    a_grids;
-    m_domain       =    a_domain;
-    m_stencilName  =    a_stencilName;
-    m_dx           =    a_dx;
-    m_prestring[0] = '\0';
[…]

### 2023-04-07 example/HO-WLS/common/EBPetscSolver.H

@@ -21,7 +21,55 @@
 #include "Chombo_EBChombo.H"
 #include "Chombo_EBLevelBoxData.H"
 #include "hoeb/Proto_EBDomainBC.H"
-#include "EBMultigridFunctions.H"
+
+/****/
+//lph comes in holding beta*div(F)--leaves holding alpha phi + beta div(F)
+PROTO_KERNEL_START
+unsigned int  addAlphaPhiPtF(int a_pt[DIM],
+                             Var<Real, 1>     a_lph,
+                             Var<Real, 1>     a_phi,
+                             Var<Real, 1>     a_kap,
+                             Real    a_alpha,
+                             Real    a_beta)
+{
+  //kappa and beta are already in lph
+  //kappa because we did not divide by kappa
+  //beta was sent in to ebstencil::apply
+  //begin debug
+  int ideb = 6;
+  int jdeb = 16;
+  int istop = 0;
+  if ((a_pt[0] == ideb) && (a_pt[1]==jdeb))
+  {
+    istop = 1;
+  }
+
+  Real kappdiv = a_lph(0);
+  Real bkdivF  = a_beta*kappdiv;
+  Real phival  = a_phi(0);
+  Real kapval  = a_kap(0);
+  a_lph(0) = a_alpha*phival*kapval + bkdivF;
+  return 0;
+}
+PROTO_KERNEL_END(addAlphaPhiPtF, addAlphaPhiPt)
+PROTO_KERNEL_START
+unsigned int  addAlphaPhiF(Var<Real, 1>     a_lph,
+                           Var<Real, 1>     a_phi,
+                           Var<Real, 1>     a_kap,
+                           Real    a_alpha,
+                           Real    a_beta)
+{
+  //kappa and beta are already in lph
+  //kappa because we did not divide by kappa
+  //beta was sent in to ebstencil::apply
+  Real kappdiv = a_lph(0);
+  Real bkdivF  = a_beta*kappdiv;
+  Real phival  = a_phi(0);
+  Real kapval  = a_kap(0);
+  a_lph(0) = a_alpha*phival*kapval + bkdivF;
+  return 0;
+}
+PROTO_KERNEL_END(addAlphaPhiF, addAlphaPhi)
 
 /// Framework to solve an elliptic equation using PETSc
 /// Probably a good candidate to move into Chombo4/src
@@ -30,8 +78,8 @@ class EBPetscSolver
 {
 public:
   typedef GraphConstructorFactory< EBBoxData<CELL, int, 1> >  devifactint_t;
[…]

### 2023-04-07 src/EBProto/hoeb/Proto_WLSCellImplem.H

@@ -2027,7 +2027,7 @@ namespace Proto
       string ebbcName = a_domainBC.getBCtypes().getEBComp();
       if(ebbcName == string("Neumann"))
       {
-        auto ebfneighNorm = a_neigh.getEBFaceNorm(iface);
+        auto ebfneighNorm = a_neigh.getEBFaceNormal(iface);
         bcValue = NeumannExactSoln<order>::
                                getEBIntegral(ebfneighNorm,
                                              ebfLocDiff,

### 2023-04-07 src/EBProto/implem/Proto_Normalizor.H

@@ -422,9 +422,12 @@ namespace Proto
         RealVect faceLoc;
         RealVect shift = RealVect::Unit();
         if (cent==XFACE) {shift[0] = 0;}
+#if DIM>=2
         else if (cent==YFACE) {shift[1] = 0;}
+#endif
+#if DIM>=3
         else if (cent==ZFACE) {shift[2] = 0;}
-
+#endif
         for (int idir = 0; idir != DIM; idir++)
           {
             faceLoc[idir] = a_dx * (0.5*shift[idir] + a_face.m_pt[idir]);

### 2023-04-07 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
paper preliminaries pushed

@@
 
-\section
+\section{Computing Taylor coefficients}
+
+Consider a finite volume grid where we know all geometric moments to
+order $P$.   Given values of $<\psi>$ everwhere on the grid, we wish to
+approximate the Taylor coefficients at a volume $\ibold$ given that we
+know $\cn_\ibold = \{\jbold\}$, the set of $N_v$ closest neighbors of
+the volume $\ibold$.   Using the Taylor expansion at each point gives
+us $N_v$ equations for $C^p$
+\begin{equation}
+  V_\jbold <\psi>_\jbold = \sum\limits_{p < P} C^p_\ibold m^p_\jbold.
+\end{equation}
+Let's say there are $N_p$ Taylor coefficients.   We can force
+$N_v > N_p$ by getting a large enough neighborhood.    This means that
+we have an overdetermined system of the form
+\begin{equation*}
+M C = P 
+\end{equation*}
+where $M = \{\{m^{pi}_\jbold\}\}$ and $P= \{<\psi_\jbold>\}$.
+Since the system is overdetermined, we can introduce a 
+meaningful weighting matrix $W$ and solve
+\begin{equation*}
+WMC = WP.
+\end{equation*}
+Diagonal weighing matricies are common.  Typically, the equations for volumes near the
+target volume receive higher weights.   Since these matricies are
+(deliberately) not square, we approximate the solution using a
+Moore-Penrose pseudo-inverse:
+\begin{equation*}
+C = ((WM)^T(WM))^{-1} (WM)^T P.
+\end{equation*}
+The matrix inversion at the heart of this  method requires that we
+need know to what degree the matrix $A = (WM)^T(WM)$  is invertable.
+
 \end{document}

### 2023-04-08 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
broad strokes of paper strategy outlined

@@
    \and D. T. Graves    \footnotemark[1]
-   \and D. Devendran    \footnotemark[1]
+   \and D. Devendran    \footnotemark[2]
    \and O. Anteparra    \footnotemark[1]}
@@
 \maketitle
-\footnotetext[1]{Lawrence Berkeley National Laboratory, Berkeley,
-  CA. Research at LBNL was supported financially by the Office of
-  Advanced Scientific Computing Research of the US Department of
-  Energy under contract number DE-AC02-05CH11231.}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}\
 
@@
 
-EB grids can produce cells that arbitrarily small.    This produces
+EB grids can contain volumes that are arbitrarily small.    This
+"small-cell problem'' produces
 algorithmic difficulties that generations of researchers have labored
@@
 \begin{equation}
-  C^p =\frac(1){p!}
+  C^p =\frac{1}{p!}
       \frac{\partial^{p_0}}{\partial x_0}
@@
 $\ibold$ expressed in terms moments ($m$) which are the natural
-products of grid generation.
-Modern, higher order embedded boundary methods use this description
-directly to generate stencils
- \cite{nate-stokes-paper,  dharshi-poisson, geometry-paper}.    At the core
-of these algorithms is a similar procedure for finding the Taylor
-coefficients $C$ which is
-worth discussing.
+products of grid generation.  Modern, higher order embedded boundary
+methods use this description directly to generate stencils
+\cite{nate-stokes-paper, dharshi-poisson, geometry-paper}.  At the
+core, all these algorithms have a similar procedure for finding the
+Taylor coefficients $C$ which is worth discussing.
 
-\section{Computing Taylor coefficients}
+\section{Computing Taylor coefficients and Matrix Conditioning}
 
@@
 \end{equation}
-Let's say there are $N_p$ Taylor coefficients.   We can force
-$N_v > N_p$ by getting a large enough neighborhood.    This means that
-we have an overdetermined system of the form
+Let's say there are $N_p$ Taylor coefficients.  We can force $N_v >
+N_p$ by getting a large enough neighborhood.  This means that we have
+an overdetermined system of the form
 \begin{equation*}
@@
 \end{equation*}
-where $M = \{\{m^{pi}_\jbold\}\}$ and $P= \{<\psi_\jbold>\}$.
+where $M = \{\{m^{pi}_\jbold\}\}$, $C=\{C^p\}$,  and $P= \{<\psi_\jbold>\}$.
 Since the system is overdetermined, we can introduce a 
-meaningful weighting matrix $W$ and solve
+meaningful weighting matrix $W$ \footnotemark[3].  Choice of $W$
+is crucial to the stability of these algorithms
+\footnotemark[4].
+We multiply and solve
 \begin{equation*}
@@
 \end{equation*}
-Diagonal weighing matricies are common.  Typically, the equations for volumes near the
-target volume receive higher weights.   Since these matricies are
-(deliberately) not square, we approximate the solution using a
-Moore-Penrose pseudo-inverse:
+Since these matricies are (deliberately) not square, we approximate
+the solution using a Moore-Penrose pseudo-inverse:
 \begin{equation*}
@@
 \end{equation*}
-The matrix inversion at the heart of this  method requires that we
-need know to what degree the matrix $A = (WM)^T(WM)$  is invertable.
+The matrix inversion at the heart of this method requires that we need
+know to what degree the matrix $A \equiv (WM)^T(WM)$ is
+well-conditioned.  Experience suggests that small cells play a role in
+that conditioning and that the weighting matrix $W$ can be used to
+mitigate conditioning issues that unweighted least squares may
+produce.
+
+To explore the roles of small cells and weighting functions, we first
+introduce a merged cut cell space where there are no small cells.
+This merged space still has geometric moments accurate to the same order 
+as the original cut cell space.
+
+We study how weighting matricies change the conditioning of $A$.  This is
+done both with and without cell merger in the hope hope that this
+exploration may lead to simpler, more robust cut cell algorithms to
+solve partial differential equations at high order.
+
+\section{Cell Merger}
+
+Dammit I have to insert pictures here.
+
+\footnotetext[1]{Lawrence Berkeley National Laboratory, Berkeley,
+  CA. Research at LBNL was supported financially by the Office of
+  Advanced Scientific Computing Research of the US Department of
+  Energy under contract number DE-AC02-05CH11231.}
+\footnotetext[2]{Ford Motor Company, Sunnyvale California.}
+\footnotetext[3]{If the matrix $M$ is square, a weighting matrix can
+  have no effect and the Moore-Penrose psueudoinverse becomes
+  $M^{-1}$.}
+\footnotetext[4]{Defining $\xbar_\ibold = 0$, the
+  equations for volumes $\jbold$ where $\xbar_\jbold$ target receive
+  higher weights.  Diagonal weighting matricies are common.  Usually,
+  these algorithms define a distance metric $D(\ibold, \jbold)$ for
+  two volumes $\ibold$ and $\jbold$.  Typically they make
+  $W_{\jbold,\jbold}$ decrease strongly with increasing $D(\ibold,
+  \jbold)$ to assign higher importance to the equations for volumes
+  closer to $\ibold$.  Devendran, for example \cite{poisson-paper},
+  uses a weighting function that varies with $W_{\ibold,\jbold}
+  \approx 1./D(\ibold,\jbold)^5$ }.
+
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}\
 

### 2023-04-08 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
progress

@@
 are very attactive because grid generation is a solved problem
-and not computationally overwhelming \cite{trebotich-graves}.
+and not computationally overwhelming even in a moving-boundary context
+\cite{MillerTrebotich2012}.
 
@@
 For smooth ($I$),  moments can be generated to any
-accuracy \cite{geometry_paper}.
+accuracy \cite{Schwartz2015}.
 
@@
 to overcome with great success.   EB methods are used for high speed
-compressible flows \cite{compresible_ns_paper, ebamrhscl} and for
-slower, incompressible applications \cite{miller-trebotich}.
+compressible flows \cite{Colella2006, Graves2013} and for
+slower, incompressible applications \cite{Trebotich2015} and conjugate
+heat transfer \cite{Crockett2010}.
 
@@
 methods use this description directly to generate stencils
-\cite{nate-stokes-paper, dharshi-poisson, geometry-paper}.  At the
+\cite{Overton2022a, Devendran2017, Schwartz2015}.  At the
 core, all these algorithms have a similar procedure for finding the
-Taylor coefficients $C$ which is worth discussing.
+Taylor coefficients $C^p$ which is worth discussing.
 
@@
 
-\section{Cell Merger}
+\section{Cell Merger Algorithm}
 
-Dammit I have to insert pictures here.
+We use a very simple cell merger algorithm.  Given a cut cell
+$\ibold$, we define the box containing only that cell
+$B_c = B(\ibold, \ibold)$ 
+We form a $2^D$ cell rectangular region
+by coarsening and then refining $B_c$ to form $B_v = R(C(B_c))$
+\footnotemark[6].
+After that process, any left over small cells are merged with their
+biggest neighbor.    See figures \ref{fig::unmerged2dmap} and
+\ref{fig::merged2dmap} for a simple example of how this algorithm
+creates fairly chunky grids   \footnotemark[5].
+
+We define the volume fraction $\kappa_\ibold \equiv  V_\ibold/h^D$.
+For unmerged grids, $ 0 < \kappa <= 1$.   When merged using this
+algorithm, $\kappa$ can be larger than $2^D$.
+
+\begin{figure}
+\centerline{\epsfig{figure=unmerged.ps,width=0.4\linewidth }} 
+\caption{Map for EB grid produced by a cutting cirle. $\kappa <= 1$.
+  Each cut cell has a unique positive integer.}
+\end{figure}
+
+\begin{figure}
+\centerline{\epsfig{figure=merged.ps,width=0.4\linewidth } }
+\label{fig::merged2dmap}
+\caption{Map of EB grid shown in \ref{fig::unmerged2dmap} after using
+  cell merger algorithm.
+  Each cut cell has a unique positive integer. $\kappa <= 4.1433$}
+\end{figure}
 
@@
   Energy under contract number DE-AC02-05CH11231.}
-\footnotetext[2]{Ford Motor Company, Sunnyvale California.}
+\footnotetext[2]{Ford Motor Company, Sunnyvale, CA.}
 \footnotetext[3]{If the matrix $M$ is square, a weighting matrix can
@@
   $M^{-1}$.}
+
 \footnotetext[4]{Defining $\xbar_\ibold = 0$, the
@@
   \jbold)$ to assign higher importance to the equations for volumes
-  closer to $\ibold$.  Devendran, for example \cite{poisson-paper},
+  closer to $\ibold$.  Devendran for example \cite{Devendran2017},
   uses a weighting function that varies with $W_{\ibold,\jbold}
@@
 
+\footnotetext[5] {Merging two cells is simply a matter of removing the
+  intervening faces, shifting all moments them to a common location
+  and adding them together.  No accuracy is lost in this process
+  outside of the fact that we have fewer degress of freedom because
+  semantically, we are just adding volume integrals over distinct
+  volumes, which is exact.}
+
+\footnotetext[6] {We mean a Box as defined in Chombo, a subset of
+  $Z^D$.  Coarsening and refining has the standard Chombo semantic
+  \cite{ChomboDesign, ChomboDesignEB}.}
+
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\
+\bibliography{references}
 

### 2023-04-13 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
added disclaimer about using only volume equations

@@
 \end{equation}  
-
 In finite volume  methods, we define grid data to be
@@
 core, all these algorithms have a similar procedure for finding the
-Taylor coefficients $C^p$ which is worth discussing.
+Taylor coefficients $C^p$ which is worth discussing \footnotemark[7].
 
@@
 
+\footnotetext[6] {The discerning reader will notice that this
+  discussion assumes that the equation set used to create $C$ only
+  includes the volume equations.   Devendran \cite{Devendran2017} also
+  include boundary condition equations in the equation set.  For
+  simple enough boundary conditions, this works very well.   There are
+  many equation sets, however, which do not lend themselves easily to
+  this approach.   Notably, hyperbolic equations often have boundary 
+  conditions which are fomulated in terms of characteristic
+  variables.    Using this information in the system of equations used
+  to calculate Taylor coefficients is still a matter of research.}
+
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-04-13 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
the footnote puts its foot in the door

@@
 core, all these algorithms have a similar procedure for finding the
-Taylor coefficients $C^p$ which is worth discussing \footnotemark[7].
+Taylor coefficients $C^p$ which is worth discussing
+
+The discerning reader will notice that
+the equation set used to create $C$ only includes the volume
+equations.  Devendran \cite{Devendran2017} also include boundary
+condition equations in the equation set.  For simple enough boundary
+conditions, this works very well.  There are many equation sets,
+however, which do not lend themselves easily to this approach.
+Notably, hyperbolic equations often have boundary conditions which are
+fomulated in terms of characteristic variables.  Using this
+information in the system of equations for Taylor coefficients is
+still a matter of research.  We therefore believe that restricting
+ourselves to the volume equations can provide insight valuable to
+developers of this class of algorithms.
 
@@
 
-\footnotetext[6] {The discerning reader will notice that this
-  discussion assumes that the equation set used to create $C$ only
-  includes the volume equations.   Devendran \cite{Devendran2017} also
-  include boundary condition equations in the equation set.  For
-  simple enough boundary conditions, this works very well.   There are
-  many equation sets, however, which do not lend themselves easily to
-  this approach.   Notably, hyperbolic equations often have boundary 
-  conditions which are fomulated in terms of characteristic
-  variables.    Using this information in the system of equations used
-  to calculate Taylor coefficients is still a matter of research.}
+\footnotetext[7] {.}
 

### 2023-04-13 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp
initial ebcm framework compiles

@@ -20,281 +20,443 @@
 
 #include "DebugFunctions.H"
 #include "Hoeb_ExactSolutions.H"
-//this one defines HOEB_MAX_ORDER
-#include "Hoeb_Utilities.H"
+
 #include "Chombo_LAPACKMatrix.H"
 #include <iomanip>
 
-typedef Chombo4::GeometryService<      HOEB_MAX_ORDER >   ch_geoserv;
-typedef    EBCM::MetaDataLevel<        HOEB_MAX_ORDER >   ebcm_meta;
-typedef    EBCM::SubVolumeVector  <    HOEB_MAX_ORDER >   ebcm_subvol_vec;
-typedef    EBCM::EBCM_Volu<            HOEB_MAX_ORDER >   ebcm_volume;
-typedef    EBCM::EBCM_Graph<           HOEB_MAX_ORDER >   ebcm_graph;
-typedef    EBCM::HostLevelData<Real,1, HOEB_MAX_ORDER>    ebcm_leveldata;
 
-
-typedef Chombo4::Box               ch_box;
-typedef Chombo4::DisjointBoxLayout ch_dbl;
-typedef Chombo4::ProblemDomain     ch_probdom;
-typedef Chombo4::DataIterator      ch_dit;
-typedef Chombo4::IntVect           ch_iv;
-typedef Chombo4::MayDay            ch_mayday;
-typedef Chombo4::LAPACKMatrix      ch_mat;
-/****/
-void
-makeMergedGeometry(   shared_ptr< ebcm_meta  >  & a_ebcm,
-                      ch_dbl                    & a_grids,
-                      double                    & a_dx,
-                      ch_probdom                & a_domain)
-{
-  using Chombo4::pout;
-
-  int nx               = 32;
-  int maxGrid          = 32;
-  bool mergeSmallCells = true;
-    
-  ParmParse pp;
-
-  pp.get("nx"             , nx);
-  pp.get("maxGrid"        , maxGrid);
-  pp.get("mergeSmallCells", mergeSmallCells);
-
-
-  pout() << "nx"        << " = " <<  nx         << endl;
-  pout() << "max_grid"  << " = " <<  maxGrid    << endl;
-  if(mergeSmallCells)
-  {
-    pout() << "Cell merging is turned ON."  << endl;
-  }
-  else
-  {
-    pout() << "Cell merging is turned OFF."  << endl;
-  }
-  
-
[…]

### 2023-04-13 example/DomainDecomposition/hoeb_common/Hoeb_Utilities.cpp

@@ -206,59 +206,6 @@ namespace hoeb
     }
   }
 
-  shared_ptr<BaseIF> getImplicitFunction()
-  {
-    using Proto::BaseIF;
-    shared_ptr<BaseIF>  retval;
-    ParmParse pp;
-    string which_geom;
-    pp.get("which_geom", which_geom);
-    using Chombo4::pout;
-    if(which_geom == string("sphere"))
-    {
-      RealVect center = 0.5*RealVect::Unit();
-      Real radius = 0.1;
-      bool inside = false;
-      std::vector<Real> centvec;
-      pp.get("radius", radius);
-      pp.get("inside", inside);
-      pp.getarr("center", centvec, 0, DIM);
-      for(int idir = 0; idir < DIM; idir++)
-      {
-        center[idir] = centvec[idir];
-      }
-      Proto::SimpleSphereIF* sphereptr = new Proto::SimpleSphereIF(center, radius, inside);
-      pout() << "sphere implicit function with radius = " << radius << ", center = " << center << ", and inside = " << inside << endl;
-      retval = shared_ptr<BaseIF>(static_cast<BaseIF*>(sphereptr));
-    }
-    else if(which_geom == string("all_regular"))
-    {
-      pout() << "all regular geometry" << endl;
-      retval = shared_ptr<BaseIF>(new Proto::AllRegularIF());
-    }
-    else if(which_geom == string("plane"))
-    {
-      using Proto::PlaneIF;
-      pout() << "plane implicit function" << endl;
-      RealVect normal, startPt;
-      vector<double> v_norm, v_start;
-      pp.getarr("geom_normal", v_norm, 0, DIM);
-      pp.getarr("geom_start_pt", v_start, 0, DIM);
-      for(int idir = 0; idir < DIM; idir++)
-      {
-        normal[ idir] = v_norm[ idir];
-        startPt[idir] = v_start[idir];
-        pout() << "normal ["<< idir << "] = " << normal [idir]  << endl;
-        pout() << "startPt["<< idir << "] = " << startPt[idir]  << endl;
-      }
-      retval = shared_ptr<BaseIF>(new PlaneIF(startPt, normal));
-    }
-    else
-    {
-      Chombo4::MayDay::Error("bogus geometry");
-    }
-    return retval;
-  }
 
   /****/
   shared_ptr<hoeb::BaseExactSolution<HOEB_MAX_ORDER> > 

### 2023-04-17 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp
starting to get numbers that may not be complete trash

@@ -194,7 +194,11 @@ public:
     int                              m_nghost;
     pr_rv                            m_startloc;
     shared_ptr<ebcm_subvol_vec>      m_volumes;
+    //this is the actual distance stuff gets shifted
+    vector<pr_rv>                    m_xbar;
+    ///this is the distance used in  calculating weights
     vector<Real>                     m_distance;
+    ///this is the weight of each equation (the diagonal of the weight matrix)
     vector<Real>                     m_eqweight;
   
     neighborhood_t(const ebcm_graph    & a_graph,
@@ -223,33 +227,33 @@ public:
                << a_start << endl;
         ch_mayday::Error();
       }
+      m_xbar.resize(    m_volumes->size());
       m_distance.resize(m_volumes->size());
       m_eqweight.resize(m_volumes->size());
     
       for(int ivec = 0; ivec < m_volumes->size(); ivec++)
       {
         const auto& curVol = (*m_volumes)[ivec];
-        Real xbar = getXBar(curVol);
-      
-        m_distance[ivec] = xbar;
-        m_eqweight[ivec] = 1;
-        for(int iweight = 0; iweight < a_weightPower; iweight++)
+        m_xbar[ivec] = curVol.m_centroid - m_startloc;
+        m_distance[ivec] = getManhattanDistance(curVol);
+        double eqnweight = 1;
+        if(m_distance[ivec] > 1)
         {
-          m_eqweight[ivec] /= xbar;
+          for(int iweight = 0; iweight < a_weightPower; iweight++)
+          {
+            eqnweight /= m_distance[ivec];
+          }
         }
+        m_eqweight[ivec] = eqnweight;
+        //debug
+        //m_eqweight[ivec] = 1;
+        //end debug
       }
     }
 
 
-    double getXBar(const ebcm_volu & a_volu)  const
+    double getManhattanDistance(const ebcm_volu & a_volu)  const
     {
-      //cartesian with weird flooring and all that
-      //pr_rv  vectDist = a_volu.m_centroid - this->m_startloc;
-      //double xbar = vectDist.vectorLength();
-      //xbar /= a_volu.m_dx;
-      //xbar  = std::max(xbar, 1.);
-      //return xbar;
-      //manhattan
       double xbar = 1; //important that it not go to zero.
       for(int idir = 0; idir < DIM; idir++)
       {
@@ -257,7 +261,6 @@ public:
[…]

### 2023-04-17 src/LinearAlgebra/Chombo_EigenMatrix.H

@@ -173,8 +173,27 @@ namespace ch_eigen
       a_smallestEigenvalue = omega;
     }
 
+    ///
+    inline void
+    poutEigenvalues() const
+    {
+      Chombo4::pout() << setprecision(15)
+                      << setiosflags(ios::showpoint)
+                      << setiosflags(ios::scientific);
+      
+      Eigen::JacobiSVD<Eigen::MatrixXd> svd(*m_mat_p);
+      int neig = svd.singularValues().size();
+      int ifirs = 0;
+      int ilast =  neig - 1;
+      Chombo4::pout() << neig << " matrix eigenvalues: " << endl;
+      for(int ivec = 0; ivec < neig; ivec++)
+      {
+        double beta = svd.singularValues()(ivec);
+        Chombo4::pout() << "(" << ivec << "): " << beta << endl;
+      }
+    }
     ///Eigen probably has way faster ways to do this 
-    void writeToFile(std::string a_filename) const
+    inline void writeToFile(std::string a_filename) const
     {
       ofstream outfile;
       outfile    << setprecision(15)

### 2023-04-18 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
initial ebcm framework compiles
added eigen comment and started documenting first example

@@
 core, all these algorithms have a similar procedure for finding the
-Taylor coefficients $C^p$ which is worth discussing
+Taylor coefficients $C^p$ which is worth discussing.
 
@@
 \end{equation*}
+This formulation can woven into the computation for stencil
+components;  Devendran \cite{Dendran2017}, for example, explains the
+process for Poisson's equation.
+
+Unfortunately, the matrix $A \equiv (WM)^T(WM)$ can be poorly conditioned.
+That these algorithms invert a matrix to compute
+stencil coefficients introduces an interesting type of uncertainty: error in
+the very coefficients of a stencil operation.   If the matrix is poorly
+conditioned, the coefficients of the stencil can only be known to
+limited precision.   This lack of precision is measurable as are its
+consequences.
+
+\section{All Regular geometry}
+
+To investigate the consequences of this geometry, we consider as a
+motivating example a geometry wherein all cells are uncut.
+
 The matrix inversion at the heart of this method requires that we need
@@
 
-\footnotetext[7] {.}
-
+\footnotetext[7] {All matrix computations here are performed using
+  Eigen \cite{eigenweb}, a beautifully designed and implemented
+  package for on-processor linear algebra that is freely available.}
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-04-18 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
lots of refinements on data acquisition for the paper

@@
 Given a sufficiently smooth function $\psi$, we can approximate $\psi$
-in the neighborhood of $\xbar$ using a Taylor expansion to order $P$:
+in the neighborhood of $\xbar$ using a Taylor expansion to order $P_T$:
 \begin{equation}
-\psi(\xbold)  =  \sum\limits_{p < P} C^p (\xbar - \xbar)^p \label{eqn::taylor}
+\psi(\xbold)  =  \sum\limits_{p < P_T} C^p (\xbar -
+\xbar)^p \label{eqn::taylor}
+\label{eqn::taylor}
 \end{equation}
@@
 If we insert the Taylor expansion \ref{eqn::taylor}, we get a discrete
-approximation to the smooth function $\psi$ that is accurate to order $P$.
+approximation to the smooth function $\psi$ that is accurate to order $P_T$.
 \begin{equation*}
- V_\ibold <\psi>_\ibold = \sum\limits_{p < P} C^p m^p. 
+ V_\ibold <\psi>_\ibold = \sum\limits_{p < P_T} C^p m^p. 
 \end{equation*}
@@
 the equation set used to create $C$ only includes the volume
-equations.  Devendran \cite{Devendran2017} also include boundary
+equations.  Devendran et al. \cite{Devendran2017} also include boundary
 condition equations in the equation set.  For simple enough boundary
@@
 Consider a finite volume grid where we know all geometric moments to
-order $P$.  Given values of $<\psi>$ everwhere on the grid, we wish to
+order $P_T$.  Given values of $<\psi>$ everwhere on the grid, we wish to
 approximate the Taylor coefficients at a volume $\ibold$ given that we
@@
 \begin{equation}
-  V_\jbold <\psi>_\jbold = \sum\limits_{p < P} C^p_\ibold m^p_\jbold.
+  V_\jbold <\psi>_\jbold = \sum\limits_{p < P_T} C^p_\ibold m^p_\jbold.
 \end{equation}
@@
 the solution using a Moore-Penrose pseudo-inverse:
-\begin{equation*}
+\begin{equation}
   C = ((WM)^T(WM))^{-1} (WM)^T P.
-\end{equation*}
+\label{eqn::getC}  
+\end{equation}
 This formulation can woven into the computation for stencil
@@
 Unfortunately, the matrix $A \equiv (WM)^T(WM)$ can be poorly conditioned.
-That these algorithms invert a matrix to compute
+That these algorithms can invert a poorly-conditioned matrix to compute
 stencil coefficients introduces an interesting type of uncertainty: error in
@@
 
-\section{All Regular geometry}
+\section{Condition number measurements}
 
-To investigate the consequences of this geometry, we consider as a
-motivating example a geometry wherein all cells are uncut.
+To gain insight into this process, we evaluate the matrix $A \equiv
+(WM)^T(WM)$ at every volume in a computational grid and analyze its
+eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
+$\{ \lambda_{i}\}$, the inverse of the condition number $I_i$ is given by
+\begin{equation*}
+  I_i = \frac{\lambda_i|_{min}}{\lambda_i|_{max}},
+\end{equation*}
+which goes to zero as the maximum and minimum eigenvalues diverge and
+the matrix becomes more poorly conditioned.   These eigenvalues are
+obtained through  SVD decompostion \footnotemark[7].
 
-The matrix inversion at the heart of this method requires that we need
-know to what degree the matrix $A \equiv (WM)^T(WM)$ is
-well-conditioned.  Experience suggests that small cells play a role in
-that conditioning and that the weighting matrix $W$ can be used to
-mitigate conditioning issues that unweighted least squares may
-produce.
+First we  measure   an uncut, Cartesian mesh to
+provide a baseline without the complications involved with cut cells.
+Next we cut the mesh with a very smooth implicit function and do the
+same measurements.   Finally we take this cut mesh and merge its small
+cells to neighbors to eliminate all cells smaller than a Cartesian
+volume to isolate the effects of small cells.
 
-To explore the roles of small cells and weighting functions, we first
-introduce a merged cut cell space where there are no small cells.
-This merged space still has geometric moments accurate to the same order 
-as the original cut cell space.
+All volumes $V_i$ start with a index $i \in Z^D$.
+We start from volume $V_0$.   For 
+weighting function, we need to measure $D_{w, V_0}(V_1)$,
+the Manhattan disance to the volume $V_1$:
+\begin{equation}
+  D_{W, V_0}}(V_1) = \sum\limits_{d \in {1...D}} |i_1^d - i_0^d|.
+\label{eqn::uptownFunk}
+\end{equation}
+We define $W_{v_0}(V_1)$, the weighting function used by volume $V_0$ for the
+equation describing  volume $V_1$ we use is given by
+\begin{equation}
+  W_{v_0}(V_1)  \equiv \frac{1}{D^{P_w}_{V_0}(V_1)},
+\label{eqn::weightFunk}  
+\end{equation}
+where $ 0 < P_w < 6$, the weighting power.   We present results for
+polynomial order $0 < P_T < 5$.
 
-We study how weighting matricies change the conditioning of $A$.  This is
-done both with and without cell merger in the hope hope that this
-exploration may lead to simpler, more robust cut cell algorithms to
-solve partial differential equations at high order.
+\subsection{All Regular geometry}
 
-\section{Cell Merger Algorithm}
+We begin with a motivating example a geometry wherein all cells are uncut.
+
+\subsection{Cut Cell Geometry}
+\subsection{Merged Geometry}
+
+\section{Conclusions}
+\section{Appendix:Cell Merger Algorithm}
 
@@
 \begin{figure}
-\centerline{\epsfig{figure=unmerged.ps,width=0.4\linewidth }} 
+\centerline{\epsfig{figure=_fig/unmerged.ps,width=0.4\linewidth }} 
 \caption{Map for EB grid produced by a cutting cirle. $\kappa <= 1$.
@@
 \begin{figure}
-\centerline{\epsfig{figure=merged.ps,width=0.4\linewidth } }
+\centerline{\epsfig{figure=_figmerged.ps,width=0.4\linewidth } }
 \label{fig::merged2dmap}
@@
   two volumes $\ibold$ and $\jbold$.  Typically they make
-  $W_{\jbold,\jbold}$ decrease strongly with increasing $D(\ibold,
-  \jbold)$ to assign higher importance to the equations for volumes
+  $W_{\jbold,\jbold}$ decrease strongly with increasing 
+  $D(\ibold,\jbold)$ to assign higher importance to the equations for volumes
   closer to $\ibold$.  Devendran for example \cite{Devendran2017},

### 2023-04-18 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp

@@ -64,6 +64,7 @@ public:
   typedef Chombo4::GeometryService<       ebcm_order >   ch_geoserv;
   typedef Proto::IndexedMoments<DIM  ,    ebcm_order >   pr_mom_dim;
   typedef Proto::IndexedMoments<DIM-1,    ebcm_order >   pr_mom_dmo;
+  typedef Proto::Point pr_pt;
 
   
   static shared_ptr<pr_baseif> getImplicitFunction()
@@ -215,8 +216,8 @@ public:
 
       m_volumes = shared_ptr<ebcm_subvol_vec>(new ebcm_subvol_vec(a_graph, region, a_printStuff));
       //begin debug
-      Chombo4::pout() << "first volmom in the neighborhood" << endl;
-      (*m_volumes)[0].m_volmom.print();
+      //Chombo4::pout() << "first volmom in the neighborhood" << endl;
+      //(*m_volumes)[0].m_volmom.print();
       //end debug
       int n_equations =  m_volumes->size();
       int n_unknowns  = pr_mom_dim::size();
@@ -410,9 +411,12 @@ public:
     return Amat_p;
   }
   ///
-  static inline Real
-  getInvCondNumber(const ebcm_volu     &  a_volu,
-                   const ebcm_graph    &  a_graph)
+  static inline void
+  getConditionNumberInfo(double & a_invCondNumber,
+                         double & a_maxEigenvalue,
+                         double & a_minEigenvalue,
+                         const ebcm_volu     &  a_volu,
+                         const ebcm_graph    &  a_graph)
   {
     //this stuff is probably more general than just this function
     //but the perfect API is eluding me at the moment so we will just
@@ -421,32 +425,65 @@ public:
     int stenrad, weightpower;
     pp.get("radius", stenrad);
     pp.get("weight_power", weightpower);
-    //just print everything for the first one
-    static bool printedAlready = false;
-    shared_ptr<eigen_mat> Amat = getAMatrix(a_volu, a_graph, stenrad, weightpower, !printedAlready);
-  
-    Real retval = Amat->invConditionNumber();
 
-    if(!printedAlready)
-    {
-      Amat->poutEigenvalues();
-      printedAlready = true;
-    }
+    shared_ptr<eigen_mat> Amat = getAMatrix(a_volu, a_graph, stenrad, weightpower, false);
 
-    return retval;
[…]

### 2023-04-18 src/LinearAlgebra/Chombo_EigenMatrix.H

@@ -199,7 +199,6 @@ namespace ch_eigen
       outfile    << setprecision(15)
                  << setiosflags(ios::showpoint)
                  << setiosflags(ios::scientific);
-      
       outfile.open(a_filename.c_str(), ios::out);
       int nrow = m_mat_p->rows();
       int ncol = m_mat_p->cols();

### 2023-04-21 src/LinearAlgebra/Chombo_EigenMatrix.H
took out chatty debugging

@@ -163,7 +163,6 @@ namespace ch_eigen
     getLargestAndSmallestEigenvalues(double & a_biggestEigenvalue,
                                      double & a_smallestEigenvalue) const
     {
-      poutEigenvalues();
       Eigen::JacobiSVD<Eigen::MatrixXd> svd(*m_mat_p);
       int ifirs = 0;
       int ilast = svd.singularValues().size()-1;

### 2023-04-21 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
They have us surrounded.   That simplifies matters.   -L. Puller

@@
 \begin{equation}
-\psi(\xbold)  =  \sum\limits_{p < P_T} C^p (\xbar -
-\xbar)^p \label{eqn::taylor}
+\psi(\xbold)  =  \sum\limits_{p < P_T} C^p (\xbar -\xbar)^p
 \label{eqn::taylor}
@@
 core, all these algorithms have a similar procedure for finding the
-Taylor coefficients $C^p$ which is worth discussing.
-
-The discerning reader will notice that
-the equation set used to create $C$ only includes the volume
-equations.  Devendran et al. \cite{Devendran2017} also include boundary
-condition equations in the equation set.  For simple enough boundary
-conditions, this works very well.  There are many equation sets,
-however, which do not lend themselves easily to this approach.
-Notably, hyperbolic equations often have boundary conditions which are
-fomulated in terms of characteristic variables.  Using this
-information in the system of equations for Taylor coefficients is
-still a matter of research.  We therefore believe that restricting
-ourselves to the volume equations can provide insight valuable to
-developers of this class of algorithms.
+Taylor coefficients $C^p$ which is worth discussing.  \footnotemark[8]
 
@@
 This formulation can woven into the computation for stencil
-components;  Devendran \cite{Dendran2017}, for example, explains the
+components;  Devendran \cite{Devendran2017}, for example, explains the
 process for Poisson's equation.
@@
 
+Broadly speaking, there are two approaches to dealing with this poor
+conditioning. One can improve the accuracy of the matrix
+representation so she can absorb the reduction in precision and still
+produce coefficients of sufficient accuracy.
+Lo, et al. \cite{Lo2019} show good results using quad-precision arithmetic
+for matrices which produce double precision coefficients.
+The other approach is to improve the
+conditioning of the matrix by careful choices of weighting matrix and
+neighborhood.
+
 \section{Condition number measurements}
 
-To gain insight into this process, we evaluate the matrix $A \equiv
-(WM)^T(WM)$ at every volume in a computational grid and analyze its
+To gain insight into the connection between solvability, weighting and
+order, we evaluate the matrix $A \equiv (WM)^T(WM)$
+at every volume in a computational grid and analyze its
 eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
@@
 \begin{equation}
-  D_{W, V_0}}(V_1) = \sum\limits_{d \in {1...D}} |i_1^d - i_0^d|.
+  D_{W, V_0}(V_1) = \sum\limits_{d \in {1...D}} |i_1^d - i_0^d|.
 \label{eqn::uptownFunk}
@@
 
-We begin with a motivating example a geometry wherein all cells are uncut.
+We begin with the simplest possible motivating example: a two
+dimensional Cartesian geometry wherein all cells are uncut.  Figure  
+\ref{fig::T3W3} shows $I$ with $P_w = P_T = 3$.  Table
+\ref{tab::all_reg2d}  shows the worst condition number in this simple
+grid for a number of values of $P_w$ and $P_T$.
+We hshow  that $I$ can get quite small, especially near the domain
+boundaries.   The data show clearly that there is a connection between
+solvability, weighting  funciton, and polynomial order.  Very interestingly,
+we show, that for a fixed polynomial order,
+a higher weighting power can make the solvability
+problem worse.
+
+\begin{figure}
+\centerline{\epsfig{figure=_fig/all_reg_t3_w3_inv_cond.ps,width=0.4\linewidth } }
+\label{fig::T3W3}
+\caption{$I$ (inverse of ondition number for matrix $A$ for a $32^2$
+  uncut grid where $P_w = P_T = 3$.}
+
+\end{figure}
+\begin{table}
+\begin{center}
+\begin{tabular}{|ccc|ccc|} \hline
+$P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+\hline
+1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
+1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
+1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
+1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
+1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\ 
+2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
+2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
+2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
+2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
+2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
+3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
+3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
+3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
+3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
+3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
+4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
+4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
+4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
+4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
+4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
+\hline
+
+\label{tab::all_reg2d}
+\end{tabular}
+\end{center}
+  \caption{$I$ for a variety of Taylor power $P^T$ and weighting
+    function exponents $P^W$.}
+
+\end{table}
 
@@
   Each cut cell has a unique positive integer.}
+\label{fig::unmerged2dmap}
 \end{figure}
@@
 \begin{figure}
-\centerline{\epsfig{figure=_figmerged.ps,width=0.4\linewidth } }
-\label{fig::merged2dmap}
+\centerline{\epsfig{figure=_fig/merged.ps,width=0.4\linewidth } }
 \caption{Map of EB grid shown in \ref{fig::unmerged2dmap} after using
@@
   Each cut cell has a unique positive integer. $\kappa <= 4.1433$}
+\label{fig::merged2dmap}
 \end{figure}
@@
   package for on-processor linear algebra that is freely available.}
+
+\footnotetext[8]{The discerning reader will notice that
+the equation set used to create $C$ only includes the volume
+equations.  Devendran et al. \cite{Devendran2017} also include boundary
+condition equations in the equation set.  For simple enough boundary
+conditions, this works very well.  There are many equation sets,
+however, which do not lend themselves easily to this approach.
+Notably, hyperbolic equations often have boundary conditions which are
+fomulated in terms of characteristic variables.  Using this
+information in the system of equations for Taylor coefficients is
+still a matter of research.  We therefore believe that restricting
+ourselves to the volume equations can provide insight valuable to
+developers of this class of algorithms.}
+
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-04-21 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp

@@ -454,10 +454,17 @@ public:
     double m_max_eigenvalue;
     double m_min_eigenvalue;
     pr_pt  m_pt;
-    inline void poutLatexTable(int a_P, int a_G) const
+    inline void poutLatexTable() const
     {
 
       using Chombo4::pout;
+
+      ParmParse ppmain("main");
+      ParmParse ppsten("stencil");
+      int stnrad, wgtpow, taymax;
+      ppmain.get("polynomial_order", taymax);
+      ppsten.get("weight_power"    , wgtpow);
+      ppsten.get("radius"          , stnrad);
       
       pout() << setw(12)
              << setprecision(6)
@@ -465,11 +472,11 @@ public:
              << setiosflags(ios::scientific);
       pout() << "\\begin{table}" << endl;
       pout() << "\\begin{center}" << endl;
-      pout() << "\\begin{tabular}{|cc|ccc|} \\hline" << endl;
+      pout() << "\\begin{tabular}{|ccc|ccc|} \\hline" << endl;
 
-      pout() << " P & G & \\lambda_{max} & \\lambda_{min}   & $I$ \\\\"<< endl;
+      pout() << " Order  & $P^W$ & $R_s$ & \\lambda_{max} & \\lambda_{min}   & $I$ \\\\"<< endl;
       pout() << "\\hline " << endl;
-      pout() << a_P << " & " << a_G << " & " << m_max_eigenvalue << " & " << m_min_eigenvalue << " & "  << m_inv_condition;
+      pout() <<  "GREP_HOOK" << taymax << " & " << wgtpow << " & " <<  stnrad << " & "<< m_max_eigenvalue << " & " << m_min_eigenvalue << " & "  << m_inv_condition;
       pout() << " \\\\ " << endl;
 
       pout() << "\\hline " << endl;
@@ -629,12 +636,7 @@ public:
     shared_ptr<condition_t>    worst;
     getConditionNumberData(invCondition, worst, ebcm);
 
-    int P = ebcm_order;
-    int G;
-    ParmParse ppsten("stencil");
-    ppsten.get("radius", G);
-    
-    worst->poutLatexTable(P, G);
+    worst->poutLatexTable();
     Chombo4::pout() << "worst condition number at point " << worst->m_pt << endl;
     
     string plot_filename;

### 2023-04-22 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
this could blow this town wide open (progress on paper)

@@
 \end{equation}
-where $ 0 < P_w < 6$, the weighting power.   We present results for
-polynomial order $0 < P_T < 5$.
+where we vary $P_w$, and the 
+polynomial order $P_T$.
 
@@
 
-We begin with the simplest possible motivating example: a two
-dimensional Cartesian geometry wherein all cells are uncut.  Figure  
-\ref{fig::T3W3} shows $I$ with $P_w = P_T = 3$.  Table
-\ref{tab::all_reg2d}  shows the worst condition number in this simple
-grid for a number of values of $P_w$ and $P_T$.
-We hshow  that $I$ can get quite small, especially near the domain
-boundaries.   The data show clearly that there is a connection between
-solvability, weighting  funciton, and polynomial order.  Very interestingly,
-we show, that for a fixed polynomial order,
-a higher weighting power can make the solvability
-problem worse.
+We begin with the simplest possible motivating example: a
+$D$-dimensional Cartesian geometry wherein all cells are uncut.
+Figure \ref{fig::T3W3} shows all values of $I$ for $D=2$, $I$ with
+$P_w = P_T = 3$.  Table \ref{tab::worst_all_reg_inv_conv} shows the
+worst condition number in this simple grid for a number of values of
+$P_w$ and $P_T$.  We show first that for a safe (low) choice of
+$P_T$, even the worst condition number in a given grid can be quite
+reasonable. With more aggressive choices of $P_T$, $I$ can be quite
+small (especially near the domain boundaries).  The data also
+show clearly that there is a connection between solvability, weighting
+function, and polynomial order.  Unexpectedly, we show that for a
+fixed polynomial order $P_T$, a higher weighting power $P_w$ can make the
+solvability problem worse.
 
@@
 \label{fig::T3W3}
-\caption{$I$ (inverse of ondition number for matrix $A$ for a $32^2$
-  uncut grid where $P_w = P_T = 3$.}
+\caption
+    {
+      $I$ (inverse of the condition number for matrix $A$ for a $32^2$
+      uncut grid where $P_w = P_T = 3$.
+    }
+\end{figure}
 
-\end{figure}
 \begin{table}
 \begin{center}
-\begin{tabular}{|ccc|ccc|} \hline
-$P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+\begin{tabular}{|cccc|ccc|} \hline
+$D$ $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
   \hline
-1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
-1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
-1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
-1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
-1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\ 
-2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
-2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
-2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
-2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
-2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
-3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
-3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
-3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
-3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
-3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
-4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
-4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
-4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
-4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
-4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
+2 & 1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
+2 & 1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
+2 & 1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
+2 & 1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
+2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\ 
+2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
+2 & 2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
+2 & 2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
+2 & 2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
+2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
+2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
+2 & 3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
+2 & 3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
+2 & 3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
+2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
+2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
+2 & 4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
+2 & 4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
+2 & 4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
+2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
+3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
+3 & 1 & 2 & 3 & 1.335375e+00 & 2.299835e-04 & 1.722239e-04 \\ 
+3 & 1 & 3 & 3 & 1.058688e+00 & 2.726319e-05 & 2.575186e-05 \\ 
+3 & 1 & 4 & 3 & 1.012826e+00 & 4.843834e-06 & 4.782494e-06 \\ 
+3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
+3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
+3 & 2 & 2 & 3 & 1.335376e+00 & 1.349331e-07 & 1.010450e-07 \\ 
+3 & 2 & 3 & 3 & 1.058688e+00 & 6.504992e-09 & 6.144388e-09 \\ 
+3 & 2 & 4 & 3 & 1.012826e+00 & 3.782273e-10 & 3.734376e-10 \\ 
+3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
+3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
+3 & 3 & 2 & 3 & 1.335376e+00 & 6.641096e-11 & 4.973204e-11 \\ 
+3 & 3 & 3 & 3 & 1.058688e+00 & 3.224905e-12 & 3.046133e-12 \\ 
+3 & 3 & 4 & 3 & 1.012826e+00 & 1.004670e-13 & 9.919476e-14 \\ 
+3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
+3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
+3 & 4 & 2 & 3 & 1.474014e+00 & 1.231139e-27 & 8.352288e-28 \\ 
+3 & 4 & 3 & 3 & 1.102368e+00 & 5.433012e-27 & 4.928491e-27 \\ 
+3 & 4 & 4 & 3 & 1.012826e+00 & 1.327379e-23 & 1.310570e-23 \\ 
+3 & 4 & 5 & 3 & 1.003042e+00 & 6.807789e-25 & 6.787141e-25 \\ 
 \hline
-
-\label{tab::all_reg2d}
+\label{tab::worst_all_reg_inv_conv}
 \end{tabular}
 \end{center}
-  \caption{$I$ for a variety of Taylor power $P^T$ and weighting
-    function exponents $P^W$.}
-
+\caption
+    {
+      We show the lowest value 
+      $I$ for an entire Cartesian grid of size $32^D$.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$. 
+    }
 \end{table}
 
-\subsection{Cut Cell Geometry}
-\subsection{Merged Geometry}
-
-\section{Conclusions}
-\section{Appendix:Cell Merger Algorithm}
-
-We use a very simple cell merger algorithm.  Given a cut cell
-$\ibold$, we define the box containing only that cell
-$B_c = B(\ibold, \ibold)$ 
-We form a $2^D$ cell rectangular region
-by coarsening and then refining $B_c$ to form $B_v = R(C(B_c))$
-\footnotemark[6].
-After that process, any left over small cells are merged with their
-biggest neighbor.    See figures \ref{fig::unmerged2dmap} and
-\ref{fig::merged2dmap} for a simple example of how this algorithm
-creates fairly chunky grids   \footnotemark[5].
-
-We define the volume fraction $\kappa_\ibold \equiv  V_\ibold/h^D$.
-For unmerged grids, $ 0 < \kappa <= 1$.   When merged using this
-algorithm, $\kappa$ can be larger than $2^D$.
+\section{Cut Cell Geometry}
+\label{sec::eb}
+Our next  grid is a Cartesian grid cut  by a sphere (or a circle in two
+dimensions). The computational domain is the unit cube.   The cutting
+sphere center is the center of the cube.   The radius of the cutting
+sphere is 0.45.  The grid moments are generated using the algorithm
+specified in \cite{Schwartz2015}.  The moments are accurate to
+order $h^{P^T}$.   The map for the 2D case is shown in figure
+\ref{fig::unmerged2dmap}.
 
@@
 \centerline{\epsfig{figure=_fig/unmerged.ps,width=0.4\linewidth }} 
-\caption{Map for EB grid produced by a cutting cirle. $\kappa <= 1$.
+\caption
+    {
+      Map for EB grid produced by a cutting cirle. $0 <  \kappa <= 1$.
   Each cut cell has a unique positive integer.}
@@
 \end{figure}
+
+\subsection{Merged Geometry}
+
+Our next  grid is a the same grid show in section \ref{sec::eb}.
+Here, however, we  use a very simple cell merger algorithm to force
+all cells to have a volume at least as large as an uncut cell.
+
+Given a cut cell $\ibold$, we define the box containing only that cell
+$B_c = B(\ibold, \ibold)$ We form a $2^D$ cell rectangular region by
+coarsening and then refining $B_c$ to form $B_v = R(C(B_c))$
+\footnotemark[6].  After that process, any left over small cells are
+merged with their biggest neighbor.  See figures
+\ref{fig::unmerged2dmap} and \ref{fig::merged2dmap} for a simple
+example of how this algorithm creates fairly chunky grids
+
+Merging two cells is simply a matter of removing the
+intervening faces, shifting all moments them to a common location
+and adding them together.  No accuracy is lost in this process
+outside of the fact that we have fewer degress of freedom because
+semantically, we are just adding volume integrals over distinct
+volumes, which is exact.
+
+For unmerged grids, the volume fraction $\kappa_\ibold \equiv
+V_\ibold/h^D$ can be arbitrarily small ($ 0 < \kappa <= 1$).
+When merged using this algorithm, $\kappa$ can be larger than $2^D$.
 
@@
   cell merger algorithm.
-  Each cut cell has a unique positive integer. $\kappa <= 4.1433$}
+  Each cut cell has a unique positive integer. $ 1 <= \kappa <= 4.1433$}
 \label{fig::merged2dmap}
 \end{figure}
+
+\section{Conclusions}
+\section{Appendix:Cell Merger Algorithm}
 
@@
   \approx 1./D(\ibold,\jbold)^5$ }.
-
-\footnotetext[5] {Merging two cells is simply a matter of removing the
-  intervening faces, shifting all moments them to a common location
-  and adding them together.  No accuracy is lost in this process
-  outside of the fact that we have fewer degress of freedom because
-  semantically, we are just adding volume integrals over distinct
-  volumes, which is exact.}
 

### 2023-04-22 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp

@@ -474,9 +474,10 @@ public:
       pout() << "\\begin{center}" << endl;
       pout() << "\\begin{tabular}{|ccc|ccc|} \\hline" << endl;
 
-      pout() << " Order  & $P^W$ & $R_s$ & \\lambda_{max} & \\lambda_{min}   & $I$ \\\\"<< endl;
+      pout() << " $D$ & $P^T$  & $P^W$ & $R_s$ & \\lambda_{max} & \\lambda_{min}   & $I$ \\\\"<< endl;
       pout() << "\\hline " << endl;
-      pout() <<  "GREP_HOOK" << taymax << " & " << wgtpow << " & " <<  stnrad << " & "<< m_max_eigenvalue << " & " << m_min_eigenvalue << " & "  << m_inv_condition;
+      int dim = DIM;
+      pout() <<  "-GREP_HOOK-" << dim << " & " << taymax << " & " << wgtpow << " & " <<  stnrad << " & "<< m_max_eigenvalue << " & " << m_min_eigenvalue << " & "  << m_inv_condition;
       pout() << " \\\\ " << endl;
 
       pout() << "\\hline " << endl;

### 2023-04-22 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
first draft finished

@@
 This formulation can woven into the computation for stencil
-components;  Devendran \cite{Devendran2017}, for example, explains the
+components;  Devendran et al. \cite{Devendran2017}, for example, explains the
 process for Poisson's equation.
@@
 conditioned, the coefficients of the stencil can only be known to
-limited precision.   This lack of precision is measurable as are its
-consequences.
+limited precision.   This lack of precision is measurable as it tracks
+the condition number of the matrix.
 
@@
 worst condition number in this simple grid for a number of values of
-$P_w$ and $P_T$.  We show first that for a safe (low) choice of
-$P_T$, even the worst condition number in a given grid can be quite
-reasonable. With more aggressive choices of $P_T$, $I$ can be quite
-small (especially near the domain boundaries).  The data also
-show clearly that there is a connection between solvability, weighting
-function, and polynomial order.  Unexpectedly, we show that for a
-fixed polynomial order $P_T$, a higher weighting power $P_w$ can make the
-solvability problem worse.
+$P_w$ and $P_T$.
 
@@
     {
-      We show the lowest value 
+      We show the lowest value of
       $I$ for an entire Cartesian grid of size $32^D$.
@@
 \label{sec::eb}
+
 Our next  grid is a Cartesian grid cut  by a sphere (or a circle in two
@@
 specified in \cite{Schwartz2015}.  The moments are accurate to
-order $h^{P^T}$.   The map for the 2D case is shown in figure
-\ref{fig::unmerged2dmap}.
+order $h^{P^T}$.
+
+If we use grid volumes at this point, the volume fraction
+\begin{equation*}
+\kappa_\ibold \equiv V_\ibold/h^D$ 
+\end{equation*}
+can be arbitrarily small ($ 0 < \kappa <= 1$).   We can also choose to
+merge small volumes with larger neighbors without formal loss of
+accuracy. The simple merger we use is described in
+described in appendix \ref{appendix::merge}.
+When merged using this algorithm, $\kappa$ can be larger than $2^D$.
+
+Without using cell merger, the volume map in two dimensions is shown
+in figure \ref{fig::unmerged2dmap}.   With cell merger, that same map
+becomes the grid shown in figure{fig::unmerged2dmap}.
+Tables \ref{tab::worst_unmerged_inv_conv} and
+\ref{tab::worst_merged_inv_conv}
+show the worst condition number for the unmerged and merged  grids
+respectively while varying $P_w$ and $P_T$.   Merger does not seem to
+help substantially with this issue.
 
@@
 
-\subsection{Merged Geometry}
+\begin{table}
+\begin{center}
+\begin{tabular}{|cccc|ccc|} \hline
+$D$ $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+  \hline
+2 & 1 & 1 & 3 & 2.652364e+00 & 1.404997e-03 & 5.297151e-04 \\ 
+2 & 1 & 2 & 3 & 1.208056e+00 & 1.014262e-04 & 8.395817e-05 \\ 
+2 & 1 & 3 & 3 & 1.038877e+00 & 8.361926e-06 & 8.049002e-06 \\ 
+2 & 1 & 4 & 3 & 1.008924e+00 & 1.034928e-06 & 1.025774e-06 \\ 
+2 & 1 & 5 & 3 & 1.002428e+00 & 1.818655e-07 & 1.814249e-07 \\ 
+2 & 2 & 1 & 3 & 2.714706e+00 & 6.503682e-07 & 2.395722e-07 \\ 
+2 & 2 & 2 & 3 & 1.208056e+00 & 4.514952e-08 & 3.737369e-08 \\ 
+2 & 2 & 3 & 3 & 1.038878e+00 & 2.933277e-09 & 2.823506e-09 \\ 
+2 & 2 & 4 & 3 & 1.008924e+00 & 1.838097e-10 & 1.821840e-10 \\ 
+2 & 2 & 5 & 3 & 1.002428e+00 & 1.202042e-11 & 1.199130e-11 \\ 
+2 & 3 & 1 & 3 & 2.714706e+00 & 2.057098e-10 & 7.577609e-11 \\ 
+2 & 3 & 2 & 3 & 1.208056e+00 & 1.761011e-11 & 1.457723e-11 \\ 
+2 & 3 & 3 & 3 & 1.039039e+00 & 1.175442e-12 & 1.131278e-12 \\ 
+2 & 3 & 4 & 3 & 1.008867e+00 & 6.513002e-14 & 6.455759e-14 \\ 
+2 & 3 & 5 & 3 & 1.002428e+00 & 3.467198e-15 & 3.458798e-15 \\ 
+2 & 4 & 1 & 3 & 2.714706e+00 & 1.027685e-15 & 3.785620e-16 \\   
+2 & 4 & 2 & 3 & 1.211905e+00 & 6.107792e-17 & 5.039827e-17 \\ 
+2 & 4 & 3 & 3 & 1.056037e+00 & 5.698627e-18 & 5.396236e-18 \\ 
+2 & 4 & 4 & 3 & 1.012707e+00 & 1.518532e-18 & 1.499478e-18 \\ 
+2 & 4 & 5 & 3 & 1.003135e+00 & 5.995871e-19 & 5.977134e-19 \\ 
+3 & 1 & 1 & 3 & 6.913890e+00 & 3.982271e-03 & 5.759812e-04 \\ 
+3 & 1 & 2 & 3 & 1.457799e+00 & 1.829378e-04 & 1.254890e-04 \\ 
+3 & 1 & 3 & 3 & 1.066961e+00 & 8.913398e-06 & 8.354003e-06 \\ 
+3 & 1 & 4 & 3 & 1.014131e+00 & 7.252280e-07 & 7.151226e-07 \\ 
+3 & 1 & 5 & 3 & 1.003774e+00 & 1.047053e-07 & 1.043116e-07 \\ 
+3 & 2 & 1 & 3 & 7.173851e+00 & 1.868373e-06 & 2.604421e-07 \\ 
+3 & 2 & 2 & 3 & 1.457801e+00 & 7.350629e-08 & 5.042274e-08 \\ 
+3 & 2 & 3 & 3 & 1.066958e+00 & 3.054784e-09 & 2.863077e-09 \\ 
+3 & 2 & 4 & 3 & 1.014128e+00 & 1.439525e-10 & 1.419470e-10 \\ 
+3 & 2 & 5 & 3 & 1.003771e+00 & 6.965181e-12 & 6.939012e-12 \\ 
+3 & 3 & 1 & 3 & 7.173852e+00 & 5.736142e-10 & 7.995902e-11 \\ 
+3 & 3 & 2 & 3 & 1.463399e+00 & 3.367341e-11 & 2.301041e-11 \\ 
+3 & 3 & 3 & 3 & 1.067176e+00 & 1.250758e-12 & 1.172027e-12 \\ 
+3 & 3 & 4 & 3 & 1.014128e+00 & 4.489644e-14 & 4.427098e-14 \\ 
+3 & 3 & 5 & 3 & 1.003771e+00 & 1.609961e-15 & 1.603912e-15 \\ 
+3 & 4 & 1 & 3 & 7.173852e+00 & 8.922302e-15 & 1.243725e-15 \\ 
+3 & 4 & 2 & 3 & 1.463399e+00 & 3.078368e-16 & 2.103574e-16 \\ 
+3 & 4 & 3 & 3 & 1.067186e+00 & 2.577668e-17 & 2.415387e-17 \\ 
+3 & 4 & 4 & 3 & 1.014048e+00 & 4.440651e-18 & 4.379133e-18 \\ 
+3 & 4 & 5 & 3 & 1.005227e+00 & 8.527341e-19 & 8.483000e-19 \\
 
-Our next  grid is a the same grid show in section \ref{sec::eb}.
-Here, however, we  use a very simple cell merger algorithm to force
-all cells to have a volume at least as large as an uncut cell.
+  \label{tab::worst_unmerged_inv_conv}
+\end{tabular}
+\end{center}
+\caption
+    {
+      We show the lowest value of
+      $I$ for an entire Cartesian grid of size $32^D$.
+      Volumes are  formed by a sphere (or circle in 2D) cutting the
+      grid.   Volumes here can be arbitrarily small (no cell merging
+      happens here).
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$. 
+    }
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|cccc|ccc|} \hline
+$D$ $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+  \hline
+2 & 1 & 1 & 3 & 2.516834e+00 & 1.345987e-04 & 5.347936e-05 \\ 
+2 & 1 & 2 & 3 & 1.940391e+00 & 5.761694e-06 & 2.969347e-06 \\ 
+2 & 1 & 3 & 3 & 1.890620e+00 & 3.134007e-07 & 1.657661e-07 \\ 
+2 & 1 & 4 & 3 & 2.315204e+00 & 2.362198e-08 & 1.020298e-08 \\ 
+2 & 1 & 5 & 3 & 2.314798e+00 & 1.256411e-09 & 5.427736e-10 \\ 
+2 & 2 & 1 & 3 & 5.133178e+00 & 3.150951e-08 & 6.138402e-09 \\ 
+2 & 2 & 2 & 3 & 3.875948e+00 & 1.019905e-09 & 2.631369e-10 \\ 
+2 & 2 & 3 & 3 & 3.677407e+00 & 3.374831e-11 & 9.177202e-12 \\ 
+2 & 2 & 4 & 3 & 3.633887e+00 & 1.196563e-12 & 3.292791e-13 \\ 
+2 & 2 & 5 & 3 & 1.100852e+00 & 1.071019e-14 & 9.729001e-15 \\ 
+2 & 3 & 1 & 3 & 1.461766e+00 & 8.698889e-14 & 5.950944e-14 \\ 
+2 & 3 & 2 & 3 & 1.118751e+00 & 4.096970e-15 & 3.662093e-15 \\ 
+2 & 3 & 3 & 3 & 1.102424e+00 & 1.662951e-16 & 1.508449e-16 \\ 
+2 & 3 & 4 & 3 & 3.178329e+00 & 1.221190e-16 & 3.842238e-17 \\ 
+2 & 3 & 5 & 3 & 1.924223e+00 & 3.044738e-18 & 1.582320e-18 \\ 
+3 & 1 & 1 & 3 & 5.278376e+00 & 5.346601e-04 & 1.012926e-04 \\ 
+3 & 1 & 2 & 3 & 2.898394e+00 & 1.760686e-05 & 6.074697e-06 \\ 
+3 & 1 & 3 & 3 & 2.480330e+00 & 4.867477e-07 & 1.962431e-07 \\ 
+3 & 1 & 4 & 3 & 2.602304e+00 & 1.708061e-08 & 6.563648e-09 \\ 
+3 & 1 & 5 & 3 & 2.594257e+00 & 5.017396e-10 & 1.934039e-10 \\ 
+3 & 2 & 1 & 3 & 8.172169e+00 & 1.320095e-07 & 1.615355e-08 \\ 
+3 & 2 & 2 & 3 & 4.770044e+00 & 3.005370e-09 & 6.300508e-10 \\ 
+3 & 2 & 3 & 3 & 4.426838e+00 & 7.734334e-11 & 1.747146e-11 \\ 
+3 & 2 & 4 & 3 & 4.521378e+00 & 1.996373e-12 & 4.415410e-13 \\ 
+3 & 2 & 5 & 3 & 4.508090e+00 & 4.439516e-14 & 9.847886e-15 \\ 
+3 & 3 & 1 & 3 & 5.015663e+00 & 9.627815e-12 & 1.919550e-12 \\ 
+3 & 3 & 2 & 3 & 6.602139e+00 & 4.969235e-13 & 7.526705e-14 \\ 
+3 & 3 & 3 & 3 & 6.132610e+00 & 1.126536e-14 & 1.836961e-15 \\ 
+3 & 3 & 4 & 3 & 5.482751e+00 & 3.670736e-16 & 6.695062e-17 \\ 
+3 & 3 & 5 & 3 & 5.346895e+00 & 4.774068e-17 & 8.928674e-18 \\ 
+3 & 4 & 1 & 3 & 1.161979e+01 & 5.372252e-18 & 4.623365e-19 \\ 
+3 & 4 & 2 & 3 & 4.069086e+00 & 1.622222e-17 & 3.986699e-18 \\ 
+\hline
+\label{tab::worst_merged_inv_conv}
+\end{tabular}
+\end{center}
+\caption
+    {
+      We show the lowest value of
+      $I$ for an entire Cartesian grid of size $32^D$.
+      Volumes are  formed by a sphere (or circle in 2D) cutting the
+      grid.   Small volumes here are merged with neighbors.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$. 
+    }
+\end{table}
+
+\section{Conclusions}
+
+We show first that for a safe (low) choice of
+$P_T$, even the worst condition number in a given grid can be quite
+reasonable. With more aggressive choices of $P_T$, $I$ can be very
+small.  The data also
+show clearly that there is a connection between solvability, weighting
+function, and polynomial order.  Unexpectedly, we show that for a
+fixed polynomial order $P_T$, a higher weighting power $P_w$ can make the
+solvability problem worse.
+
+We do also show that matrix conditioning is a  potential issue for
+this class of algorihms.   In fact, for certain parameters,
+the condition number  can be so severe that an
+increase in matrix arithmetic precision will not be sufficient.
+Since cell merger does not really help the
+problem, this lack of conditioning is not an issue with small cells.
+With careful choices of polynomial order and weighting matrix, the
+solvability problem can be managed, however.
+
+\section{Appendix: Simple algorithm for cell merger}
+\label{appendix::merger}
 
@@
 \ref{fig::unmerged2dmap} and \ref{fig::merged2dmap} for a simple
-example of how this algorithm creates fairly chunky grids
+example of how this algorithm creates fairly chunky grids.
 
@@
 
-\section{Conclusions}
-\section{Appendix:Cell Merger Algorithm}
-
 \footnotetext[1]{Lawrence Berkeley National Laboratory, Berkeley,
@@
   $D(\ibold,\jbold)$ to assign higher importance to the equations for volumes
-  closer to $\ibold$.  Devendran for example \cite{Devendran2017},
+  closer to $\ibold$.  Devendran et al. for example \cite{Devendran2017},
   uses a weighting function that varies with $W_{\ibold,\jbold}

### 2023-04-24 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
finished first draft of paper
took out the the conclusion I was expecting and I put in what
the data actually shows

@@
   functions.    A very rudimentary but stable cell merger algorithm is
-  presented as we present evidence that these solvability issues may be
+  presented as we show that these solvability issues are not 
   an artifact of small-cell instabilties.
@@
 \begin{equation*}
-\kappa_\ibold \equiv V_\ibold/h^D$ 
+\kappa_\ibold \equiv V_\ibold/h^D 
 \end{equation*}
@@
 accuracy. The simple merger we use is described in
-described in appendix \ref{appendix::merge}.
+described in appendix \ref{appendix::merger}.
 When merged using this algorithm, $\kappa$ can be larger than $2^D$.

### 2023-04-24 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
finally got the latex tables too look decent

@@
   presented as we show that these solvability issues are not 
-  an artifact of small-cell instabilties.
+  an artifact of small-cell instabilties.    We show that one can
+  manage these solvability issues with careful algorithm choices.
 
@@
 conditioning. One can improve the accuracy of the matrix
-representation so she can absorb the reduction in precision and still
+representation so she may absorb the reduction in precision and still
 produce coefficients of sufficient accuracy.
@@
 
-All volumes $V_i$ start with a index $i \in Z^D$.
+All volumes $V_i$ start with an  index $i \in Z^D$.
 We start from volume $V_0$.   For 
@@
 \end{equation}
-where we vary $P_w$, and the 
+where we vary the weighting exponent $P_w$, and the 
 polynomial order $P_T$.
@@
 
+\begin{small}
 \begin{table}
@@
 \begin{tabular}{|cccc|ccc|} \hline
-$D$ $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
 \hline
@@
 \hline
-\label{tab::worst_all_reg_inv_conv}
 \end{tabular}
 \end{center}
+\label{tab::worst_all_reg_inv_conv}
 \caption
@@
 \end{table}
+\end{small}
 
@@
 \begin{tabular}{|cccc|ccc|} \hline
-$D$ $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
   \hline
@@
 3 & 4 & 5 & 3 & 1.005227e+00 & 8.527341e-19 & 8.483000e-19 \\
-
-  \label{tab::worst_unmerged_inv_conv}
+\hline
 \end{tabular}
 \end{center}
+\label{tab::worst_unmerged_inv_conv}
 \caption
@@
 \hline
-\label{tab::worst_merged_inv_conv}
 \end{tabular}
 \end{center}
+\label{tab::worst_merged_inv_conv}
 \caption

### 2023-04-25 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
further refinements on the document.   EBCM framework coming out the cold.

@@
 To gain insight into the connection between solvability, weighting and
-order, we evaluate the matrix $A \equiv (WM)^T(WM)$
+order, we evaluate the matrix
+\begin{equation}
+A \equiv (WM)^T(WM)
+\label{eqn::normalEq}
+\end{equation}
 at every volume in a computational grid and analyze its
@@
 obtained through  SVD decompostion \footnotemark[7].
+
+Solving the normal equations (\ref{eqn::normalEq}) for the
+coeffients is not ideal because the condition number of $A$ is the
+square of the condition number of
+$WM$  \cite{BigCheese}.     SVD can be used to solve the system with
+the condition number of $WM$.   That, however, requires interweaving
+the computation of the stencil with  the target application's
+equations.   Since we are doing this 
+analysis in the absence of a
+specific target stancil, one should interpret our condition number
+results as the square of the effective condition number that algorithm
+developers will encounter.
 
@@
 2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\
+\hline
 2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
@@
 2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
+\hline
 2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
@@
 2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
+\hline
 2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
@@
 2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
+\hline
 3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
@@
 3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
+\hline
 3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
@@
 3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
+\hline
 3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
@@
 3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
+\hline
 3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
@@
       We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$. 
+      function exponents $P^W$, and dimensionality $D$.   Keep in mind
+      that the effective condition number of the problem will be $(1/\sqrt(I))$.
     }
@@
 2 & 1 & 5 & 3 & 1.002428e+00 & 1.818655e-07 & 1.814249e-07 \\
+\hline
 2 & 2 & 1 & 3 & 2.714706e+00 & 6.503682e-07 & 2.395722e-07 \\ 
@@
 2 & 2 & 5 & 3 & 1.002428e+00 & 1.202042e-11 & 1.199130e-11 \\ 
+\hline
 2 & 3 & 1 & 3 & 2.714706e+00 & 2.057098e-10 & 7.577609e-11 \\ 
@@
 2 & 3 & 5 & 3 & 1.002428e+00 & 3.467198e-15 & 3.458798e-15 \\ 
+\hline
 2 & 4 & 1 & 3 & 2.714706e+00 & 1.027685e-15 & 3.785620e-16 \\   
@@
 2 & 4 & 5 & 3 & 1.003135e+00 & 5.995871e-19 & 5.977134e-19 \\ 
+\hline
 3 & 1 & 1 & 3 & 6.913890e+00 & 3.982271e-03 & 5.759812e-04 \\ 
@@
 3 & 1 & 5 & 3 & 1.003774e+00 & 1.047053e-07 & 1.043116e-07 \\ 
+\hline
 3 & 2 & 1 & 3 & 7.173851e+00 & 1.868373e-06 & 2.604421e-07 \\ 
@@
 3 & 2 & 5 & 3 & 1.003771e+00 & 6.965181e-12 & 6.939012e-12 \\ 
+\hline
 3 & 3 & 1 & 3 & 7.173852e+00 & 5.736142e-10 & 7.995902e-11 \\ 
@@
 3 & 3 & 5 & 3 & 1.003771e+00 & 1.609961e-15 & 1.603912e-15 \\ 
+\hline
 3 & 4 & 1 & 3 & 7.173852e+00 & 8.922302e-15 & 1.243725e-15 \\ 
@@
       function exponents $P^W$, and dimensionality $D$. 
+      Keep in mind
+      that the effective condition number of the problem will be $(1/\sqrt(I))$.
     }
@@
 2 & 1 & 5 & 3 & 2.314798e+00 & 1.256411e-09 & 5.427736e-10 \\ 
+\hline
 2 & 2 & 1 & 3 & 5.133178e+00 & 3.150951e-08 & 6.138402e-09 \\ 
@@
 2 & 2 & 5 & 3 & 1.100852e+00 & 1.071019e-14 & 9.729001e-15 \\ 
+\hline
 2 & 3 & 1 & 3 & 1.461766e+00 & 8.698889e-14 & 5.950944e-14 \\ 
@@
 2 & 3 & 5 & 3 & 1.924223e+00 & 3.044738e-18 & 1.582320e-18 \\ 
+\hline
 3 & 1 & 1 & 3 & 5.278376e+00 & 5.346601e-04 & 1.012926e-04 \\ 
@@
 3 & 1 & 5 & 3 & 2.594257e+00 & 5.017396e-10 & 1.934039e-10 \\ 
+\hline
 3 & 2 & 1 & 3 & 8.172169e+00 & 1.320095e-07 & 1.615355e-08 \\ 
@@
 3 & 2 & 5 & 3 & 4.508090e+00 & 4.439516e-14 & 9.847886e-15 \\ 
+\hline
 3 & 3 & 1 & 3 & 5.015663e+00 & 9.627815e-12 & 1.919550e-12 \\ 
@@
 3 & 3 & 5 & 3 & 5.346895e+00 & 4.774068e-17 & 8.928674e-18 \\ 
+\hline
 3 & 4 & 1 & 3 & 1.161979e+01 & 5.372252e-18 & 4.623365e-19 \\ 
@@
 increase in matrix arithmetic precision will not be sufficient.
-Since cell merger does not really help the
+Since cell merger does not help the
 problem, this lack of conditioning is not an issue with small cells.

### 2023-04-25 example/DomainDecomposition/EBCellMerge/hoeb_framework_test/framework_test.cpp

@@ -1,0 +1,110 @@
+#include <cmath>
+#include <cstdio>
+#include <iostream>
+
+#include "EBProto.H"
+#include "Chombo_EBLevelBoxData.H"
+#include "Chombo_LevelData.H"
+#include "Chombo_BaseFab.H"
+
+#include "Chombo_ParmParse.H"
+#include "Chombo_LoadBalance.H"
+#include "Chombo_ProtoInterface.H"
+#include "Chombo_BRMeshRefine.H"
+#include "Chombo_GeometryService.H"
+#include "Chombo_EBDictionary.H"
+#include "Chombo_EBChombo.H"
+#include "Chombo_EBCM_Graph.H"
+#include "Chombo_EBCM_HostLevelData.H"
+#include "Chombo_EBCM_Algorithm_Framework.H"
+#include "Chombo_EigenMatrix.H"
+#include "EBMultigrid.H"
+
+#include "DebugFunctions.H"
+#include "Hoeb_ExactSolutions.H"
+
+#include "Chombo_LAPACKMatrix.H"
+#include <iomanip>
+
+
+typedef Chombo4::Box                                   ch_box;
+typedef Chombo4::DisjointBoxLayout                     ch_dbl;
+typedef Chombo4::ProblemDomain                         ch_probdom;
+typedef Chombo4::DataIterator                          ch_dit;
+typedef Chombo4::IntVect                               ch_iv;
+typedef Chombo4::MayDay                                ch_mayday;
+//typedef Chombo4::LAPACKMatrix                          ch_mat;
+typedef Proto::RealVect                                pr_rv;
+typedef Proto::IndexTM<Real, DIM>                      pr_itm_r_dim;
+typedef Proto::IndexTM<int , DIM>                      pr_itm_i_dim;
+typedef Proto::IndexTM<Real, DIM-1>                    pr_itm_r_dmo;
+typedef Proto::IndexTM<int , DIM-1>                    pr_itm_i_dmo;
+typedef Proto::BaseIF                                  pr_baseif;
+typedef ch_eigen::Matrix                               eigen_mat;
+
+/****/
+
+int main(int a_argc, char* a_argv[])
+{
+#ifdef CH_MPI
+  MPI_Init(&a_argc, &a_argv);
+  Chombo4::pout() << "MPI INIT called" << std::endl;
+#endif
+
+  using Chombo4::pout;
+  CH_TIMER_SETFILE("ebcm_framework_time_table");
+  {
+    
+    if (a_argc < 2)
[…]

### 2023-04-25 src/EBCM/Chombo_EBCM_Algorithm_Framework.H

@@ -1,0 +1,460 @@
+#ifndef _EBCM_ALGO_DEV_FRAMEWORK__
+#define _EBCM_ALGO_DEV_FRAMEWORK__
+#include <cmath>
+#include <cstdio>
+#include <iostream>
+
+#include "EBProto.H"
+#include "Chombo_EBLevelBoxData.H"
+#include "Chombo_LevelData.H"
+#include "Chombo_BaseFab.H"
+
+#include "Chombo_ParmParse.H"
+#include "Chombo_LoadBalance.H"
+#include "Chombo_ProtoInterface.H"
+#include "Chombo_BRMeshRefine.H"
+#include "Chombo_GeometryService.H"
+#include "Chombo_EBDictionary.H"
+#include "Chombo_EBChombo.H"
+#include "Chombo_EBCM_Graph.H"
+#include "Chombo_EBCM_HostLevelData.H"
+#include "Chombo_EigenMatrix.H"
+
+#include "Chombo_LAPACKMatrix.H"
+#include <iomanip>
+
+namespace EBCM
+{
+  typedef Chombo4::Box                                   ch_box;
+  typedef Chombo4::DisjointBoxLayout                     ch_dbl;
+  typedef Chombo4::ProblemDomain                         ch_probdom;
+  typedef Chombo4::DataIterator                          ch_dit;
+  typedef Chombo4::IntVect                               ch_iv;
+  typedef Chombo4::MayDay                                ch_mayday;
+//typedef Chombo4::LAPACKMatrix                          ch_mat;
+  typedef Proto::RealVect                                pr_rv;
+  typedef Proto::IndexTM<Real, DIM>                      pr_itm_r_dim;
+  typedef Proto::IndexTM<int , DIM>                      pr_itm_i_dim;
+  typedef Proto::IndexTM<Real, DIM-1>                    pr_itm_r_dmo;
+  typedef Proto::IndexTM<int , DIM-1>                    pr_itm_i_dmo;
+  typedef Proto::BaseIF                                  pr_baseif;
+  typedef ch_eigen::Matrix                               eigen_mat;
+///
+/**
+   Purely functional framework for doing tests in EBCM.
+   The framework has no data but lots of common  typedefs.
+   All functions are static.
+*/
+  template <int ebcm_order>
+  class EBCM_Framework
+  {
+  public:
+    EBCM_Framework()
+    {}    
+  
+
+  
[…]

### 2023-04-26 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
this is the version I am submitting

@@
 \newcommand{\face}{\mathcal{F}}
+\newcommand{\cali}{\mathcal{I}}
+\newcommand{\calc}{\mathcal{C}}
 \newcommand{\zerobold}{{\bf{0}}}
@@
 
-Embedded boundary (EB) grids are formed when one passes an  surface
+Embedded boundary (EB) grids are formed when one passes a surface
 through a Cartesian mesh.    For sufficiently complex geomtries, these methods
@@
 In the current context, we form the cutting surface as the zero
-surface of a function  of space $I(\xbold)$, $\xbold \in R^D$.
+surface of an implicit function  of space
+$I(\xbold) = 0, \xbold \in R^D$.
 For smooth ($I$),  moments can be generated to any
@@
 eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
-$\{ \lambda_{i}\}$, the inverse of the condition number $I_i$ is given by
+$\{ \lambda_{i}\}$, the inverse of the condition number $\_i$ is given by
 \begin{equation*}
-  I_i = \frac{\lambda_i|_{min}}{\lambda_i|_{max}},
+  \cali_i = \frac{|\lambda_i|_{min}}{|\lambda_i|_{max}},
 \end{equation*}
@@
 Solving the normal equations (\ref{eqn::normalEq}) for the
-coeffients is not ideal because the condition number of $A$ is the
-square of the condition number of
-$WM$  \cite{BigCheese}.     SVD can be used to solve the system with
-the condition number of $WM$.   That, however, requires interweaving
-the computation of the stencil with  the target application's
-equations.   Since we are doing this 
-analysis in the absence of a
-specific target stancil, one should interpret our condition number
-results as the square of the effective condition number that algorithm
-developers will encounter.
+coeffients is not ideal because the $\calc_A$, condition number of $A$ is the
+square of the $\calc_{WM}$,  condition number of $WM$  \cite{BigCheese}.  
+\begin{equation}
+  \calc_A = \calc^2_{WM}
+\end{equation}  
+SVD can be used to solve the system with the condition number of
+$\calc_{WM}$.  That, however, requires interweaving the computation of
+the stencil with the target application's equations.  Since we are
+doing this analysis independent of a specific target stancil, one should
+interpret our condition number results as the square of the effective
+condition number that algorithm developers will encounter.
 
-First we  measure   an uncut, Cartesian mesh to
+First we  measure   an uncut Cartesian mesh to
 provide a baseline without the complications involved with cut cells.
@@
 
-\subsection{All Regular geometry}
+\section{Test description}
+\label{sec::eb}
 
@@
 $D$-dimensional Cartesian geometry wherein all cells are uncut.
-Figure \ref{fig::T3W3} shows all values of $I$ for $D=2$, $I$ with
+Figure \ref{fig::T3W3} shows all values of $\cali$ for $D=2$, $\cali$ with
 $P_w = P_T = 3$.  Table \ref{tab::worst_all_reg_inv_conv} shows the
@@
 $P_w$ and $P_T$.
+
+Our next  grid is a Cartesian grid cut  by a sphere (or a circle in two
+dimensions). The computational domain is the unit cube.   The cutting
+sphere center is the center of the cube.   The radius of the cutting
+sphere is 0.45.  The grid moments are generated using the algorithm
+specified in \cite{Schwartz2015}.  The moments are accurate to
+order $h^{P^T}$.
+
+If we use grid volumes at this point, the volume fraction
+\begin{equation*}
+\kappa_\ibold \equiv V_\ibold/h^D 
+\end{equation*}
+can be arbitrarily small ($ 0 < \kappa <= 1$).
+
+We can also choose to
+merge small volumes with larger neighbors without formal loss of
+accuracy. The simple merger we use is described in
+described in appendix \ref{appendix::merger}.
+When merged using this algorithm, $\kappa$ can be larger than $2^D$.
+
+Without using cell merger, the volume map in two dimensions is shown
+in figure \ref{fig::unmerged2dmap}.   With cell merger, that same map
+becomes the grid shown in figure{fig::unmerged2dmap}.
+Tables \ref{tab::worst_unmerged_inv_conv} and
+\ref{tab::worst_merged_inv_conv}
+show the worst $\cali$ for the unmerged and merged  grids
+respectively while varying $P_w$ and $P_T$.
 
@@
 \caption
-    {
-      $I$ (inverse of the condition number for matrix $A$ for a $32^2$
-      uncut grid where $P_w = P_T = 3$.
+    {   Values of of the inverse of the condition number
+      $\cali_A = 1/\calc_A$
+      for an uncut Cartesian $32^2$
+      grid where $P_w = P_T = 3$.
+      Keep in mind that $\calc_A = \calc^2_{WM}$.
     }
@@
 \begin{tabular}{|cccc|ccc|} \hline
-$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
 \hline
@@
       We show the lowest value of
-      $I$ for an entire Cartesian grid of size $32^D$.
+      $\cali$ for an entire Cartesian grid of size $32^D$.
       We vary Taylor power $P^T$, weighting
       function exponents $P^W$, and dimensionality $D$.   Keep in mind
-      that the effective condition number of the problem will be $(1/\sqrt(I))$.
+      that the effective condition number of the problem will be 
+      $C_{WM} = (1/\sqrt(\cali))$.
     }
@@
 \end{small}
-
-\section{Cut Cell Geometry}
-\label{sec::eb}
-
-Our next  grid is a Cartesian grid cut  by a sphere (or a circle in two
-dimensions). The computational domain is the unit cube.   The cutting
-sphere center is the center of the cube.   The radius of the cutting
-sphere is 0.45.  The grid moments are generated using the algorithm
-specified in \cite{Schwartz2015}.  The moments are accurate to
-order $h^{P^T}$.
-
-If we use grid volumes at this point, the volume fraction
-\begin{equation*}
-\kappa_\ibold \equiv V_\ibold/h^D 
-\end{equation*}
-can be arbitrarily small ($ 0 < \kappa <= 1$).   We can also choose to
-merge small volumes with larger neighbors without formal loss of
-accuracy. The simple merger we use is described in
-described in appendix \ref{appendix::merger}.
-When merged using this algorithm, $\kappa$ can be larger than $2^D$.
-
-Without using cell merger, the volume map in two dimensions is shown
-in figure \ref{fig::unmerged2dmap}.   With cell merger, that same map
-becomes the grid shown in figure{fig::unmerged2dmap}.
-Tables \ref{tab::worst_unmerged_inv_conv} and
-\ref{tab::worst_merged_inv_conv}
-show the worst condition number for the unmerged and merged  grids
-respectively while varying $P_w$ and $P_T$.   Merger does not seem to
-help substantially with this issue.
 
@@
 \begin{tabular}{|cccc|ccc|} \hline
-$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
+$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
   \hline
@@
       We show the lowest value of
-      $I$ for an entire Cartesian grid of size $32^D$.
+      $\cali$ for an entire Cartesian grid of size $32^D$.
       Volumes are  formed by a sphere (or circle in 2D) cutting the
@@
       Keep in mind
-      that the effective condition number of the problem will be $(1/\sqrt(I))$.
+      that the effective condition number of the problem will be 
+      $C_{WM} = (1/\sqrt(\cali))$.
     }
@@
       Keep in mind
-      that the effective condition number of the problem will be $(1/\sqrt(I))$.
+      that the effective condition number of the problem will be $(1/\sqrt(\cali))$.
     }
@@
 $P_T$, even the worst condition number in a given grid can be quite
-reasonable. With more aggressive choices of $P_T$, $I$ can be very
+reasonable. With more aggressive choices of $P_T$, $\cali$ can be very
 small.  The data also

### 2023-04-26 example/DomainDecomposition/EBCellMerge/hoeb_petsc_test/_doc/paper.tex
this is the version I am submitting

--- 2023-04-25 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
@@
 
-\newcommand{\Abold}{{\bf A}}
-\newcommand{\abold}{{\bf a}}
-\newcommand{\bbold}{{\bf b}}
-\newcommand{\cbold}{{\bf c}}
-\newcommand{\dbold}{{\bf d}}
-\newcommand{\ebold}{{\bf e}}
-\newcommand{\fbold}{{\bf f}}
-\newcommand{\Fbold}{{\bf F}}
-\newcommand{\gbold}{{\bf g}}
-\newcommand{\hbold}{{\bf h}}
-\newcommand{\ibold}{{\bf i}}
-\newcommand{\jbold}{{\bf j}}
-\newcommand{\kbold}{{\bf k}}
-\newcommand{\lbold}{{\bf l}}
-\newcommand{\mbold}{{\bf m}}
-\newcommand{\Mbold}{{\bf M}}
-\newcommand{\nbold}{{\bf n}}
-\newcommand{\obold}{{\bf o}}
-\newcommand{\pbold}{{\bf p}}
-\newcommand{\qbold}{{\bf q}}
-\newcommand{\rbold}{{\bf r}}
-\newcommand{\sbold}{{\bf s}}
-\newcommand{\tbold}{{\bf t}}
-\newcommand{\ubold}{{\bf u}}
-\newcommand{\vbold}{{\bf v}}
-\newcommand{\wbold}{{\bf w}}
-\newcommand{\xbold}{{\bf x}}
-\newcommand{\ybold}{{\bf y}}
-\newcommand{\zbold}{{\bf z}}
-\newcommand{\bigzbold}{{\bf Z}}
-\newcommand{\xspace}{\hspace{2 mm}}
-
-\newcommand{\ahat}{{\hat a}}
-\newcommand{\bhat}{{\hat b}}
-\newcommand{\chat}{{\hat c}}
-\newcommand{\dhat}{{\hat d}}
-\newcommand{\ehat}{{\hat e}}
-\newcommand{\fhat}{{\hat f}}
-\newcommand{\ghat}{{\hat g}}
-\newcommand{\hhat}{{\hat h}}
-\newcommand{\ihat}{{\hat i}}
-\newcommand{\jhat}{{\hat j}}
-\newcommand{\khat}{{\hat k}}
-\newcommand{\lhat}{{\hat l}}
-\newcommand{\mhat}{{\hat m}}
-\newcommand{\nhat}{{\hat n}}
-\newcommand{\ohat}{{\hat o}}
-\newcommand{\phat}{{\hat p}}
-\newcommand{\qhat}{{\hat q}}
-\newcommand{\rhat}{{\hat r}}
-\newcommand{\shat}{{\hat s}}
-\newcommand{\that}{{\hat t}}
-\newcommand{\uhat}{{\hat u}}
-\newcommand{\vhat}{{\hat v}}
-\newcommand{\what}{{\hat w}}
-\newcommand{\xhat}{{\hat x}}
-\newcommand{\yhat}{{\hat y}}
-\newcommand{\zhat}{{\hat z}}
-
-\newcommand{\abar}{{\bar {\bf a}}}
-\newcommand{\bbar}{{\bar {\bf b}}}
-\newcommand{\cbar}{{\bar {\bf c}}}
-\newcommand{\dbar}{{\bar {\bf d}}}
-\newcommand{\ebar}{{\bar {\bf e}}}
-\newcommand{\fbar}{{\bar {\bf f}}}
-\newcommand{\gbar}{{\bar {\bf g}}}
-%\newcommand{\hbar}{{\bar {\bf h}}}
-\newcommand{\ibar}{{\bar {\bf i}}}
-\newcommand{\jbar}{{\bar {\bf j}}}
-\newcommand{\kbar}{{\bar {\bf k}}}
-\newcommand{\lbar}{{\bar {\bf l}}}
-\newcommand{\mbar}{{\bar {\bf m}}}
-\newcommand{\nbar}{{\bar {\bf n}}}
-\newcommand{\obar}{{\bar {\bf o}}}
-\newcommand{\pbar}{{\bar {\bf p}}}
-\newcommand{\qbar}{{\bar {\bf q}}}
-\newcommand{\rbar}{{\bar {\bf r}}}
-\newcommand{\sbar}{{\bar {\bf s}}}
-\newcommand{\tbar}{{\bar {\bf t}}}
-\newcommand{\ubar}{{\bar {\bf u}}}
-\newcommand{\vbar}{{\bar {\bf v}}}
-\newcommand{\wbar}{{\bar {\bf w}}}
-\newcommand{\xbar}{{\bar {\bf x}}}
-\newcommand{\ybar}{{\bar {\bf y}}}
-\newcommand{\zbar}{{\bar {\bf z}}}
-
-\newcommand{\dx}{{h}}
-\newcommand{\nph}{{n + \frac{1}{2}}}
-\newcommand{\iph}{{\ibold + \frac{1}{2}\ebold_d}}
-\newcommand{\ipmh}{{\ibold \pm \frac{1}{2}\ebold_d}}
-\newcommand{\imh}{{\ibold - \frac{1}{2}\ebold_d}}
-
-\newcommand{\half}{\frac{1}{2}}
-%\newcommand{\Fbold}{\mathbf{F}}
-%\newcommand{\iphed}{{\ibold+\half\ebold^d}}
-\newcommand{\deriv}{\partial}
-\newcommand{\area}{\mathcal{A}}
-\newcommand{\R}[1]{\mathbb{R}^{#1}}
-\newcommand{\cf}{{\scriptscriptstyle F}}
-\newcommand{\cn}{{\scriptscriptstyle N}}
-\newcommand{\sEB}{{\scriptscriptstyle EB}}
-\renewcommand{\vec}[1]{\mathbf{#1}} % Vector (bold)
-\newcommand{\tens}[1]{\mathbf{#1}} % Tensor (bold)
-\newcommand{\mat}[1]{\mathbf{#1}} % Matrix (bold)
-\newcommand{\hatvec}[1]{\hat{\vec{#1}}} % Vector with a hat (bold)
-\newcommand{\ddt}[1]{\frac{\partial #1}{\partial t}} % partial d/dt
-\newcommand{\DDt}[1]{\frac{\text{d}#1}{\text{d}t}} % "total" d/dt
-\newcommand{\ddr}[1]{\frac{\partial #1}{\partial r}} % d/dr
-\newcommand{\ddx}[1]{\frac{\partial #1}{\partial x}} % d/dx
-\newcommand{\ddy}[1]{\frac{\partial #1}{\partial y}} % d/dy
-\newcommand{\ddz}[1]{\frac{\partial #1}{\partial y}} % d/dz
-\newcommand{\ddxi}[1]{\frac{\partial #1}{\partial x_i}} % d/dx_i
-\newcommand{\diverg}[1]{\nabla\cdot#1} % Divergence operator
-\newcommand{\curl}[1]{\nabla \times #1} % Curl operator
-\newcommand{\dOmega}{\text{d}\Omega} % Volume differential (Omega style)
-\newcommand{\dV}{\text{d}V} % Volume differential
-\newcommand{\dA}{\text{d}A} % Area differential
-\newcommand{\labelEq}[1]{\label{eq:#1}\hbox{\tt #1 \quad}} % Use this to label an equation.
-\newcommand{\refEq}[1]{(\ref{eq:#1})}   % Use this to reference an equation.
-\newcommand{\labelSec}[1]{\label{sec:#1}} % Use this to label a section.
-\newcommand{\refSec}[1]{\S\ref{sec:#1}} % Use this to reference a section.
-\newcommand{\labelChap}[1]{\label{chap:#1}} % Use this to label a chapter.
-\newcommand{\refChap}[1]{Chapter \ref{chap:#1}} % Use this to reference a chapter.
-\newcommand{\labelApp}[1]{\label{app:#1}} % Use this to label an appendix.
-\newcommand{\refApp}[1]{Appendix \ref{app:#1}} % Use this to reference an appendix.
-\newcommand{\ib}{{\bf{i}}}    % bold italic i
-\newcommand{\jb}{{\bf{j}}}    % bold italic j
-\newcommand{\kb}{{\bf{k}}}    % bold italic k
-\newcommand{\lb}{{\bf{l}}}    % bold italic l
-\newcommand{\mb}{{\bf{m}}}    % bold italic m
-\newcommand{\ub}{{\bf{u}}}    % bold italic u
-\newcommand{\xb}{{\bf{x}}}    % bold italic x
-\newcommand{\vb}{{\bf{v}}}    % (bold italic) VoF index
-\newcommand{\fb}{{\bf{f}}}    % (bold italic) face index
-\newcommand{\pb}{{\bf{p}}}    % (bold italic) multi-index p
-\newcommand{\qb}{{\bf{q}}}    % (bold italic) multi-index q
-\newcommand{\ebd}{{\bf{e}^d}}
-\newcommand{\normal}[1]{\vec{n}_{#1}} % Outward normal.
-\newcommand{\order}[1]{\mathcal{O}(#1)} % Order notation
-
-\newcommand{\ed}{{\bf{e}_d}}
-\newcommand{\Zbold}{{\bf{0}}}
-\newcommand{\unitV}{\mathds{1}}
-\newcommand{\eb}{\text{EB}}
-\newcommand{\EB}{\text{EB}}
-\newcommand{\vol}{\mathcal{V}}
-\newcommand{\face}{\mathcal{F}}
-\newcommand{\zerobold}{{\bf{0}}}
-\newcommand{\xz}{{\bf{x}_0}}
-
-\newcommand{\Dim}{D}
-\newcommand{\dif}{\mathrm{d}}
-\newcommand{\dt}{{\Delta t}}
-\newcommand{\avg}[1]{\overline{#1}}
-\newcommand{\avgI}[1]{\overline{#1}_{\ibold}}
-\newcommand{\imhed}{{\ibold+\frac{1}{2}\ebold_d}}
-\newcommand{\ipmhj}{{\ibold\pm\frac{1}{2}\ebold_d}}
-\newcommand{\iphj}{{\ibold+\frac{1}{2}\ebold_d}}
-\newcommand{\imhj}{{\ibold-\frac{1}{2}\ebold_d}}
-
-\newcommand{\ipfed}[1]{\ibold+\frac{#1}{2}\ebold_d}
-\newcommand{\imfed}[1]{\ibold-\frac{#1}{2}\ebold_d}
-\newcommand{\ipmfed}[1]{\ibold\pm\frac{#1}{2}\ebold_d}
-\newcommand{\eq}[1]{(\ref{#1})}
-
-\newcommand{\nref}{n_{\text{ref}}}
-\newcommand{\phio}{\phi^{\circ}}
+\input{abbrev.tex}
 
@@
 
-\title{Polynomial expansions of finite volume data in a cut cell context}
+\title{Elliptic operator stability and small cells on  finite volume grids}
 \author{N. Overton-Katz \footnotemark[1]
@@
 
-  We discuss the mechanics of forming stable local polynomial
+  Numerical stability for elliptic operators is well understood.  To
+  be numerically stable, a numerical operator for an elliptic equation
+  cannot have non-zero positive real eigenvalues.  We explore a family
+  of elliptic operators and attempt to define the boundaries of
+  stability for this family of algorithms.
+
+\end{abstract}
+
+\section{Introduction}
+Embedded boundary (EB) grids are formed when one passes an  surface
+through a Cartesian mesh.    For sufficiently complex geomtries, these methods
+are very attactive because grid generation is a solved problem
+\cite{MillerTrebotich2012}.
+
+Devendran, et al. \cite{Devendran2017} 
+  real component of an operator eigenvalue
+  Using the basic framework of the elliptic operator in Devendran, et al.
   expansions of finite volume data in the context of cut cell grids.
@@
   manage these solvability issues with careful algorithm choices.
-
-\end{abstract}
-
-\section{Introduction}
-
-Embedded boundary (EB) grids are formed when one passes an  surface
-through a Cartesian mesh.    For sufficiently complex geomtries, these methods
-are very attactive because grid generation is a solved problem
-and not computationally overwhelming even in a moving-boundary context
-\cite{MillerTrebotich2012}.
 

### 2023-04-27 example/HO-WLS/common/EBPetscSolver.H
Splitting the high-order wls work into its own application. Common floating point info as part of Real

@@ -1,1181 +1,0 @@
-#ifdef CH_LANG_CC
-/*
- *      _______              __
- *     / ___/ /  ___  __ _  / /  ___
- *    / /__/ _ \/ _ \/  V \/ _ \/ _ \
- *    \___/_//_/\___/_/_/_/_.__/\___/
- *    Please refer to Copyright.txt, in Chombo's root directory.
- */
-#endif
-
-#ifndef _EBPoissonPetscSolver_H_
-#define _EBPoissonPetscSolver_H_
-
-#ifdef CH_USE_PETSC
-#include "petsc.h"
-#include "petscerror.h"
-#include "petscmat.h"
-#include "petscvec.h"
-#include "petscksp.h"
-#include "petscviewer.h"
-#include "Chombo_EBChombo.H"
-#include "Chombo_EBLevelBoxData.H"
-#include "hoeb/Proto_EBDomainBC.H"
-
-/****/
-//lph comes in holding beta*div(F)--leaves holding alpha phi + beta div(F)
-PROTO_KERNEL_START
-unsigned int  addAlphaPhiPtF(int a_pt[DIM],
-                             Var<Real, 1>     a_lph,
-                             Var<Real, 1>     a_phi,
-                             Var<Real, 1>     a_kap,
-                             Real    a_alpha,
-                             Real    a_beta)
-{
-  //kappa and beta are already in lph
-  //kappa because we did not divide by kappa
-  //beta was sent in to ebstencil::apply
-  //begin debug
-  int ideb = 6;
-  int jdeb = 16;
-  int istop = 0;
-  if ((a_pt[0] == ideb) && (a_pt[1]==jdeb))
-  {
-    istop = 1;
-  }
-
-  Real kappdiv = a_lph(0);
-  Real bkdivF  = a_beta*kappdiv;
-  Real phival  = a_phi(0);
-  Real kapval  = a_kap(0);
-  a_lph(0) = a_alpha*phival*kapval + bkdivF;
-  return 0;
-}
-PROTO_KERNEL_END(addAlphaPhiPtF, addAlphaPhiPt)
-PROTO_KERNEL_START
-unsigned int  addAlphaPhiF(Var<Real, 1>     a_lph,
-                           Var<Real, 1>     a_phi,
-                           Var<Real, 1>     a_kap,
-                           Real    a_alpha,
-                           Real    a_beta)
-{
-  //kappa and beta are already in lph
-  //kappa because we did not divide by kappa
-  //beta was sent in to ebstencil::apply
[…]

### 2023-04-27 src/BaseTools/Chombo_REAL.H

@@ -11,6 +11,10 @@
 #ifndef _Chombo_REAL_H_
 #define _Chombo_REAL_H_
 
+#include <cmath>
+#include <limits>
+#include <algorithm>
+
 #  undef  CH_USE_FLOAT
 #  undef  CH_USE_DOUBLE
 #  define CH_USE_DOUBLE 1
@@ -20,5 +24,52 @@
 #    define CH_BADVAL           (Real)1.0e99
 
 typedef double Real;
+
+// define common floating point limits
+const static Real REAL_MIN = std::numeric_limits<Real>::min();
+const static Real REAL_MAX = std::numeric_limits<Real>::max();
+const static Real REAL_LOW = std::numeric_limits<Real>::lowest();
+const static Real REAL_EPS = std::numeric_limits<Real>::epsilon();
+const static Real REAL_INF = std::numeric_limits<Real>::infinity();
+// A reasonable floating point tolerance for general applications
+// about 3/4 of the available digits (1e-12 for double, 1e-6 for float)
+const static Real REAL_TOL = std::pow(REAL_EPS, 3./4.);
+
+// Does a == b within floating point tolerance?
+inline bool
+approxEqual(Real a, Real b, Real tol=REAL_TOL)
+{
+    Real absA = std::abs(a);
+    Real absB = std::abs(b);
+    Real diff = std::abs(a - b);
+
+    if (a == b) // shortcut for exact equality
+      {
+        return true;
+      }
+    else if (a == 0 || b == 0 || diff < REAL_LOW)
+      { // handle cases where one or both numbers are close to zero or
+        // the difference between the two numbers is very small
+        return diff < (tol * REAL_LOW);
+      }
+    else // use relative error
+      {
+        return diff < (tol * std::min((absA + absB), REAL_MAX));
+      }
+}
+
+// Does c = a + b have a meaningful contribution from both a and b?
+// Default tolerance is the minimum visible value
+inline bool
+isSignificant(Real a, Real b, Real tol=REAL_EPS) {
+    Real abs_a = std::abs(a);
+    Real abs_b = std::abs(b);
+
+    Real minVal = std::min(abs_a, abs_b);
+    Real maxVal = std::max(abs_a, abs_b);
+
+    return minVal > (tol*maxVal);
+}
+
 
 #endif

### 2023-04-27 src/EBProto/EBProto.H

@@ -113,4 +113,4 @@ namespace Proto
 #include "Proto_EBHostData.H"
 #include "Proto_EBHostFluxData.H"
 
-#include "hoeb/Proto_EBStencilHO.H"
+//#include "hoeb/Proto_EBStencilHO.H"

### 2023-04-27 src/EBProto/Proto_EBExactSolutions.H

@@ -1806,7 +1806,7 @@ public:
             // p = 0
             if((a_p[0] == 0)&&(a_p[1] == 0))
               {
-                retval *= 2*m_lambda+3-2*m_vel[0]*a2/r2;
+                retval *= (2*m_lambda+3-2*a2/r2)*m_vel[0];
               }
             //p = 1
             else if((a_p[0] == 1)&&(a_p[1] == 0))
@@ -1871,7 +1871,7 @@ public:
             // beyond
             else
               {
-                //Chombo4::MayDay::Error("ran out of deriv cases");
+                Chombo4::MayDay::Error("ran out of deriv cases");
                 retval = 0;
               }
           }
@@ -1879,19 +1879,19 @@ public:
           {
             if((a_p[0] == 0)&&(a_p[1] == 0))
               {
-                retval *= m_vel[1]*xi[0]*xi[1]/a2;
+                retval *= m_vel[0]*xi[0]*xi[1]/a2;
               }
             else if((a_p[0] == 1)&&(a_p[1] == 0))
               {
-                retval *= m_vel[1]*xi[1]/a2;
+                retval *= m_vel[0]*xi[1]/a2;
               }
             else if((a_p[0] == 0)&&(a_p[1] == 1))
               {
-                retval *= m_vel[1]*xi[0]/a2;
+                retval *= m_vel[0]*xi[0]/a2;
               }
             else if((a_p[0] == 1)&&(a_p[1] == 1))
               {
-                retval *= m_vel[1]/a2;
+                retval *= m_vel[0]/a2;
               }
             else
               {

### 2023-04-27 src/EBProto/Proto_EBStencil.H

@@ -19,7 +19,7 @@
 #include "base/Proto_Stencil.H"
 
 //for HOEB
-#include "hoeb/Proto_EBStencilHO.H"
+//#include "hoeb/Proto_EBStencilHO.H"
 
 using std::shared_ptr;
 using std::vector;
@@ -38,7 +38,7 @@ namespace Proto
 
   public:
     typedef EBStencilArchive<srcCenter, dstCenter, order, data_t> archive_t;
-    typedef EBStencilHO<srcCenter, dstCenter, order, data_t> ho_t;
+    //typedef EBStencilHO<srcCenter, dstCenter, order, data_t> ho_t;
 
     typedef IndexedMoments<DIM  , order> IndMomDIM;
     typedef IndexedMoments<DIM-1, order> IndMomSDMinOne;

### 2023-04-27 src/EBProto/hoeb/Proto_EBStencilHO.H

@@ -1,232 +1,0 @@
-#ifndef _Proto_EBStencilHO_H_
-#define _Proto_EBStencilHO_H_
-
-#include "EBProto.H"
-#include "Proto_EBExactSolutions.H"
-#include "Proto_MomentHolder.H"
-//#include "Proto_Normalizor.H"
-#include "Proto_EBDomainBC.H"
-#include "Chombo_ParmParse.H"
-
-// Call these to generate a order-variable stencil for the specified operator
-// These in general no longer conform to the dictionary approach, since it is too restrictive, especially with regards to high-order BC treatment, and multi-component operators.
-//
-// The regular apply content is generally not supported
-//
-// Ideally this will come back to the dictionary concept eventually
-
-namespace Proto
-{
-  template <CENTERING srcCenter, CENTERING dstCenter, int order, typename data_t>
-  class EBStencilHO
-  {
-  public:
-    EBStencilHO() {}
-    ~EBStencilHO() {}
-
-    typedef IndexedMoments<DIM  , order> IndMomDIM;
-    typedef IndexedMoments<DIM-1, order> IndMomSDMinOne;
-    typedef MomentIterator<DIM  , order> MomItDIM;
-    typedef MomentIterator<DIM-1, order> MomItSDMinOne;
-    typedef HostIrregData<CELL,     IndMomDIM  , 1>  VoluData;
-    typedef HostIrregData<BOUNDARY, IndMomDIM  , 1>  EBFaData;
-    typedef HostIrregData<XFACE, IndMomSDMinOne, 1>  XFacData;
-    typedef HostIrregData<YFACE, IndMomSDMinOne, 1>  YFacData;
-    typedef HostIrregData<ZFACE, IndMomSDMinOne, 1>  ZFacData;
-    typedef HostIrregData<CELL,      IndMomDIM , 1>  EBNormalData;
-
-  };
-
-  ///
-  /**
-   * EBStencil for high-order methods class. First implementation will get you
-   * the corrresponding stencil for Poisson operator.
-   */
-  template <int order>
-  class EBStencilHO<CELL, CELL, order, Real>
-  {
-  public:
-    typedef IndexedMoments<DIM  , order> IndMomDIM;
-    typedef IndexedMoments<DIM-1, order> IndMomSDMinOne;
-    typedef MomentIterator<DIM  , order> MomItDIM;
-    typedef MomentIterator<DIM-1, order> MomItSDMinOne;
[…]

### 2023-04-27 src/EBProto/hoeb/Proto_WLSCell.H

@@ -1,979 +1,0 @@
-#ifndef _Proto_WLSCell_H_
-#define _Proto_WLSCell_H_
-
-#include "Chombo_ProtoInterface.H"
-#include "Chombo_LAPACKMatrix.H"
-#include "EBProto.H"
-#include "Proto_EBExactSolutions.H"
-#include "Proto_MomentHolder.H"
-#include "Proto_WLSneighbors.H"
-
-namespace Proto
-{
-
-  /// A small class to hold parameters about how a stencil should be formed
-  /// This exists for the meta data we need about stencil creation, and as an interface
-  class StencilAttributes
-  {
-  public:
-    void
-    readInputs(const std::string a_PPprefix)
-      {
-        // FIXME use prefix, and better names
-        ParmParse pp;
-        pp.get("radius", m_radius);
-        pp.get("powerE", m_weightPower);
-      }
-
-    void
-    defaultStencilAttributes(const int a_order)
-      {
-        // defaults are an over-estimate but sufficiently large, and the minimal reasonable weighting
-        m_radius = a_order; // how many cells out to grab
-        m_weightPower = -(a_order+1); // WLS weighting power dist^P
-      }
-
-    StencilAttributes()
-      {
-        readInputs("");
-      }
-
-    StencilAttributes(const int a_order)
-      {
-        defaultStencilAttributes(a_order);
-      }
-
-    inline int radius() const
-      { return m_radius;}
-
-    inline int weightPower() const
-      { return m_weightPower;}
-
-    // inline int neighListType() const
-    //   { return m_neighListType;}
-
-    inline Real smallCellTol() const
-      { return m_smallCellTol;}
-
-  private:
-    /// Defaults are generally invalid, should be set in the constructor
-    // How many cells around the stencil center to grab
-    int m_radius = 0;
-    // The weighting power to use
-    int m_weightPower = 0;
-    // at what point do small cells stop being relevant
-    Real m_smallCellTol = 1e-11; // FIXME real aware
-  };
-
-  template<int order> 
-  class BaseExactVelocity // FIXME a subset of exact solutions, don't reinvent them here
-  {
-  public:
-    typedef IndexedMoments<DIM  , order> IndMomDIM;
-    typedef IndexedMoments<DIM-1, order> IndMomSDMinOne;
-    typedef MomentIterator<DIM  , order> MomItDIM;
-
-    bool locationBased() const
-    {
-      return m_locationBased;
-    }
-  
[…]

### 2023-04-27 src/EBProto/hoeb/Proto_WLSCellImplem.H

@@ -1,2757 +1,0 @@
-#ifndef _Proto_WLSCellImplem_H_
-#define _Proto_WLSCellImplem_H_
-
-namespace Proto
-{
-  //Compute the Moments Matrix
-  template<CENTERING cent, int order>
-  void
-  BaseWLSFlux<cent, order>::
-  getShiftedMomentMatrix(Chombo4::LAPACKMatrix    & a_Mvol,
-                         RealVect               & a_faceLoc,
-                         Real                     a_dx,
-                         const Neighbors<order> & a_neigh,
-                         string                   a_ebbcName,
-                         string                   a_dombcName[2*DIM]) const
-  {
-    PR_TIME("getShiftedMomentMatrix");
-    using Chombo4::pout;
-
-    int nvol = a_neigh.sizeVols();
-    int nfac = a_neigh.sizeFaces();
-    int nebf = a_neigh.sizeEB();
-
-    int nrows = a_neigh.size();
-    MomentIterator<DIM, order> momit;
-    a_Mvol.define(nrows, momit.size());
-    CH_assert(nrows >= momit.size());
-
-    if (m_verbose) 
-    {
-      pout() << "Size Moments matrix "<< nrows << " " << momit.size() << std::endl;
-      pout() << "With nvol + nfac + nebf " << nvol << " " << nfac << " " << nebf << std::endl;
-      pout() << "Moments matrix" << endl;
-    }
-
-    // Start of the volume block matrix (row, column)
-    IndexTM<int, 2> start = IndexTM<int, 2>{0, 0};
-    // fill in the sub-matrix
-    this->getShiftedMomentMatrixVolumes(a_Mvol,
-                                        a_faceLoc,
-                                        a_dx,
-                                        a_neigh,
-                                        start);
-
-    // Start of the face block matrix
-    start = IndexTM<int, 2>{nvol, 0};
-    // fill in the sub-matrix
-    this->getShiftedMomentMatrixRegFaces(a_Mvol,
-                                         a_faceLoc,
-                                         a_dx,
-                                         a_neigh,
-                                         a_dombcName,
-                                         start);
-
-    // Start of the EB block matrix
-    start = IndexTM<int, 2>{nvol+nfac, 0};
-    // fill in the sub-matrix
-    this->getShiftedMomentMatrixEBFaces(a_Mvol,
-                                        a_faceLoc,
[…]

### 2023-04-27 src/EBProto/hoeb/Proto_WLSStencilImplem.H

@@ -1,1704 +1,0 @@
-#ifndef _Proto_WLSStencilImplem_H_
-#define _Proto_WLSStencilImplem_H_
-
-namespace Proto
-{
-  // Get a single face flux stencil at a face by a distance weighted average between
-  // two cell-centered flux stencils states computed by the neighbor cells sharing the face
-  // This was originally designed for the Laplacian stencil, but is generally applicable
-  template <int order>
-  void
-  WLSStencil<order>::
-  getDistanceWeightedFluxAvgCoeffs(
-    Real&    a_loSideWeight,
-    Real&    a_hiSideWeight,
-    const RealVect        a_faceCentroid,
-    const EBIndex<CELL> & a_voflo,
-    const EBIndex<CELL> & a_vofhi,
-    const int             a_dir,
-    const VoluData       & a_voludata,
-    const EBGraph        & a_graph,
-    const Real             a_dx)
-  {
-    Real expD = 1.0; // fixed power?
-    // get the normalized centroids
-    RealVect centroidM, centroidP;
-    Real kappaM, kappaP;
-    Normalizor<order>::normalizedVoluMoments(kappaM, centroidM, a_voludata, a_voflo, a_graph, a_dx);
-    Normalizor<order>::normalizedVoluMoments(kappaP, centroidP, a_voludata, a_vofhi, a_graph, a_dx);
-    // shift centroid to be relative to the shared face between them
-    centroidM -= 0.5*BASISREALV(a_dir);
-    centroidP += 0.5*BASISREALV(a_dir);
-    // get the distance from cell centroid to face centroid
-    Real distM = pow(((centroidM-a_faceCentroid)).vectorLength(), expD);
-    Real distP = pow(((centroidP-a_faceCentroid)).vectorLength(), expD);
-    // eval the weighted distances
-    a_loSideWeight = distP/(distM+distP);
-    a_hiSideWeight = distM/(distM+distP);
-    // a_loSideWeight = distM/(distM+distP); // this does better?
-    // a_hiSideWeight = distP/(distM+distP);
-  }
-
-    // Get a single face flux stencil at a face by a distance weighted average between
-  // two cell-centered flux stencils states computed by the neighbor cells sharing the face
-  // This was originally designed for the Laplacian stencil, but is generally applicable
-  template <int order>
-  LocalStencil<CELL,  Real>
-  WLSStencil<order>::
[…]

### 2023-04-27 example/DomainDecomposition/EBCellMerge/hoeb_petsc_test/_doc/paper.tex
paper outline started

@@
 \title{Elliptic operator stability and small cells on  finite volume grids}
-\author{N. Overton-Katz \footnotemark[1]
+\author{
+        O. Antepara    \footnotemark[1]
+   \and D. Devendran    \footnotemark[2]
+   \and D. T. Graves    \footnotemark[1]
    \and H. Johansen     \footnotemark[1]
-   \and D. T. Graves    \footnotemark[1]
-   \and D. Devendran    \footnotemark[2]
-   \and O. Anteparra    \footnotemark[1]}
+   \and N. Overton-Katz \footnotemark[1]
+        }
 
@@
 
-Devendran, et al. \cite{Devendran2017} 
-  real component of an operator eigenvalue
-  Using the basic framework of the elliptic operator in Devendran, et al.
-  expansions of finite volume data in the context of cut cell grids.
-  We show that significant solvability issues can arise from certain weighting
-  functions.    A very rudimentary but stable cell merger algorithm is
-  presented as we show that these solvability issues are not 
-  an artifact of small-cell instabilties.    We show that one can
-  manage these solvability issues with careful algorithm choices.
+Devendran, et al. \cite{Devendran2017} present an algorithm that
+solves Poisson's equation to fourth-order accuracy using an EB grid.
+Katz, et al. \cite{Katz2023} looked more closely at the mechanics of
+this algorithm and discussed solvability for stencil coefficients for
+a while varying dimensionality, weighting
+function exponents, and polynomial order.   They present results for
+uncut, standard EB, and merged grids.
+
+We take this analysis to the entire numerical system.  We vary these
+same algorithm parameters and analyze the eigenstructure of the
 
@@
 accuracy \cite{Schwartz2015}.
-
-EB grids can contain volumes that are arbitrarily small.    This
-"small-cell problem'' produces
-algorithmic difficulties that generations of researchers have labored
-to overcome with great success.   EB methods are used for high speed
-compressible flows \cite{Colella2006, Graves2013} and for
-slower, incompressible applications \cite{Trebotich2015} and conjugate
-heat transfer \cite{Crockett2010}.
 
@@
 = \partial \Omega \bigcap \Upsilon_\ibold$.
-
-\section {Finite volume notation}
 
@@
 methods use this description directly to generate stencils
-\cite{Overton2022a, Devendran2017, Schwartz2015}.  At the
-core, all these algorithms have a similar procedure for finding the
-Taylor coefficients $C^p$ which is worth discussing.  \footnotemark[8]
+\cite{Overton2022a, Devendran2017, Schwartz2015}.
 
-\section{Computing Taylor coefficients and Matrix Conditioning}
-
-Consider a finite volume grid where we know all geometric moments to
-order $P_T$.  Given values of $<\psi>$ everwhere on the grid, we wish to
-approximate the Taylor coefficients at a volume $\ibold$ given that we
-know $\cn_\ibold = \{\jbold\}$, the set of $N_v$ closest neighbors of
-the volume $\ibold$.  Using the Taylor expansion at each point gives
-us $N_v$ equations for $C^p$
-\begin{equation}
-  V_\jbold <\psi>_\jbold = \sum\limits_{p < P_T} C^p_\ibold m^p_\jbold.
-\end{equation}
-Let's say there are $N_p$ Taylor coefficients.  We can force $N_v >
-N_p$ by getting a large enough neighborhood.  This means that we have
-an overdetermined system of the form
-\begin{equation*}
-M C = P 
-\end{equation*}
-where $M = \{\{m^{pi}_\jbold\}\}$, $C=\{C^p\}$,  and $P= \{<\psi_\jbold>\}$.
-Since the system is overdetermined, we can introduce a 
-meaningful weighting matrix $W$ \footnotemark[3].  Choice of $W$
-is crucial to the stability of these algorithms
-\footnotemark[4].
-We multiply and solve
-\begin{equation*}
-WMC = WP.
-\end{equation*}
-Since these matricies are (deliberately) not square, we approximate
-the solution using a Moore-Penrose pseudo-inverse:
-\begin{equation}
-  C = ((WM)^T(WM))^{-1} (WM)^T P.
-\label{eqn::getC}  
-\end{equation}
-This formulation can woven into the computation for stencil
-components;  Devendran et al. \cite{Devendran2017}, for example, explains the
-process for Poisson's equation.
-
-Unfortunately, the matrix $A \equiv (WM)^T(WM)$ can be poorly conditioned.
-That these algorithms can invert a poorly-conditioned matrix to compute
-stencil coefficients introduces an interesting type of uncertainty: error in
-the very coefficients of a stencil operation.   If the matrix is poorly
-conditioned, the coefficients of the stencil can only be known to
-limited precision.   This lack of precision is measurable as it tracks
-the condition number of the matrix.
-
-Broadly speaking, there are two approaches to dealing with this poor
-conditioning. One can improve the accuracy of the matrix
-representation so she may absorb the reduction in precision and still
-produce coefficients of sufficient accuracy.
-Lo, et al. \cite{Lo2019} show good results using quad-precision arithmetic
-for matrices which produce double precision coefficients.
-The other approach is to improve the
-conditioning of the matrix by careful choices of weighting matrix and
-neighborhood.
-
-\section{Condition number measurements}
-
-To gain insight into the connection between solvability, weighting and
-order, we evaluate the matrix
-\begin{equation}
-A \equiv (WM)^T(WM)
-\label{eqn::normalEq}
-\end{equation}
-at every volume in a computational grid and analyze its
-eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
-$\{ \lambda_{i}\}$, the inverse of the condition number $I_i$ is given by
-\begin{equation*}
-  I_i = \frac{\lambda_i|_{min}}{\lambda_i|_{max}},
-\end{equation*}
-which goes to zero as the maximum and minimum eigenvalues diverge and
-the matrix becomes more poorly conditioned.   These eigenvalues are
-obtained through  SVD decompostion \footnotemark[7].
-
-Solving the normal equations (\ref{eqn::normalEq}) for the
-coeffients is not ideal because the condition number of $A$ is the
-square of the condition number of
-$WM$  \cite{BigCheese}.     SVD can be used to solve the system with
-the condition number of $WM$.   That, however, requires interweaving
-the computation of the stencil with  the target application's
-equations.   Since we are doing this 
-analysis in the absence of a
-specific target stancil, one should interpret our condition number
-results as the square of the effective condition number that algorithm
-developers will encounter.
-
-First we  measure   an uncut, Cartesian mesh to
-provide a baseline without the complications involved with cut cells.
-Next we cut the mesh with a very smooth implicit function and do the
-same measurements.   Finally we take this cut mesh and merge its small
-cells to neighbors to eliminate all cells smaller than a Cartesian
-volume to isolate the effects of small cells.
-
-All volumes $V_i$ start with an  index $i \in Z^D$.
-We start from volume $V_0$.   For 
-weighting function, we need to measure $D_{w, V_0}(V_1)$,
-the Manhattan disance to the volume $V_1$:
-\begin{equation}
-  D_{W, V_0}(V_1) = \sum\limits_{d \in {1...D}} |i_1^d - i_0^d|.
-\label{eqn::uptownFunk}
-\end{equation}
-We define $W_{v_0}(V_1)$, the weighting function used by volume $V_0$ for the
-equation describing  volume $V_1$ we use is given by
-\begin{equation}
-  W_{v_0}(V_1)  \equiv \frac{1}{D^{P_w}_{V_0}(V_1)},
-\label{eqn::weightFunk}  
-\end{equation}
-where we vary the weighting exponent $P_w$, and the 
-polynomial order $P_T$.
-
-\subsection{All Regular geometry}
-
-We begin with the simplest possible motivating example: a
-$D$-dimensional Cartesian geometry wherein all cells are uncut.
-Figure \ref{fig::T3W3} shows all values of $I$ for $D=2$, $I$ with
-$P_w = P_T = 3$.  Table \ref{tab::worst_all_reg_inv_conv} shows the
-worst condition number in this simple grid for a number of values of
-$P_w$ and $P_T$.
-
-\begin{figure}
-\centerline{\epsfig{figure=_fig/all_reg_t3_w3_inv_cond.ps,width=0.4\linewidth } }
-\label{fig::T3W3}
-\caption
-    {
-      $I$ (inverse of the condition number for matrix $A$ for a $32^2$
-      uncut grid where $P_w = P_T = 3$.
-    }
-\end{figure}
-
-\begin{small}
-\begin{table}
-\begin{center}
-\begin{tabular}{|cccc|ccc|} \hline
-$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
-\hline
-2 & 1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
-2 & 1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
-2 & 1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
-2 & 1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
-2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\
-\hline
-2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
-2 & 2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
-2 & 2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
-2 & 2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
-2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
-\hline
-2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
-2 & 3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
-2 & 3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
-2 & 3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
-2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
-\hline
-2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
-2 & 4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
-2 & 4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
-2 & 4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
-2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
-\hline
-3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
-3 & 1 & 2 & 3 & 1.335375e+00 & 2.299835e-04 & 1.722239e-04 \\ 
-3 & 1 & 3 & 3 & 1.058688e+00 & 2.726319e-05 & 2.575186e-05 \\ 
-3 & 1 & 4 & 3 & 1.012826e+00 & 4.843834e-06 & 4.782494e-06 \\ 
-3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
-\hline
-3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
-3 & 2 & 2 & 3 & 1.335376e+00 & 1.349331e-07 & 1.010450e-07 \\ 
-3 & 2 & 3 & 3 & 1.058688e+00 & 6.504992e-09 & 6.144388e-09 \\ 
-3 & 2 & 4 & 3 & 1.012826e+00 & 3.782273e-10 & 3.734376e-10 \\ 
-3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
-\hline
-3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
-3 & 3 & 2 & 3 & 1.335376e+00 & 6.641096e-11 & 4.973204e-11 \\ 
-3 & 3 & 3 & 3 & 1.058688e+00 & 3.224905e-12 & 3.046133e-12 \\ 
-3 & 3 & 4 & 3 & 1.012826e+00 & 1.004670e-13 & 9.919476e-14 \\ 
-3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
-\hline
-3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
-3 & 4 & 2 & 3 & 1.474014e+00 & 1.231139e-27 & 8.352288e-28 \\ 
-3 & 4 & 3 & 3 & 1.102368e+00 & 5.433012e-27 & 4.928491e-27 \\ 
-3 & 4 & 4 & 3 & 1.012826e+00 & 1.327379e-23 & 1.310570e-23 \\ 
-3 & 4 & 5 & 3 & 1.003042e+00 & 6.807789e-25 & 6.787141e-25 \\
-\hline
-\end{tabular}
-\end{center}
-\label{tab::worst_all_reg_inv_conv}
-\caption
-    {
-      We show the lowest value of
-      $I$ for an entire Cartesian grid of size $32^D$.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$.   Keep in mind
-      that the effective condition number of the problem will be $(1/\sqrt(I))$.
-    }
-\end{table}
-\end{small}
-
-\section{Cut Cell Geometry}
-\label{sec::eb}
-
-Our next  grid is a Cartesian grid cut  by a sphere (or a circle in two
-dimensions). The computational domain is the unit cube.   The cutting
-sphere center is the center of the cube.   The radius of the cutting
-sphere is 0.45.  The grid moments are generated using the algorithm
-specified in \cite{Schwartz2015}.  The moments are accurate to
-order $h^{P^T}$.
-
-If we use grid volumes at this point, the volume fraction
-\begin{equation*}
-\kappa_\ibold \equiv V_\ibold/h^D 
-\end{equation*}
-can be arbitrarily small ($ 0 < \kappa <= 1$).   We can also choose to
-merge small volumes with larger neighbors without formal loss of
-accuracy. The simple merger we use is described in
-described in appendix \ref{appendix::merger}.
-When merged using this algorithm, $\kappa$ can be larger than $2^D$.
-
-Without using cell merger, the volume map in two dimensions is shown
-in figure \ref{fig::unmerged2dmap}.   With cell merger, that same map
-becomes the grid shown in figure{fig::unmerged2dmap}.
-Tables \ref{tab::worst_unmerged_inv_conv} and
-\ref{tab::worst_merged_inv_conv}
-show the worst condition number for the unmerged and merged  grids
-respectively while varying $P_w$ and $P_T$.   Merger does not seem to
-help substantially with this issue.
-
-\begin{figure}
-\centerline{\epsfig{figure=_fig/unmerged.ps,width=0.4\linewidth }} 
-\caption
-    {
-      Map for EB grid produced by a cutting cirle. $0 <  \kappa <= 1$.
-  Each cut cell has a unique positive integer.}
-\label{fig::unmerged2dmap}
-\end{figure}
-
-\begin{small}
-\begin{table}
-\begin{center}
-\begin{tabular}{|cccc|ccc|} \hline
-$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
-  \hline
-2 & 1 & 1 & 3 & 2.652364e+00 & 1.404997e-03 & 5.297151e-04 \\ 
-2 & 1 & 2 & 3 & 1.208056e+00 & 1.014262e-04 & 8.395817e-05 \\ 
-2 & 1 & 3 & 3 & 1.038877e+00 & 8.361926e-06 & 8.049002e-06 \\ 
-2 & 1 & 4 & 3 & 1.008924e+00 & 1.034928e-06 & 1.025774e-06 \\ 
-2 & 1 & 5 & 3 & 1.002428e+00 & 1.818655e-07 & 1.814249e-07 \\
-\hline
-2 & 2 & 1 & 3 & 2.714706e+00 & 6.503682e-07 & 2.395722e-07 \\ 
-2 & 2 & 2 & 3 & 1.208056e+00 & 4.514952e-08 & 3.737369e-08 \\ 
-2 & 2 & 3 & 3 & 1.038878e+00 & 2.933277e-09 & 2.823506e-09 \\ 
-2 & 2 & 4 & 3 & 1.008924e+00 & 1.838097e-10 & 1.821840e-10 \\ 
-2 & 2 & 5 & 3 & 1.002428e+00 & 1.202042e-11 & 1.199130e-11 \\ 
-\hline
-2 & 3 & 1 & 3 & 2.714706e+00 & 2.057098e-10 & 7.577609e-11 \\ 
-2 & 3 & 2 & 3 & 1.208056e+00 & 1.761011e-11 & 1.457723e-11 \\ 
-2 & 3 & 3 & 3 & 1.039039e+00 & 1.175442e-12 & 1.131278e-12 \\ 
-2 & 3 & 4 & 3 & 1.008867e+00 & 6.513002e-14 & 6.455759e-14 \\ 
-2 & 3 & 5 & 3 & 1.002428e+00 & 3.467198e-15 & 3.458798e-15 \\ 
-\hline
-2 & 4 & 1 & 3 & 2.714706e+00 & 1.027685e-15 & 3.785620e-16 \\   
-2 & 4 & 2 & 3 & 1.211905e+00 & 6.107792e-17 & 5.039827e-17 \\ 
-2 & 4 & 3 & 3 & 1.056037e+00 & 5.698627e-18 & 5.396236e-18 \\ 
-2 & 4 & 4 & 3 & 1.012707e+00 & 1.518532e-18 & 1.499478e-18 \\ 
-2 & 4 & 5 & 3 & 1.003135e+00 & 5.995871e-19 & 5.977134e-19 \\ 
-\hline
-3 & 1 & 1 & 3 & 6.913890e+00 & 3.982271e-03 & 5.759812e-04 \\ 
-3 & 1 & 2 & 3 & 1.457799e+00 & 1.829378e-04 & 1.254890e-04 \\ 
-3 & 1 & 3 & 3 & 1.066961e+00 & 8.913398e-06 & 8.354003e-06 \\ 
-3 & 1 & 4 & 3 & 1.014131e+00 & 7.252280e-07 & 7.151226e-07 \\ 
-3 & 1 & 5 & 3 & 1.003774e+00 & 1.047053e-07 & 1.043116e-07 \\ 
-\hline
-3 & 2 & 1 & 3 & 7.173851e+00 & 1.868373e-06 & 2.604421e-07 \\ 
-3 & 2 & 2 & 3 & 1.457801e+00 & 7.350629e-08 & 5.042274e-08 \\ 
-3 & 2 & 3 & 3 & 1.066958e+00 & 3.054784e-09 & 2.863077e-09 \\ 
-3 & 2 & 4 & 3 & 1.014128e+00 & 1.439525e-10 & 1.419470e-10 \\ 
-3 & 2 & 5 & 3 & 1.003771e+00 & 6.965181e-12 & 6.939012e-12 \\ 
-\hline
-3 & 3 & 1 & 3 & 7.173852e+00 & 5.736142e-10 & 7.995902e-11 \\ 
-3 & 3 & 2 & 3 & 1.463399e+00 & 3.367341e-11 & 2.301041e-11 \\ 
-3 & 3 & 3 & 3 & 1.067176e+00 & 1.250758e-12 & 1.172027e-12 \\ 
-3 & 3 & 4 & 3 & 1.014128e+00 & 4.489644e-14 & 4.427098e-14 \\ 
-3 & 3 & 5 & 3 & 1.003771e+00 & 1.609961e-15 & 1.603912e-15 \\ 
-\hline
-3 & 4 & 1 & 3 & 7.173852e+00 & 8.922302e-15 & 1.243725e-15 \\ 
-3 & 4 & 2 & 3 & 1.463399e+00 & 3.078368e-16 & 2.103574e-16 \\ 
-3 & 4 & 3 & 3 & 1.067186e+00 & 2.577668e-17 & 2.415387e-17 \\ 
-3 & 4 & 4 & 3 & 1.014048e+00 & 4.440651e-18 & 4.379133e-18 \\ 
-3 & 4 & 5 & 3 & 1.005227e+00 & 8.527341e-19 & 8.483000e-19 \\
-\hline
-\end{tabular}
-\end{center}
-\label{tab::worst_unmerged_inv_conv}
-\caption
-    {
-      We show the lowest value of
-      $I$ for an entire Cartesian grid of size $32^D$.
-      Volumes are  formed by a sphere (or circle in 2D) cutting the
-      grid.   Volumes here can be arbitrarily small (no cell merging
-      happens here).
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$. 
-      Keep in mind
-      that the effective condition number of the problem will be $(1/\sqrt(I))$.
-    }
-\end{table}
-\end{small}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|cccc|ccc|} \hline
-$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
-  \hline
-2 & 1 & 1 & 3 & 2.516834e+00 & 1.345987e-04 & 5.347936e-05 \\ 
-2 & 1 & 2 & 3 & 1.940391e+00 & 5.761694e-06 & 2.969347e-06 \\ 
-2 & 1 & 3 & 3 & 1.890620e+00 & 3.134007e-07 & 1.657661e-07 \\ 
-2 & 1 & 4 & 3 & 2.315204e+00 & 2.362198e-08 & 1.020298e-08 \\ 
-2 & 1 & 5 & 3 & 2.314798e+00 & 1.256411e-09 & 5.427736e-10 \\ 
-\hline
-2 & 2 & 1 & 3 & 5.133178e+00 & 3.150951e-08 & 6.138402e-09 \\ 
-2 & 2 & 2 & 3 & 3.875948e+00 & 1.019905e-09 & 2.631369e-10 \\ 
-2 & 2 & 3 & 3 & 3.677407e+00 & 3.374831e-11 & 9.177202e-12 \\ 
-2 & 2 & 4 & 3 & 3.633887e+00 & 1.196563e-12 & 3.292791e-13 \\ 
-2 & 2 & 5 & 3 & 1.100852e+00 & 1.071019e-14 & 9.729001e-15 \\ 
-\hline
-2 & 3 & 1 & 3 & 1.461766e+00 & 8.698889e-14 & 5.950944e-14 \\ 
-2 & 3 & 2 & 3 & 1.118751e+00 & 4.096970e-15 & 3.662093e-15 \\ 
-2 & 3 & 3 & 3 & 1.102424e+00 & 1.662951e-16 & 1.508449e-16 \\ 
-2 & 3 & 4 & 3 & 3.178329e+00 & 1.221190e-16 & 3.842238e-17 \\ 
-2 & 3 & 5 & 3 & 1.924223e+00 & 3.044738e-18 & 1.582320e-18 \\ 
-\hline
-3 & 1 & 1 & 3 & 5.278376e+00 & 5.346601e-04 & 1.012926e-04 \\ 
-3 & 1 & 2 & 3 & 2.898394e+00 & 1.760686e-05 & 6.074697e-06 \\ 
-3 & 1 & 3 & 3 & 2.480330e+00 & 4.867477e-07 & 1.962431e-07 \\ 
-3 & 1 & 4 & 3 & 2.602304e+00 & 1.708061e-08 & 6.563648e-09 \\ 
-3 & 1 & 5 & 3 & 2.594257e+00 & 5.017396e-10 & 1.934039e-10 \\ 
-\hline
-3 & 2 & 1 & 3 & 8.172169e+00 & 1.320095e-07 & 1.615355e-08 \\ 
-3 & 2 & 2 & 3 & 4.770044e+00 & 3.005370e-09 & 6.300508e-10 \\ 
-3 & 2 & 3 & 3 & 4.426838e+00 & 7.734334e-11 & 1.747146e-11 \\ 
-3 & 2 & 4 & 3 & 4.521378e+00 & 1.996373e-12 & 4.415410e-13 \\ 
-3 & 2 & 5 & 3 & 4.508090e+00 & 4.439516e-14 & 9.847886e-15 \\ 
-\hline
-3 & 3 & 1 & 3 & 5.015663e+00 & 9.627815e-12 & 1.919550e-12 \\ 
-3 & 3 & 2 & 3 & 6.602139e+00 & 4.969235e-13 & 7.526705e-14 \\ 
-3 & 3 & 3 & 3 & 6.132610e+00 & 1.126536e-14 & 1.836961e-15 \\ 
-3 & 3 & 4 & 3 & 5.482751e+00 & 3.670736e-16 & 6.695062e-17 \\ 
-3 & 3 & 5 & 3 & 5.346895e+00 & 4.774068e-17 & 8.928674e-18 \\ 
-\hline
-3 & 4 & 1 & 3 & 1.161979e+01 & 5.372252e-18 & 4.623365e-19 \\ 
-3 & 4 & 2 & 3 & 4.069086e+00 & 1.622222e-17 & 3.986699e-18 \\
-\hline
-\end{tabular}
-\end{center}
-\label{tab::worst_merged_inv_conv}
-\caption
-    {
-      We show the lowest value of
-      $I$ for an entire Cartesian grid of size $32^D$.
-      Volumes are  formed by a sphere (or circle in 2D) cutting the
-      grid.   Small volumes here are merged with neighbors.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$. 
-      Keep in mind
-      that the effective condition number of the problem will be $(1/\sqrt(I))$.
-    }
-\end{table}
+\section{Results}
 
 \section{Conclusions}
-
-We show first that for a safe (low) choice of
-$P_T$, even the worst condition number in a given grid can be quite
-reasonable. With more aggressive choices of $P_T$, $I$ can be very
-small.  The data also
-show clearly that there is a connection between solvability, weighting
-function, and polynomial order.  Unexpectedly, we show that for a
-fixed polynomial order $P_T$, a higher weighting power $P_w$ can make the
-solvability problem worse.
-
-We do also show that matrix conditioning is a  potential issue for
-this class of algorihms.   In fact, for certain parameters,
-the condition number  can be so severe that an
-increase in matrix arithmetic precision will not be sufficient.
-Since cell merger does not help the
-problem, this lack of conditioning is not an issue with small cells.
-With careful choices of polynomial order and weighting matrix, the
-solvability problem can be managed, however.
-
-\section{Appendix: Simple algorithm for cell merger}
-\label{appendix::merger}
-
-Given a cut cell $\ibold$, we define the box containing only that cell
-$B_c = B(\ibold, \ibold)$ We form a $2^D$ cell rectangular region by
-coarsening and then refining $B_c$ to form $B_v = R(C(B_c))$
-\footnotemark[6].  After that process, any left over small cells are
-merged with their biggest neighbor.  See figures
-\ref{fig::unmerged2dmap} and \ref{fig::merged2dmap} for a simple
-example of how this algorithm creates fairly chunky grids.
-
-Merging two cells is simply a matter of removing the
-intervening faces, shifting all moments them to a common location
-and adding them together.  No accuracy is lost in this process
-outside of the fact that we have fewer degress of freedom because
-semantically, we are just adding volume integrals over distinct
-volumes, which is exact.
-
-For unmerged grids, the volume fraction $\kappa_\ibold \equiv
-V_\ibold/h^D$ can be arbitrarily small ($ 0 < \kappa <= 1$).
-When merged using this algorithm, $\kappa$ can be larger than $2^D$.
-
-\begin{figure}
-\centerline{\epsfig{figure=_fig/merged.ps,width=0.4\linewidth } }
-\caption{Map of EB grid shown in \ref{fig::unmerged2dmap} after using
-  cell merger algorithm.
-  Each cut cell has a unique positive integer. $ 1 <= \kappa <= 4.1433$}
-\label{fig::merged2dmap}
-\end{figure}
 
@@
 \footnotetext[2]{Ford Motor Company, Sunnyvale, CA.}
-\footnotetext[3]{If the matrix $M$ is square, a weighting matrix can
-  have no effect and the Moore-Penrose psueudoinverse becomes
-  $M^{-1}$.}
-
-\footnotetext[4]{Defining $\xbar_\ibold = 0$, the
-  equations for volumes $\jbold$ where $\xbar_\jbold$ target receive
-  higher weights.  Diagonal weighting matricies are common.  Usually,
-  these algorithms define a distance metric $D(\ibold, \jbold)$ for
-  two volumes $\ibold$ and $\jbold$.  Typically they make
-  $W_{\jbold,\jbold}$ decrease strongly with increasing 
-  $D(\ibold,\jbold)$ to assign higher importance to the equations for volumes
-  closer to $\ibold$.  Devendran et al. for example \cite{Devendran2017},
-  uses a weighting function that varies with $W_{\ibold,\jbold}
-  \approx 1./D(\ibold,\jbold)^5$ }.
-
-\footnotetext[6] {We mean a Box as defined in Chombo, a subset of
-  $Z^D$.  Coarsening and refining has the standard Chombo semantic
-  \cite{ChomboDesign, ChomboDesignEB}.}
-
-\footnotetext[7] {All matrix computations here are performed using
-  Eigen \cite{eigenweb}, a beautifully designed and implemented
-  package for on-processor linear algebra that is freely available.}
-
-\footnotetext[8]{The discerning reader will notice that
-the equation set used to create $C$ only includes the volume
-equations.  Devendran et al. \cite{Devendran2017} also include boundary
-condition equations in the equation set.  For simple enough boundary
-conditions, this works very well.  There are many equation sets,
-however, which do not lend themselves easily to this approach.
-Notably, hyperbolic equations often have boundary conditions which are
-fomulated in terms of characteristic variables.  Using this
-information in the system of equations for Taylor coefficients is
-still a matter of research.  We therefore believe that restricting
-ourselves to the volume equations can provide insight valuable to
-developers of this class of algorithms.}
-
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-04-28 example/DomainDecomposition/EBCellMerge/hoeb_petsc_test/_doc/paper.tex
bit of progress on new document

@@
   cannot have non-zero positive real eigenvalues.  We explore a family
-  of elliptic operators and attempt to define the boundaries of
-  stability for this family of algorithms.
+  of high order finite volume elliptic operators. We attempt to
+  define for this family of algorithms the boundaries of stability
+  within its parameter space.
 
@@
 
-\section{Introduction}
+\section{Underlying mathematics}
+
 Embedded boundary (EB) grids are formed when one passes an  surface
@@
 are very attactive because grid generation is a solved problem
-\cite{MillerTrebotich2012}.
-
-Devendran, et al. \cite{Devendran2017} present an algorithm that
-solves Poisson's equation to fourth-order accuracy using an EB grid.
-Katz, et al. \cite{Katz2023} looked more closely at the mechanics of
-this algorithm and discussed solvability for stencil coefficients for
-a while varying dimensionality, weighting
-function exponents, and polynomial order.   They present results for
-uncut, standard EB, and merged grids.
-
-We take this analysis to the entire numerical system.  We vary these
-same algorithm parameters and analyze the eigenstructure of the
-
+even for moving grids \cite{MillerTrebotich2012}.
 In the current context, we form the cutting surface as the zero
@@
 
-Throughout this paper, we use the following compact notation:
+We use the compact notation
 \begin{align*}
@@
 \end{align*}
-Given a point in space $\xbar$, and a $D$-dimensional integer vector
-$\pbold$, we define $m_v^\pbold(\xbar)$ to be the $\pbold^{th}$
-moment of the volume $V$ relative to the point $\xbar$.
+Given a $D$-dimensional region of space $\ibold$, 
+and a $D$-dimensional integer vector
+$\pbold$, we define $m_\ibold^\pbold(\xbar)$ to be the $\pbold^{th}$
+moment of $\ibold$ to the point $\xbar$.
 \begin{equation}
-m_v^\pbold(\xbar)  =  \int\limits_{V} (\xbold - \xbar)^\pbold dV
+m_\ibold^\pbold(\xbar)  =  \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV^D.
 \label{eqn::volmoment}
 \end{equation}
+This breaks out into three different cases, volumes, coordinate faces
+and irregular faces.
+A coordinate face $f_{12}$  is the area where two
+volumes ($V_1, V_2$) intersect.
+A irregular face $f_V$  is area where the cutting surface
+intersects the volume $V$.
+The volume moment for a particular power $\pbold$  is
+given by
+\begin{equation}
+  m^\pold_V = \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV
+  \label{eqn::volmom}
+\end{equation}
+The $\pbold^{th}$ coordinate face moment for the area of where volumes $V_1, V2$
+intersect is given by
+\begin{equation}
+  m^\pold_{f_{12}} = \int\limits_{A(V_1\bigcap V_2)} (\xbold - \xbar)^\pbold dA.
+  \label{eqn::facmom}
+\end{equation}
+The cutting surface of the boundary $G$ is given by  the zero
+surface of the  implicit function ($I(\xbold)= 0$) used in grid generation.
+The $\pbold^{th}$ irregular face moment is given by an integral over
+the intersection of this cutting surface and the Euclidean volume:
+\begin{equation}
+  m^\pold_{V}} = \int\limits_{A(V \bigcap G)} (\xbold - \xbar)^\pbold dA.
+  \label{eqn::irrmom}
+\end{equation}
+These moments are the natural product of the grid generation algorithm
+in \cite{Schwartz2015}.
 
@@
 \begin{equation*}
- V_\ibold <\psi>_\ibold = \sum\limits_{p < P_T} C^p m^p. 
+  <\psi>_\ibold = \frac{1}{V_\ibold} \sum\limits_{p < P_T} C^p m^p
+  \label{eqn::vol}.
 \end{equation*}
 This forms a local polynomial expansion of $\psi$ around the volume
-$\ibold$ expressed in terms moments ($m$) which are the natural
-products of grid generation.  Modern, higher order embedded boundary
-methods use this description directly to generate stencils
-\cite{Overton2022a, Devendran2017, Schwartz2015}.
+$\ibold$ expressed in terms moments ($m$).
+Modern, higher order embedded boundary
+methods use this description directly to generate stencil coefficients
+\cite{Overton2022a, Devendran2017, Schwartz2015, Katz2023}.
 
-\section{Results}
+\section{Family of finite volume elliptic operators}
+
+Devendran, et al. \cite{Devendran2017} present an algorithm that
+solves Poisson's equation to fourth-order accuracy using an EB grid.
+Generalizing somewhat  the framework they present, one can define an
+elliptic operator of any accuracy.
+
+At each volume $V$, we define the neighborhood $\neigh_v$
+volumes within a radius $R_s$ number of cells from the volume.
+Fix $\xbar$ to be the distance from the center of the target cell.
+Let's say there are
+$N_v$ volumes in the neighborhood and $F_D$ domain faces and $F_C$ cut
+cell faces in the domain.  Following (\cite{Devendran2017}), we create
+an equation for each volume and boundary condition within the
+neighborhood to form an  overdetermined system of equation for the
+Taylor coefficients in $V$.    Each volume gets an equation of the
+form of equation \ref{eqn::vol}.    Faces at the boundary domain with
+Neumann boundary conditions get an equation of the form 
+by We For each volume, we have The equations for the volumes and the
+boundary conditions form an overdetermined  system.
+
+\section{Stability and Conditioning}
+
+The matrix $A_{P_T, P_W}$ for a particular polynomial order $P_T$ and
+weighting exponent  $P_W$ may be unstable or poorly conditioned.   We
+measure both while varying $P_T, P_W$ in both two and three
+dimensions.    All these calculations are done using SLEPc and PETc
+\cite{petsc-user-ref, petsc-efficient, slepc}.
 

### 2023-04-29 src/EBCM/Chombo_EBCM_Algorithm_Framework.H
made a documents directory on the top level

@@ -46,10 +46,10 @@ namespace EBCM
    All functions are static.
 */
   template <int ebcm_order>
-  class EBCM_Framework
+  class Algorithm_Framework
   {
   public:
-    EBCM_Framework()
+    Algorithm_Framework()
     {}    
   
 
@@ -68,7 +68,7 @@ namespace EBCM
   
     static shared_ptr<pr_baseif> getImplicitFunction()
     {
-      CH_TIME("EBCM_Framework::getImplicitFunction");
+      CH_TIME("Algorithm_Framework::getImplicitFunction");
       shared_ptr<pr_baseif>  retval;
       ParmParse pp("getImplicitFunction");
       string which_geom;
@@ -128,7 +128,7 @@ namespace EBCM
                           bool a_outputGraph,
                           bool a_printStuff)
     {
-      CH_TIME("EBCM_Framework::makeMergedGeometry");
+      CH_TIME("Algorithm_Framework::makeMergedGeometry");
       using Chombo4::pout;
 
       int nx               = 32;
@@ -207,7 +207,7 @@ namespace EBCM
                      const ch_iv         & a_start,
                      int a_nghost, int a_weightPower, bool a_printStuff)
       {
-        CH_TIME("EBCM_Framework::neigborhood_t constructor");
+        CH_TIME("Algorithm_Framework::neigborhood_t constructor");
         m_startiv = a_start;
         m_nghost  = a_nghost;
         m_startloc.setToCCLocation(a_start, a_graph.m_dx);
@@ -291,7 +291,7 @@ namespace EBCM
                           const int         & a_currentRow,
                           bool a_printStuff)
     {
-      CH_TIME("EBCM_Framework::shiftMomentAndFillRow");
+      CH_TIME("Algorithm_Framework::shiftMomentAndFillRow");
       if(a_printStuff)
       {
         Chombo4::pout() << "shiftMomentAndFillRow: a_currentRow = " << a_currentRow << endl;
@@ -347,7 +347,7 @@ namespace EBCM
     getMomentMatrix(shared_ptr<neighborhood_t> a_locality,
                     bool a_printStuff)
     {
-      CH_TIME("EBCM_Framework::getMomentMatrix");
+      CH_TIME("Algorithm_Framework::getMomentMatrix");
       //number of equations
       int n_equations = a_locality->m_volumes->size();
       int n_unknowns  = pr_mom_dim::size();
@@ -380,7 +380,7 @@ namespace EBCM
[…]

### 2023-05-02 src/EBTools/Chombo_DistributedData.H
changed default distributeddata behavior for this branch

@@ -232,7 +232,7 @@ namespace CH4_Data_Choreography
     DistributedData(const Chombo4::DisjointBoxLayout     & a_grids,
                     const Chombo4::IntVect               & a_ghost,
                     const Chombo4::DataFactory<fabtype_t>& a_factory,
-                    bool                                   a_enableStaticCache = false)
+                    bool                                   a_enableStaticCache = true)
     {
       define(a_grids, a_ghost, a_factory);
     }

### 2023-05-02 src/EBCM/Chombo_EBCM_Graph.H
MPI-ification of EBCM objects is well underway

@@ -33,7 +33,7 @@ namespace EBCM
     pr_vof  m_lo;
     pr_vof  m_hi;
     IndexedMoments<DIM-1, order> m_facmom;
-    void defineAsRegular(pr_vof a_lo, pr_vof a_hi, Real a_dx)
+    void defineAsRegular(pr_vof a_lo, pr_vof a_hi, double a_dx)
     {                                                  
       m_lo = a_lo;
       m_hi = a_hi;
@@ -78,6 +78,28 @@ namespace EBCM
   class EBCM_Volu
   {
   public:
+
+    ///Get the size of this object 
+    size_t charsize() const
+    {
+      size_t retval = 0;
+
+      ch_mayday::Error("EBCM_Volu::linearSize not implemented");
+      return retval;
+    }
+
+    void linearOut(void* const a_outbuf) const
+    {
+      ch_mayday::Error("EBCM_Volu::linearOut not implemented");
+
+    }
+
+    void linearIn(const void* const a_inbuf)
+    {
+     ch_mayday::Error("EBCM_Volu::linearIn  not implemented");
+    }
+
+
     typedef Chombo4::GeometryService<order> ch_geoserv;
     typedef Proto::IndexedMoments<DIM-1, order> IndMomSDMinOne;
     typedef Proto::IndexedMoments<DIM  , order> IndMomSpaceDim;
@@ -90,13 +112,13 @@ namespace EBCM
     bool                          m_regular;
     //centroid location in global space (not relative to cell center)
     RealVect m_centroid;
-    Real     m_kappa; //volume fraction
+    double     m_kappa; //volume fraction
     IndexedMoments<DIM, order> m_volmom;
 
     //used as a unique identifier.  
     //Also volume moments are centered around this cell center.  Hence dx.
     Point    m_pt; 
-    Real     m_dx;
+    double     m_dx;
 
     inline void print() const
     {
@@ -223,16 +245,16 @@ namespace EBCM
       defineDerivedMeasures(a_dx);
     }
 
-    void defineDerivedMeasures(Real a_dx)
+    void defineDerivedMeasures(double a_dx)
     {
-      Real cellVol = D_TERM(a_dx, *a_dx, *a_dx);
+      double cellVol = D_TERM(a_dx, *a_dx, *a_dx);
       m_kappa = m_volmom[0]/cellVol;
       //relies upon volmom  and dx being set
[…]

### 2023-05-02 src/EBTools/Chombo_DistributedData.H

@@ -234,7 +234,7 @@ namespace CH4_Data_Choreography
                     const Chombo4::DataFactory<fabtype_t>& a_factory,
                     bool                                   a_enableStaticCache = true)
     {
-      define(a_grids, a_ghost, a_factory);
+      define(a_grids, a_ghost, a_factory, a_enableStaticCache);
     }
 
     
@@ -242,7 +242,7 @@ namespace CH4_Data_Choreography
     void define(const Chombo4::DisjointBoxLayout     & a_grids,
                 const Chombo4::IntVect               & a_ghost,
                 const Chombo4::DataFactory<fabtype_t>& a_factory,
-                bool                                   a_enableStaticCache = false)
+                bool                                   a_enableStaticCache = true)
     {
       CH_TIME("DistributedData constructor");
       m_procID = CH4_SPMD::procID();

### 2023-05-03 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/ebcellMerge.cpp
first pass at MPI stuff for cell merge stuff.  Also took out some commented out code from Box

@@ -172,9 +172,9 @@ public:
     shared_ptr< ch_geoserv > geoserv
       (new ch_geoserv(impfunc, origin, dx, domain.domainBox(), vecgrids, geomGhost));
 
-  
+    int ghost = 0;
     shared_ptr< ebcm_meta  >
-      metaDataPtr(new ebcm_meta(geoserv, domain.domainBox(), dx,
+      metaDataPtr(new ebcm_meta(geoserv, domain.domainBox(), dx, ghost,
                                 mergeSmallCells, a_printStuff));
 
     string graph_filename;

### 2023-05-03 example/DomainDecomposition/EBCellMerge/hoeb_petsc_test/framework_test.cpp

@@ -71,27 +71,27 @@ int main(int a_argc, char* a_argv[])
     Chombo4::pout() <<  "Running test for polynomial order = " << order << endl;
     if(order == 6)
     {
-      EBCM_Framework<6>::runTests();
+      EBCM::Algorithm_Framework<6>::runTests();
     }
     else if(order == 5)
     {
-      EBCM_Framework<5>::runTests();
+      EBCM::Algorithm_Framework<5>::runTests();
     }
     if(order == 4)
     {
-      EBCM_Framework<4>::runTests();
+      EBCM::Algorithm_Framework<4>::runTests();
     }
     else if(order == 3)
     {
-      EBCM_Framework<3>::runTests();
+      EBCM::Algorithm_Framework<3>::runTests();
     }
     else if(order == 2)
     {
-      EBCM_Framework<2>::runTests();
+      EBCM::Algorithm_Framework<2>::runTests();
     }
     else if(order == 1)
     {
-      EBCM_Framework<1>::runTests();
+      EBCM::Algorithm_Framework<1>::runTests();
     }
     else
     {

### 2023-05-03 src/BoxTools/Chombo_Box.cpp

@@ -1346,90 +1346,6 @@ adjCellHi (const Box& b,
 bool Box::s_tempestOutputFormat = false;
 
 #include "Chombo_NamespaceFooter.H"
-//#include "Chombo_UsingNamespace.H"
-
-//
-//template < >
-//void
-//::CH4_SPMD::
-//linearIn<Chombo4::Box>(Chombo4::Box& a_outputT, const void* const a_inBuf)
-//{
-//  int* intBuf = (int*)a_inBuf;
-//  IntVect lo, hi;
-//  //output is lo[0],lo[1],...
-//  for (int idir = 0; idir < SpaceDim; idir++)
-//    {
-//      lo[idir] = intBuf[idir];
-//      hi[idir] = intBuf[idir+SpaceDim];
-//    }
-//  if (lo <= hi)
-//    a_outputT = Chombo4::Box(lo,hi);
-//  else
-//    a_outputT = Chombo4::Box();
-//}
-//
-//template < >
-//void
-//::CH4_SPMD::
-//linearOut<Chombo4::Box>(void* const a_outBuf, const Chombo4::Box& a_inputT)
-//{
-//  int* intBuf = (int*)a_outBuf;
-//  const IntVect& lo = a_inputT.smallEnd();
-//  const IntVect& hi = a_inputT.bigEnd();
-//  //output is lo[0],lo[1],...
-//  for (int idir = 0; idir < SpaceDim; idir++)
-//    {
-//      intBuf[idir] = lo[idir];
-//      intBuf[idir+SpaceDim] = hi[idir];
-//    }
-//}
-//
-//template < >
-//size_t
-//::CH4_SPMD::
-//linearSize<Chombo4::Box>(const Chombo4::Box& a_input)
-//{
-//  //box is stored as 2*spaceDim integers
-//  return(2*SpaceDim*sizeof(int));
-//}
-//
-//
-//
-////vector<Box> specialization of linearSize
-//template < >
-//size_t
-//::CH4_SPMD::
-//linearSize(const std::vector<Chombo4::Box>& a_input)
-//{
-//  return linearListSize(a_input, false);
-//}
-//
-////vector<Box> specialization of linearIn
-//template < >
-//void
-//::CH4_SPMD::
-//linearIn(std::vector<Chombo4::Box>& a_outputT, const void* const a_inBuf)
-//{
-//  size_t boxsize = 2*SpaceDim*sizeof(int);
[…]

### 2023-05-03 src/EBCM/Chombo_EBCM_Algorithm_Framework.H

@@ -28,10 +28,8 @@ namespace EBCM
   typedef Chombo4::Box                                   ch_box;
   typedef Chombo4::DisjointBoxLayout                     ch_dbl;
   typedef Chombo4::ProblemDomain                         ch_probdom;
-  typedef Chombo4::DataIterator                          ch_dit;
   typedef Chombo4::IntVect                               ch_iv;
   typedef Chombo4::MayDay                                ch_mayday;
-//typedef Chombo4::LAPACKMatrix                          ch_mat;
   typedef Proto::RealVect                                pr_rv;
   typedef Proto::IndexTM<Real, DIM>                      pr_itm_r_dim;
   typedef Proto::IndexTM<int , DIM>                      pr_itm_i_dim;
@@ -125,6 +123,7 @@ namespace EBCM
                           ch_dbl                    & a_grids,
                           double                    & a_dx,
                           ch_probdom                & a_domain,
+                          int  a_ghost,
                           bool a_outputGraph,
                           bool a_printStuff)
     {
@@ -173,7 +172,7 @@ namespace EBCM
 
   
       shared_ptr< ebcm_meta  >
-        metaDataPtr(new ebcm_meta(geoserv, domain.domainBox(), dx,
+        metaDataPtr(new ebcm_meta(geoserv, domain.domainBox(), dx, a_ghost,
                                   mergeSmallCells, a_printStuff));
 
       string graph_filename;
@@ -465,7 +464,8 @@ namespace EBCM
       ch_dbl                   grids;
       double                   dx;
       ch_probdom               domain;
-      makeMergedGeometry(ebcm, grids, dx, domain, true, true);
+      int nghost = 0;
+      makeMergedGeometry(ebcm, grids, dx, domain, nghost, true, true);
 
       Real maxKapp, minKapp;
       //this tries out iteration and checks kappa

### 2023-05-03 src/EBCM/Chombo_EBCM_Graph.H

@@ -15,14 +15,18 @@ namespace EBCM
   using std::shared_ptr;
   using Chombo4::pout;
   using Chombo4::MayDay;
+//  using CH4_SPMD::linearIn;  
+//  using CH4_SPMD::linearOut;  
+//  using CH4_SPMD::linearSize;
   
-  typedef Proto::EBGraph       pr_ebgrap;
-  
-  typedef Proto::EBIndex<CELL> pr_vof;
-  typedef Proto::Point         pr_pt;
-  typedef Proto::Box           pr_box;
-  typedef Chombo4::Box         ch_box;
-  typedef Chombo4::DataIndex   ch_dit;
+  typedef Proto::EBGraph           pr_ebgrap;
+  typedef Proto::EBIndex<CELL>     pr_vof;
+  typedef Proto::Point             pr_pt;
+  typedef Proto::Box               pr_box;
+  typedef Chombo4::Box             ch_box;
+  typedef Chombo4::DataIterator    ch_dit;
+  typedef Chombo4::DataIndex       ch_datind;
+  typedef Chombo4::MayDay          ch_mayday;
   
   ///
   template<CENTERING cent, int order>
@@ -84,7 +88,7 @@ namespace EBCM
     {
       size_t retval = 0;
 
-      ch_mayday::Error("EBCM_Volu::linearSize not implemented");
+      ch_mayday::Error("EBCM_Volu::charsize not implemented");
       return retval;
     }
 
@@ -96,7 +100,7 @@ namespace EBCM
 
     void linearIn(const void* const a_inbuf)
     {
-     ch_mayday::Error("EBCM_Volu::linearIn  not implemented");
+      ch_mayday::Error("EBCM_Volu::linearIn  not implemented");
     }
 
 
@@ -194,7 +198,7 @@ namespace EBCM
     void defineAsIrregular(const pr_vof                          & a_vof,
                            const shared_ptr<ch_geoserv>          & a_geoserv,
                            const ch_box                          & a_domain,
-                           const ch_dit                          & a_dit,
+                           const ch_datind                       & a_dit,
                            const double                          & a_dx)
     {
       m_regular = false;
@@ -307,7 +311,7 @@ namespace EBCM
   ///
   /**
      Class to make merged sparse embedded boundary description. 
-   */
+  */
   template< int order>
   class EBCM_Graph
   {
@@ -628,8 +632,8 @@ namespace EBCM
 
     ///
     /**
-      This coarsens, then refines the input cell to get a 2x2x2
[…]

### 2023-05-06 example/DomainDecomposition/EBCM/hoeb_spmd/_doc/paper.tex
made progress on hoeb_spmd document

\documentclass{article}

\bibliographystyle{plain}

\usepackage{epsfig}
\usepackage{xcolor}
\usepackage{amsmath}

\input{abbrev.tex}

\begin{document}

\title{Communication test for EBCM framework}
\author{
    D. Devendran   \footnotemark[2] \and
    D. T. Graves    \footnotemark[1]
        }
\date{May 4, 2023 ce.}
\maketitle

\section{Introduction}

We are testing the communications infrastructure for {\tt
Chombo4/src/EBCM}, the bits of Chombo that handle calculations
within the context merged and
unmerged cut cell geometries.

See Katz, et al (\cite{Katz 2023}) for a basic idea of the mathematical
framework in which higher order cut cell algorithms live.

\subsection{The blessed shortcut}

Important note: we are not dealing multivalued cells (cells in which
more than one computational volume lives in a Cartesian grid cell) for
EBCM calculations yet.  They are a difficult case that we can easily
avoid.  For EB aficionados, here are the technical reasons we are
taking this blessed shortcut:
\begin{itemize}
  \item Multivalued cells create enormous complications in data
    structures and require special graph-based data holders instead of
    much simpler box-based data holders.
 \item That means they require a whole new set of serialization
   routines that are difficult to debug.   
 \item Because we have cell merging, we are never forced to use
   multivalued cells.
 \item Chombo does not produces multivalued cells at the finest EB
   level, which is all the EBCM uses.
 \item Premature generalization is as bad as premature optimization.
\end{itemize}
Here is the downside of the blessed shortcut.
\begin{itemize}
\item Cell merging makes adaptivew mesh refinement (AMR)
  and geometric multigrid (GMG) more difficult.   
\item A volume's possible graph connections to finer and coarser
  volumes can no longer be inferred by its Cartesian cell.
\item The blessed shortcut makes the process of managing coarse and
  fine connections even more complicated because it forces merging at
  coarser levels. 
\item For the class of algorithms in which we are interested, however,
  both  reliable GMG and AMR are both still research  problems.
\item  Devendran, et al. provide some insight into the difficulties
  geometric multigrid in a higher order EB context \cite{Devendran2014}.
\end{itemize}

\section{The bit we are testing}

\section{Conclusions}

\footnotetext[1]{Lawrence Berkeley National Laboratory, Berkeley,
  CA. Research at LBNL was supported financially by the Office of
  Advanced Scientific Computing Research of the US Department of
  Energy under contract number DE-AC02-05CH11231.}
\footnotetext[2]{Ford Motor Company, Sunnyvale, CA.}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}\
\bibliography{references}

\end{document}

### 2023-05-07 example/DomainDecomposition/EBCM/hoeb_spmd/_doc/paper.tex
completed firt draft on ebcm spmd example document

@@
 
-See Katz, et al (\cite{Katz 2023}) for a basic idea of the mathematical
+See Katz, et al (\cite{Katz2023}) for a basic idea of the mathematical
 framework in which higher order cut cell algorithms live.
@@
    multivalued cells.
+ \item In fact, cell merging makes even some of the
+   regular grid redundant (which is a complication we already manage
+   when it comes to covered cells).
  \item Chombo does not produces multivalued cells at the finest EB
-   level, which is all the EBCM uses.
- \item Premature generalization is as bad as premature optimization.
+   level (which is all the EBCM infrastructure uses).
+ \item Premature generalization is bad and can lead to all kinds of
+   problems.   
 \end{itemize}
-Here is the downside of the blessed shortcut.
-\begin{itemize}
-\item Cell merging makes adaptivew mesh refinement (AMR)
-  and geometric multigrid (GMG) more difficult.   
-\item A volume's possible graph connections to finer and coarser
-  volumes can no longer be inferred by its Cartesian cell.
-\item The blessed shortcut makes the process of managing coarse and
-  fine connections even more complicated because it forces merging at
-  coarser levels. 
-\item For the class of algorithms in which we are interested, however,
-  both  reliable GMG and AMR are both still research  problems.
-\item  Devendran, et al. provide some insight into the difficulties
-  geometric multigrid in a higher order EB context \cite{Devendran2014}.
-\end{itemize}
+Here is the downside of the blessed shortcut: cell merging makes
+geometric multigrid (GMG) more difficult.  With cell merging, managing
+coarse and fine graph connections becomes more complicated. A volume's
+possible graph connections to finer and coarser volumes can no longer
+be inferred by its Cartesian cell. On the other hand, for the class of
+algorithms in which we are interested, reliable GMG is an ongoing
+research problem.  Devendran, et al. \cite{Devendran2014}
+provide some insight into the difficulties geometric multigrid in a
+higher order EB context.  The current effort will only use PETSc
+\cite{petsc-user-ref, petsc-efficient} algebraic multigrid (AMG)
+solvers.
 
@@
 
-\section{Conclusions}
+We need to test two bits of infrastructure, both of them related to
+SPMD communication.  
+\begin{itemize}
+  \item We need ghost cells for the geometric data which lives in {\tt
+    EBCM::MetaDataLevel }.
+  \item We need ghost cells for the simulation data which lives in {\tt
+    EBCM::HostLevelData}.
+\end{itemize}
+In both cases, we do the obvious test.
+For $T \in \{\mbox{MetaDataLevel, HostLevelData} \}$:
+\begin{itemize}
+  \item We make $T_{dom}$, where one box covers the whole domain, and
+    $T_{dist}$, which covers the domain with many boxes.
+  \item The test passes if $T_{dom} == T_{dist}$ everywhere in the domain.
+\end{itemize}
+
+\section{Unreasonable expectations}
+
+When the infrastructure is working the code should simply return that
+all tests have passed.
 

### 2023-05-07 example/DomainDecomposition/EBCM/roadmap.tex
document early and often

\documentclass{article}

\begin{document}

\title{EBCM Directory Roadmap}
\author{
    D. T. Graves    \footnotemark[1]
        }
\date{May 7, 2023 ce.}
\maketitle

\section{hoeb geometry test}

This test makes a single-box EBCM::MetaDataLevel.  It then makes a ton
of data on matrix conditioning in an hoeb/ebcm context.    The
associated technical report is quite complete.

\section{hoeb spmd}

This tests the communications infrastructure for {\tt
Chombo4/src/EBCM}, the bits of Chombo that handle calculations
within the context merged and
unmerged cut cell geometries.   The associated document is complete
but minimal.

\section{hoeb petsc}

This test investigates the eigenvalues and eigenvectors of stencils to
solve Poisson's equation.

\end{document}

### 2023-05-19 example/EBCM/hoeb_geometry/_saved_data/_sphere/notes.tex
moved cell merged examples into their own space

2d:

unmerged output:
nx = 32
max_grid = 32
Cell merging is turned OFF.
making grids
sphere implicit function with radius = 0.45, center = (0.5,0.5), and inside = 1
defining geometry in EB land
makeTheBlobs: number of small cells = 0, min kappa = 0.00880994
maximum (non covered) volume fraction for grids[0] = 1
minimum (non covered) volume fraction for grids[0] = 0.00880994
maximum volume fraction overall = 1
minimum volume fraction overall = 0.00880994
printing time table

merged output:

spencer(101)<hoeb_geometry_test> ./main.exe _inputs/sphere.inputs 
nx = 32
max_grid = 32
Cell merging is turned ON.
making grids
sphere implicit function with radius = 0.45, center = (0.5,0.5), and inside = 1
defining geometry in EB land
makeTheBlobs: number of small cells = 20, min kappa = 0.0661023
maximum (non covered) volume fraction for grids[0] = 4.1433
minimum (non covered) volume fraction for grids[0] = 1
maximum volume fraction overall = 4.1433
minimum volume fraction overall = 1
printing time table

### 2023-05-19 example/EBCM/roadmap.tex
moved cell merged examples into their own space

--- 2023-05-07 example/DomainDecomposition/EBCM/roadmap.tex
@@
 \title{EBCM Directory Roadmap}
-\author{
-    D. T. Graves    \footnotemark[1]
-        }
-\date{May 7, 2023 ce.}
+\author{ D. T. Graves }
+\date{May 7, 2023 c.e.}
 \maketitle
@@
 Chombo4/src/EBCM}, the bits of Chombo that handle calculations
-within the context merged and
-unmerged cut cell geometries.   The associated document is complete
-but minimal.
+within the context of  cut cell geometries where merger is an option.
+The associated document is complete but minimal.
 

### 2023-05-19 example/EBCM/hoeb_geometry/ebcellMerge.cpp
few small changes to get stuff working with new directory structure

@@ -17,12 +17,7 @@
 #include "Chombo_EBCM_Graph.H"
 #include "Chombo_EBCM_HostLevelData.H"
 #include "Chombo_EigenMatrix.H"
-#include "EBMultigrid.H"
 
-#include "DebugFunctions.H"
-#include "Hoeb_ExactSolutions.H"
-
-#include "Chombo_LAPACKMatrix.H"
 #include <iomanip>
 
 
@@ -494,7 +489,7 @@ public:
   {
     
     CH_TIME("EBCM_Framework::getConditionNumberData");
-    a_data  = shared_ptr<ebcm_leveldata>(new ebcm_leveldata(a_ebcm, Chombo4::IntVect::Zero));
+    a_data  = shared_ptr<ebcm_leveldata>(new ebcm_leveldata(a_ebcm, 0));
     a_worst = shared_ptr<condition_t>(new condition_t());
 
     double minInvCond = 1.0e30;

### 2023-05-19 example/EBCM/hoeb_spmd/spmd_test.cpp

@@ -18,10 +18,6 @@
 #include "Chombo_EBCM_HostLevelData.H"
 #include "Chombo_EBCM_Algorithm_Framework.H"
 #include "Chombo_EigenMatrix.H"
-#include "EBMultigrid.H"
-
-#include "DebugFunctions.H"
-#include "Hoeb_ExactSolutions.H"
 
 #include "Chombo_LAPACKMatrix.H"
 #include <iomanip>

### 2023-05-19 src/EBTools/Chombo_DistributedData.H

@@ -658,7 +658,7 @@ namespace CH4_Data_Choreography
     {
       CH_TIME("DistributedData::doLocalCopies");
       bool goFaster = !a_printStuff;
-      goFaster = true;
+      //goFaster = true;
       if(goFaster)
       {
         //this is probably faster

### 2023-05-19 example/EBCM/hoeb_geometry/_doc/paper.tex
missed one of the small words

--- 2023-04-26 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
@@
 \author{N. Overton-Katz \footnotemark[1]
-   \and H. Johansen     \footnotemark[1]
    \and D. T. Graves    \footnotemark[1]
    \and D. Devendran    \footnotemark[2]
-   \and O. Anteparra    \footnotemark[1]}
+   \and O. Antepara    \footnotemark[1]}
 
@@
 \end{equation}
-This formulation can woven into the computation for stencil
+This formulation can be woven into the computation for stencil
 components;  Devendran et al. \cite{Devendran2017}, for example, explains the
@@
 We start from volume $V_0$.   For 
-weighting function, we need to measure $D_{w, V_0}(V_1)$,
+a weighting function, we need to measure $D_{w, V_0}(V_1)$,
 the Manhattan disance to the volume $V_1$:

### 2023-05-19 example/EBCM/hoeb_petsc/_doc/paper.tex
good progress on document

--- 2023-04-28 example/DomainDecomposition/EBCellMerge/hoeb_petsc_test/_doc/paper.tex
@@
 \author{
-        O. Antepara    \footnotemark[1]
    \and D. Devendran    \footnotemark[2]
    \and D. T. Graves    \footnotemark[1]
-   \and H. Johansen     \footnotemark[1]
-   \and N. Overton-Katz \footnotemark[1]
         }
@@
 
-  Numerical stability for elliptic operators is well understood.  To
-  be numerically stable, a numerical operator for an elliptic equation
-  cannot have non-zero positive real eigenvalues.  We explore a family
-  of high order finite volume elliptic operators. We attempt to
-  define for this family of algorithms the boundaries of stability
-  within its parameter space.
+Devendran, et al. \cite{Devendran2017} present an algorithm that
+solves Poisson's equation to fourth-order accuracy using an EB grid.
+Generalizing somewhat  the framework they present, we can define a
+family of elliptic operators.
+Here we investigate how the accuracy and stability of this family
+of operators varies within its parameter space.
 
@@
 \begin{equation}
-  m^\pold_V = \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV
+  m^\pbold_V = \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV
   \label{eqn::volmom}
@@
 \begin{equation}
-  m^\pold_{f_{12}} = \int\limits_{A(V_1\bigcap V_2)} (\xbold - \xbar)^\pbold dA.
+  m^\pbold_{f_{12}} = \int\limits_{A(V_1\bigcap V_2)} (\xbold - \xbar)^\pbold dA.
   \label{eqn::facmom}
@@
 \begin{equation}
-  m^\pold_{V}} = \int\limits_{A(V \bigcap G)} (\xbold - \xbar)^\pbold dA.
+  m^\pbold_V = \int\limits_{A(V \bigcap G)} (\xbold - \xbar)^\pbold dA.
   \label{eqn::irrmom}
@@
 
-Given a sufficiently smooth function $\psi$, we can approximate $\psi$
+\section{Family of finite volume elliptic operators}
+
+Devendran, et al. \cite{Devendran2017} present an algorithm that
+solves Poisson's equation to fourth-order accuracy using embedded
+boundaries.  Generalizing somewhat  the framework they present, we
+present a family of elliptic operators.
+
+We are solving Poisson's equation for field $\psi$, given charge $\rho$:
+\begin{equation}
+  \nabla \cdot (\nabla \psi) = \rho
+  \label{eqn::poisson}
+\end{equation}
+If we integrate equation \ref{eqn::poisson} and apply the divergence theorem 
+over control volumes we get
+\begin{equation}
+\int_{V_\ibold} \nabla \cdot (\nabla \phi ) dV = \int_{\partial
+  V_\ibold} \nabla \phi\cdot \nhat  dA = \int_{V_\ibold} \rho dV
+\end{equation}
+Without approximation, we can say that the surface integral can be
+computed by a sum over the faces that comprise the surface of the
+volume.
+\begin{equation}
+\sum_{f: f \in \partial V_\ibold} \nabla \phi \cdot \nhat dA = \int_{V_\ibold} \rho dV
+\end{equation}
+Using equations \ref{eqn::faceavg} and \ref{eqn::volavg}, this becomes 
+\begin{equation}
+\sum_{f: f \in \partial V_\ibold} \avg{\nabla \phi \cdot \nhat}_f A_f
+= \avg{\rho}_\ibold V_\ibold
+\label{eqn::discretePoisson}
+\end{equation}
+A finite volume operator is defined by the algorithm to
+compute the integral of  fluxes at each face.   We have three types of
+face, open faces (the faces between two volumes that are aligned with
+coordinate directions), domain  faces, and cut faces.    For now, let's say we have
+homogeneous Neumann boundary conditions at domain and cut faces $\nabla \psi
+\cdot \nhat  = 0 |\partial \Omega$.   In this case, to describe the
+algorithm, we need only describe how to compute $<\nabla \psi \cdot
+\nhat>$ on open faces.
+
+\section{Open face flux}
+\section{Dirichlet fluxes at boundaries}
+We can approximate $\psi$
 in the neighborhood of $\xbar$ using a Taylor expansion to order $P_T$:
@@
 \end{equation}
+If we know the local Taylor coeffiencts,
+the gradient of the field  in direction $d$ is given by
+\begin{equation}
+  \frac{\partial \psi}{\partial x^d} \psi =
+  \sum\limits_{p < P_T} p^d C^{p-e^d} (\xbar -\xbar)^{p-e^d}
+\end{equation}
+
 In finite volume  methods, we define grid data to be
-averages over volumes.   So if we discretize the smooth function
-$\psi$, the average over the volume $\ibold$ is given by
+averages over volumes and fluxes between volumes are averages over the
+faces between volumes.   
+For the field $\psi$, the average over the volume $\ibold$ is given by
 \begin{equation*}
@@
 \end{equation*}
-This forms a local polynomial expansion of $\psi$ around the volume
-$\ibold$ expressed in terms moments ($m$).
-Modern, higher order embedded boundary
-methods use this description directly to generate stencil coefficients
-\cite{Overton2022a, Devendran2017, Schwartz2015, Katz2023}.
+Similarly, integrating the flux over a d-directional face $\fbold$:
+\begin{equation*}
+  <\nabla \psi_d>_\ibold = \frac{1}{A_f\bold}
+  \sum\limits_{p < P_T} p^d C^{p-e^d} m^{p-e^d}
+  \label{eqn::vol}.
+\end{equation*}
+To solve for the Taylor coefficients, we use the neighboring volumes's
+values  to form a system of equations (equation \eqn::vol
+for each volume $\ibold \in N_f$, the neighborhood of $f$).  Boundary
+condition equations are also added to the system.   We force there
+to be enough neighbors so that this system is overdetermined.
 
-\section{Family of finite volume elliptic operators}
-
-Devendran, et al. \cite{Devendran2017} present an algorithm that
-solves Poisson's equation to fourth-order accuracy using an EB grid.
-Generalizing somewhat  the framework they present, one can define an
-elliptic operator of any accuracy.
-
-At each volume $V$, we define the neighborhood $\neigh_v$
-volumes within a radius $R_s$ number of cells from the volume.
-Fix $\xbar$ to be the distance from the center of the target cell.
-Let's say there are
-$N_v$ volumes in the neighborhood and $F_D$ domain faces and $F_C$ cut
-cell faces in the domain.  Following (\cite{Devendran2017}), we create
-an equation for each volume and boundary condition within the
-neighborhood to form an  overdetermined system of equation for the
-Taylor coefficients in $V$.    Each volume gets an equation of the
-form of equation \ref{eqn::vol}.    Faces at the boundary domain with
-Neumann boundary conditions get an equation of the form 
-by We For each volume, we have The equations for the volumes and the
-boundary conditions form an overdetermined  system.
+\section{}
 

### 2023-05-19 example/EBCM/hoeb_petsc/_doc/paper.tex
this math stuff is cool

@@
 \end{equation}
-A finite volume operator is defined by the algorithm to
-compute the integral of  fluxes at each face.   We have three types of
-face, open faces (the faces between two volumes that are aligned with
-coordinate directions), domain  faces, and cut faces.    For now, let's say we have
-homogeneous Neumann boundary conditions at domain and cut faces $\nabla \psi
-\cdot \nhat  = 0 |\partial \Omega$.   In this case, to describe the
-algorithm, we need only describe how to compute $<\nabla \psi \cdot
-\nhat>$ on open faces.
+A finite volume operator is defined by the algorithm to compute the
+integral of fluxes at each face.  We have three types of face, open
+faces (the faces between two volumes that are aligned with coordinate
+directions), domain faces, and cut faces.  For now, let's say we have
+homogeneous Neumann boundary conditions at domain and cut faces
+$\nabla \psi \cdot \nhat = 0 |\partial \Omega$.  In this case, to
+describe the algorithm, we need only describe how to compute $<\nabla
+\psi \cdot \nhat>$ on open faces.
 
-\section{Open face flux}
+\section{Open face flux computation}
 \section{Dirichlet fluxes at boundaries}

### 2023-05-22 example/EBCM/hoeb_petsc/_doc/paper.tex
finished documentation of algorithm when all Neumann

@@
 \begin{equation}
-m_\ibold^\pbold(\xbar)  =  \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV^D.
+\mcal_\ibold^\pbold(\xbar)  =  \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV^D.
 \label{eqn::volmoment}
@@
 \begin{equation}
-  m^\pbold_V = \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV
+  \mcal^\pbold_V = \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV
   \label{eqn::volmom}
@@
 \begin{equation}
-  m^\pbold_{f_{12}} = \int\limits_{A(V_1\bigcap V_2)} (\xbold - \xbar)^\pbold dA.
+  \mcal^\pbold_{f_{12}} = \int\limits_{A(V_1\bigcap V_2)} (\xbold - \xbar)^\pbold dA.
   \label{eqn::facmom}
@@
 \begin{equation}
-  m^\pbold_V = \int\limits_{A(V \bigcap G)} (\xbold - \xbar)^\pbold dA.
+  \mcal^\pbold_V = \int\limits_{A(V \bigcap G)} (\xbold - \xbar)^\pbold dA.
   \label{eqn::irrmom}
@@
 
-\section{Open face flux computation}
-\section{Dirichlet fluxes at boundaries}
-We can approximate $\psi$
+\section{Open face Poisson flux computation with Neumann boundary conditions}
+
+An open face is one that connects two volumes in the solution.  These
+faces are aligned with a coordinate direction.   Consider an open face
+$\fbold$ aligned with coordinate direction $d$.   We define $\ncal_\fbold$
+to be all the volumes within $N_G$ ghost cells of $\fbold$ \footnotemark{3].
+
+We approximate $\psi$
 in the neighborhood of $\xbar$ using a Taylor expansion to order $P_T$:
@@
 \begin{equation}
-  \frac{\partial \psi}{\partial x^d} \psi =
+  \frac{\partial \psi}{\partial x^d}  =
   \sum\limits_{p < P_T} p^d C^{p-e^d} (\xbar -\xbar)^{p-e^d}
@@
 \begin{equation*}
-  <\psi>_\ibold = \frac{1}{V_\ibold} \sum\limits_{p < P_T} C^p m^p
+  <\psi>_\ibold = \frac{1}{V_\ibold} \sum\limits_{p < P_T} C^p \mcal^p
   \label{eqn::vol}.
@@
   <\nabla \psi_d>_\ibold = \frac{1}{A_f\bold}
-  \sum\limits_{p < P_T} p^d C^{p-e^d} m^{p-e^d}
+  \sum\limits_{p < P_T} p^d C^{p-e^d} \mcal^{p-e^d}
   \label{eqn::vol}.
@@
 To solve for the Taylor coefficients, we use the neighboring volumes's
-values  to form a system of equations (equation \eqn::vol
+values  to form a system of equations (equation \ref{eqn::vol}.
 for each volume $\ibold \in N_f$, the neighborhood of $f$).  Boundary
-condition equations are also added to the system.   We force there
-to be enough neighbors so that this system is overdetermined.
+condition equations are also added to the system.   Since we have
+homogeneous Neumann boundary conditions, for every domain face $\bbold$
+within $\ncal_\fbold$, we have an equation of the form
+\begin{equation}
+  <\frac{\partial \psi}{\partial x^d}>_\bbold  =
+  \sum\limits_{p < P_T} p^d C^{p} m\limits^{p-e^d}_\bbold = 0.
+\end{equation}
+Consider a face $\cbold$ which is cut by a surface whose
+normal in direction $d$ is given by $n^d(\xbold)$.  We define the
+normal moments $\ecal^d$ to be the integral of this product:
+\begin{equation}
+\ecal^{\pbold, d}_\cbold  =  \int\limits_{A(\cbold)} \xminxbar n^d dA.
+\label{eqn::normmoment}
+\end{equation}
+These normal moments are natural products of the \cite{Schwartz:2015}
+grid generation algorithm. 
+For each $\cbold$ within the $\ncal_\fbold$, we get an equation of the form
+\begin{equation}
+  \int\limits_{A(\cbold)}  \nabla \psi \cdot \nhat dA =
+  \sum\limits_{d < D} \int\limits_{A(\cbold)} \sum_{p < P} p_d C_p
+  \xminxbar^{p-e^d} dA
+  = 
+\sum\limits_{d < D} \sum_{p < P}  p_d C_p \ecal^{p-e^d,d}_\cbold = 0.
+\end{equation}
+We force there to be enough neighbors so that this system is
+overdetermined.  Let's say $\ncal_\fbold$ contains $N_B$ boundary faces and
+$N_V$ volumes.   If we are solving for $N_T$ Taylor coefficients, this
+means that we require that $N_T < (N_B+ N_V)$.
 
-\section{}
+\section{Truncation error for Poisson operator with Neumann boundary conditions}
+\section{Dirichlet fluxes at boundaries}
 
@@
 \footnotetext[2]{Ford Motor Company, Sunnyvale, CA.}
+\footnotetext[3]{This includes corner volumes.   The neighborhood is
+  formed by taking all the volumes within a grown box. The grown box
+  is formed by growning the box made from the low and high cells of
+  the target face, growing it by $N_G$ and itersecting with the
+  domain.  We use the   Chombo
+  (\cite{ChomboDesign,ChomboDesignEB,ChomboDesign3}
+  box grow semantic. 
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-05-22 example/EBCM/hoeb_petsc/_doc/paper.tex
hoeb_petsc document proceeds apace

@@
 
+\subsection{Moment matrix}
+
 We approximate $\psi$
@@
   <\psi>_\ibold = \frac{1}{V_\ibold} \sum\limits_{p < P_T} C^p \mcal^p
-  \label{eqn::vol}.
+  \label{eqn::volavg}.
 \end{equation*}
@@
 \begin{equation*}
-  <\nabla \psi_d>_\ibold = \frac{1}{A_f\bold}
+  <\nabla \psi_d>_\ibold = \frac{1}{A_\fbold}
   \sum\limits_{p < P_T} p^d C^{p-e^d} \mcal^{p-e^d}
-  \label{eqn::vol}.
+  \label{eqn::faceavg}.
 \end{equation*}
+
+\subsection{Taylor expansion around face}
+
 To solve for the Taylor coefficients, we use the neighboring volumes's
-values  to form a system of equations (equation \ref{eqn::vol}.
+values  to form a system of equations (equation \ref{eqn::volavg}.
 for each volume $\ibold \in N_f$, the neighborhood of $f$).  Boundary
@@
   <\frac{\partial \psi}{\partial x^d}>_\bbold  =
-  \sum\limits_{p < P_T} p^d C^{p} m\limits^{p-e^d}_\bbold = 0.
+  \sum\limits_{p < P_T} p^d C^{p} \mcal^{p-e^d}_\bbold = 0.
 \end{equation}
@@
 \end{equation}
-These normal moments are natural products of the \cite{Schwartz:2015}
+These normal moments are natural products of the \cite{Schwartz2015}
 grid generation algorithm. 
@@
 overdetermined.  Let's say $\ncal_\fbold$ contains $N_B$ boundary faces and
-$N_V$ volumes.   If we are solving for $N_T$ Taylor coefficients, this
-means that we require that $N_T < (N_B+ N_V)$.
+$N_V$ volumes.   To solve for Taylor coefficients, we have a system 
+of the form
+\begin{equation*}
+M C = P 
+\end{equation*}
+where $C=\{C^p\}$,
+
+\begin{equation}
+  M_\fbold =\left\{
+    \begin{array}{c} 
+       m^p_\jbold  \\
+       p^d b^{p-e^d}_\bbold  \\
+       p^d c^{p-e^d}_\cbold  
+    \end{array}
+ \right\},
+\end{equation}
+and
+\begin{equation}
+  P_\fbold =
+    \left\{
+    \begin{array}{c} 
+       <\psi>_\jbold  \\
+      0  \\
+      0  
+    \end{array}
+    \right\}
+\end{equation}
+for every volume $\jbold$, cut face $\cbold$ and domain face $\bbold$
+in $\ncal_\fbold$.
+Since the system is overdetermined, we can introduce a 
+meaningful weighting matrix $W$ \footnotemark[4].
 
@@
   (\cite{ChomboDesign,ChomboDesignEB,ChomboDesign3}
-  box grow semantic. 
+  box grow semantic. }
+\footnotetext[4]{If the matrix $M$ is square, a weighting matrix can
+  have no effect and the Moore-Penrose psueudoinverse becomes
+  $M^{-1}$.}
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-05-23 example/EBCM/hoeb_petsc/_doc/paper.tex
The man that looks behind the door has stood behind the
door.    Checking condition numbers is kinda looking behind the door.

@@
 
-\subsection{Moment matrix}
+\subsection{Taylor expansion around face}
 
@@
 
-\subsection{Taylor expansion around face}
-
 To solve for the Taylor coefficients, we use the neighboring volumes's
-values  to form a system of equations (equation \ref{eqn::volavg}.
+values  to form a system of equations (equation \ref{eqn::volavg})
 for each volume $\ibold \in N_f$, the neighborhood of $f$).  Boundary
@@
 
-\section{Truncation error for Poisson operator with Neumann boundary conditions}
-\section{Dirichlet fluxes at boundaries}
+\section{Solvability of the $A$ matrix}
+
+Overton-Katz, et al. \cite{Katz2023} present the above procedure in
+the absence of boundary condition equtions   They show that, for
+certain values of $P_T$ and $P_N$, the resulting $A$ matrix can have a
+severe mismatch between its largest and smallest eigenvalues,
+resulting in poorly-conditioned matrices.    Their data shows the
+worst solvability issues near the domain boundary.    It stands to
+reason that including boundary condition equations could improve the
+conditioning of the resultant matricies. To test this, we present the
+same measurement of condition number for  several values of $P_T$ and
+$P_N$ where boundary condition equations are included when they are
+part of the neighborhood.
 

### 2023-05-23 example/EBCM/hoeb_petsc/_doc/paper.tex
progress on hoeb_petsc document

@@
 
-\title{Elliptic operator stability and small cells on  finite volume grids}
+\title{Accuracy and stability for elliptic operators
+  in a finite volume context}
 \author{
@@
 \end{equation}
-These moments are the natural product of the grid generation algorithm
+These moments are natural products of the grid generation algorithm
 in \cite{Schwartz2015}.
@@
 \begin{equation}
-\int_{V_\ibold} \nabla \cdot (\nabla \phi ) dV = \int_{\partial
-  V_\ibold} \nabla \phi\cdot \nhat  dA = \int_{V_\ibold} \rho dV
+\int_{V_\ibold} \nabla \cdot (\nabla \psi ) dV = \int_{\partial
+  V_\ibold} \nabla \psi\cdot \nhat  dA = \int_{V_\ibold} \rho dV
 \end{equation}
@@
 \begin{equation}
-\sum_{f: f \in \partial V_\ibold} \nabla \phi \cdot \nhat dA = \int_{V_\ibold} \rho dV
+\sum_{f: f \in \partial V_\ibold} \nabla \psi \cdot \nhat dA = \int_{V_\ibold} \rho dV
 \end{equation}
@@
 \begin{equation}
-\sum_{f: f \in \partial V_\ibold} \avg{\nabla \phi \cdot \nhat}_f A_f
+\sum_{f: f \in \partial V_\ibold} \avg{\nabla \psi \cdot \nhat}_f A_f
 = \avg{\rho}_\ibold V_\ibold
@@
 \begin{equation}
-\psi(\xbold)  =  \sum\limits_{p < P_T} C^p (\xbar -\xbar)^p
+\psi(\xbold)  =  \sum\limits_{p < P_T} C^p (\xbold -\xbar)^p
 \label{eqn::taylor}
@@
   \frac{\partial \psi}{\partial x^d}  =
-  \sum\limits_{p < P_T} p^d C^{p-e^d} (\xbar -\xbar)^{p-e^d}
+  \sum\limits_{p < P_T} p^d C^{p} (\xbar -\xbar)^{p-e^d}
 \end{equation}
@@
   <\nabla \psi_d>_\ibold = \frac{1}{A_\fbold}
-  \sum\limits_{p < P_T} p^d C^{p-e^d} \mcal^{p-e^d}
+  \sum\limits_{p < P_T} p^d C^{p} \mcal^{p-e^d}
   \label{eqn::faceavg}.
 \end{equation*}
+
+\subsection{Boundary condition equations}
 
@@
 grid generation algorithm.
+
+\subsection{Moment matrix $M$ and system matrix $A$}
+
 For each $\cbold$ within the $\ncal_\fbold$, we get an equation of the form
@@
   \int\limits_{A(\cbold)}  \nabla \psi \cdot \nhat dA =
-  \sum\limits_{d < D} \int\limits_{A(\cbold)} \sum_{p < P} p_d C_p
+  \sum\limits_{d < D} \int\limits_{A(\cbold)} \sum_{p < P} p_d C^p
   \xminxbar^{p-e^d} dA
@@
 meaningful weighting matrix $W$ \footnotemark[4]. 
+ Choice of $W$
+is crucial to the stability of these algorithms
+\footnotemark[5].   
+We multiply and solve
+\begin{equation*}
+WMC = WP.
+\end{equation*}
+Since the system is (deliberately) not square, we approximate
+the solution using a Moore-Penrose pseudo-inverse:
+\begin{equation}
+  C = ((WM)^T(WM))^{-1} (WM)^T P.
+\label{eqn::getC}  
+\end{equation}
+where $A \equiv ((WM)^T(WM))_\fbold$ is the system matrix for face
+$\fbold$.
+
+\subsection{Manhattan Distance and the weighting matrix $W$}
+
+All volumes and faces  start with an  index $\ibold \in Z^D$.
+We start from face $\fbold$.   Say we want to get
+the distance from $\fbold$ with index $\ibold$ to a volume $V_1$
+with index $\vbold$.  The distance $D_\fbold(V_1)$ is given by
+the Manhattan disance:
+\begin{equation}
+  D_\fbold{V_1) = \sum\limits_{d \in {1...D}} |\vbold^d - \ibold_0^d|.
+\label{eqn::uptownFunk}
+\end{equation}
+$\gbold_\fbold(V_1)$, the weight of the $V_1$ equation in $\fbold$ system
+is given by
+\begin{equation}
+  \gbold_\fbold(V_1))  \equiv \frac{1}{D\fbold(\V1)^{P_w})},
+\label{eqn::weightFunk}  
+\end{equation}
+where we call $P_w$ the weighting exponent.
+The weighting matrix $W_\fbold = \{\{\wbold_{i,j}\}\}$ is diagonal
+\begin{equation}
+w_{i,j} =
+\left(
+\begin{array}{l}
+ \gbold_\fbold(V_i) \mbox{ if } $(i==j)$)
+ 0  \mbox{otherwise}}
+\end{array}
+\right)
+$$
+Once one has the Taylor coefficients, she can compute the flux through
+the open face using  equation \ref{eqn::faceavg}.   Put into matrix
+form, we define  vector  $Q_\fbold = \{q^p_\fbold\}$:
+$$
+q^p_\fbold = p^d \mcal^{p-e^d}_\fbold
+$$
+and the flux at the face is given by
+$$
+<\nabla \psi>_\fbold = Q C P= Q ((WM)^T(WM))^{-1} (WM)^T  P.
+$$
+One would like to avoid inverting $A$ every time one withes to apply
+an elliptic operator at a point.  Since everything in sight is a
+linear operator, we can simply say that there must exist an equivalent
+operator $S$ such that
+$$
+(S P)_\fbold = <\nabla \psi>_\fbold = Q C= (Q ((WM)^T(WM))^{-1} (WM)^T  P)_\fbold.
+$$
+Since this has to work for all $\psi$, we can define the stencil as
+$$
+ S_\fbold = Q C = (Q ((WM)^T(WM))^{-1} (WM)^T  )_\fbold = Q A^{-1} WM^T.
+ $$
 
@@
 Overton-Katz, et al. \cite{Katz2023} present the above procedure in
-the absence of boundary condition equtions   They show that, for
+the absence of boundary condition equations   They show that, for
 certain values of $P_T$ and $P_N$, the resulting $A$ matrix can have a
 severe mismatch between its largest and smallest eigenvalues,
-resulting in poorly-conditioned matrices.    Their data shows the
-worst solvability issues near the domain boundary.    It stands to
+signalling poorly-conditioned matrices.    Their data shows the
+worst solvability issues occur near the domain boundary.    It stands to
 reason that including boundary condition equations could improve the
@@
 
-\section{Stability and Conditioning}
+\section{Stability and Conditioning of the entire system}
 
-The matrix $A_{P_T, P_W}$ for a particular polynomial order $P_T$ and
+The matrix $L_{P_T, P_W}$ for a particular polynomial order $P_T$ and
 weighting exponent  $P_W$ may be unstable or poorly conditioned.   We
@@
   domain.  We use the   Chombo
-  (\cite{ChomboDesign,ChomboDesignEB,ChomboDesign3}
-  box grow semantic. }
+  (\cite{ChomboDesign,ChomboDesignEB,ChomboDesign3})
+  box growth semantic. }
 \footnotetext[4]{If the matrix $M$ is square, a weighting matrix can
@@
   $M^{-1}$.}
+\footnotetext[5]{The 
+  equations for volumes $\jbold$ where $\xbar_\jbold$ is large
+  receive  higher weights.  Diagonal weighting matricies are common.
+  Usually, these algorithms define a distance metric $D(\ibold, \jbold)$ for
+  two volumes $\ibold$ and $\jbold$.  Typically they make
+  $W_{\jbold,\jbold}$ decrease strongly with increasing 
+  $D(\ibold,\jbold)$ to assign higher importance to the equations for volumes
+  closer to $\ibold$.  Devendran et al. for example \cite{Devendran2017},
+  uses a weighting function that varies with $W_{\ibold,\jbold}
+  \approx 1./D(\ibold,\jbold)^5$ }.
+
 \renewcommand{\thefootnote}{\fnsymbol{footnote}}\

### 2023-05-24 example/EBCM/hoeb_petsc/_doc/paper.tex
I believe that this document clearly defines how the next angel will enter the dance on our particular pinhead

@@
 $\nabla \psi \cdot \nhat = 0 |\partial \Omega$.  In this case, to
-describe the algorithm, we need only describe how to compute $<\nabla
-\psi \cdot \nhat>$ on open faces.
+describe the algorithm, we need only describe how to compute 
+$<\nabla\psi \cdot \nhat>$ on open faces.
 
@@
 \begin{equation}
-  D_\fbold{V_1) = \sum\limits_{d \in {1...D}} |\vbold^d - \ibold_0^d|.
+  D_\fbold(V_1) = \sum\limits_{0 <= d < D} |\vbold^d - \ibold_0^d|.
 \label{eqn::uptownFunk}
@@
 \begin{equation}
-  \gbold_\fbold(V_1))  \equiv \frac{1}{D\fbold(\V1)^{P_w})},
+  \gbold_\fbold(V_1)  \equiv \left(\frac{1}{D_\fbold(V_1) } \right)^{P_w},
 \label{eqn::weightFunk}  
@@
 \left(
-\begin{array}{l}
- \gbold_\fbold(V_i) \mbox{ if } $(i==j)$)
- 0  \mbox{otherwise}}
+\begin{array}{ll}
+ \gbold_\fbold(V_i) & \mbox{ if } $(i==j)$ \\
+ 0   & \mbox{ otherwise }
 \end{array}
 \right)
-$$
+\end{equation}
 Once one has the Taylor coefficients, she can compute the flux through
@@
 form, we define  vector  $Q_\fbold = \{q^p_\fbold\}$:
-$$
+\begin{equation}
 q^p_\fbold = p^d \mcal^{p-e^d}_\fbold
-$$
+\end{equation}
 and the flux at the face is given by
-$$
+\begin{equation}
 <\nabla \psi>_\fbold = Q C P= Q ((WM)^T(WM))^{-1} (WM)^T  P.
-$$
-One would like to avoid inverting $A$ every time one withes to apply
+\end{equation}
+
+\subsection{Stencil formulation}
+One would like to avoid inverting $A$ every time she wishes to apply
 an elliptic operator at a point.  Since everything in sight is a
@@
 operator $S$ such that
-$$
+\begin{equation}
 (S P)_\fbold = <\nabla \psi>_\fbold = Q C= (Q ((WM)^T(WM))^{-1} (WM)^T  P)_\fbold.
-$$
+\end{equation}
 Since this has to work for all $\psi$, we can define the stencil as
-$$
+\begin{equation}
  S_\fbold = Q C = (Q ((WM)^T(WM))^{-1} (WM)^T  )_\fbold = Q A^{-1} WM^T.
- $$
+\end{equation}
 

### 2023-05-24 example/EBCM/hoeb_petsc/_doc/paper.tex
some grammar fixes

@@
 linear operator, we can simply say that there must exist an equivalent
-operator $S$ such that
+linear operator $S$ such that
 \begin{equation}
@@
 \end{equation}
-Since this has to work for all $\psi$, we can define the stencil as
+Since this equivalence has to hold for all $\psi$, the stencil $S$ must be
+given by:
 \begin{equation}
@@
 Overton-Katz, et al. \cite{Katz2023} present the above procedure in
-the absence of boundary condition equations   They show that, for
+the absence of boundary condition equations.   They show that, for
 certain values of $P_T$ and $P_N$, the resulting $A$ matrix can have a
 severe mismatch between its largest and smallest eigenvalues,
-signalling poorly-conditioned matrices.    Their data shows the
+signalling that $A$ is poorly conditioned.    Their data show the
 worst solvability issues occur near the domain boundary.    It stands to

### 2023-05-24 example/EBCM/hoeb_petsc/elliptic_operator_test.cpp
three yards and a cloud of dust

@@ -44,6 +44,7 @@ typedef ch_eigen::Matrix                               eigen_mat;
 
 /****/
 
+
 int main(int a_argc, char* a_argv[])
 {
 #ifdef CH_MPI
@@ -68,30 +69,30 @@ int main(int a_argc, char* a_argv[])
     int order;
     ParmParse pp("main");
     pp.get("polynomial_order", order);
-    Chombo4::pout() <<  "Running test for polynomial order = " << order << endl;
+    Chombo4::pout() <<  "Running hoeb_petsc_test for polynomial order = " << order << endl;
     if(order == 6)
     {
-      EBCM::Algorithm_Framework<6>::runTests();
+      EBCM::Algorithm_Framework<6>::run_hoeb_petsc_tests();
     }
     else if(order == 5)
     {
-      EBCM::Algorithm_Framework<5>::runTests();
+      EBCM::Algorithm_Framework<5>::run_hoeb_petsc_tests();
     }
     if(order == 4)
     {
-      EBCM::Algorithm_Framework<4>::runTests();
+      EBCM::Algorithm_Framework<4>::run_hoeb_petsc_tests();
     }
     else if(order == 3)
     {
-      EBCM::Algorithm_Framework<3>::runTests();
+      EBCM::Algorithm_Framework<3>::run_hoeb_petsc_tests();
     }
     else if(order == 2)
     {
-      EBCM::Algorithm_Framework<2>::runTests();
+      EBCM::Algorithm_Framework<2>::run_hoeb_petsc_tests();
     }
     else if(order == 1)
     {
-      EBCM::Algorithm_Framework<1>::runTests();
+      EBCM::Algorithm_Framework<1>::run_hoeb_petsc_tests();
     }
     else
     {

### 2023-05-24 src/EBCM/Chombo_EBCM_Algorithm_Framework.H

@@ -47,6 +47,38 @@ namespace EBCM
   class Algorithm_Framework
   {
   public:
+    ///test function for example/EBCM/hoeb_petsc_test
+  static  void run_hoeb_petsc_tests()
+    {
+    CH_TIME("EBCM_Framework::runTests");
+    //linear algebra machinery check
+    runEigenTests();
+    //the important stuff
+    //see if we can make a geometry
+    shared_ptr< ebcm_meta  > ebcm;
+    ch_dbl                   grids;
+    double                   dx;
+    ch_probdom               domain;
+    makeMergedGeometry(ebcm, grids, dx, domain, true, true);
+
+    Real maxKapp, minKapp;
+    //this tries out iteration and checks kappa
+    checkKappa(maxKapp, minKapp, ebcm, grids);
+
+    //makes data of inv condition number info and plots it out
+    shared_ptr<ebcm_leveldata> invCondition;
+    shared_ptr<condition_t>    worst;
+    getConditionNumberData(invCondition, worst, ebcm);
+
+    worst->poutLatexTable();
+    Chombo4::pout() << "worst condition number at point " << worst->m_pt << endl;
+    
+    string plot_filename;
+    ParmParse ppmain("main");  //kinda pendantic to use anything else
+    ppmain.get("inv_cond_filename",   plot_filename);
+    invCondition->writeToHDF5(plot_filename);
+    
+  }
     Algorithm_Framework()
     {}    
   

### 2023-05-25 example/EBCM/hoeb_petsc/_doc/paper.tex
made an appalling sentence a bit less egregious

@@
   receive  higher weights.  Diagonal weighting matricies are common.
-  Usually, these algorithms define a distance metric $D(\ibold, \jbold)$ for
-  two volumes $\ibold$ and $\jbold$.  Typically they make
+  Usually these algorithms define a distance metric $D(\ibold, \jbold)$ for
+  two volumes $\ibold$ and $\jbold$ and make
   $W_{\jbold,\jbold}$ decrease strongly with increasing 
-  $D(\ibold,\jbold)$ to assign higher importance to the equations for volumes
+  $D(\ibold,\jbold)$.  This assign higher importance to the equations for volumes
   closer to $\ibold$.  Devendran et al. for example \cite{Devendran2017},
-  uses a weighting function that varies with $W_{\ibold,\jbold}
+  uses a weighting function  $W_{\ibold,\jbold}
   \approx 1./D(\ibold,\jbold)^5$ }.

### 2023-05-25 example/EBCM/hoeb_petsc/_doc/paper.tex
made inroads into next framework test

@@
 
-To solve for the Taylor coefficients, we use the neighboring volumes's
-values  to form a system of equations (equation \ref{eqn::volavg})
+To solve for the Taylor coefficients, we use the neighboring volumes'
+values  to form a system of equations (equation \ref{eqn::volavg}
 for each volume $\ibold \in N_f$, the neighborhood of $f$).  Boundary

### 2023-05-30 src/EBCM/Chombo_EBCM_Algorithm_Framework.H
the Neumann domain bc equation code now compiles

@@ -32,9 +32,9 @@ namespace EBCM
   typedef Chombo4::IntVect                               ch_iv;
   typedef Chombo4::MayDay                                ch_mayday;
   typedef Proto::RealVect                                pr_rv;
-  typedef Proto::IndexTM<Real, DIM>                      pr_itm_r_dim;
+  typedef Proto::IndexTM<double, DIM>                      pr_itm_r_dim;
   typedef Proto::IndexTM<int , DIM>                      pr_itm_i_dim;
-  typedef Proto::IndexTM<Real, DIM-1>                    pr_itm_r_dmo;
+  typedef Proto::IndexTM<double, DIM-1>                    pr_itm_r_dmo;
   typedef Proto::IndexTM<int , DIM-1>                    pr_itm_i_dmo;
   typedef Proto::BaseIF                                  pr_baseif;
   typedef Proto::Point                                   pr_pt;
@@ -49,7 +49,7 @@ namespace EBCM
   class Algorithm_Framework
   {
   public:
-    typedef EBCM::HostLevelData<Real, 1, ebcm_order >      ebcm_leveldata;
+    typedef EBCM::HostLevelData<double, 1, ebcm_order >      ebcm_leveldata;
     typedef    EBCM::MetaDataLevel<         ebcm_order >   ebcm_meta;
     typedef    EBCM::SubVolumeVector  <     ebcm_order >   ebcm_subvol_vec;
     typedef    EBCM::EBCM_Volu<             ebcm_order >   ebcm_volu;
@@ -101,7 +101,9 @@ namespace EBCM
     static inline void
     getConditionNumberData(shared_ptr<ebcm_leveldata>      & a_data,
                            shared_ptr<condition_t>         & a_worst,
-                           const shared_ptr< ebcm_meta  >  & a_ebcm)
+                           const shared_ptr< ebcm_meta  >  & a_ebcm,
+                           const string                    & a_dom_bc,
+                           const string                    & a_eb_bc)
     {
     
       CH_TIME("EBCM_Framework::getConditionNumberData");
@@ -132,7 +134,7 @@ namespace EBCM
           int worst_face_dir, worst_face_index;
           getWorstConditionNumberInfo(invCondNum, maxEig, minEig,
                                       worst_face_dir, worst_face_index,
-                                      volu, graph, printedOne);
+                                      volu, graph, a_dom_bc, a_eb_bc, printedOne);
[…]

### 2023-06-02 src/EBCM/Chombo_EBCM_Algorithm_Framework.H
hoeb_petsc test seems to work.  on to data collection

@@ -196,7 +196,7 @@ namespace EBCM
         int vecIndex;
         getWorstConditionNumberInfo<YFACE>(worstCond, maxEigen, minEigen, vecIndex,
                                            a_volu.m_yfaces, a_graph, stenrad, weightpower,
-                                           a_dom_bc, a_eb_bc, a_print);
+                                           a_dom_bc, a_eb_bc, false);
         if(worstCond < a_invCondNumber)
         {
           a_face_dir       = 1;
@@ -215,7 +215,7 @@ namespace EBCM
         int    vecIndex;
         getWorstConditionNumberInfo<ZFACE>(worstCond, maxEigen, minEigen, vecIndex,
                                            a_volu.m_zfaces, a_graph, stenrad, weightpower, 
-                                           a_dom_bc, a_eb_bc, a_print);
+                                           a_dom_bc, a_eb_bc, false);
         if(worstCond < a_invCondNumber)
         {
           a_face_dir      = 2;

### 2023-06-02 example/EBCM/hoeb_petsc/_test_harness/submit_the_world.sh
let the machine do the work

@@ -1,0 +1,20 @@
+#!/bin/csh -f
+
+
+echo "cd _all_regular_2d_6_2_2023; source ./submit.all_regular_2d.jobs >& submit.out; cd .."
+cd       _all_regular_2d_6_2_2023; source ./submit.all_regular_2d.jobs >& submit.out; cd ..
+
+echo "cd      _merged_2d_6_2_2023; source      ./submit.merged_2d.jobs >& submit.out; cd .."
+cd            _merged_2d_6_2_2023; source      ./submit.merged_2d.jobs >& submit.out; cd ..
+
+echo "cd    _unmerged_2d_6_2_2023; source    ./submit.unmerged_2d.jobs >& submit.out; cd .."
+cd          _unmerged_2d_6_2_2023; source    ./submit.unmerged_2d.jobs >& submit.out; cd ..
+
+echo "cd _all_regular_3d_6_2_2023; source ./submit.all_regular_3d.jobs >& submit.out; cd .."
+cd       _all_regular_3d_6_2_2023; source ./submit.all_regular_3d.jobs >& submit.out; cd ..
+
+echo "cd      _merged_3d_6_2_2023; source      ./submit.merged_3d.jobs >& submit.out; cd .."
+cd            _merged_3d_6_2_2023; source      ./submit.merged_3d.jobs >& submit.out; cd ..
+
+echo "cd    _unmerged_3d_6_2_2023; source    ./submit.unmerged_3d.jobs >& submit.out; cd .."
+cd          _unmerged_3d_6_2_2023; source    ./submit.unmerged_3d.jobs >& submit.out; cd ..

### 2023-06-22 example/EBCM/hoeb_petsc/_doc/paper.tex
the Neumann domain bc equation code now compiles
getting pretty consistent solvability results

@@
 
-\section{Solvability of the $A$ matrix}
+\section{Solvability of the system matrix $A$}
 
@@
 $P_N$ where boundary condition equations are included when they are
-part of the neighborhood.
+part of the neighborhood.    We present the results for the same three
+different geometries used in \cite{Katz2023}.  In figure \ref{fig::allRegSolvability} we show
+the worst condition numbers where there are no cut cells.
+In figure \ref{fig::unmergedSolvability}, we show the worst condition
+number where we cut the unit domain with a centered sphere of radius
+0.45 (this geometry includes very small volumes).    Finally, in
+figure \ref{fig::mergedSolvability}, we present results all small
+volumes have been merged with neighbors.
+
+The data paint a very consistent picture,   Though adding boundary
+condition equations does improve the solvability of $A$, aggressive
+choices of $P_W$ and $P_T$ can lead to system matricies that cannot be
+credibly solved without very high precision numerical arithmetic.
+\begin{small}
+\begin{table}
+\begin{center}
+\begin{tabular}{|ccc|ccc|} \hline
+ $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
+ \hline
+2 & 1 & 1 &  1.537125e+00 & 1.150772e-03 & 7.486517e-04 \\
+2 & 1 & 2 &  4.940953e-01 & 9.196245e-05 & 1.861229e-04 \\
+2 & 1 & 3 &  3.324177e-01 & 1.064946e-05 & 3.203639e-05 \\
+2 & 1 & 4 &  2.853322e-01 & 1.705230e-06 & 5.976295e-06 \\
+2 & 1 & 5 &  2.665812e-01 & 3.349335e-07 & 1.256403e-06 \\
+2 & 2 & 1 &  2.407807e+00 & 1.457063e-06 & 6.051408e-07 \\
+2 & 2 & 2 &  4.940956e-01 & 5.469314e-08 & 1.106934e-07 \\
+2 & 2 & 3 &  3.324177e-01 & 2.879583e-09 & 8.662545e-09 \\
+2 & 2 & 4 &  2.853323e-01 & 1.628939e-10 & 5.708921e-10 \\
+2 & 2 & 5 &  2.665812e-01 & 1.084310e-11 & 4.067466e-11 \\
+2 & 3 & 1 &  2.407807e+00 & 5.822902e-10 & 2.418342e-10 \\
+2 & 3 & 2 &  9.272889e-01 & 4.520282e-11 & 4.874729e-11 \\ 
+2 & 3 & 3 &  3.324177e-01 & 1.618058e-12 & 4.867544e-12 \\
+2 & 3 & 4 &  2.853323e-01 & 7.227717e-14 & 2.533088e-13 \\
+2 & 3 & 5 &  2.665812e-01 & 3.194386e-15 & 1.198279e-14 \\
+2 & 4 & 1 &  1.880177e+00 & 1.535955e-25 & 8.169205e-26 \\
+2 & 4 & 2 &  9.272889e-01 & 1.098665e-27 & 1.184814e-27 \\
+2 & 4 & 3 &  6.561304e-01 & 5.104096e-28 & 7.779089e-28 \\
+2 & 4 & 4 &  2.868930e-01 & 3.731928e-27 & 1.300808e-26 \\
+2 & 4 & 5 &  5.327046e-01 & 5.118416e-25 & 9.608357e-25 \\
+\hline
+3 & 1 & 1 &  4.639099e+00 & 3.887142e-03 & 8.379088e-04 \\ 
+3 & 1 & 2 &  1.079504e+00 & 2.369894e-04 & 2.195354e-04 \\ 
+3 & 1 & 3 &  6.747118e-01 & 2.359590e-05 & 3.497182e-05 \\ 
+3 & 1 & 4 &  5.721834e-01 & 3.540976e-06 & 6.188534e-06 \\ 
+3 & 1 & 5 &  5.333668e-01 & 6.792558e-07 & 1.273525e-06 \\ 
+3 & 2 & 1 &  4.639156e+00 & 3.176883e-06 & 6.847975e-07 \\ 
+3 & 2 & 2 &  1.079505e+00 & 1.512048e-07 & 1.400686e-07 \\ 
+3 & 2 & 3 &  6.747119e-01 & 6.991076e-09 & 1.036157e-08 \\ 
+3 & 2 & 4 &  5.721835e-01 & 3.641527e-10 & 6.364265e-10 \\ 
+3 & 2 & 5 &  2.669165e-01 & 1.146071e-11 & 4.293744e-11 \\ 
+3 & 3 & 1 &  4.639157e+00 & 1.340233e-09 & 2.888959e-10 \\ 
+3 & 3 & 2 &  1.079505e+00 & 7.151353e-11 & 6.624659e-11 \\ 
+3 & 3 & 3 &  6.747119e-01 & 3.977531e-12 & 5.895155e-12 \\ 
+3 & 3 & 4 &  2.869943e-01 & 5.757645e-14 & 2.006188e-13 \\ 
+3 & 3 & 5 &  2.669165e-01 & 1.723124e-15 & 6.455665e-15 \\ 
+3 & 4 & 1 &  6.402997e+00 & 5.729285e-26 & 8.947817e-27 \\ 
+3 & 4 & 2 &  1.079505e+00 & 1.226846e-27 & 1.136489e-27 \\ 
+3 & 4 & 3 &  6.907344e-01 & 1.049444e-28 & 1.519317e-28 \\ 
+3 & 4 & 4 &  2.903904e-01 & 8.442770e-26 & 2.907386e-25 \\ 
+3 & 4 & 5 &  5.333668e-01 & 5.987514e-25 & 1.122588e-24 \\ 
+\hline
+\end{tabular}
+\end{center}
+\label{fig::allRegSolvability}
+\caption
+    {
+      We show the lowest value of
+      $\cali$ for an entire Cartesian grid of size $32^D$.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$. 
+    }
+\end{table}
+\end{small}
+
+\begin{small}
+\begin{table}
+\begin{center}
+\begin{tabular}{|ccc|ccc|} \hline
+ $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$  \\
+   \hline
+2 & 1 & 1 &  3.244145e+00 & 5.576001e-03 & 1.718789e-03 \\ 
+2 & 1 & 2 &  1.108699e+00 & 5.218520e-04 & 4.706884e-04 \\ 
+2 & 1 & 3 &  6.816993e-01 & 4.992473e-05 & 7.323570e-05 \\ 
+2 & 1 & 4 &  5.736425e-01 & 7.273424e-06 & 1.267937e-05 \\ 
+2 & 1 & 5 &  5.336857e-01 & 1.374234e-06 & 2.574988e-06 \\ 
+2 & 2 & 1 &  2.762140e+00 & 6.863083e-06 & 2.484698e-06 \\ 
+2 & 2 & 2 &  9.453294e-01 & 7.653732e-07 & 8.096365e-07 \\ 
+2 & 2 & 3 &  6.816994e-01 & 4.112367e-08 & 6.032523e-08 \\ 
+2 & 2 & 4 &  5.736426e-01 & 3.156232e-09 & 5.502089e-09 \\ 
+2 & 2 & 5 &  5.336858e-01 & 4.220417e-10 & 7.908057e-10 \\ 
+2 & 3 & 1 &  2.762140e+00 & 2.066812e-09 & 7.482649e-10 \\ 
+2 & 3 & 2 &  9.453294e-01 & 1.559241e-10 & 1.649416e-10 \\ 
+2 & 3 & 3 &  6.574277e-01 & 2.360967e-11 & 3.591220e-11 \\ 
+2 & 3 & 4 &  5.705795e-01 & 4.724557e-12 & 8.280278e-12 \\ 
+2 & 3 & 5 &  5.336858e-01 & 2.690617e-13 & 5.041575e-13 \\ 
+2 & 4 & 1 &  2.762140e+00 & 3.535738e-13 & 1.280072e-13 \\ 
+2 & 4 & 2 &  9.453294e-01 & 3.267022e-14 & 3.455962e-14 \\ 
+2 & 4 & 3 &  6.574277e-01 & 3.738186e-15 & 5.686079e-15 \\ 
+2 & 4 & 4 &  5.691873e-01 & 3.830503e-16 & 6.729777e-16 \\ 
+2 & 4 & 5 &  5.328410e-01 & 8.531691e-17 & 1.601170e-16 \\
+\hline
+3 & 1 & 1 &  7.242861e+00 & 4.674236e-03 & 6.453577e-04 \\ 
+3 & 1 & 2 &  1.181250e+00 & 2.657202e-04 & 2.249483e-04 \\ 
+3 & 1 & 3 &  6.863432e-01 & 3.329115e-05 & 4.850511e-05 \\ 
+3 & 1 & 4 &  5.741086e-01 & 4.562521e-06 & 7.947139e-06 \\ 
+3 & 1 & 5 &  5.350591e-01 & 1.455556e-06 & 2.720366e-06 \\ 
+3 & 2 & 1 &  7.433403e+00 & 2.264150e-06 & 3.045914e-07 \\ 
+3 & 2 & 2 &  1.181248e+00 & 1.685503e-07 & 1.426883e-07 \\ 
+3 & 2 & 3 &  6.804738e-01 & 1.353871e-08 & 1.989600e-08 \\ 
+3 & 2 & 4 &  5.806933e-01 & 2.036542e-09 & 3.507086e-09 \\ 
+3 & 2 & 5 &  5.350591e-01 & 1.066432e-10 & 1.993110e-10 \\ 
+3 & 3 & 1 &  7.433404e+00 & 8.925217e-10 & 1.200690e-10 \\ 
+3 & 3 & 2 &  1.182547e+00 & 8.635683e-11 & 7.302615e-11 \\ 
+3 & 3 & 3 &  6.804738e-01 & 4.819403e-12 & 7.082423e-12 \\ 
+3 & 3 & 4 &  5.729018e-01 & 3.780488e-13 & 6.598842e-13 \\ 
+3 & 3 & 5 &  5.350591e-01 & 6.218451e-14 & 1.162199e-13 \\ 
+3 & 4 & 1 &  7.433404e+00 & 1.727339e-13 & 2.323753e-14 \\ 
+3 & 4 & 2 &  1.182547e+00 & 2.186136e-14 & 1.848668e-14 \\ 
+3 & 4 & 3 &  6.804738e-01 & 1.827956e-15 & 2.686299e-15 \\ 
+3 & 4 & 4 &  5.728477e-01 & 7.990908e-17 & 1.394944e-16 \\ 
+3 & 4 & 5 &  5.338853e-01 & 1.743421e-17 & 3.265535e-17 \\ 
+\hline
+\end{tabular}
+\end{center}
+\label{fig::unmergedSolvability}
+\caption
+    {
+      We show the lowest value of
+      $\cali$ for an entire Cartesian grid of size $32^D$.
+      The grid covers the unit square and is cut by a sphere of radius 0.45.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$.    This grid
+      includes very small volumes.
+    }
+\end{table}
+\end{small}
+
+\begin{small}
+\begin{table}
+\begin{center}
+  \begin{tabular}{|ccc|ccc|} \hline
+ $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
+  \hline
+2 & 1 & 1 &  3.110810e+00 & 6.876828e-04 & 2.210623e-04 \\ 
+2 & 1 & 2 &  1.820276e+00 & 2.935551e-04 & 1.612695e-04 \\ 
+2 & 1 & 3 &  6.689318e-01 & 2.783647e-05 & 4.161332e-05 \\ 
+2 & 1 & 4 &  3.112964e-01 & 3.804498e-06 & 1.222146e-05 \\ 
+2 & 1 & 5 &  2.931197e-01 & 4.648824e-07 & 1.585981e-06 \\ 
+2 & 2 & 1 &  4.649575e+00 & 1.222691e-06 & 2.629683e-07 \\ 
+2 & 2 & 2 &  2.800875e+00 & 4.389241e-07 & 1.567096e-07 \\ 
+2 & 2 & 3 &  1.156823e+00 & 4.756446e-08 & 4.111647e-08 \\ 
+2 & 2 & 4 &  1.020254e+00 & 3.829097e-09 & 3.753083e-09 \\   
+2 & 2 & 5 &  9.591803e-01 & 4.980114e-10 & 5.192052e-10 \\ 
+2 & 3 & 1 &  8.598864e-01 & 3.926204e-10 & 4.565956e-10 \\ 
+2 & 3 & 2 &  3.682481e+00 & 6.386263e-10 & 1.734228e-10 \\ 
+2 & 3 & 3 &  1.036128e+00 & 1.177339e-11 & 1.136288e-11 \\ 
+2 & 3 & 4 &  9.070960e-01 & 5.028483e-13 & 5.543495e-13 \\ 
+2 & 3 & 5 &  8.510270e-01 & 3.323827e-14 & 3.905666e-14 \\ 
+2 & 4 & 1 &  9.197999e-01 & 3.623068e-14 & 3.938974e-14 \\ 
+2 & 4 & 2 &  7.945940e-02 & 1.618085e-15 & 2.036366e-14 \\ 
+2 & 4 & 3 &  1.186857e+00 & 4.379402e-15 & 3.689917e-15 \\ 
+2 & 4 & 4 &  1.039000e+00 & 3.390648e-16 & 3.263375e-16 \\ 
+2 & 4 & 5 &  2.958494e-01 & 1.292309e-17 & 4.368131e-17 \\
+\hline
+3 & 1 & 1 &  5.044398e+00 & 6.813020e-04 & 1.350611e-04 \\
+3 & 1 & 2 &  2.141787e+00 & 2.336010e-05 & 1.090683e-05 \\
+3 & 1 & 3 &  1.663929e+00 & 8.355671e-07 & 5.021651e-07 \\
+3 & 1 & 4 &  1.479289e+00 & 9.414478e-08 & 6.364192e-08 \\
+3 & 1 & 5 &  3.223939e-01 & 1.193480e-08 & 3.701931e-08 \\
+3 & 2 & 1 &  6.441253e+00 & 1.723363e-07 & 2.675509e-08 \\
+3 & 2 & 2 &  3.588187e+00 & 1.066316e-08 & 2.971741e-09 \\
+3 & 2 & 3 &  2.800032e+00 & 9.932906e-10 & 3.547425e-10 \\
+3 & 2 & 4 &  2.491816e+00 & 2.063069e-10 & 8.279378e-11 \\
+3 & 2 & 5 &  6.820526e-01 & 2.306368e-11 & 3.381511e-11 \\
+3 & 3 & 1 &  2.508964e+00 & 1.541288e-11 & 6.143127e-12 \\
+3 & 3 & 2 &  4.951047e+00 & 1.076120e-11 & 2.173521e-12 \\
+3 & 3 & 3 &  3.867831e+00 & 1.354407e-12 & 3.501722e-13 \\
+3 & 3 & 4 &  2.166936e+00 & 8.701202e-14 & 4.015441e-14 \\
+3 & 3 & 5 &  2.040600e+00 & 3.890155e-15 & 1.906378e-15 \\
+3 & 4 & 1 &  2.418622e+00 & 1.859733e-15 & 7.689226e-16 \\
+3 & 4 & 2 &  1.286816e+00 & 1.115219e-15 & 8.666503e-16 \\
+3 & 4 & 3 &  9.013057e-01 & 9.738926e-17 & 1.080535e-16 \\
+3 & 4 & 4 &  7.856540e-01 & 2.968168e-17 & 3.777958e-17 \\
+3 & 4 & 5 &  9.668729e-01 & 1.139377e-17 & 1.178415e-17 \\
+\hline
+\end{tabular}
+\end{center}
+\label{fig::mergedSolvability}
+\caption
+    {
+      We show the lowest value of
+      $\cali$ for an entire Cartesian grid of size $32^D$.
+      The grid covers the unit square and is cut by a sphere of radius 0.45.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$.    This grid
+      has had its small volumes merged with neighboring volumes.
+    }
+\end{table}
+\end{small}
 

### 2023-06-26 example/EBCM/hoeb_petsc/_doc/paper.tex
added some text on Dirichlet boundary conditions

@@
 \section{Open face Poisson flux computation with Neumann boundary conditions}
-
+\label{sec::openface}
 An open face is one that connects two volumes in the solution.  These
@@
 
+\section{Domain face Poisson flux computation with Dirichlet boundary
+  conditions}
+
+Neumann boundary conditions are a proscribed flux when solving
+Poisson's equation.     When we have Dirichlet boundary conditions
+either at the domain box boundary or at a cut face, we must calculate
+the flux through that face.
+
+For context, allow us to recap a relevant bit of finite volume formalism.
+Consider a volume $\ibold$ bounded by the set of faces
+$\{f\}  = \partial \ibold$, where the outward-facing normal $\nhat$ of
+each face is known, as is its  $V_\ibold$.
+Given a flux function $F$, the average divergence $< \nabla \cdot F >$
+is given by the divergence theorem:
+\begin{equation}
+\begin{array}{l l}
+< \nabla \cdot F > &= \frac{1}{V_\ibold} \int_\ibold \nabla \cdot F dV \\
+           &= \frac{1}{V_\ibold} \int_{\partial \ibold} F\cdot \nhat dA \\
+           &= \frac{1}{V_\ibold} \sum_{f \in \partial
+  \ibold}\int_{\partial \ibold} F\cdot \nhat dA.
+\end{array}
+\label{eqn::discreteDivergence}
+\end{equation}
+For all coordinate-alligned faces, the section above's description for how to
+compute the flux is adequate.   What remains are fluxes through cut
+faces.
+
+We start with a smooth function $\psi$ which we we expand using Taylor
+(equation \ref{eqn::taylor}).  At each cut face $f$ with area $A_f$,
+we wish to compute the average flux $< \nabla \psi \cdot \nhat >_f$
+through that face.
+\begin{equation}
+\begin{array}{l l }
+  < \nabla \psi \cdot \nhat >_f
+  &= \frac{1}{A_f} \int_f \nabla \psi \cdot \nhat dA \\
+  &= \frac{1}{A_f} \int_f \sum_{p \in P} \sum_{0 <= d <D}  (p-e^d) C_p
+  \ecal^{p-e^d} n^d dA
+\end{array}
+\end{equation}
+where the normal moments
+\begin{equation}
+$$
+\ecal^{\pbold, d}_\cbold  =  \int\limits_{A(\cbold)} \xminxbar n^d  dA
+$$
+are natural products of the \cite{Schwartz2015} grid generation
+algorithm.   Except in that we are using the normal moments, this is
+semantically the same dance we used to calculate open face fluxes.
+
+\subsection{The effect of Dirichlet boundary conditions on
+  solvability}
+In section \label{sec::openface}, we discuss how  adding Neumann
+boundary condition equations can improve the conditioning of the
+system matrix.
+
 \section{Stability and Conditioning of the entire system}

### 2023-06-29 example/EBCM/hoeb_petsc/_doc/paper.tex
updating hoeb_petsc document to include Dirichlet data

@@
       We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$.
+      $\cali$ for an entire Cartesian grid of size $32^D$
+      with all
+      boundary conditions homogeneous Neumann.
       We vary Taylor power $P^T$, weighting
@@
       We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$.
+      $\cali$ for an entire Cartesian grid of size $32^D$ with all
+      boundary conditions homogeneous Neumann.
       The grid covers the unit square and is cut by a sphere of radius 0.45.
@@
       We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$.
+      $\cali$ for an entire Cartesian grid of size $32^D$
+      with all
+      boundary conditions homogeneous Neumann.
       The grid covers the unit square and is cut by a sphere of radius 0.45.
@@
 \begin{equation}
-$$
 \ecal^{\pbold, d}_\cbold  =  \int\limits_{A(\cbold)} \xminxbar n^d  dA
-$$
+\end{equation}
 are natural products of the \cite{Schwartz2015} grid generation
@@
 \subsection{The effect of Dirichlet boundary conditions on
-  solvability}
-In section \label{sec::openface}, we discuss how  adding Neumann
-boundary condition equations can improve the conditioning of the
-system matrix.
+  system matrix conditioning} In section \ref{sec::openface}, we
+discuss how adding Neumann boundary condition equations can improve
+the conditioning of the system matrix.  When the boundary conditions
+are set to Dirichlet, we get similar results.  See tables
+\ref{fig::mergedDiri}, \ref{fig::unmergedDiri}, and
+\ref{fig::allRegDiri} for details.  Again, boundary conditions help
+stabilize the system but it is still the case that agressive choices
+of $P_T$ or $P_W$ can result in system matrices that cannot be
+credibly inverted without very high precision numerical arithmetic.
+Again, this seems less a matter of a particular grid configuration and
+more  a property of the mathematical framework used to generate the stencil.
+\begin{small}
+\begin{table}
+\begin{center}
+\begin{tabular}{|ccc|ccc|} \hline
+ $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
+ \hline
+2 & 1 & 1 &  1.537125e+00 & 1.150772e-03 & 7.486517e-04 \\ 
+2 & 1 & 2 &  4.940953e-01 & 9.196245e-05 & 1.861229e-04 \\ 
+2 & 1 & 3 &  3.324177e-01 & 1.064946e-05 & 3.203639e-05 \\ 
+2 & 1 & 4 &  2.853322e-01 & 1.705230e-06 & 5.976295e-06 \\ 
+2 & 1 & 5 &  2.665812e-01 & 3.349335e-07 & 1.256403e-06 \\ 
+2 & 2 & 1 &  2.407807e+00 & 1.457063e-06 & 6.051408e-07 \\ 
+2 & 2 & 2 &  4.940956e-01 & 5.469314e-08 & 1.106934e-07 \\ 
+2 & 2 & 3 &  3.324177e-01 & 2.879583e-09 & 8.662545e-09 \\ 
+2 & 2 & 4 &  2.853323e-01 & 1.628939e-10 & 5.708921e-10 \\ 
+2 & 2 & 5 &  2.665812e-01 & 1.084310e-11 & 4.067466e-11 \\ 
+2 & 3 & 1 &  2.407807e+00 & 5.822902e-10 & 2.418342e-10 \\ 
+2 & 3 & 2 &  9.272889e-01 & 4.520282e-11 & 4.874729e-11 \\ 
+2 & 3 & 3 &  3.324177e-01 & 1.618058e-12 & 4.867544e-12 \\ 
+2 & 3 & 4 &  2.853323e-01 & 7.227717e-14 & 2.533088e-13 \\ 
+2 & 3 & 5 &  2.665812e-01 & 3.194386e-15 & 1.198279e-14 \\ 
+2 & 4 & 1 &  2.943604e+00 & 6.445948e-26 & 2.189815e-26 \\ 
+2 & 4 & 2 &  9.877639e-01 & 6.302117e-27 & 6.380185e-27 \\ 
+2 & 4 & 3 &  6.561304e-01 & 6.778809e-28 & 1.033150e-27 \\ 
+2 & 4 & 4 &  2.868930e-01 & 5.733222e-27 & 1.998383e-26 \\ 
+2 & 4 & 5 &  5.327046e-01 & 5.117605e-25 & 9.606835e-25 \\
+\hline
+3 & 1 & 1 &  4.639099e+00 & 3.887142e-03 & 8.379088e-04 \\ 
+3 & 1 & 2 &  1.079504e+00 & 2.369894e-04 & 2.195354e-04 \\ 
+3 & 1 & 3 &  6.747118e-01 & 2.359590e-05 & 3.497182e-05 \\ 
+3 & 1 & 4 &  5.721834e-01 & 3.540976e-06 & 6.188534e-06 \\ 
+3 & 1 & 5 &  5.333668e-01 & 6.792558e-07 & 1.273525e-06 \\ 
+3 & 2 & 1 &  4.639156e+00 & 3.176883e-06 & 6.847975e-07 \\ 
+3 & 2 & 2 &  1.079505e+00 & 1.512048e-07 & 1.400686e-07 \\ 
+3 & 2 & 3 &  6.747119e-01 & 6.991076e-09 & 1.036157e-08 \\ 
+3 & 2 & 4 &  5.721835e-01 & 3.641527e-10 & 6.364265e-10 \\ 
+3 & 2 & 5 &  2.669165e-01 & 1.146071e-11 & 4.293744e-11 \\ 
+3 & 3 & 1 &  4.639157e+00 & 1.340233e-09 & 2.888959e-10 \\ 
+3 & 3 & 2 &  1.079505e+00 & 7.151353e-11 & 6.624659e-11 \\ 
+3 & 3 & 3 &  6.747119e-01 & 3.977531e-12 & 5.895155e-12 \\ 
+3 & 3 & 4 &  2.869943e-01 & 5.757645e-14 & 2.006188e-13 \\ 
+\hline
+\end{tabular}
+\end{center}
+\label{fig::allRegDiri}
+\caption
+    {
+      We show the lowest value of
+      $\cali$ for an entire Cartesian grid of size $32^D$ with all
+      boundary conditions homogeneous Dirichlet.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$.
+%%(as of 6-28-2023, some 3d results still pending).      
+    }
+\end{table}
+\end{small}
+
+\begin{small}
+\begin{table}
+\begin{center}
+  \begin{tabular}{|ccc|ccc|} \hline
+ $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
+  \hline
+2 & 1 & 1  & 2.518893e+00 & 1.601156e-04 & 6.356588e-05 \\ 
+2 & 1 & 2  & 2.362043e+00 & 1.461371e-05 & 6.186896e-06 \\ 
+2 & 1 & 3  & 1.094261e+00 & 9.635190e-07 & 8.805204e-07 \\ 
+2 & 1 & 4  & 1.093340e+00 & 1.270395e-07 & 1.161940e-07 \\ 
+2 & 1 & 5  & 1.094367e+00 & 2.036717e-08 & 1.861091e-08 \\ 
+2 & 2 & 1  & 1.462450e+00 & 2.819426e-08 & 1.927879e-08 \\ 
+2 & 2 & 2  & 1.118414e+00 & 3.603335e-09 & 3.221825e-09 \\ 
+2 & 2 & 3  & 1.101878e+00 & 6.259208e-10 & 5.680491e-10 \\ 
+2 & 2 & 4  & 1.787419e+00 & 1.261851e-10 & 7.059628e-11 \\ 
+2 & 2 & 5  & 1.786900e+00 & 8.059615e-12 & 4.510389e-12 \\ 
+2 & 3 & 1  & 1.463079e+00 & 5.935296e-12 & 4.056717e-12 \\ 
+2 & 3 & 2  & 1.119064e+00 & 1.346836e-12 & 1.203538e-12 \\ 
+2 & 3 & 3  & 3.180167e+00 & 2.412859e-13 & 7.587209e-14 \\ 
+2 & 3 & 4  & 3.171902e+00 & 1.108072e-14 & 3.493399e-15 \\ 
+2 & 3 & 5  & 1.101546e+00 & 1.869284e-16 & 1.696964e-16 \\ 
+2 & 4 & 1  & 4.679500e+00 & 1.267360e-17 & 2.708324e-18 \\ 
+2 & 4 & 2  & 3.730996e+00 & 2.933117e-18 & 7.861486e-19 \\ 
+2 & 4 & 3  & 3.640428e+00 & 2.031473e-17 & 5.580313e-18 \\ 
+2 & 4 & 4  & 1.101662e+00 & 2.052912e-18 & 1.863468e-18 \\ 
+2 & 4 & 5  & 1.101600e+00 & 5.403550e-19 & 4.905182e-19 \\
+\hline
+3 & 1 & 1  & 5.278503e+00 & 5.349129e-04 & 1.013380e-04 \\ 
+3 & 1 & 2  & 2.898423e+00 & 1.765977e-05 & 6.092890e-06 \\ 
+3 & 1 & 3  & 2.480335e+00 & 5.055998e-07 & 2.038433e-07 \\ 
+3 & 1 & 4  & 2.468916e+00 & 2.823132e-08 & 1.143471e-08 \\ 
+3 & 1 & 5  & 2.528326e+00 & 3.761767e-09 & 1.487849e-09 \\ 
+3 & 2 & 1  & 1.845660e+00 & 1.814540e-08 & 9.831389e-09 \\ 
+3 & 2 & 2  & 4.774894e+00 & 4.503397e-09 & 9.431406e-10 \\ 
+3 & 2 & 3  & 2.880922e+00 & 1.193187e-10 & 4.141685e-11 \\ 
+3 & 2 & 4  & 2.864876e+00 & 1.430923e-11 & 4.994711e-12 \\ 
+3 & 2 & 5  & 4.150386e+00 & 3.315285e-12 & 7.987897e-13 \\ 
+3 & 3 & 1  & 1.936290e+00 & 1.161631e-12 & 5.999263e-13 \\ 
+3 & 3 & 2  & 2.897250e+00 & 5.681304e-13 & 1.960930e-13 \\ 
+3 & 3 & 3  & 3.447497e+00 & 9.616076e-14 & 2.789292e-14 \\ 
+3 & 3 & 4  & 2.751616e+00 & 1.135060e-14 & 4.125067e-15 \\ 
+3 & 3 & 5  & 2.750524e+00 & 4.977018e-16 & 1.809480e-16 \\ 
+3 & 4 & 1  & 2.390817e+00 & 4.437506e-16 & 1.856062e-16 \\ 
+3 & 4 & 2  & 4.045567e+00 & 2.572870e-16 & 6.359727e-17 \\ 
+3 & 4 & 3  & 2.967273e+00 & 4.916614e-17 & 1.656947e-17 \\ 
+3 & 4 & 4  & 6.914527e+00 & 6.809812e-17 & 9.848559e-18 \\ 
+  \hline
+\end{tabular}
+\end{center}
+\label{fig::mergedDiri}
+\caption
+    {
+      We show the lowest value of
+      $\cali$ for an entire Cartesian grid of size $32^D$ with all
+      boundary conditions homogeneous Dirichlet.
+      The grid covers the unit square and is cut by a sphere of radius 0.45.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$.    This grid
+      has had its small volumes merged with neighboring volumes.
+%%(as of 6-28-2023, some 3d results still pending).      
+    }
+\end{table}
+\end{small}
+
+\begin{small}
+\begin{table}
+\begin{center}
+\begin{tabular}{|ccc|ccc|} \hline
+ $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$  \\
+\hline
+2 & 1 & 1 &  2.659761e+00 & 1.406481e-03 & 5.287997e-04 \\ 
+2 & 1 & 2 &  1.215453e+00 & 1.019228e-04 & 8.385575e-05 \\ 
+2 & 1 & 3 &  1.046275e+00 & 8.724426e-06 & 8.338562e-06 \\ 
+2 & 1 & 4 &  1.016321e+00 & 1.289568e-06 & 1.268859e-06 \\ 
+2 & 1 & 5 &  1.009826e+00 & 4.105645e-07 & 4.065697e-07 \\ 
+2 & 2 & 1 &  2.721312e+00 & 6.510187e-07 & 2.392297e-07 \\ 
+2 & 2 & 2 &  1.215454e+00 & 4.619552e-08 & 3.800680e-08 \\ 
+2 & 2 & 3 &  1.046439e+00 & 3.123629e-09 & 2.985008e-09 \\ 
+2 & 2 & 4 &  1.016267e+00 & 2.184707e-10 & 2.149737e-10 \\ 
+2 & 2 & 5 &  1.009758e+00 & 1.769343e-11 & 1.752244e-11 \\ 
+2 & 3 & 1 &  2.721312e+00 & 2.062962e-10 & 7.580764e-11 \\ 
+2 & 3 & 2 &  1.215454e+00 & 1.829550e-11 & 1.505240e-11 \\ 
+2 & 3 & 3 &  1.046275e+00 & 1.297942e-12 & 1.240537e-12 \\ 
+2 & 3 & 4 &  1.016321e+00 & 7.989181e-14 & 7.860883e-14 \\ 
+2 & 3 & 5 &  1.009826e+00 & 5.099447e-15 & 5.049829e-15 \\ 
+2 & 4 & 1 &  2.721312e+00 & 1.944812e-15 & 7.146596e-16 \\ 
+2 & 4 & 2 &  1.218511e+00 & 6.245987e-16 & 5.125916e-16 \\ 
+2 & 4 & 3 &  1.045681e+00 & 1.558421e-16 & 1.490342e-16 \\ 
+2 & 4 & 4 &  1.016267e+00 & 5.658955e-17 & 5.568374e-17 \\ 
+2 & 4 & 5 &  1.009906e+00 & 2.092151e-17 & 2.071630e-17 \\ 
+\hline
+3 & 1 & 1 &  6.913939e+00 & 3.982281e-03 & 5.759786e-04 \\ 
+3 & 1 & 2 &  1.457848e+00 & 1.829414e-04 & 1.254873e-04 \\ 
+3 & 1 & 3 &  1.067010e+00 & 8.920278e-06 & 8.360072e-06 \\ 
+3 & 1 & 4 &  1.014179e+00 & 7.322700e-07 & 7.220320e-07 \\ 
+3 & 1 & 5 &  1.003823e+00 & 1.115560e-07 & 1.111311e-07 \\ 
+3 & 2 & 1 &  7.173899e+00 & 1.868378e-06 & 2.604411e-07 \\ 
+3 & 2 & 2 &  1.457849e+00 & 7.351431e-08 & 5.042654e-08 \\ 
+3 & 2 & 3 &  1.067007e+00 & 3.063086e-09 & 2.870728e-09 \\ 
+3 & 2 & 4 &  1.014193e+00 & 1.481290e-10 & 1.460561e-10 \\ 
+3 & 2 & 5 &  1.003823e+00 & 8.189605e-12 & 8.158418e-12 \\ 
+3 & 3 & 1 &  7.173899e+00 & 5.736164e-10 & 7.995881e-11 \\ 
+3 & 3 & 2 &  1.463446e+00 & 3.367536e-11 & 2.301099e-11 \\ 
+3 & 3 & 3 &  1.067224e+00 & 1.254264e-12 & 1.175258e-12 \\ 
+3 & 3 & 4 &  1.014176e+00 & 4.631105e-14 & 4.566371e-14 \\ 
+3 & 3 & 5 &  1.003820e+00 & 1.806297e-15 & 1.799424e-15 \\ 
+3 & 4 & 1 &  7.173899e+00 & 8.925826e-15 & 1.244208e-15 \\ 
+3 & 4 & 2 &  1.463446e+00 & 3.102967e-16 & 2.120315e-16 \\ 
+\hline
+\end{tabular}
+\end{center}
+\label{fig::unmergedDiri}
+\caption
+    {
+      We show the lowest value of
+      $\cali$ for an entire Cartesian grid of size $32^D$ with all
+      boundary conditions homogeneous Dirichlet.
+      The grid covers the unit square and is cut by a sphere of radius 0.45.
+      We vary Taylor power $P^T$, weighting
+      function exponents $P^W$, and dimensionality $D$.    This grid
+      includes very small volumes.
+%%(as of 6-28-2023, some 3d results still pending).      
+    }
+\end{table}
+\end{small}
 

### 2023-06-29 src/EBCM/Chombo_EBCM_Algorithm_Framework.H
hoeb_petsc test was way too chatty

@@ -129,13 +129,11 @@ namespace EBCM
           auto allpts= volu.m_cells;
           double invCondNum, maxEig, minEig;
 
-          static bool printedOne = false;
           ///info about where the worst one was
           int worst_face_dir, worst_face_index;
           getWorstConditionNumberInfo(invCondNum, maxEig, minEig,
                                       worst_face_dir, worst_face_index,
-                                      volu, graph, a_dom_bc, a_eb_bc, !printedOne);
-          printedOne = true;
+                                      volu, graph, a_dom_bc, a_eb_bc, false);
           if(invCondNum < minInvCond)
           {
             minInvCond = invCondNum;

### 2023-06-29 example/EBCM/hoeb_petsc/_doc/paper.tex
gearing up for EBCM petsc solver

@@
 
+\section{Truncation error convergence rates}
+
+For this family of operators, $P_T$ should be entirely determinative
+of the truncation error convergence rate.   For completeness, we
+intend to verify this.    But as has been shown,
+for aggressive choices of $P_T$ and $P_W$ the system matrix can be
+poorly conditioned, leading to some degree of uncertainty about the
+stencil coefficients.
+In this section, we also explore how these conditioning issues affect the
+measured truncation error of the operator.
+
 \section{Stability and Conditioning of the entire system}
@@
 \cite{petsc-user-ref, petsc-efficient, slepc}.
+
+\section{Solution error convergence rates}
 

### 2023-06-29 src/EBCM/Chombo_EBCM_PetscSolver.H

@@ -1,0 +1,810 @@
+#ifdef CH_LANG_CC
+/*
+ *      _______              __
+ *     / ___/ /  ___  __ _  / /  ___
+ *    / /__/ _ \/ _ \/  V \/ _ \/ _ \
+ *    \___/_//_/\___/_/_/_/_.__/\___/
+ *    Please refer to Copyright.txt, in Chombo's root directory.
+ */
+#endif
+
+#ifndef _EBPoissonPetscSolver_H_
+#define _EBPoissonPetscSolver_H_
+
+#ifdef CH_USE_PETSC
+#include "petsc.h"
+#include "petscmat.h"
+#include "petscvec.h"
+#include "petscksp.h"
+#include "petscviewer.h"
+#include "petscmat.h"
+#include "Chombo_EBChombo.H"
+#include "Chombo_EBLevelBoxData.H"
+
+/// Stuff petsc frameworks have in common
+/**
+*/
+template <int order>
+class BaseEBPetscSolver
+{
+public:
+  typedef GraphConstructorFactory< EBBoxData<CELL, int, 1> >  devifactint_t;
+  typedef GraphConstructorFactory<EBHostData<CELL, int, 1> >  host_fact_int_t;
+  typedef GraphConstructorFactory<EBHostData<CELL,Real, 1> >  host_fact_real_t;
+  typedef EBDictionary<order, Real, CELL, CELL>                dictionary_t;
+  typedef CH4_Data_Choreography::DistributedData<EBBoxData< CELL, Real, 1> > devi_distrib_real_t;
+  typedef CH4_Data_Choreography::DistributedData<EBHostData<CELL, Real, 1> > host_distrib_real_t;
+  typedef CH4_Data_Choreography::DistributedData<EBBoxData< CELL, int , 1> > devi_distrib_int_t;
+  typedef CH4_Data_Choreography::DistributedData<EBHostData<CELL, int , 1> > host_distrib_int_t;
+  typedef CH4_Data_Choreography::DistributedData<EBGraph>                    graph_distrib_t;
+
+  virtual ~BaseEBPetscSolver()
+  {
+  }
+  
+  BaseEBPetscSolver(const shared_ptr<GeometryService<order> >  & a_geoserv,
+                    const shared_ptr<dictionary_t           >  & a_ebdictionary,
+                    const shared_ptr<graph_distrib_t>          & a_graphs,
[…]

### 2023-06-30 src/EBCM/Chombo_EBCM_Algorithm_Framework.H
fixed latex printout

@@ -88,7 +88,7 @@ namespace EBCM
         pout() << " $D$ & $P^T$  & $P^W$ & $R_s$ & \\lambda_{max} & \\lambda_{min}   & $I$ \\\\"<< endl;
         pout() << "\\hline " << endl;
         int dim = DIM;
-        pout() <<  "-GREP_HOOK-" << dim << " & " << taymax << " & " << wgtpow << " & " <<  stnrad << " & "<< m_max_eigenvalue << " & " << m_min_eigenvalue << " & "  << m_inv_condition;
+        pout() <<  "-GREP_HOOK-" << dim << " & " << taymax << " & " << wgtpow << " & " << m_max_eigenvalue << " & " << m_min_eigenvalue << " & "  << m_inv_condition;
         pout() << " \\\\ " << endl;
 
         pout() << "\\hline " << endl;

### 2023-06-30 example/EBCM/hoeb_petsc/elliptic_operator_test.cpp
starting on EBCM PETSc framework

@@ -17,6 +17,7 @@
 #include "Chombo_EBCM_Graph.H"
 #include "Chombo_EBCM_HostLevelData.H"
 #include "Chombo_EBCM_Algorithm_Framework.H"
+#include "Chombo_EBCM_PETSc_Framework.H"
 #include "Chombo_EigenMatrix.H"
 
 #include <iomanip>
@@ -50,29 +51,47 @@ int main(int a_argc, char* a_argv[])
     ParmParse pp("main");
     pp.get("polynomial_order", order);
     Chombo4::pout() <<  "Running hoeb_petsc_test for polynomial order = " << order << endl;
+
     if(order == 6)
     {
-      EBCM::Algorithm_Framework<6>::run_hoeb_petsc_tests();
+      shared_ptr< EBCM::MetaDataLevel< 6 > >             ebcm_meta;      
+      EBCM::Algorithm_Framework<6>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<    6>::run_hoeb_petsc_tests(ebcm_meta);
     }
     else if(order == 5)
     {
-      EBCM::Algorithm_Framework<5>::run_hoeb_petsc_tests();
+      shared_ptr< EBCM::MetaDataLevel< 5 > >             ebcm_meta;      
+      EBCM::Algorithm_Framework<5>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<    5>::run_hoeb_petsc_tests(ebcm_meta);
+
     }
     if(order == 4)
     {
-      EBCM::Algorithm_Framework<4>::run_hoeb_petsc_tests();
+      shared_ptr< EBCM::MetaDataLevel< 4 > >             ebcm_meta;      
+      EBCM::Algorithm_Framework<4>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<    4>::run_hoeb_petsc_tests(ebcm_meta);
+
     }
     else if(order == 3)
     {
-      EBCM::Algorithm_Framework<3>::run_hoeb_petsc_tests();
+      shared_ptr< EBCM::MetaDataLevel< 3 > >             ebcm_meta;      
+      EBCM::Algorithm_Framework<3>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<    3>::run_hoeb_petsc_tests(ebcm_meta);
+
     }
[…]

### 2023-06-30 src/EBCM/Chombo_EBCM_Algorithm_Framework.H

@@ -21,7 +21,6 @@
 #include "Chombo_EigenMatrix.H"
 #include "Chombo_EBCM_Basics.H"
 
-
 #include <iomanip>
 
 namespace EBCM
@@ -49,15 +48,14 @@ namespace EBCM
   class Algorithm_Framework
   {
   public:
-    typedef EBCM::HostLevelData<double, 1, ebcm_order >      ebcm_leveldata;
-    typedef    EBCM::MetaDataLevel<         ebcm_order >   ebcm_meta;
-    typedef    EBCM::SubVolumeVector  <     ebcm_order >   ebcm_subvol_vec;
-    typedef    EBCM::EBCM_Volu<             ebcm_order >   ebcm_volu;
-    typedef    EBCM::EBCM_Graph<            ebcm_order >   ebcm_graph;
-    typedef Chombo4::GeometryService<       ebcm_order >   ch_geoserv;
-    typedef   Proto::IndexedMoments<DIM  ,  ebcm_order >   pr_mom_dim;
-    typedef   Proto::IndexedMoments<DIM-1,  ebcm_order >   pr_mom_dmo;
-
+    typedef    EBCM::HostLevelData<double, 1,    ebcm_order >   ebcm_leveldata;
+    typedef    EBCM::MetaDataLevel<              ebcm_order >   ebcm_meta;
+    typedef    EBCM::SubVolumeVector  <          ebcm_order >   ebcm_subvol_vec;
+    typedef    EBCM::EBCM_Volu<                  ebcm_order >   ebcm_volu;
+    typedef    EBCM::EBCM_Graph<                 ebcm_order >   ebcm_graph;
+    typedef Chombo4::GeometryService<            ebcm_order >   ch_geoserv;
+    typedef   Proto::IndexedMoments<DIM  ,       ebcm_order >   pr_mom_dim;
+    typedef   Proto::IndexedMoments<DIM-1,       ebcm_order >   pr_mom_dmo;
     class condition_t
     {
     public:
@@ -469,7 +467,7 @@ namespace EBCM
       Chombo4::pout() << "minimum volume fraction overall = " << minKappa << endl;
     }
     ///test function for example/EBCM/hoeb_petsc_test
-    static  void run_hoeb_petsc_tests()
+    static  void run_hoeb_petsc_tests(shared_ptr< ebcm_meta  >&  a_ebcm)
     {
       CH_TIME("EBCM_Framework::runTests");
 
@@ -500,7 +498,9 @@ namespace EBCM
[…]

### 2023-06-30 src/EBCM/Chombo_EBCM_Graph.H

@@ -8,6 +8,7 @@
 using std::vector;
 using std::set;
 
+///okay, maybe not the greatest choice of namespace name
 namespace EBCM
 {
   using std::set;

### 2023-06-30 src/EBCM/Chombo_EBCM_PETSc_Framework.H

@@ -1,0 +1,107 @@
+#ifndef __Chombo_EBCM_PETSC_Framework_
+#define __Chombo_EBCM_PETSC_Framework_
+
+#ifdef CH_USE_PETSC
+#include "petsc.h"
+#include "petscmat.h"
+#include "petscvec.h"
+#include "petscksp.h"
+#include "petscviewer.h"
+#include "petscmat.h"
+/**
+   This is where MetaDataLevel lives.  It made sense at the time.
+   I should use this opportunity to apologize to the world for the many 
+   awful choices I have made in this life in relation to file names and organization.  
+   I regret all the consternation I have caused.
+**/
+#include "Chombo_EBCM_Graph.H"
+#include "Chombo_EBLevelBoxData.H"
+
+/// An EBCM interface to the magical world of PETSc,  where the evil bits of linear algebra are done for us.
+/**
+   I plan to use this for everything.  Geometric multigrid requires
+   more infrastructure than I am willing to write so I will use PETSc
+   for solves and truncation error tests and I will be hooking in
+   SLEPc to do the eigenvalue analysis. --dtg
+**/
+namespace EBCM
+{
+
+  template <int ebcm_order>
+  class PETSc_Framework
+  {
+  public:
+    typedef Chombo4::Box                            ch_box;
+    typedef Chombo4::DisjointBoxLayout              ch_dbl;
+    typedef EBCM::MetaDataLevel<ebcm_order>         ebcm_meta;
+    typedef ::Mat                                   petsc_mat;
+    typedef Proto::Point                            pr_pt;
+    typedef Chombo4::IntVect                         ch_iv;
+    typedef EBCM::HostLevelData<int, 1, ebcm_order> ebcm_data;
+
+    ///
+    /**
+       This is a wrapper around PETSc's  ::Mat object.  The specfics of the stencil 
+       are computed in the derived class.   All data is public because
+       this design is cleaner than hiding behind access functions.
+    **/
+    class Base_PETSc_Op
+    {
+    public:
+
+    
+    
+      shared_ptr<petsc_mat> m_mat_ptr;
+      shared_ptr<ebcm_data> m_row_map_ptr; 
+      shared_ptr<ebcm_meta> m_meta_ptr;
+      pr_pt                 m_ptghost;
+      ch_iv                 m_ivghost;
+    
+      virtual ~Base_PETSc_Op()
+      {;}
+  
[…]

### 2023-07-07 example/EBCM/hoeb_petsc/_doc/paper.tex
added latest 3d data
millions of typos cry out at once

--- 2023-06-29 example/EBCM/hoeb_petsc/_doc/paper.tex
@@
 
-\title{Accuracy and stability for elliptic operators
-  in a finite volume context}
+\title{High order finite volume operators in a cut cell context,
+  Part 1: system  matrix conditioning for finite volume elliptic operators}
 \author{
@@
 Generalizing somewhat  the framework they present, we can define a
-family of elliptic operators.
-Here we investigate how the accuracy and stability of this family
-of operators varies within its parameter space.
+family of elliptic operators.   That algorithm is a special case of a
+family of finite volume elliptic operators.   We present the formal
+process to generate these operators which includes inverting a system
+matrix.    Overton-Katz, et al. \cite{Katz2023}, show that the system
+matrix can have solvability problems in the absence of boundary
+condition equations in the system matrix  but Devendran uses
+boundary condition equations.   We present data that shows these extra
+equations can improve the system matrix condition number.
+We also show that, for certain parameters of operator,
+this system matrix is still quite poorly conditioned.
 
@@
 Embedded boundary (EB) grids are formed when one passes an  surface
-through a Cartesian mesh.    For sufficiently complex geomtries, these methods
-are very attactive because grid generation is a solved problem
+through a Cartesian mesh.    For sufficiently complex geometries, these methods
+are very attractive because grid generation is a solved problem
 even for moving grids \cite{MillerTrebotich2012}.
@@
 \end{equation}
-If we know the local Taylor coeffiencts,
+If we know the local Taylor coefficients,
 the gradient of the field  in direction $d$ is given by
@@
 We force there to be enough neighbors so that this system is
-overdetermined.  Let's say $\ncal_\fbold$ contains $N_B$ boundary faces and
+over-determined.  Let's say $\ncal_\fbold$ contains $N_B$ boundary faces and
 $N_V$ volumes.   To solve for Taylor coefficients, we have a system 
@@
 in $\ncal_\fbold$.
-Since the system is overdetermined, we can introduce a 
+Since the system is over-determined, we can introduce a 
 meaningful weighting matrix $W$ \footnotemark[4]. 
@@
 with index $\vbold$.  The distance $D_\fbold(V_1)$ is given by
-the Manhattan disance:
+the Manhattan distance:
 \begin{equation}
@@
 severe mismatch between its largest and smallest eigenvalues,
-signalling that $A$ is poorly conditioned.    Their data show the
+signaling that $A$ is poorly conditioned.    Their data show the
 worst solvability issues occur near the domain boundary.    It stands to
 reason that including boundary condition equations could improve the
-conditioning of the resultant matricies. To test this, we present the
+conditioning of the resultant matrices. To test this, we present the
 same measurement of condition number for  several values of $P_T$ and
@@
 condition equations does improve the solvability of $A$, aggressive
-choices of $P_W$ and $P_T$ can lead to system matricies that cannot be
+choices of $P_W$ and $P_T$ can lead to system matrices that cannot be
 credibly solved without very high precision numerical arithmetic.
@@
 \end{equation}
-For all coordinate-alligned faces, the section above's description for how to
+For all coordinate-aligned faces, the section above's description for how to
 compute the flux is adequate.   What remains are fluxes through cut
@@
 \ref{fig::allRegDiri} for details.  Again, boundary conditions help
-stabilize the system but it is still the case that agressive choices
+stabilize the system but it is still the case that aggressive choices
 of $P_T$ or $P_W$ can result in system matrices that cannot be
@@
 Again, this seems less a matter of a particular grid configuration and
-more  a property of the mathematical framework used to generate the stencil.
+more  a property of the mathematical framework used to generate the
+stencil.
+
 \begin{small}
@@
 3 & 3 & 4 & 2.869943e-01 & 5.757645e-14 & 2.006188e-13 \\ 
+3 & 3 & 5 & 2.669165e-01 & 1.723124e-15 & 6.455665e-15 \\ 
+3 & 4 & 1 & 3.106689e+00 & 3.897434e-26 & 1.254530e-26 \\ 
+3 & 4 & 2 & 1.171168e+00 & 3.832896e-28 & 3.272712e-28 \\ 
+3 & 4 & 3 & 7.002071e-01 & 3.537134e-28 & 5.051555e-28 \\ 
+3 & 4 & 4 & 2.903904e-01 & 8.048694e-26 & 2.771680e-25 \\ 
 \hline
@@
       function exponents $P^W$, and dimensionality $D$.
-%%(as of 6-28-2023, some 3d results still pending).      
     }
@@
 3 & 4 & 4  & 6.914527e+00 & 6.809812e-17 & 9.848559e-18 \\ 
+3 & 4 & 5  & 6.132492e+00 & 9.581151e-18 & 1.562359e-18 \\ 
 \hline
@@
       has had its small volumes merged with neighboring volumes.
-%%(as of 6-28-2023, some 3d results still pending).      
     }
@@
 3 & 4 & 2 & 1.463446e+00 & 3.102967e-16 & 2.120315e-16 \\ 
+3 & 4 & 3 & 1.102822e+00 & 3.089983e-17 & 2.801888e-17 \\ 
+3 & 4 & 4 & 1.014074e+00 & 7.854565e-18 & 7.745552e-18 \\ 
+3 & 4 & 5 & 5.339547e-01 & 2.224403e-18 & 4.165902e-18 \\ 
 \hline
@@
       includes very small volumes.
-%%(as of 6-28-2023, some 3d results still pending).      
     }
@@
 
-\section{Stability and Conditioning of the entire system}
+\section{Conclusions}
 
-The matrix $L_{P_T, P_W}$ for a particular polynomial order $P_T$ and
-weighting exponent  $P_W$ may be unstable or poorly conditioned.   We
-measure both while varying $P_T, P_W$ in both two and three
-dimensions.    All these calculations are done using SLEPc and PETc
-\cite{petsc-user-ref, petsc-efficient, slepc}.
-
-\section{Conclusions}
+We present a family of elliptic operators and we investigate the
+solvability of the system matrix used in generating these operators.
+We find that using boundary condition equations in the system matrix
+helps its solvability.   For aggressive choices of weighting power and
+Taylor power, however, the system matrix that results is not credibly
+solvable without high precision arithmetic.
 
@@
   formed by taking all the volumes within a grown box. The grown box
-  is formed by growning the box made from the low and high cells of
-  the target face, growing it by $N_G$ and itersecting with the
+  is formed by growing the box made from the low and high cells of
+  the target face, growing it by $N_G$ and intersecting with the
   domain.  We use the   Chombo
@@
   equations for volumes $\jbold$ where $\xbar_\jbold$ is large
-  receive  higher weights.  Diagonal weighting matricies are common.
+  receive  higher weights.  Diagonal weighting matrices are common.
   Usually these algorithms define a distance metric $D(\ibold, \jbold)$ for

### 2023-07-07 example/EBCM/roadmap.tex
let the machine do the work
updated directory roadmap to reflect current traffic conditions

@@
 \author{ D. T. Graves }
-\date{May 7, 2023 c.e.}
+\date{July 7, 2023 c.e.}
 \maketitle
@@
 of data on matrix conditioning in an hoeb/ebcm context.    The
-associated technical report is quite complete.
+associated document (Lawrence Berkeley National Laboratory
+Technical Report LBNL-2001528)
+technical report is quite complete.
 
@@
 
-This test investigates the eigenvalues and eigenvectors of stencils to
-solve Poisson's equation.
+This test investigates the solvability of the system matrix when
+boundary condition equations are included in the system.
+The associated document
+(Lawrence Berkeley National Laboratory
+Technical Report LBNL-2001537)
+is complete to the point of being downright
+chatty. Does not use petsc so the test name needs work.
+
+\section{hoeb truncation}
+
+This continues the story by investigating the truncation error of
+the family of finite volume operators.   This one does use quite a bit
+of petsc and includes yet another user interface to the petsc
+infrastructure.   The document vaporware as of July 7 2023.
 

### 2023-07-07 example/EBCM/hoeb_truncation/_doc/paper.tex
gearing up for merging with the master branch

--- 2023-06-29 example/EBCM/hoeb_petsc/_doc/paper.tex
@@
 
-\title{Accuracy and stability for elliptic operators
-  in a finite volume context}
+\title{High order finite volume operators in a cut cell context,
+  part 2: truncation error measurements}
 \author{
@@
 Generalizing somewhat  the framework they present, we can define a
-family of elliptic operators.
-Here we investigate how the accuracy and stability of this family
-of operators varies within its parameter space.
-
-\end{abstract}
-
-\section{Underlying mathematics}
-
-Embedded boundary (EB) grids are formed when one passes an  surface
-through a Cartesian mesh.    For sufficiently complex geomtries, these methods
-are very attactive because grid generation is a solved problem
-even for moving grids \cite{MillerTrebotich2012}.
-In the current context, we form the cutting surface as the zero
-surface of a function  of space $I(\xbold)$, $\xbold \in R^D$.
-For smooth ($I$),  moments can be generated to any
-accuracy \cite{Schwartz2015}.
-
-Formally, the underlying description of space
-is given by rectangular control volumes on a Cartesian mesh
-$\Upsilon_\ibold = [(\ibold-\half {\ubold})h, (\ibold+\half
-{\ubold})h], \ibold \in \bigzbold^D$, where $D$ is the dimensionality
-of the problem, $h$ is the mesh spacing, and ${\ubold}$ is the vector
-whose entries are all one (note we use bold font $\ubold = (u_1, \dots, u_d,
-\dots, u_D)$ to indicate a vector quantity).
-Given an irregular domain $\Omega$, we
-obtain control volumes $V_\ibold = \Upsilon_\ibold \bigcap \Omega$ and
-faces $A_{\ibold,d\pm} = A_{\ibold \pm \half \ebold_d}$ which are the
-intersection of the boundary of $\partial V_\ibold$ with the
-coordinate planes $\{{\xbold}:x_d = (i_d \pm \half)h \}$ ($\ebold_d$ is
-the unit vector in the $d$ direction).  We also
-define $A_{B,\ibold}$ to be the intersection of the boundary of the
-irregular domain with the Cartesian control volume: $A_{B,\ibold}
-= \partial \Omega \bigcap \Upsilon_\ibold$.
-
-We use the compact notation
-\begin{align*}
-(\xbold - \xbar)^\pbold &= \prod\limits^D_{d=1} (x_d - {\bar x}_d)^{p_d} \\
-\pbold! &= \prod\limits^D_{d = 1} p_d!
-\end{align*}
-Given a $D$-dimensional region of space $\ibold$, 
-and a $D$-dimensional integer vector
-$\pbold$, we define $m_\ibold^\pbold(\xbar)$ to be the $\pbold^{th}$
-moment of $\ibold$ to the point $\xbar$.
-\begin{equation}
-\mcal_\ibold^\pbold(\xbar)  =  \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV^D.
-\label{eqn::volmoment}
-\end{equation}
-This breaks out into three different cases, volumes, coordinate faces
-and irregular faces.
-A coordinate face $f_{12}$  is the area where two
-volumes ($V_1, V_2$) intersect.
-A irregular face $f_V$  is area where the cutting surface
-intersects the volume $V$.
-The volume moment for a particular power $\pbold$  is
-given by
-\begin{equation}
-  \mcal^\pbold_V = \int\limits_{\ibold} (\xbold - \xbar)^\pbold dV
-  \label{eqn::volmom}
-\end{equation}
-The $\pbold^{th}$ coordinate face moment for the area of where volumes $V_1, V2$
-intersect is given by
-\begin{equation}
-  \mcal^\pbold_{f_{12}} = \int\limits_{A(V_1\bigcap V_2)} (\xbold - \xbar)^\pbold dA.
-  \label{eqn::facmom}
-\end{equation}
-The cutting surface of the boundary $G$ is given by  the zero
-surface of the  implicit function ($I(\xbold)= 0$) used in grid generation.
-The $\pbold^{th}$ irregular face moment is given by an integral over
-the intersection of this cutting surface and the Euclidean volume:
-\begin{equation}
-  \mcal^\pbold_V = \int\limits_{A(V \bigcap G)} (\xbold - \xbar)^\pbold dA.
-  \label{eqn::irrmom}
-\end{equation}
-These moments are natural products of the grid generation algorithm
-in \cite{Schwartz2015}.
-
-\section{Family of finite volume elliptic operators}
-
-Devendran, et al. \cite{Devendran2017} present an algorithm that
-solves Poisson's equation to fourth-order accuracy using embedded
-boundaries.  Generalizing somewhat  the framework they present, we
-present a family of elliptic operators.
-
-We are solving Poisson's equation for field $\psi$, given charge $\rho$:
-\begin{equation}
-  \nabla \cdot (\nabla \psi) = \rho
-  \label{eqn::poisson}
-\end{equation}
-If we integrate equation \ref{eqn::poisson} and apply the divergence theorem 
-over control volumes we get
-\begin{equation}
-\int_{V_\ibold} \nabla \cdot (\nabla \psi ) dV = \int_{\partial
-  V_\ibold} \nabla \psi\cdot \nhat  dA = \int_{V_\ibold} \rho dV
-\end{equation}
-Without approximation, we can say that the surface integral can be
-computed by a sum over the faces that comprise the surface of the
-volume.
-\begin{equation}
-\sum_{f: f \in \partial V_\ibold} \nabla \psi \cdot \nhat dA = \int_{V_\ibold} \rho dV
-\end{equation}
-Using equations \ref{eqn::faceavg} and \ref{eqn::volavg}, this becomes 
-\begin{equation}
-\sum_{f: f \in \partial V_\ibold} \avg{\nabla \psi \cdot \nhat}_f A_f
-= \avg{\rho}_\ibold V_\ibold
-\label{eqn::discretePoisson}
-\end{equation}
-A finite volume operator is defined by the algorithm to compute the
-integral of fluxes at each face.  We have three types of face, open
-faces (the faces between two volumes that are aligned with coordinate
-directions), domain faces, and cut faces.  For now, let's say we have
-homogeneous Neumann boundary conditions at domain and cut faces
-$\nabla \psi \cdot \nhat = 0 |\partial \Omega$.  In this case, to
-describe the algorithm, we need only describe how to compute 
-$<\nabla\psi \cdot \nhat>$ on open faces.
-
-\section{Open face Poisson flux computation with Neumann boundary conditions}
-\label{sec::openface}
-An open face is one that connects two volumes in the solution.  These
-faces are aligned with a coordinate direction.   Consider an open face
-$\fbold$ aligned with coordinate direction $d$.   We define $\ncal_\fbold$
-to be all the volumes within $N_G$ ghost cells of $\fbold$ \footnotemark{3].
-
-\subsection{Taylor expansion around face}
-
-We approximate $\psi$
-in the neighborhood of $\xbar$ using a Taylor expansion to order $P_T$:
-\begin{equation}
-\psi(\xbold)  =  \sum\limits_{p < P_T} C^p (\xbold -\xbar)^p
-\label{eqn::taylor}
-\end{equation}
-where $C^p$ this appropriate Taylor coefficient.  In three dimensions,
-\begin{equation}
-  C^p =\frac{1}{p!}
-      \frac{\partial^{p_0}}{\partial x_0}
-      \frac{\partial^{p_1}}{\partial x_1}
-      \frac{\partial^{p_2}}{\partial x_2}  (\psi).
-\end{equation}
-If we know the local Taylor coeffiencts,
-the gradient of the field  in direction $d$ is given by
-\begin{equation}
-  \frac{\partial \psi}{\partial x^d}  =
-  \sum\limits_{p < P_T} p^d C^{p} (\xbar -\xbar)^{p-e^d}
-\end{equation}
-
-In finite volume  methods, we define grid data to be
-averages over volumes and fluxes between volumes are averages over the
-faces between volumes.   
-For the field $\psi$, the average over the volume $\ibold$ is given by
-\begin{equation*}
- V_\ibold <\psi>_\ibold = \int\limits_{V_\ibold} \psi(\xbold) dV
-\end{equation*}
-If we insert the Taylor expansion \ref{eqn::taylor}, we get a discrete
-approximation to the smooth function $\psi$ that is accurate to order $P_T$.
-\begin{equation*}
-  <\psi>_\ibold = \frac{1}{V_\ibold} \sum\limits_{p < P_T} C^p \mcal^p
-  \label{eqn::volavg}.
-\end{equation*}
-Similarly, integrating the flux over a d-directional face $\fbold$:
-\begin{equation*}
-  <\nabla \psi_d>_\ibold = \frac{1}{A_\fbold}
-  \sum\limits_{p < P_T} p^d C^{p} \mcal^{p-e^d}
-  \label{eqn::faceavg}.
-\end{equation*}
-
-\subsection{Boundary condition equations}
-
-To solve for the Taylor coefficients, we use the neighboring volumes'
-values  to form a system of equations (equation \ref{eqn::volavg}
-for each volume $\ibold \in N_f$, the neighborhood of $f$).  Boundary
-condition equations are also added to the system.   Since we have
-homogeneous Neumann boundary conditions, for every domain face $\bbold$
-within $\ncal_\fbold$, we have an equation of the form
-\begin{equation}
-  <\frac{\partial \psi}{\partial x^d}>_\bbold  =
-  \sum\limits_{p < P_T} p^d C^{p} \mcal^{p-e^d}_\bbold = 0.
-\end{equation}
-Consider a face $\cbold$ which is cut by a surface whose
-normal in direction $d$ is given by $n^d(\xbold)$.  We define the
-normal moments $\ecal^d$ to be the integral of this product:
-\begin{equation}
-\ecal^{\pbold, d}_\cbold  =  \int\limits_{A(\cbold)} \xminxbar n^d dA.
-\label{eqn::normmoment}
-\end{equation}
-These normal moments are natural products of the \cite{Schwartz2015}
-grid generation algorithm.
-
-\subsection{Moment matrix $M$ and system matrix $A$}
-
-For each $\cbold$ within the $\ncal_\fbold$, we get an equation of the form
-\begin{equation}
-  \int\limits_{A(\cbold)}  \nabla \psi \cdot \nhat dA =
-  \sum\limits_{d < D} \int\limits_{A(\cbold)} \sum_{p < P} p_d C^p
-  \xminxbar^{p-e^d} dA
-  = 
-\sum\limits_{d < D} \sum_{p < P}  p_d C_p \ecal^{p-e^d,d}_\cbold = 0.
-\end{equation}
-We force there to be enough neighbors so that this system is
-overdetermined.  Let's say $\ncal_\fbold$ contains $N_B$ boundary faces and
-$N_V$ volumes.   To solve for Taylor coefficients, we have a system 
-of the form
-\begin{equation*}
-M C = P 
-\end{equation*}
-where $C=\{C^p\}$,
-
-\begin{equation}
-  M_\fbold =\left\{
-    \begin{array}{c} 
-       m^p_\jbold  \\
-       p^d b^{p-e^d}_\bbold  \\
-       p^d c^{p-e^d}_\cbold  
-    \end{array}
- \right\},
-\end{equation}
-and
-\begin{equation}
-  P_\fbold =
-    \left\{
-    \begin{array}{c} 
-       <\psi>_\jbold  \\
-      0  \\
-      0  
-    \end{array}
-    \right\}
-\end{equation}
-for every volume $\jbold$, cut face $\cbold$ and domain face $\bbold$
-in $\ncal_\fbold$.
-Since the system is overdetermined, we can introduce a 
-meaningful weighting matrix $W$ \footnotemark[4]. 
- Choice of $W$
-is crucial to the stability of these algorithms
-\footnotemark[5].   
-We multiply and solve
-\begin{equation*}
-WMC = WP.
-\end{equation*}
-Since the system is (deliberately) not square, we approximate
-the solution using a Moore-Penrose pseudo-inverse:
-\begin{equation}
-  C = ((WM)^T(WM))^{-1} (WM)^T P.
-\label{eqn::getC}  
-\end{equation}
-where $A \equiv ((WM)^T(WM))_\fbold$ is the system matrix for face
-$\fbold$.
-
-\subsection{Manhattan Distance and the weighting matrix $W$}
-
-All volumes and faces  start with an  index $\ibold \in Z^D$.
-We start from face $\fbold$.   Say we want to get
-the distance from $\fbold$ with index $\ibold$ to a volume $V_1$
-with index $\vbold$.  The distance $D_\fbold(V_1)$ is given by
-the Manhattan disance:
-\begin{equation}
-  D_\fbold(V_1) = \sum\limits_{0 <= d < D} |\vbold^d - \ibold_0^d|.
-\label{eqn::uptownFunk}
-\end{equation}
-$\gbold_\fbold(V_1)$, the weight of the $V_1$ equation in $\fbold$ system
-is given by
-\begin{equation}
-  \gbold_\fbold(V_1)  \equiv \left(\frac{1}{D_\fbold(V_1) } \right)^{P_w},
-\label{eqn::weightFunk}  
-\end{equation}
-where we call $P_w$ the weighting exponent.
-The weighting matrix $W_\fbold = \{\{\wbold_{i,j}\}\}$ is diagonal
-\begin{equation}
-w_{i,j} =
-\left(
-\begin{array}{ll}
- \gbold_\fbold(V_i) & \mbox{ if } $(i==j)$ \\
- 0   & \mbox{ otherwise }
-\end{array}
-\right)
-\end{equation}
-Once one has the Taylor coefficients, she can compute the flux through
-the open face using  equation \ref{eqn::faceavg}.   Put into matrix
-form, we define  vector  $Q_\fbold = \{q^p_\fbold\}$:
-\begin{equation}
-q^p_\fbold = p^d \mcal^{p-e^d}_\fbold
-\end{equation}
-and the flux at the face is given by
-\begin{equation}
-<\nabla \psi>_\fbold = Q C P= Q ((WM)^T(WM))^{-1} (WM)^T  P.
-\end{equation}
-
-\subsection{Stencil formulation}
-One would like to avoid inverting $A$ every time she wishes to apply
-an elliptic operator at a point.  Since everything in sight is a
-linear operator, we can simply say that there must exist an equivalent
-linear operator $S$ such that
-\begin{equation}
-(S P)_\fbold = <\nabla \psi>_\fbold = Q C= (Q ((WM)^T(WM))^{-1} (WM)^T  P)_\fbold.
-\end{equation}
-Since this equivalence has to hold for all $\psi$, the stencil $S$ must be
-given by:
-\begin{equation}
- S_\fbold = Q C = (Q ((WM)^T(WM))^{-1} (WM)^T  )_\fbold = Q A^{-1} WM^T.
-\end{equation}
-
-\section{Solvability of the system matrix $A$}
-
-Overton-Katz, et al. \cite{Katz2023} present the above procedure in
-the absence of boundary condition equations.   They show that, for
-certain values of $P_T$ and $P_N$, the resulting $A$ matrix can have a
-severe mismatch between its largest and smallest eigenvalues,
-signalling that $A$ is poorly conditioned.    Their data show the
-worst solvability issues occur near the domain boundary.    It stands to
-reason that including boundary condition equations could improve the
-conditioning of the resultant matricies. To test this, we present the
-same measurement of condition number for  several values of $P_T$ and
-$P_N$ where boundary condition equations are included when they are
-part of the neighborhood.    We present the results for the same three
-different geometries used in \cite{Katz2023}.  In figure \ref{fig::allRegSolvability} we show
-the worst condition numbers where there are no cut cells.
-In figure \ref{fig::unmergedSolvability}, we show the worst condition
-number where we cut the unit domain with a centered sphere of radius
-0.45 (this geometry includes very small volumes).    Finally, in
-figure \ref{fig::mergedSolvability}, we present results all small
-volumes have been merged with neighbors.
-
-The data paint a very consistent picture,   Though adding boundary
-condition equations does improve the solvability of $A$, aggressive
-choices of $P_W$ and $P_T$ can lead to system matricies that cannot be
-credibly solved without very high precision numerical arithmetic.
-\begin{small}
-\begin{table}
-\begin{center}
-\begin{tabular}{|ccc|ccc|} \hline
- $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
- \hline
-2 & 1 & 1 &  1.537125e+00 & 1.150772e-03 & 7.486517e-04 \\
-2 & 1 & 2 &  4.940953e-01 & 9.196245e-05 & 1.861229e-04 \\
-2 & 1 & 3 &  3.324177e-01 & 1.064946e-05 & 3.203639e-05 \\
-2 & 1 & 4 &  2.853322e-01 & 1.705230e-06 & 5.976295e-06 \\
-2 & 1 & 5 &  2.665812e-01 & 3.349335e-07 & 1.256403e-06 \\
-2 & 2 & 1 &  2.407807e+00 & 1.457063e-06 & 6.051408e-07 \\
-2 & 2 & 2 &  4.940956e-01 & 5.469314e-08 & 1.106934e-07 \\
-2 & 2 & 3 &  3.324177e-01 & 2.879583e-09 & 8.662545e-09 \\
-2 & 2 & 4 &  2.853323e-01 & 1.628939e-10 & 5.708921e-10 \\
-2 & 2 & 5 &  2.665812e-01 & 1.084310e-11 & 4.067466e-11 \\
-2 & 3 & 1 &  2.407807e+00 & 5.822902e-10 & 2.418342e-10 \\
-2 & 3 & 2 &  9.272889e-01 & 4.520282e-11 & 4.874729e-11 \\ 
-2 & 3 & 3 &  3.324177e-01 & 1.618058e-12 & 4.867544e-12 \\
-2 & 3 & 4 &  2.853323e-01 & 7.227717e-14 & 2.533088e-13 \\
-2 & 3 & 5 &  2.665812e-01 & 3.194386e-15 & 1.198279e-14 \\
-2 & 4 & 1 &  1.880177e+00 & 1.535955e-25 & 8.169205e-26 \\
-2 & 4 & 2 &  9.272889e-01 & 1.098665e-27 & 1.184814e-27 \\
-2 & 4 & 3 &  6.561304e-01 & 5.104096e-28 & 7.779089e-28 \\
-2 & 4 & 4 &  2.868930e-01 & 3.731928e-27 & 1.300808e-26 \\
-2 & 4 & 5 &  5.327046e-01 & 5.118416e-25 & 9.608357e-25 \\
-\hline
-3 & 1 & 1 &  4.639099e+00 & 3.887142e-03 & 8.379088e-04 \\ 
-3 & 1 & 2 &  1.079504e+00 & 2.369894e-04 & 2.195354e-04 \\ 
-3 & 1 & 3 &  6.747118e-01 & 2.359590e-05 & 3.497182e-05 \\ 
-3 & 1 & 4 &  5.721834e-01 & 3.540976e-06 & 6.188534e-06 \\ 
-3 & 1 & 5 &  5.333668e-01 & 6.792558e-07 & 1.273525e-06 \\ 
-3 & 2 & 1 &  4.639156e+00 & 3.176883e-06 & 6.847975e-07 \\ 
-3 & 2 & 2 &  1.079505e+00 & 1.512048e-07 & 1.400686e-07 \\ 
-3 & 2 & 3 &  6.747119e-01 & 6.991076e-09 & 1.036157e-08 \\ 
-3 & 2 & 4 &  5.721835e-01 & 3.641527e-10 & 6.364265e-10 \\ 
-3 & 2 & 5 &  2.669165e-01 & 1.146071e-11 & 4.293744e-11 \\ 
-3 & 3 & 1 &  4.639157e+00 & 1.340233e-09 & 2.888959e-10 \\ 
-3 & 3 & 2 &  1.079505e+00 & 7.151353e-11 & 6.624659e-11 \\ 
-3 & 3 & 3 &  6.747119e-01 & 3.977531e-12 & 5.895155e-12 \\ 
-3 & 3 & 4 &  2.869943e-01 & 5.757645e-14 & 2.006188e-13 \\ 
-3 & 3 & 5 &  2.669165e-01 & 1.723124e-15 & 6.455665e-15 \\ 
-3 & 4 & 1 &  6.402997e+00 & 5.729285e-26 & 8.947817e-27 \\ 
-3 & 4 & 2 &  1.079505e+00 & 1.226846e-27 & 1.136489e-27 \\ 
-3 & 4 & 3 &  6.907344e-01 & 1.049444e-28 & 1.519317e-28 \\ 
-3 & 4 & 4 &  2.903904e-01 & 8.442770e-26 & 2.907386e-25 \\ 
-3 & 4 & 5 &  5.333668e-01 & 5.987514e-25 & 1.122588e-24 \\ 
-\hline
-\end{tabular}
-\end{center}
-\label{fig::allRegSolvability}
-\caption
-    {
-      We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$
-      with all
-      boundary conditions homogeneous Neumann.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$. 
-    }
-\end{table}
-\end{small}
-
-\begin{small}
-\begin{table}
-\begin{center}
-\begin{tabular}{|ccc|ccc|} \hline
- $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$  \\
-   \hline
-2 & 1 & 1 &  3.244145e+00 & 5.576001e-03 & 1.718789e-03 \\ 
-2 & 1 & 2 &  1.108699e+00 & 5.218520e-04 & 4.706884e-04 \\ 
-2 & 1 & 3 &  6.816993e-01 & 4.992473e-05 & 7.323570e-05 \\ 
-2 & 1 & 4 &  5.736425e-01 & 7.273424e-06 & 1.267937e-05 \\ 
-2 & 1 & 5 &  5.336857e-01 & 1.374234e-06 & 2.574988e-06 \\ 
-2 & 2 & 1 &  2.762140e+00 & 6.863083e-06 & 2.484698e-06 \\ 
-2 & 2 & 2 &  9.453294e-01 & 7.653732e-07 & 8.096365e-07 \\ 
-2 & 2 & 3 &  6.816994e-01 & 4.112367e-08 & 6.032523e-08 \\ 
-2 & 2 & 4 &  5.736426e-01 & 3.156232e-09 & 5.502089e-09 \\ 
-2 & 2 & 5 &  5.336858e-01 & 4.220417e-10 & 7.908057e-10 \\ 
-2 & 3 & 1 &  2.762140e+00 & 2.066812e-09 & 7.482649e-10 \\ 
-2 & 3 & 2 &  9.453294e-01 & 1.559241e-10 & 1.649416e-10 \\ 
-2 & 3 & 3 &  6.574277e-01 & 2.360967e-11 & 3.591220e-11 \\ 
-2 & 3 & 4 &  5.705795e-01 & 4.724557e-12 & 8.280278e-12 \\ 
-2 & 3 & 5 &  5.336858e-01 & 2.690617e-13 & 5.041575e-13 \\ 
-2 & 4 & 1 &  2.762140e+00 & 3.535738e-13 & 1.280072e-13 \\ 
-2 & 4 & 2 &  9.453294e-01 & 3.267022e-14 & 3.455962e-14 \\ 
-2 & 4 & 3 &  6.574277e-01 & 3.738186e-15 & 5.686079e-15 \\ 
-2 & 4 & 4 &  5.691873e-01 & 3.830503e-16 & 6.729777e-16 \\ 
-2 & 4 & 5 &  5.328410e-01 & 8.531691e-17 & 1.601170e-16 \\
-\hline
-3 & 1 & 1 &  7.242861e+00 & 4.674236e-03 & 6.453577e-04 \\ 
-3 & 1 & 2 &  1.181250e+00 & 2.657202e-04 & 2.249483e-04 \\ 
-3 & 1 & 3 &  6.863432e-01 & 3.329115e-05 & 4.850511e-05 \\ 
-3 & 1 & 4 &  5.741086e-01 & 4.562521e-06 & 7.947139e-06 \\ 
-3 & 1 & 5 &  5.350591e-01 & 1.455556e-06 & 2.720366e-06 \\ 
-3 & 2 & 1 &  7.433403e+00 & 2.264150e-06 & 3.045914e-07 \\ 
-3 & 2 & 2 &  1.181248e+00 & 1.685503e-07 & 1.426883e-07 \\ 
-3 & 2 & 3 &  6.804738e-01 & 1.353871e-08 & 1.989600e-08 \\ 
-3 & 2 & 4 &  5.806933e-01 & 2.036542e-09 & 3.507086e-09 \\ 
-3 & 2 & 5 &  5.350591e-01 & 1.066432e-10 & 1.993110e-10 \\ 
-3 & 3 & 1 &  7.433404e+00 & 8.925217e-10 & 1.200690e-10 \\ 
-3 & 3 & 2 &  1.182547e+00 & 8.635683e-11 & 7.302615e-11 \\ 
-3 & 3 & 3 &  6.804738e-01 & 4.819403e-12 & 7.082423e-12 \\ 
-3 & 3 & 4 &  5.729018e-01 & 3.780488e-13 & 6.598842e-13 \\ 
-3 & 3 & 5 &  5.350591e-01 & 6.218451e-14 & 1.162199e-13 \\ 
-3 & 4 & 1 &  7.433404e+00 & 1.727339e-13 & 2.323753e-14 \\ 
-3 & 4 & 2 &  1.182547e+00 & 2.186136e-14 & 1.848668e-14 \\ 
-3 & 4 & 3 &  6.804738e-01 & 1.827956e-15 & 2.686299e-15 \\ 
-3 & 4 & 4 &  5.728477e-01 & 7.990908e-17 & 1.394944e-16 \\ 
-3 & 4 & 5 &  5.338853e-01 & 1.743421e-17 & 3.265535e-17 \\ 
-\hline
-\end{tabular}
-\end{center}
-\label{fig::unmergedSolvability}
-\caption
-    {
-      We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$ with all
-      boundary conditions homogeneous Neumann.
-      The grid covers the unit square and is cut by a sphere of radius 0.45.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$.    This grid
-      includes very small volumes.
-    }
-\end{table}
-\end{small}
-
-\begin{small}
-\begin{table}
-\begin{center}
-  \begin{tabular}{|ccc|ccc|} \hline
- $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
-  \hline
-2 & 1 & 1 &  3.110810e+00 & 6.876828e-04 & 2.210623e-04 \\ 
-2 & 1 & 2 &  1.820276e+00 & 2.935551e-04 & 1.612695e-04 \\ 
-2 & 1 & 3 &  6.689318e-01 & 2.783647e-05 & 4.161332e-05 \\ 
-2 & 1 & 4 &  3.112964e-01 & 3.804498e-06 & 1.222146e-05 \\ 
-2 & 1 & 5 &  2.931197e-01 & 4.648824e-07 & 1.585981e-06 \\ 
-2 & 2 & 1 &  4.649575e+00 & 1.222691e-06 & 2.629683e-07 \\ 
-2 & 2 & 2 &  2.800875e+00 & 4.389241e-07 & 1.567096e-07 \\ 
-2 & 2 & 3 &  1.156823e+00 & 4.756446e-08 & 4.111647e-08 \\ 
-2 & 2 & 4 &  1.020254e+00 & 3.829097e-09 & 3.753083e-09 \\   
-2 & 2 & 5 &  9.591803e-01 & 4.980114e-10 & 5.192052e-10 \\ 
-2 & 3 & 1 &  8.598864e-01 & 3.926204e-10 & 4.565956e-10 \\ 
-2 & 3 & 2 &  3.682481e+00 & 6.386263e-10 & 1.734228e-10 \\ 
-2 & 3 & 3 &  1.036128e+00 & 1.177339e-11 & 1.136288e-11 \\ 
-2 & 3 & 4 &  9.070960e-01 & 5.028483e-13 & 5.543495e-13 \\ 
-2 & 3 & 5 &  8.510270e-01 & 3.323827e-14 & 3.905666e-14 \\ 
-2 & 4 & 1 &  9.197999e-01 & 3.623068e-14 & 3.938974e-14 \\ 
-2 & 4 & 2 &  7.945940e-02 & 1.618085e-15 & 2.036366e-14 \\ 
-2 & 4 & 3 &  1.186857e+00 & 4.379402e-15 & 3.689917e-15 \\ 
-2 & 4 & 4 &  1.039000e+00 & 3.390648e-16 & 3.263375e-16 \\ 
-2 & 4 & 5 &  2.958494e-01 & 1.292309e-17 & 4.368131e-17 \\
-\hline
-3 & 1 & 1 &  5.044398e+00 & 6.813020e-04 & 1.350611e-04 \\
-3 & 1 & 2 &  2.141787e+00 & 2.336010e-05 & 1.090683e-05 \\
-3 & 1 & 3 &  1.663929e+00 & 8.355671e-07 & 5.021651e-07 \\
-3 & 1 & 4 &  1.479289e+00 & 9.414478e-08 & 6.364192e-08 \\
-3 & 1 & 5 &  3.223939e-01 & 1.193480e-08 & 3.701931e-08 \\
-3 & 2 & 1 &  6.441253e+00 & 1.723363e-07 & 2.675509e-08 \\
-3 & 2 & 2 &  3.588187e+00 & 1.066316e-08 & 2.971741e-09 \\
-3 & 2 & 3 &  2.800032e+00 & 9.932906e-10 & 3.547425e-10 \\
-3 & 2 & 4 &  2.491816e+00 & 2.063069e-10 & 8.279378e-11 \\
-3 & 2 & 5 &  6.820526e-01 & 2.306368e-11 & 3.381511e-11 \\
-3 & 3 & 1 &  2.508964e+00 & 1.541288e-11 & 6.143127e-12 \\
-3 & 3 & 2 &  4.951047e+00 & 1.076120e-11 & 2.173521e-12 \\
-3 & 3 & 3 &  3.867831e+00 & 1.354407e-12 & 3.501722e-13 \\
-3 & 3 & 4 &  2.166936e+00 & 8.701202e-14 & 4.015441e-14 \\
-3 & 3 & 5 &  2.040600e+00 & 3.890155e-15 & 1.906378e-15 \\
-3 & 4 & 1 &  2.418622e+00 & 1.859733e-15 & 7.689226e-16 \\
-3 & 4 & 2 &  1.286816e+00 & 1.115219e-15 & 8.666503e-16 \\
-3 & 4 & 3 &  9.013057e-01 & 9.738926e-17 & 1.080535e-16 \\
-3 & 4 & 4 &  7.856540e-01 & 2.968168e-17 & 3.777958e-17 \\
-3 & 4 & 5 &  9.668729e-01 & 1.139377e-17 & 1.178415e-17 \\
-\hline
-\end{tabular}
-\end{center}
-\label{fig::mergedSolvability}
-\caption
-    {
-      We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$
-      with all
-      boundary conditions homogeneous Neumann.
-      The grid covers the unit square and is cut by a sphere of radius 0.45.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$.    This grid
-      has had its small volumes merged with neighboring volumes.
-    }
-\end{table}
-\end{small}
-
-\section{Domain face Poisson flux computation with Dirichlet boundary
-  conditions}
-
-Neumann boundary conditions are a proscribed flux when solving
-Poisson's equation.     When we have Dirichlet boundary conditions
-either at the domain box boundary or at a cut face, we must calculate
-the flux through that face.
-
-For context, allow us to recap a relevant bit of finite volume formalism.
-Consider a volume $\ibold$ bounded by the set of faces
-$\{f\}  = \partial \ibold$, where the outward-facing normal $\nhat$ of
-each face is known, as is its  $V_\ibold$.
-Given a flux function $F$, the average divergence $< \nabla \cdot F >$
-is given by the divergence theorem:
-\begin{equation}
-\begin{array}{l l}
-< \nabla \cdot F > &= \frac{1}{V_\ibold} \int_\ibold \nabla \cdot F dV \\
-           &= \frac{1}{V_\ibold} \int_{\partial \ibold} F\cdot \nhat dA \\
-           &= \frac{1}{V_\ibold} \sum_{f \in \partial
-  \ibold}\int_{\partial \ibold} F\cdot \nhat dA.
-\end{array}
-\label{eqn::discreteDivergence}
-\end{equation}
-For all coordinate-alligned faces, the section above's description for how to
-compute the flux is adequate.   What remains are fluxes through cut
-faces.
-
-We start with a smooth function $\psi$ which we we expand using Taylor
-(equation \ref{eqn::taylor}).  At each cut face $f$ with area $A_f$,
-we wish to compute the average flux $< \nabla \psi \cdot \nhat >_f$
-through that face.
-\begin{equation}
-\begin{array}{l l }
-  < \nabla \psi \cdot \nhat >_f
-  &= \frac{1}{A_f} \int_f \nabla \psi \cdot \nhat dA \\
-  &= \frac{1}{A_f} \int_f \sum_{p \in P} \sum_{0 <= d <D}  (p-e^d) C_p
-  \ecal^{p-e^d} n^d dA
-\end{array}
-\end{equation}
-where the normal moments
-\begin{equation}
-\ecal^{\pbold, d}_\cbold  =  \int\limits_{A(\cbold)} \xminxbar n^d  dA
-\end{equation}
-are natural products of the \cite{Schwartz2015} grid generation
-algorithm.   Except in that we are using the normal moments, this is
-semantically the same dance we used to calculate open face fluxes.
-
-\subsection{The effect of Dirichlet boundary conditions on
-  system matrix conditioning} In section \ref{sec::openface}, we
-discuss how adding Neumann boundary condition equations can improve
-the conditioning of the system matrix.  When the boundary conditions
-are set to Dirichlet, we get similar results.  See tables
-\ref{fig::mergedDiri}, \ref{fig::unmergedDiri}, and
-\ref{fig::allRegDiri} for details.  Again, boundary conditions help
-stabilize the system but it is still the case that agressive choices
-of $P_T$ or $P_W$ can result in system matrices that cannot be
-credibly inverted without very high precision numerical arithmetic.
-Again, this seems less a matter of a particular grid configuration and
-more  a property of the mathematical framework used to generate the stencil.
-\begin{small}
-\begin{table}
-\begin{center}
-\begin{tabular}{|ccc|ccc|} \hline
- $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
- \hline
-2 & 1 & 1 &  1.537125e+00 & 1.150772e-03 & 7.486517e-04 \\ 
-2 & 1 & 2 &  4.940953e-01 & 9.196245e-05 & 1.861229e-04 \\ 
-2 & 1 & 3 &  3.324177e-01 & 1.064946e-05 & 3.203639e-05 \\ 
-2 & 1 & 4 &  2.853322e-01 & 1.705230e-06 & 5.976295e-06 \\ 
-2 & 1 & 5 &  2.665812e-01 & 3.349335e-07 & 1.256403e-06 \\ 
-2 & 2 & 1 &  2.407807e+00 & 1.457063e-06 & 6.051408e-07 \\ 
-2 & 2 & 2 &  4.940956e-01 & 5.469314e-08 & 1.106934e-07 \\ 
-2 & 2 & 3 &  3.324177e-01 & 2.879583e-09 & 8.662545e-09 \\ 
-2 & 2 & 4 &  2.853323e-01 & 1.628939e-10 & 5.708921e-10 \\ 
-2 & 2 & 5 &  2.665812e-01 & 1.084310e-11 & 4.067466e-11 \\ 
-2 & 3 & 1 &  2.407807e+00 & 5.822902e-10 & 2.418342e-10 \\ 
-2 & 3 & 2 &  9.272889e-01 & 4.520282e-11 & 4.874729e-11 \\ 
-2 & 3 & 3 &  3.324177e-01 & 1.618058e-12 & 4.867544e-12 \\ 
-2 & 3 & 4 &  2.853323e-01 & 7.227717e-14 & 2.533088e-13 \\ 
-2 & 3 & 5 &  2.665812e-01 & 3.194386e-15 & 1.198279e-14 \\ 
-2 & 4 & 1 &  2.943604e+00 & 6.445948e-26 & 2.189815e-26 \\ 
-2 & 4 & 2 &  9.877639e-01 & 6.302117e-27 & 6.380185e-27 \\ 
-2 & 4 & 3 &  6.561304e-01 & 6.778809e-28 & 1.033150e-27 \\ 
-2 & 4 & 4 &  2.868930e-01 & 5.733222e-27 & 1.998383e-26 \\ 
-2 & 4 & 5 &  5.327046e-01 & 5.117605e-25 & 9.606835e-25 \\
-\hline
-3 & 1 & 1 &  4.639099e+00 & 3.887142e-03 & 8.379088e-04 \\ 
-3 & 1 & 2 &  1.079504e+00 & 2.369894e-04 & 2.195354e-04 \\ 
-3 & 1 & 3 &  6.747118e-01 & 2.359590e-05 & 3.497182e-05 \\ 
-3 & 1 & 4 &  5.721834e-01 & 3.540976e-06 & 6.188534e-06 \\ 
-3 & 1 & 5 &  5.333668e-01 & 6.792558e-07 & 1.273525e-06 \\ 
-3 & 2 & 1 &  4.639156e+00 & 3.176883e-06 & 6.847975e-07 \\ 
-3 & 2 & 2 &  1.079505e+00 & 1.512048e-07 & 1.400686e-07 \\ 
-3 & 2 & 3 &  6.747119e-01 & 6.991076e-09 & 1.036157e-08 \\ 
-3 & 2 & 4 &  5.721835e-01 & 3.641527e-10 & 6.364265e-10 \\ 
-3 & 2 & 5 &  2.669165e-01 & 1.146071e-11 & 4.293744e-11 \\ 
-3 & 3 & 1 &  4.639157e+00 & 1.340233e-09 & 2.888959e-10 \\ 
-3 & 3 & 2 &  1.079505e+00 & 7.151353e-11 & 6.624659e-11 \\ 
-3 & 3 & 3 &  6.747119e-01 & 3.977531e-12 & 5.895155e-12 \\ 
-3 & 3 & 4 &  2.869943e-01 & 5.757645e-14 & 2.006188e-13 \\ 
-\hline
-\end{tabular}
-\end{center}
-\label{fig::allRegDiri}
-\caption
-    {
-      We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$ with all
-      boundary conditions homogeneous Dirichlet.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$.
-%%(as of 6-28-2023, some 3d results still pending).      
-    }
-\end{table}
-\end{small}
-
-\begin{small}
-\begin{table}
-\begin{center}
-  \begin{tabular}{|ccc|ccc|} \hline
- $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$ \\
-  \hline
-2 & 1 & 1  & 2.518893e+00 & 1.601156e-04 & 6.356588e-05 \\ 
-2 & 1 & 2  & 2.362043e+00 & 1.461371e-05 & 6.186896e-06 \\ 
-2 & 1 & 3  & 1.094261e+00 & 9.635190e-07 & 8.805204e-07 \\ 
-2 & 1 & 4  & 1.093340e+00 & 1.270395e-07 & 1.161940e-07 \\ 
-2 & 1 & 5  & 1.094367e+00 & 2.036717e-08 & 1.861091e-08 \\ 
-2 & 2 & 1  & 1.462450e+00 & 2.819426e-08 & 1.927879e-08 \\ 
-2 & 2 & 2  & 1.118414e+00 & 3.603335e-09 & 3.221825e-09 \\ 
-2 & 2 & 3  & 1.101878e+00 & 6.259208e-10 & 5.680491e-10 \\ 
-2 & 2 & 4  & 1.787419e+00 & 1.261851e-10 & 7.059628e-11 \\ 
-2 & 2 & 5  & 1.786900e+00 & 8.059615e-12 & 4.510389e-12 \\ 
-2 & 3 & 1  & 1.463079e+00 & 5.935296e-12 & 4.056717e-12 \\ 
-2 & 3 & 2  & 1.119064e+00 & 1.346836e-12 & 1.203538e-12 \\ 
-2 & 3 & 3  & 3.180167e+00 & 2.412859e-13 & 7.587209e-14 \\ 
-2 & 3 & 4  & 3.171902e+00 & 1.108072e-14 & 3.493399e-15 \\ 
-2 & 3 & 5  & 1.101546e+00 & 1.869284e-16 & 1.696964e-16 \\ 
-2 & 4 & 1  & 4.679500e+00 & 1.267360e-17 & 2.708324e-18 \\ 
-2 & 4 & 2  & 3.730996e+00 & 2.933117e-18 & 7.861486e-19 \\ 
-2 & 4 & 3  & 3.640428e+00 & 2.031473e-17 & 5.580313e-18 \\ 
-2 & 4 & 4  & 1.101662e+00 & 2.052912e-18 & 1.863468e-18 \\ 
-2 & 4 & 5  & 1.101600e+00 & 5.403550e-19 & 4.905182e-19 \\
-\hline
-3 & 1 & 1  & 5.278503e+00 & 5.349129e-04 & 1.013380e-04 \\ 
-3 & 1 & 2  & 2.898423e+00 & 1.765977e-05 & 6.092890e-06 \\ 
-3 & 1 & 3  & 2.480335e+00 & 5.055998e-07 & 2.038433e-07 \\ 
-3 & 1 & 4  & 2.468916e+00 & 2.823132e-08 & 1.143471e-08 \\ 
-3 & 1 & 5  & 2.528326e+00 & 3.761767e-09 & 1.487849e-09 \\ 
-3 & 2 & 1  & 1.845660e+00 & 1.814540e-08 & 9.831389e-09 \\ 
-3 & 2 & 2  & 4.774894e+00 & 4.503397e-09 & 9.431406e-10 \\ 
-3 & 2 & 3  & 2.880922e+00 & 1.193187e-10 & 4.141685e-11 \\ 
-3 & 2 & 4  & 2.864876e+00 & 1.430923e-11 & 4.994711e-12 \\ 
-3 & 2 & 5  & 4.150386e+00 & 3.315285e-12 & 7.987897e-13 \\ 
-3 & 3 & 1  & 1.936290e+00 & 1.161631e-12 & 5.999263e-13 \\ 
-3 & 3 & 2  & 2.897250e+00 & 5.681304e-13 & 1.960930e-13 \\ 
-3 & 3 & 3  & 3.447497e+00 & 9.616076e-14 & 2.789292e-14 \\ 
-3 & 3 & 4  & 2.751616e+00 & 1.135060e-14 & 4.125067e-15 \\ 
-3 & 3 & 5  & 2.750524e+00 & 4.977018e-16 & 1.809480e-16 \\ 
-3 & 4 & 1  & 2.390817e+00 & 4.437506e-16 & 1.856062e-16 \\ 
-3 & 4 & 2  & 4.045567e+00 & 2.572870e-16 & 6.359727e-17 \\ 
-3 & 4 & 3  & 2.967273e+00 & 4.916614e-17 & 1.656947e-17 \\ 
-3 & 4 & 4  & 6.914527e+00 & 6.809812e-17 & 9.848559e-18 \\ 
-  \hline
-\end{tabular}
-\end{center}
-\label{fig::mergedDiri}
-\caption
-    {
-      We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$ with all
-      boundary conditions homogeneous Dirichlet.
-      The grid covers the unit square and is cut by a sphere of radius 0.45.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$.    This grid
-      has had its small volumes merged with neighboring volumes.
-%%(as of 6-28-2023, some 3d results still pending).      
-    }
-\end{table}
-\end{small}
-
-\begin{small}
-\begin{table}
-\begin{center}
-\begin{tabular}{|ccc|ccc|} \hline
- $D$ & $P^T$  & $P^W$  & $\lambda_{max}$ & $\lambda_{min}$   & $\cali$  \\
-\hline
-2 & 1 & 1 &  2.659761e+00 & 1.406481e-03 & 5.287997e-04 \\ 
-2 & 1 & 2 &  1.215453e+00 & 1.019228e-04 & 8.385575e-05 \\ 
-2 & 1 & 3 &  1.046275e+00 & 8.724426e-06 & 8.338562e-06 \\ 
-2 & 1 & 4 &  1.016321e+00 & 1.289568e-06 & 1.268859e-06 \\ 
-2 & 1 & 5 &  1.009826e+00 & 4.105645e-07 & 4.065697e-07 \\ 
-2 & 2 & 1 &  2.721312e+00 & 6.510187e-07 & 2.392297e-07 \\ 
-2 & 2 & 2 &  1.215454e+00 & 4.619552e-08 & 3.800680e-08 \\ 
-2 & 2 & 3 &  1.046439e+00 & 3.123629e-09 & 2.985008e-09 \\ 
-2 & 2 & 4 &  1.016267e+00 & 2.184707e-10 & 2.149737e-10 \\ 
-2 & 2 & 5 &  1.009758e+00 & 1.769343e-11 & 1.752244e-11 \\ 
-2 & 3 & 1 &  2.721312e+00 & 2.062962e-10 & 7.580764e-11 \\ 
-2 & 3 & 2 &  1.215454e+00 & 1.829550e-11 & 1.505240e-11 \\ 
-2 & 3 & 3 &  1.046275e+00 & 1.297942e-12 & 1.240537e-12 \\ 
-2 & 3 & 4 &  1.016321e+00 & 7.989181e-14 & 7.860883e-14 \\ 
-2 & 3 & 5 &  1.009826e+00 & 5.099447e-15 & 5.049829e-15 \\ 
-2 & 4 & 1 &  2.721312e+00 & 1.944812e-15 & 7.146596e-16 \\ 
-2 & 4 & 2 &  1.218511e+00 & 6.245987e-16 & 5.125916e-16 \\ 
-2 & 4 & 3 &  1.045681e+00 & 1.558421e-16 & 1.490342e-16 \\ 
-2 & 4 & 4 &  1.016267e+00 & 5.658955e-17 & 5.568374e-17 \\ 
-2 & 4 & 5 &  1.009906e+00 & 2.092151e-17 & 2.071630e-17 \\ 
-\hline
-3 & 1 & 1 &  6.913939e+00 & 3.982281e-03 & 5.759786e-04 \\ 
-3 & 1 & 2 &  1.457848e+00 & 1.829414e-04 & 1.254873e-04 \\ 
-3 & 1 & 3 &  1.067010e+00 & 8.920278e-06 & 8.360072e-06 \\ 
-3 & 1 & 4 &  1.014179e+00 & 7.322700e-07 & 7.220320e-07 \\ 
-3 & 1 & 5 &  1.003823e+00 & 1.115560e-07 & 1.111311e-07 \\ 
-3 & 2 & 1 &  7.173899e+00 & 1.868378e-06 & 2.604411e-07 \\ 
-3 & 2 & 2 &  1.457849e+00 & 7.351431e-08 & 5.042654e-08 \\ 
-3 & 2 & 3 &  1.067007e+00 & 3.063086e-09 & 2.870728e-09 \\ 
-3 & 2 & 4 &  1.014193e+00 & 1.481290e-10 & 1.460561e-10 \\ 
-3 & 2 & 5 &  1.003823e+00 & 8.189605e-12 & 8.158418e-12 \\ 
-3 & 3 & 1 &  7.173899e+00 & 5.736164e-10 & 7.995881e-11 \\ 
-3 & 3 & 2 &  1.463446e+00 & 3.367536e-11 & 2.301099e-11 \\ 
-3 & 3 & 3 &  1.067224e+00 & 1.254264e-12 & 1.175258e-12 \\ 
-3 & 3 & 4 &  1.014176e+00 & 4.631105e-14 & 4.566371e-14 \\ 
-3 & 3 & 5 &  1.003820e+00 & 1.806297e-15 & 1.799424e-15 \\ 
-3 & 4 & 1 &  7.173899e+00 & 8.925826e-15 & 1.244208e-15 \\ 
-3 & 4 & 2 &  1.463446e+00 & 3.102967e-16 & 2.120315e-16 \\ 
-\hline
-\end{tabular}
-\end{center}
-\label{fig::unmergedDiri}
-\caption
-    {
-      We show the lowest value of
-      $\cali$ for an entire Cartesian grid of size $32^D$ with all
-      boundary conditions homogeneous Dirichlet.
-      The grid covers the unit square and is cut by a sphere of radius 0.45.
-      We vary Taylor power $P^T$, weighting
-      function exponents $P^W$, and dimensionality $D$.    This grid
-      includes very small volumes.
-%%(as of 6-28-2023, some 3d results still pending).      
-    }
-\end{table}
-\end{small}
-
-\section{Stability and Conditioning of the entire system}
-
-The matrix $L_{P_T, P_W}$ for a particular polynomial order $P_T$ and
-weighting exponent  $P_W$ may be unstable or poorly conditioned.   We
-measure both while varying $P_T, P_W$ in both two and three
-dimensions.    All these calculations are done using SLEPc and PETc
-\cite{petsc-user-ref, petsc-efficient, slepc}.
-
-\section{Conclusions}
+family of elliptic operators.   That algorithm is a special case of a
+family of finite volume elliptic operators.   In part 1
+\cite{Devendran2023}, we present the formal 
+process to generate these operators and present system matrix
+conditioning data.      Here we present how truncation error varies
+within the family of operators.
 
@@
 \footnotetext[2]{Ford Motor Company, Sunnyvale, CA.}
-\footnotetext[3]{This includes corner volumes.   The neighborhood is
-  formed by taking all the volumes within a grown box. The grown box
-  is formed by growning the box made from the low and high cells of
-  the target face, growing it by $N_G$ and itersecting with the
-  domain.  We use the   Chombo
-  (\cite{ChomboDesign,ChomboDesignEB,ChomboDesign3})
-  box growth semantic. }
-\footnotetext[4]{If the matrix $M$ is square, a weighting matrix can
-  have no effect and the Moore-Penrose psueudoinverse becomes
-  $M^{-1}$.}
-\footnotetext[5]{The 
-  equations for volumes $\jbold$ where $\xbar_\jbold$ is large
-  receive  higher weights.  Diagonal weighting matricies are common.
-  Usually these algorithms define a distance metric $D(\ibold, \jbold)$ for
-  two volumes $\ibold$ and $\jbold$ and make
-  $W_{\jbold,\jbold}$ decrease strongly with increasing 
-  $D(\ibold,\jbold)$.  This assign higher importance to the equations for volumes
-  closer to $\ibold$.  Devendran et al. for example \cite{Devendran2017},
-  uses a weighting function  $W_{\ibold,\jbold}
-  \approx 1./D(\ibold,\jbold)^5$ }.
 

### 2023-07-07 example/EBCM/roadmap.tex
gearing up for merging with the master branch

@@
 
-This continues the story by investigating the truncation error of
-the family of finite volume operators.   This one does use quite a bit
+We intend to continue the story by investigating the truncation error of
+the family of finite volume operators.   This one will use quite a bit
 of petsc and includes yet another user interface to the petsc
-infrastructure.   The document vaporware as of July 7 2023.
+infrastructure.   The document (and most of the code )
+is vaporware as of July 7 2023.
 

### 2023-07-07 example/EBCM/hoeb_truncation/hoeb_truncation.cpp

@@ -17,6 +17,7 @@
 #include "Chombo_EBCM_Graph.H"
 #include "Chombo_EBCM_HostLevelData.H"
 #include "Chombo_EBCM_Algorithm_Framework.H"
+#include "Chombo_EBCM_PETSc_Framework.H"
 #include "Chombo_EigenMatrix.H"
 
 #include <iomanip>
@@ -53,33 +54,27 @@ int main(int a_argc, char* a_argv[])
 
     if(order == 6)
     {
-      shared_ptr< EBCM::MetaDataLevel< 6 > >             ebcm_meta;      
-      EBCM::Algorithm_Framework<6>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<6>::run_hoeb_truncation_tests();
     }
     else if(order == 5)
     {
-      shared_ptr< EBCM::MetaDataLevel< 5 > >             ebcm_meta;      
-      EBCM::Algorithm_Framework<5>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<5>::run_hoeb_truncation_tests();
     }
     if(order == 4)
     {
-      shared_ptr< EBCM::MetaDataLevel< 4 > >             ebcm_meta;      
-      EBCM::Algorithm_Framework<4>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<4>::run_hoeb_truncation_tests();
     }
     else if(order == 3)
     {
-      shared_ptr< EBCM::MetaDataLevel< 3 > >             ebcm_meta;      
-      EBCM::Algorithm_Framework<3>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<3>::run_hoeb_truncation_tests();
     }
     else if(order == 2)
     {
-      shared_ptr< EBCM::MetaDataLevel< 2 > >             ebcm_meta;      
-      EBCM::Algorithm_Framework<2>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<2>::run_hoeb_truncation_tests();
     }
     else if(order == 1)
     {
-      shared_ptr< EBCM::MetaDataLevel< 1 > >             ebcm_meta;      
-      EBCM::Algorithm_Framework<1>::run_hoeb_petsc_tests(ebcm_meta);
+      EBCM::PETSc_Framework<1>::run_hoeb_truncation_tests();
     }
     else
     {

### 2023-07-07 src/EBCM/Chombo_EBCM_PETSc_Framework.H
dummy truncation error test now compiles

@@ -9,7 +9,7 @@
 #include "petscviewer.h"
 #include "petscmat.h"
 /**
-   This is where MetaDataLevel lives.  It made sense at the time.
+   Chombo_EBCM_Graph.H where MetaDataLevel lives.  It made sense at the time.
    I should use this opportunity to apologize to the world for the many 
    awful choices I have made in this life in relation to file names and organization.  
    I regret all the consternation I have caused.
@@ -44,6 +44,7 @@ namespace EBCM
     typedef EBCM::EBCM_Graph<ebcm_order>            ebcm_graph;
     typedef EBCM::HostLevelData<int, 1, ebcm_order> ebcm_data;
     typedef EBCM::SubVolumeVector<      ebcm_order> ebcm_subvol_vec;
+    typedef EBCM::Algorithm_Framework<  ebcm_order> ebcm_framework;
 
     struct local_stencil_t
     {
@@ -272,12 +273,19 @@ namespace EBCM
       }
     };
     
-    ///test function for example/EBCM/hoeb_petsc_test
-    static  void run_hoeb_petsc_tests(shared_ptr< ebcm_meta > & a_meta)
+    ///test function for example/EBCM/hoeb_truncation
+    static  void run_hoeb_truncation_tests()
     {
+      
       int nghost = 4;
+      shared_ptr< ebcm_meta  > ebcm;
+      ch_dbl                   grids;
+      double                   dx;
+      ch_probdom               domain;
+      ebcm_framework::makeMergedGeometry(ebcm, grids, dx, domain, true, true);
+    
       typedef DummyDerivedOp   ebcm_petsc_op;
-      ebcm_petsc_op   testOperator(a_meta, nghost, false);
+      ebcm_petsc_op   testOperator(ebcm, nghost, false);
 
     }
   }; //end petsc_framwork class

### 2023-08-14 src/EBCM/Chombo_EBCM_PETSc_Framework.H
fixed typos in document

@@ -360,6 +360,18 @@ namespace EBCM
                                 const int                          & a_facedir,
                                 bool a_print = false)
     {
+      /**
+         From the document (Lawrence Berkeley National Laboratory Technical Report LBNL-2001537):  
+         Q : Q matrix (Unfortunately, I did not give it a fancy mathy name in the document.
+               It is the one that converts  Taylor coefficients to fluxes).
+         S : stencil matrix.  
+         P : phi vector.  
+         W : weighting matrix.
+         M : moment matrix.
+         A: system matrix =  ((WM)^T(WM))
+         (S P) = <\nabla \psi> = Q C= (Q ((WM)^T(WM))^{-1} (WM)^T  P) Q A^{-1} WM^T P.
+         S = Q C = (Q ((WM)^T(WM))^{-1} (WM)^T  ) = Q A^{-1} (WM)^T.
+      **/
       local_stencil_t retval;
       shared_ptr< EBCM::neighborhood< ebcm_order > > locality;
       shared_ptr< eigen_mat > Amat =

### 2023-08-14 src/EBCM/Chombo_EBCM_PETSc_Framework.H
Helmholtzian progress

@@ -343,12 +343,41 @@ namespace EBCM
     };
     
 
+    ///
+    static inline
+    shared_ptr<eigen_mat>
+    getHelmholtzQMatrix(shared_ptr<ebcm_neighborhood> a_locality,
+                        const EBCM_Face<cent, ebcm_order>  & a_face,
+                        bool a_print)
+    {
+      shared_ptr<eigen_mat> retval;
+      ch_mayday::Error("not implemented");
+      return retval;
+    }
     ///Returns a local stencil for \int (\grad \phi) \cdot (\ehat^facedir)
     /**
        Get stencil for integrated gradient in a  coordinate direction. 
        This is the same as the average gradient * face area.
        \int (\grad \phi) \cdot (\ehat^d) dA = A_f < \frac{\partial \phi}{\partial x_d} >
     */
+    static local_stencil_t
+    getStencilFromMatrix(const eigen_mat                                & a_matrix,
+                         shared_ptr< EBCM::neighborhood< ebcm_order > > & a_locality)
+    {
+      int nrows_volumes   = a_locality->m_weig_volumes.size();
+      local_stencil_t retval;
+      const auto& volvec = *a_locality->m_volumes;
+      for( int irow = 0; irow < nrows_volumes; irow++)
+      {
+        pair<pr_pt, double> entry;
+        const ebcm_volu& volume = volvec[irow];
+        entry.first = volume.m_pt;
+        entry.second = a_matrix(irow, 0);
+        retval.add(entry);
+      }
+      return retval;
+    }
+
     template<CENTERING cent>
     static local_stencil_t
     getHelmholtzFDotEhatStencil(const EBCM_Face<cent, ebcm_order>  & a_face,
@@ -363,7 +392,7 @@ namespace EBCM
       /**
          From the document (Lawrence Berkeley National Laboratory Technical Report LBNL-2001537):  
          Q : Q matrix (Unfortunately, I did not give it a fancy mathy name in the document.
-               It is the one that converts  Taylor coefficients to fluxes).
+               It is the one that converts  Taylor coefficients to fluxes).   
          S : stencil matrix.  
          P : phi vector.  
          W : weighting matrix.
@@ -374,11 +403,28 @@ namespace EBCM
       **/
       local_stencil_t retval;
[…]

### 2023-09-20 example/DomainDecomposition/EBINS/exec/report/main.tex
Simon first draft report

\documentclass{article}

\bibliographystyle{plain}

\usepackage{epsfig}
\usepackage{xcolor}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[export]{adjustbox}
\usepackage{afterpage}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx} % Required for inserting images

\begin{document}

\title{Performance Improvement of Chombo 4}
\author{Simon Zhang}
\date{September 2023}

\maketitle

\section{Introduction}
To improve the performance of Chombo 4, we ran weak scaling tests and manipulated inputs on the EBINS example in Chombo 4.

\section{Methodology}
\subsection{Weak Scaling Test}
\subsubsection{CPU}
To determine the performance bottlenecks of Chombo 4, weak scaling tests were run on NERSC Perlmutter CPU nodes using cray-mpich and mpich modules. We started the tests using 1 core of 1 CPU node in the domain of $nx = 32$ and maximum grid of $64$ for mpich module. From there, we increased the number of processors/core by $1.5^3$ and the domain ($nx$) by $1.5$ until the processors ran out of memory, which is $12$ processors with a domain of 72. Meanwhile, weak scaling tests were conducted using cray-mpich module starting from 1 core of 1 CPU node in the domain of $nx=32$ and maximum grid of $64$ increasing to the domain of $nx=64$ and $nx=96$, under the same increments for mpich module.

Weak scaling tests were also run on NERSC Perlmutter CPU nodes by using different number of processors and size of domain. We started the tests using 1 core of 1 CPU node in the domain of $nx = 32$ and maximum grid of $32$. From there, we increased the number of processors/core by $2^3$ and the domain ($nx$) by $2$ until the processors ran out of memory, which is $27$ processors with a domain of $96$. By doing so, Chombo 4 is handling problems with the size of 1 box, 8 boxes, and 27 boxes such that we are using the same number of processors to handle the same number of boxes.

\subsubsection{GPU}
Weak scaling tests were run on NERSC Perlmutter GPU nodes. We started the tests using 1 GPU of 1 GPU node in the domain of $nx=32$ and maximum grid of $32$. From there, we increased the number of GPUs to $8$ to handle a domain of $nx=64$ since we would get 8 boxes for this domain. However, the GPU nodes ran out of memory as we try to increase domain to $nx=96$ for $27$ GPUs due to GPU nodes having less total aggregate memory than the CPU nodes.

\subsection{W Cycle}
To improve the performance improvement of Chombo 4, we decided to manipulate $num$\_$smooth$ and $use$\_$w$\_$cycle$. $num$\_$smooth$ controls the number of times the initial system is iterated or relaxed until residual is a smooth function and $use$\_$w$\_$cycle$ controls whether w-cycle: a multigrid method, is turned on or off. 
Specifically, jobs were ran with CPU processors and GPUs under the same increment pattern as weak scaling tests, where $nx$ increase by 2, processors and GPUs increase by $2^3$ with the maximum grid of $32$. Additionally, $num$\_$smooth$ started from $2$ to $8$ increasing by a factor of 2 and $use$\_$w$\_$cycle$ is equated to true or false.

\section{Findings}
\subsection{Weak Scaling Test}
\subsubsection{CPU}

We find that runs loaded with mpich module scale better on the CPU Nodes as we increase the processor count and domain (Figure \ref{fig:mpich vs cray-mpich}).

\begin{figure}[ht]
\centering
\includegraphics[width=12cm]{Weak Scaling with CPU Nodes (1.5x).png}
\caption{Weak Scaling of CPU Nodes using mpich and cray-mpich modules}
\label{fig:mpich vs cray-mpich}
\end{figure}

\subsection{W Cycle}
We find that using $num$\_$smooth$ = 16 without w Cycle scales the best (Figure \ref{fig:CPU nodes with and without w cycle}) while any combination of $num$\_$smooth$ and $use$\_$w$\_$cycle$ does not affect the scaling of Chombo 4 significantly (Figure \ref{fig:GPU nodes with and without w cycle}).

\begin{figure}[H]
        \includegraphics[width=\textwidth]{Weak Scaling on CPU Nodes.png}
        \caption{Weak Scaling Tests of CPU Nodes with and without w Cycle}  
        \label{fig:CPU nodes with and without w cycle}
\end{figure}
\begin{figure}[H]
        \includegraphics[width=\textwidth]{Weak Scaling on GPU Nodes.png}
        \caption{Weak Scaling Tests of GPU Nodes with and without w Cycle}  
        \label{fig:GPU nodes with and without w cycle}
\end{figure}

We find that different processors/GPUs have different optimal $num$\_$smooth$ in terms of runtimes (Figure \ref{fig:Performance on CPU Nodes}, \ref{fig:Performance on GPU Nodes}).

\begin{figure}[H]
    \begin{subfigure}{0.92\textwidth}
        \includegraphics[width=\textwidth]{Performance on CPU Nodes.png}
        \caption{CPU Processors}
        \label{fig:Performance on CPU Nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.92\textwidth}
        \includegraphics[width=\textwidth]{Performance on GPU Nodes.png}
        \caption{GPUs}
        \label{fig:Performance on GPU Nodes}
    \end{subfigure}
    \caption{Performance of CPU Processors and GPUs under various $num$\_$smooth$}
\end{figure}

\end{document}

### 2023-10-23 src/EBProto/implem/Proto_SecondOrderCellImplem.H
added inflow-outflow bc fix

@@ -155,15 +155,34 @@ namespace Proto
     EBIndex<CELL> vofhi = a_face.getVoF(Side::Hi);
     a_facesten.clear();
     int ideb = 0;
-    //if(true)
+
     if(!a_face.m_isBoundary)
     {
       a_facesten.add(vofhi,  1./a_dx);
       a_facesten.add(voflo, -1./a_dx);
     }
+    else if(a_dombc == string("Neumann"))
+    {
+      //no flux here
+    }
+    else if(a_dombc == string("Dirichlet"))
+    {
+      //have to figure out which one is still in the domain
+      EBIndex<CELL> insideVoF;
+      if(a_face.m_vofIDMe >= 0)
+      {
+        insideVoF = vofhi;
+      }
+      else
+      {
+        insideVoF = voflo;
+      }
+      a_facesten.add(insideVoF,  -2./a_dx);
+    }
     else
     {
-      //boundary condition handles this.
+      Chombo4::pout() << "Poisson2ndOrder: bogus domain bc" << endl;
+      Chombo4::MayDay::Error("Doh!");
     }
   }
 

### 2023-10-23 example/DomainDecomposition/EBINS/exec/_zhang/report/main.tex

--- 2023-09-20 example/DomainDecomposition/EBINS/exec/report/main.tex
@@
 
-We find that different processors/GPUs have different optimal $num$\_$smooth$ in terms of runtimes (Figure \ref{fig:Performance on CPU Nodes}, \ref{fig:Performance on GPU Nodes}).
+We find that different processors/GPUs have different optimal $num$\_$smooth$ in terms of runtimes. Once the optimal $num$\_$smooth$ is exceeded, the runtimes increase monotonically.
+
+For CPU runs without $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 8 for 1 processor (Figure \ref{fig:1 Proc without w Cycle}) and 16 for 8 (Figure \ref{fig:8 Procs without w Cycle}) and 27 processors (Figure \ref{fig:27 Procs without w Cycle}).
 
 \begin{figure}[H]
-    \begin{subfigure}{0.92\textwidth}
-        \includegraphics[width=\textwidth]{Performance on CPU Nodes.png}
-        \caption{CPU Processors}
-        \label{fig:Performance on CPU Nodes}
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{1 Proc without w Cycle.png}
+        \caption{1 CPU Processor}
+        \label{fig:1 Proc without w Cycle}
     \end{subfigure}
-    \begin{subfigure}[b]{0.92\textwidth}
-        \includegraphics[width=\textwidth]{Performance on GPU Nodes.png}
-        \caption{GPUs}
-        \label{fig:Performance on GPU Nodes}
+    \hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{8 Proc without w Cycle.png}
+        \caption{8 CPU Processors}
+        \label{fig:8 Procs without w Cycle}
     \end{subfigure}
-    \caption{Performance of CPU Processors and GPUs under various $num$\_$smooth$}
+
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{27 Proc without w Cycle.png}
+        \caption{27 CPU Processors}
+        \label{fig:27 Procs without w Cycle}
+    \end{subfigure}
+
+    \caption{Performance of 1, 8 and 27 CPU Processors without $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
+\end{figure}
+
+For CPU runs with $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 4 for 1 (Figure \ref{fig:1 Proc with w Cycle}) and 8 processors (Figure \ref{fig:8 Procs with w Cycle}) and 8 for 27 processors (Figure \ref{fig:27 Procs with w Cycle}).
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{1 Proc with w Cycle.png}
+        \caption{1 CPU Processor}
+        \label{fig:1 Proc with w Cycle}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{8 Proc with w Cycle.png}
+        \caption{8 CPU Processors}
+        \label{fig:8 Procs with w Cycle}
+    \end{subfigure}
+
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{27 Proc with w Cycle.png}
+        \caption{27 CPU Processors}
+        \label{fig:27 Procs with w Cycle}
+    \end{subfigure}
+
+    \caption{Performance of 1, 8 and 27 CPU Processors with $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
+\end{figure}
+
+For GPU runs without $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 16 for 1 GPU (Figure \ref{fig:1 GPU without w Cycle}) and 8 for 8 GPUs (Figure \ref{fig:8 GPUs without w Cycle}).
+
+\begin{figure}[H]
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{1 GPU without w Cycle.png}
+        \caption{1 GPU}
+        \label{fig:1 GPU without w Cycle}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{8 GPUs without w Cycle.png}
+        \caption{8 GPUs}
+        \label{fig:8 GPUs without w Cycle}
+    \end{subfigure}
+    \caption{Performance of 1, 8 GPUs without $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
+\end{figure}
+
+For GPU runs with $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 16 for 1 GPU (Figure \ref{fig:1 GPU with w Cycle}) and 16 for 8 GPUs (Figure \ref{fig:8 GPUs with w Cycle}).
+
+\begin{figure}[H]
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\textwidth]{1 GPU with w Cycle.png}
+        \caption{1 GPU}
+        \label{fig:1 GPU with w Cycle}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{8 GPUs with w Cycle.png}
+        \caption{8 GPUs}
+        \label{fig:8 GPUs with w Cycle}
+    \end{subfigure}
+    \caption{Performance of 1, 8 GPUs with $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
 \end{figure}
